### 2018-08-03 scpt.tex
第一次草稿

%%original
%\documentclass[review]{elsarticle}

%%edited by wmm
%\documentclass[final,5p,times,twocolumn]{elsarticle}
\documentclass[final,5p,times,twocolumn]{elsarticle}
\usepackage[labelfont=bf,justification=raggedright]{caption}

\captionsetup[figure]{name=Fig. ,labelsep=period,singlelinecheck=true,skip=5pt}

\captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
%review
%final,5p,times,twocolumn
\usepackage{lineno,hyperref}

\usepackage{float}

\modulolinenumbers[5]

\journal{Materials and Design}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{~/format/elsarticle-num.bst}

%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Effect of Void on Fracture Behavior of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy}
%\tnotetext[mytitlenote]{*** \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

%% Group authors per affiliation:
%\author{Maomao Wang\fnref{myfootnote}}

%\address[mymainaddress]{School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China}

\begin{abstract}
 The fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects. Existing studies of defect evolution in titanium--aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
\end{abstract}

\begin{keyword}
$\alpha$+$\gamma$ two phase TiAl alloy; void; molecular dynamics
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}

TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite {int.uti.j.1}. However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titantium aliuminde alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{int.uti.m.1}.
Metal

% study on poly 
% gap

\section Molecular dynamics simulation analysis
\subsection{Mode creation of nanocrystalline alloy}

The crystal structure of $\gamma$-TiAl alloy is L10 [32,33] which is shown in Figure 1; the lattice constants

The  in the material is determined by interatomic potencial. 
We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation. The silulations were performed on the a system of 460000 atoms.
Potential function is an mathematical approximation used  to determin interatomic effect among particlesan in MD simulation. The embedded atom method (MEAM) potential by \ref() was used In the study, which is used MD simulations were performed using the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code\ref().

The simulation cells of two phase poly crystal with an initially spherical void at different position are shown in figure \ref{}. Periodic boundaryconditions are applied along all three directions, in effect creating  TiAl poly crystal with periodic nanovoid structures. Each cuboidal model, containing about 4.6 million atoms, has edge sizes of $L_x = nm$, $L_y =  nm$, $L_z =  nm$. During the construction process, the grain centers were randomly placed in a simulation cell resulting in the arbitrary shape and orientation of the grains. The construction of a specific grain would stop at a position where atoms from one grain centerwere no longer closer to the centers of other grains. There was only one intragranular or intergranular spherical void within each simulation model. The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig. 1(b). The intergranular spherical voidwas at the center of the simulation cell, as shown in Fig. 1(c). Simulation specimens of the 16.32 nm grain size models with initial void diameters at or below 13 nm were mainly considered in the analysis sections owing to the fact that their spherical void surfaces did not intersect with surrounding GBs after the equilibration process. This avoided conflict between competing sources of dislocation emission: GBs or spherical void surfaces. Different diameter intragranular voids were all embedded in the same grain and at the same position in the samples, as shown in Fig. 1(b). The intergranular voids with different initial diameters were identically at the center of the simulation model, as shown in Fig. 1(c).

\begin{table}[H]
\centering
\caption{Experimental conditions}
\begin{tabular}{l*{6}{c}r}	
		\hline
		Team              & $\alpha$ & W & D & L & F  & A & Pts \\
		\hline
		Manchester United & 6 & 4 & 0 & 2 & 10 & 5 & 12  \\
		Celtic            & 6 & 3 & 0 & 3 &  8 & 9 &  9  \\
		Benfica           & 6 & 2 & 1 & 3 &  7 & 8 &  7  \\
		FC Copenhagen     & 6 & 2 & 1 & 3 &  5 & 8 &  7  \\
		\hline
\end{tabular}
\label{Tab:par}
\end{table}

The crystal structure parameters of $\gamma$($\rm TiAl$) phase and $\alpha$($\rm Ti_3Al$) phase is shown as Table\ref{tab:str_par}. 
\subsection{Molecular Dynamics Model}
The crystal structure of $\gamma$-TiAl
is shown by Fig \ref{fig:pf_model_labeled}

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{pict/model_labeled}
	\caption{Representative nanocrystalline bulk mode}
	\centering
	\label{fig:pf_model}
\end{figure}
\subsection{Identification of Defects}

 \begin{table}[h]
 	\centering
 	\caption{Table caption}
 	\begin{tabular}{l l l}
 		\hline
 		\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
 		\hline
 		Treatment 1 & 0.0003262 & 0.562 \\
 		Treatment 2 & 0.0015681 & 0.910 \\
 		Treatment 3 & 0.0009271 & 0.296 \\
 		\hline
 	\end{tabular}

 \end{table}

$$E=\sum_{i}^n a_i=0$$

where

parameters can begiven as Table \ref{Tab:par}:

\section{Results and Discussion}

\subsection{The influence of void on strength of TiAl alloy}

The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material. Detailed observation of speciman with void inside the grain is shown in Figure ~\ref{fig:strline}.
1.In many cases the orientation of slip slip is changed because the crystallographically avalilable slip and directions are not coontinuous across teh interface. This may significantly reduce the Schmid factor and thus impede slip tansfer. At the $\gamma/\gamma$ interfaces teh orientation of the slip plan could change through a relavely large angle of about 90 degree. Reorientation of slip is always required at the $\alpha_{2} / \gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree ref{}.
2. The core of  a dislocaiton intersecting an interface often needs to be transformed. For example, an ordinary 1/2<110] dislocaiton glidng in one $\gamma$ grain has to be converted in to a <101] superdislocation with the double Burgers vector glidng in an adjacent $\gamma$ grain. At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocaitons consistent with the $L1_0$structure. These core tranfformations are associated with a change of teh dislocation line enenrgy because teh lengths of teh Burgers vectors and the shear moduli are different.
3.Dislocations crossing semicoherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{pict/stress}
	\caption{}
	\centering
	\label{fig:stress}
\end{figure}

\subsection{Decrease of Strength}

\section{Conclusion}

%\section*{References}

\bibliography{/home/alex/Documents/Bibtex/VIOLET-ref.bib}
Fig.\ref{fig:stress}.

\end{document}

### 2018-08-03 scpt.tex
compiled

@@
-%%original
+% choose one of following three
 %\documentclass[review]{elsarticle}
-
-%%edited by wmm
 %\documentclass[final,5p,times,twocolumn]{elsarticle}
@@
 
-\title{Effect of Void on Fracture Behavior of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy}
+\title{Effect of Void on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy}
 %\tnotetext[mytitlenote]{*** \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
@@
 At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocaitons consistent with the $L1_0$structure.
-These core tranfformations are associated with a change of teh dislocation line enenrgy because teh lengths of teh Burgers vectors and the shear moduli are different.
+These core tranfformations are associated with a change of teh dislocation line enenrgy because teh lengths of teh Burgers vectors and the shear module are different.
 3.Dislocations crossing semicoherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.

### 2018-08-03 scpt.tex
title changed
word corrected

@@
 
-\title{Effect of Void on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy}
+\title{Effect of Nanovoid on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy}
 %\tnotetext[mytitlenote]{*** \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
@@
  The fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects.
-Existing studies of defect evolution in titanium--aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
+Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
 \end{abstract}
@@
 TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite {int.uti.j.1}.
-However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titantium aliuminde alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{int.uti.m.1}.
+However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{int.uti.m.1}.
 Metal
@@
 
-The  in the material is determined by interatomic potencial. 
-We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation. The silulations were performed on the a system of 460000 atoms.
-Potential function is an mathematical approximation used  to determin interatomic effect among particlesan in MD simulation.
+The  in the material is determined by interatomic potential. 
+We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation. The simulations were performed on the a system of 460000 atoms.
+Potential function is an mathematical approximation used  to determine interatomic effect among particles in MD simulation.
 The embedded atom method (MEAM) potential by \ref() was used In the study, which is used MD simulations were performed using the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code\ref().
@@
 The simulation cells of two phase poly crystal with an initially spherical void at different position are shown in figure \ref{}.
-Periodic boundaryconditions are applied along all three directions, in effect creating  TiAl poly crystal with periodic nanovoid structures.
+Periodic boundary conditions are applied along all three directions, in effect creating  TiAl poly crystal with periodic nanovoid structures.
 Each cuboidal model, containing about 4.6 million atoms, has edge sizes of $L_x = nm$, $L_y =  nm$, $L_z =  nm$.
 During the construction process, the grain centers were randomly placed in a simulation cell resulting in the arbitrary shape and orientation of the grains.
-The construction of a specific grain would stop at a position where atoms from one grain centerwere no longer closer to the centers of other grains.
+The construction of a specific grain would stop at a position where atoms from one grain center were no longer closer to the centers of other grains.
 There was only one intragranular or intergranular spherical void within each simulation model.
@@
 1(b).
-The intergranular spherical voidwas at the center of the simulation cell, as shown in Fig.
+The intergranular spherical void was at the center of the simulation cell, as shown in Fig.
 1(c).
@@
 		Celtic            & 6 & 3 & 0 & 3 &  8 & 9 &  9  \\
-		Benfica           & 6 & 2 & 1 & 3 &  7 & 8 &  7  \\
+		Benefit          & 6 & 2 & 1 & 3 &  7 & 8 &  7  \\
 		FC Copenhagen     & 6 & 2 & 1 & 3 &  5 & 8 &  7  \\
@@
 \subsection{Identification of Defects}
-
+\paragraph{}
  \begin{table}[h]
@@
 
-parameters can begiven as Table \ref{Tab:par}:
+parameters can be given as Table \ref{Tab:par}:
 
@@
 The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
-Detailed observation of speciman with void inside the grain is shown in Figure ~\ref{fig:strline}.
-1.In many cases the orientation of slip slip is changed because the crystallographically avalilable slip and directions are not coontinuous across teh interface.
-This may significantly reduce the Schmid factor and thus impede slip tansfer.
-At the $\gamma/\gamma$ interfaces teh orientation of the slip plan could change through a relavely large angle of about 90 degree.
+Detailed observation of specimen with void inside the grain is shown in Figure ~\ref{fig:strline}.
+1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
+This may significantly reduce the Schmid factor and thus impede slip transfer.
+At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
 Reorientation of slip is always required at the $\alpha_{2} / \gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree ref{}.
 2.
-The core of  a dislocaiton intersecting an interface often needs to be transformed.
-For example, an ordinary 1/2<110] dislocaiton glidng in one $\gamma$ grain has to be converted in to a <101] superdislocation with the double Burgers vector glidng in an adjacent $\gamma$ grain.
-At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocaitons consistent with the $L1_0$structure.
-These core tranfformations are associated with a change of teh dislocation line enenrgy because teh lengths of teh Burgers vectors and the shear module are different.
-3.Dislocations crossing semicoherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
+The core of  a dislocation intersecting an interface often needs to be transformed.
+For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
+At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
+These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
+3.Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
 \begin{figure}

### 2018-08-03 data/code/LinePlt.py
add code

@@ -1,0 +1,23 @@
+# 读取输出文件，绘制应力应变曲线
+import matplotlib.pyplot as plt
+import pandas as pd
+# pre-set head name
+prop = ['step', 'strain', 'stress', 'energy']
+# import data from .csv file:
+ds1 = pd.read_csv('/home/alex/HDD/post/aa.csv', sep=' ', skiprows=1, names=prop)
+ds2 = pd.read_csv('/home/alex/HDD/post/ag.csv', sep=' ', skiprows=1, names=prop)
+ds3 = pd.read_csv('/home/alex/HDD/post/pf.csv', sep=' ', skiprows=1, names=prop)
+ds4 = pd.read_csv('/home/alex/HDD/post/ia.csv', sep=' ', skiprows=1, names=prop)
+# plot lines
+p1 = plt.plot(ds1.step, ds1.stress, label='aa')
+p2 = plt.plot(ds2.step, ds2.stress, label='ag')
+p3 = plt.plot(ds3.step, ds3.stress, label='pf')
+p4 = plt.plot(ds4.step, ds4.stress, label='ia')
+# config title and label
+
+plt.title('stress-strain curve')
+plt.xlabel('Step')
+plt.ylabel('Stress (GPa)')
+plt.legend()
+plt.show()
+

### 2018-08-03 data/code/SigLinePlt.py

@@ -1,0 +1,17 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# pre-set head name
+pyy = np.loadtxt('ig_10.txt')
+pxx = np.linspace(0, 0.4, (len(pyy)))
+
+plt.plot(pxx, pyy)
+plt.title('Area of Crack Surface')
+plt.xlabel('strain')
+plt.ylabel('Area/A2')
+plt.savefig('area.png')
+plt.show()
+
+
+
+

### 2018-08-03 code/LinePlt.py
pathchanged

@@ -4,10 +4,10 @@ import pandas as pd
 # pre-set head name
 prop = ['step', 'strain', 'stress', 'energy']
 # import data from .csv file:
-ds1 = pd.read_csv('/home/alex/HDD/post/aa.csv', sep=' ', skiprows=1, names=prop)
-ds2 = pd.read_csv('/home/alex/HDD/post/ag.csv', sep=' ', skiprows=1, names=prop)
-ds3 = pd.read_csv('/home/alex/HDD/post/pf.csv', sep=' ', skiprows=1, names=prop)
-ds4 = pd.read_csv('/home/alex/HDD/post/ia.csv', sep=' ', skiprows=1, names=prop)
+ds1 = pd.read_csv('data/aa.csv', sep=' ', skiprows=1, names=prop)
+ds2 = pd.read_csv('data/ag.csv', sep=' ', skiprows=1, names=prop)
+ds3 = pd.read_csv('data/pf.csv', sep=' ', skiprows=1, names=prop)
+ds4 = pd.read_csv('data/ia.csv', sep=' ', skiprows=1, names=prop)
 # plot lines
 p1 = plt.plot(ds1.step, ds1.stress, label='aa')
 p2 = plt.plot(ds2.step, ds2.stress, label='ag')

### 2018-08-04 code/LinePlt.py
tried to use path in code failed

@@ -1,13 +1,15 @@
 # 读取输出文件，绘制应力应变曲线
+import os
 import matplotlib.pyplot as plt
 import pandas as pd
+
 # pre-set head name
 prop = ['step', 'strain', 'stress', 'energy']
 # import data from .csv file:
-ds1 = pd.read_csv('data/aa.csv', sep=' ', skiprows=1, names=prop)
-ds2 = pd.read_csv('data/ag.csv', sep=' ', skiprows=1, names=prop)
-ds3 = pd.read_csv('data/pf.csv', sep=' ', skiprows=1, names=prop)
-ds4 = pd.read_csv('data/ia.csv', sep=' ', skiprows=1, names=prop)
+ds1 = pd.read_csv('~/violet/code/data/stress_strain/aa.csv', sep=' ', skiprows=1, names=prop)
+ds2 = pd.read_csv('~/violet/code/data/stress_strain/ag.csv', sep=' ', skiprows=1, names=prop)
+ds3 = pd.read_csv('~/violet/code/data/stress_strain/pf.csv', sep=' ', skiprows=1, names=prop)
+ds4 = pd.read_csv('~/violet/code/data/stress_strain/ia.csv', sep=' ', skiprows=1, names=prop)
 # plot lines
 p1 = plt.plot(ds1.step, ds1.stress, label='aa')
 p2 = plt.plot(ds2.step, ds2.stress, label='ag')

### 2018-08-04 code/SigLinePlt.py

@@ -1,8 +1,10 @@
-import matplotlib.pyplot as plt
+import os
 import numpy as np
-
+import matplotlib.pyplot as plt
+file_path = os.path.join('data', 'inflammation-01.csv')
 # pre-set head name
-pyy = np.loadtxt('ig_10.txt')
+wdir = os.path.abspath('.')
+pyy = np.loadtxt("wdir/code/data/crack_surf/ig_10.txt")
 pxx = np.linspace(0, 0.4, (len(pyy)))
 
 plt.plot(pxx, pyy)
@@ -11,7 +13,7 @@ plt.xlabel('strain')
 plt.ylabel('Area/A2')
 plt.savefig('area.png')
 plt.show()
-
+print(os.path.abspath('.'))
 
 
 

### 2018-08-04 code/SigLinePlt.py
add fig

@@ -13,7 +13,7 @@ plt.xlabel('strain')
 plt.ylabel('Area/A2')
 plt.savefig('area.png')
 plt.show()
-print(os.path.abspath('.'))
+#plt.savefig()
 
 
 

### 2018-08-04 draft/scpt.tex
dir changed
no
compiled
Method add deatials

--- 2018-08-03 scpt.tex
@@
 \captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
-%review
+%reviewc
 %final,5p,times,twocolumn
@@
 
-%\address[mymainaddress]{School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China}
+\address[mymainaddress]{School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China}
 
@@
 
-TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite {int.uti.j.1}.
+TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{int.uti.j.1}.
 However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{int.uti.m.1}.
@@
 \section Molecular dynamics simulation analysis
-\subsection{Mode creation of nanocrystalline alloy}
 
-The crystal structure of $\gamma$-TiAl alloy is L10 [32,33] which is shown in Figure 1; the lattice constants
+\subsection{Model creation of nanocrystalline}
+$\gamma  TiAl$ has a fcc-centered tetragonal with an $\L1_0$ structure \ref{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cell are shown in Fig.\ref{}, and the constructing parameters are givin by Table.\ref{}.
+The simulation cells of two phase poly crystal with an initially spherical void at different position are shown in figure \ref{}.
+Periodic boundary conditions are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
+Each cuboidal model, containing about 4.6 million atoms,The initial dimension of simulation cell is  $L_x = nm$, $L_y =  nm$, $L_z =  nm$.
+The grain orientation and size were randomly created with Voronoi method with code ATOMSK \ref{}, and resulting in the arbitrary shape and orientation of the grains.
+Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model.
+The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig.
+\ref{}.
+The intergranular spherical void was at the center of the simulation cell, as shown in Fig.
+\ref{}.
 
-The  in the material is determined by interatomic potential. 
-We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation. The simulations were performed on the a system of 460000 atoms.
-Potential function is an mathematical approximation used  to determine interatomic effect among particles in MD simulation.
-The embedded atom method (MEAM) potential by \ref() was used In the study, which is used MD simulations were performed using the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code\ref().
+\subsection{Atomic potential}
+The interaction of particle in the material is determined by interatomic potential.
+Many reported examples of crack propagation in metal materials were performed with embedded atomic method, due to is better accuracy in metal lattice compare with F-S and L/J \ref{compare LJ and other}.
+The embedded atom method (MEAM) potential developed by Zope and Mishin by \ref{} was used in the study, which is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \ref{}.
+We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation.
+\subsection{Analysis method}
 
-The simulation cells of two phase poly crystal with an initially spherical void at different position are shown in figure \ref{}.
-Periodic boundary conditions are applied along all three directions, in effect creating  TiAl poly crystal with periodic nanovoid structures.
-Each cuboidal model, containing about 4.6 million atoms, has edge sizes of $L_x = nm$, $L_y =  nm$, $L_z =  nm$.
-During the construction process, the grain centers were randomly placed in a simulation cell resulting in the arbitrary shape and orientation of the grains.
-The construction of a specific grain would stop at a position where atoms from one grain center were no longer closer to the centers of other grains.
-There was only one intragranular or intergranular spherical void within each simulation model.
-The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig.
-1(b).
-The intergranular spherical void was at the center of the simulation cell, as shown in Fig.
-1(c).
-Simulation specimens of the 16.32 nm grain size models with initial void diameters at or below 13 nm were mainly considered in the analysis sections owing to the fact that their spherical void surfaces did not intersect with surrounding GBs after the equilibration process.
-This avoided conflict between competing sources of dislocation emission: GBs or spherical void surfaces.
-Different diameter intragranular voids were all embedded in the same grain and at the same position in the samples, as shown in Fig.
-1(b).
-The intergranular voids with different initial diameters were identically at the center of the simulation model, as shown in Fig.
-1(c).
+\paragraph{defect identification}
+
+\paragraph{stress calculation}
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\linewidth]{pict/model_labeled}
-	\caption{Representative nanocrystalline bulk mode}
-	\centering
-	\label{fig:pf_model}
-\end{figure}
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.5\linewidth]{pict/model_labeled}
+%	\caption{Representative nanocrystalline bulk mode}
+%	\centering
+%	\label{fig:pf_model}
+%\end{figure}
 \subsection{Identification of Defects}
@@
 3.Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{pict/stress}
-	\caption{}
-	\centering
-	\label{fig:stress}
-\end{figure}
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.7\linewidth]{pict/stress}
+%	\caption{}
+%	\centering
+%	\label{fig:stress}
+%\end{figure}
 

### 2018-08-04 draft/scpt.tex
add virial stress

@@
 \paragraph{stress calculation}
+The atomic stress is calculated using the virial definition :
+$$\sigma_t(i)=-$$
+$$\sigma_t(i)= $$
+where $\f_\alpha$ is the interatomic force between atom i and j in the direction $\alpha$, $\gamma_\beta$ is the distance in direction
 
@@
 \subsection{Identification of Defects}
-\paragraph{}
- \begin{table}[h]
- 	\centering
- 	\caption{Table caption}
- 	\begin{tabular}{l l l}
- 		\hline
- 		\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
- 		\hline
- 		Treatment 1 & 0.0003262 & 0.562 \\
- 		Treatment 2 & 0.0015681 & 0.910 \\
- 		Treatment 3 & 0.0009271 & 0.296 \\
- 		\hline
- 	\end{tabular}
-
- \end{table}
-
-$$E=\sum_{i}^n a_i=0$$
-
-where
-
-parameters can be given as Table \ref{Tab:par}:
-
+%\paragraph{}
+% \begin{table}[h]
+% 	\centering
+% 	\caption{Table caption}
+% 	\begin{tabular}{l l l}
+% 		\hline
+% 		\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
+% 		\hline
+% 		Treatment 1 & 0.0003262 & 0.562 \\
+% 		Treatment 2 & 0.0015681 & 0.910 \\
+% 		Treatment 3 & 0.0009271 & 0.296 \\
+% 		\hline
+% 	\end{tabular}
+% 	
+% \end{table}
+%
+%
+%$$E=\sum_{i}^n a_i=0$$
+%
+%where
+%
+%
+%parameters can be given as Table \ref{Tab:par}:
+%
+%
+%
 \section{Results and Discussion}

### 2018-08-04 draft/scpt.tex
delete blankline and notes

--- 2018-08-04 draft/scpt.tex
@@
 \usepackage[labelfont=bf,justification=raggedright]{caption}
-
 \captionsetup[figure]{name=Fig. ,labelsep=period,singlelinecheck=true,skip=5pt}
-
 \captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
@@
 \usepackage{lineno,hyperref}
-
 \usepackage{float}
-
 \modulolinenumbers[5]
-
 \journal{Materials and Design}
-
+\bibliographystyle{~/format/elsarticle-num.bst}
 %%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
-\bibliographystyle{~/format/elsarticle-num.bst}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{document}
-
 \begin{frontmatter}
-
 \title{Effect of Nanovoid on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy}
 %\tnotetext[mytitlenote]{*** \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
-
 %% Group authors per affiliation:
@@
 \address[mymainaddress]{School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China}
-
 \begin{abstract}
@@
 \end{abstract}
-
 \begin{keyword}
@@
 \end{keyword}
-
 \end{frontmatter}
-
 \linenumbers
-
 \section{Introduction}
-
 TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{int.uti.j.1}.
@@
 Metal 
-
-% study on poly 
-% gap
-
 \section Molecular dynamics simulation analysis
-
 \subsection{Model creation of nanocrystalline}
@@
 \ref{}.
-
 \subsection{Atomic potential}
@@
 \subsection{Analysis method}
-
 \paragraph{defect identification}
-
 \paragraph{stress calculation}
-
+The atomic stress is calculated using the virial definition :
+$$\sigma_t(i)=-$$
+$$\sigma_t(i)= $$
+where $\f_\alpha$ is the interatomic force between atom i and j in the direction $\alpha$, $\gamma_\beta$ is the distance in direction 
 \begin{table}[H]
@@
 \end{table}
-
 The crystal structure parameters of $\gamma$($\rm TiAl$) phase and $\alpha$($\rm Ti_3Al$) phase is shown as Table\ref{tab:str_par}. 
@@
 is shown by Fig \ref{fig:pf_model_labeled}
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=0.5\linewidth]{pict/model_labeled}
-%	\caption{Representative nanocrystalline bulk mode}
-%	\centering
-%	\label{fig:pf_model}
-%\end{figure}
 \subsection{Identification of Defects}
-\paragraph{}
- \begin{table}[h]
- 	\centering
- 	\caption{Table caption}
- 	\begin{tabular}{l l l}
- 		\hline
- 		\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
- 		\hline
- 		Treatment 1 & 0.0003262 & 0.562 \\
- 		Treatment 2 & 0.0015681 & 0.910 \\
- 		Treatment 3 & 0.0009271 & 0.296 \\
- 		\hline
- 	\end{tabular}
-
- \end{table}
-
-$$E=\sum_{i}^n a_i=0$$
-
-where
-
-parameters can be given as Table \ref{Tab:par}:
-
 \section{Results and Discussion}
-
 \subsection{The influence of void on strength of TiAl alloy}
-
 The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
@@
 3.Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=0.7\linewidth]{pict/stress}
-%	\caption{}
-%	\centering
-%	\label{fig:stress}
-%\end{figure}
-
 \subsection{Decrease of Strength}
-
 \section{Conclusion}
-
 %\section*{References}
-
 \bibliography{/home/alex/Documents/Bibtex/VIOLET-ref.bib}
 Fig.\ref{fig:stress}.
-
 \end{document}

### 2018-08-05 draft/scpt.tex
edit outline

--- 2018-08-04 draft/scpt.tex
@@
 \end{keyword}
-
 \end{frontmatter}
-
 \linenumbers
@@
 \section{Introduction}
-
 TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{int.uti.j.1}.
@@
 
-% study on poly 
-% gap
-
-\section Molecular dynamics simulation analysis
+\section{Molecular dynamics simulation}
 
@@
 We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation.
+
 \subsection{Analysis method}
+The atomic stress is calculated using the virial definition :
+$$\sigma_t(i)=-$$
+$$\sigma_t(i)= $$
 
-\paragraph{defect identification}
-
-\paragraph{stress calculation}
-
+where $\f_\alpha$ is the interatomic force between atom i and j in the direction $\alpha$, $\gamma_\beta$ is the distance in direction 
 \begin{table}[H]

### 2018-08-05 draft/scpt.tex
cen formula added

@@
 
-\subsection{Analysis method}
+\subsection{data Analysis method}
+\paragraph{Cen}
+In view of the fact that dislocations cannot be easily spotted in a three-dimensional crystal, a centrosymmetry parameter \ref{C.L.
+Kelchner, S.J.
+Plimpton, J.C.
+Hamilton, Phys.
+Rev.
+B 58 (1998) 11085–11088.
+[27]} is used to identify the nucleation and propagation of dislocations.
+The said centrosymmetry parameter is defined as follow:
+$$P = \displaystyle\sum_{i=1}^{6}|\vec{R_i}+\vec{R_{i+6}}|^2$$
+where $\vec{R_i}$ and $\vec{R_{i+6}}$ are the vectors corresponding to the six pairs of opposite nearest neighbors in the fcc lattice.
+The centrosymmetry parameter is zero for atoms in a perfect lattice.
+In other words, if the lattice is distorted the value of P will not be zero.
+Instead, the parameter will have a value within the range corresponding to a particular defect.
+By removing all the perfect and surface atoms within the bulk, the existence of dislocation atoms become visible.<Details>
+\paragraph{stress}
 The atomic stress is calculated using the virial definition :
@@
 
-where $\f_\alpha$ is the interatomic force between atom i and j in the direction $\alpha$, $\gamma_\beta$ is the distance in direction 
-\begin{table}[H]
-\centering
-\caption{Experimental conditions}
-\begin{tabular}{l*{6}{c}r}	
-		\hline
-		Team              & $\alpha$ & W & D & L & F  & A & Pts \\
-		\hline
-		Manchester United & 6 & 4 & 0 & 2 & 10 & 5 & 12  \\
-		Celtic            & 6 & 3 & 0 & 3 &  8 & 9 &  9  \\
-		Benefit           & 6 & 2 & 1 & 3 &  7 & 8 &  7  \\
-		FC Copenhagen     & 6 & 2 & 1 & 3 &  5 & 8 &  7  \\
-		\hline
-\end{tabular}
-\label{Tab:par}
-\end{table}
-The crystal structure parameters of $\gamma$($\rm TiAl$) phase and $\alpha$($\rm Ti_3Al$) phase is shown as Table\ref{tab:str_par}. 
-\subsection{Molecular Dynamics Model}
-The crystal structure of $\gamma$-TiAl
-is shown by Fig \ref{fig:pf_model_labeled}
-\subsection{Identification of Defects}
 \section{Results and Discussion}

### 2018-08-06 draft/bkp/scpt.tex
ref linked

--- 2018-08-05 draft/scpt.tex
@@
-% choose one of following three
+\documentclass[review]{elsarticle}
 %\documentclass[review]{elsarticle}
+
 %\documentclass[final,5p,times,twocolumn]{elsarticle}
-\documentclass[final,5p,times,twocolumn]{elsarticle}
+%\documentclass[final,5p,times,twocolumn]{elsarticle}
 \usepackage[labelfont=bf,justification=raggedright]{caption}
 \captionsetup[figure]{name=Fig. ,labelsep=period,singlelinecheck=true,skip=5pt}
-\captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
+%\captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
 %reviewc
@@
 \usepackage{float}
+%\usepackage{cite}
 \modulolinenumbers[5]
 \journal{Materials and Design}
-\bibliographystyle{~/format/elsarticle-num.bst}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Introduction}
-TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{int.uti.j.1}.
-However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{int.uti.m.1}.
-Metal
-
-\section{Molecular dynamics simulation}
-
+TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{Xiong2015}.
+However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{intro-structure}.
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{img/cell}
+	%\label{fig:cell}
+	\caption{units cell}
+\end{figure}
 \subsection{Model creation of nanocrystalline}
-$\gamma  TiAl$ has a fcc-centered tetragonal with an $\L1_0$ structure \ref{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cell are shown in Fig.\ref{}, and the constructing parameters are givin by Table.\ref{}.
-The simulation cells of two phase poly crystal with an initially spherical void at different position are shown in figure \ref{}.
+$\gamma  TiAl$ has a fcc-centered tetragonal with an $\L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cell are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}.
+The simulation cells of two phase poly crystal with an initially spherical void at different position are shown in figure \cite{}.
 Periodic boundary conditions are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
 Each cuboidal model, containing about 4.6 million atoms,The initial dimension of simulation cell is  $L_x = nm$, $L_y =  nm$, $L_z =  nm$.
-The grain orientation and size were randomly created with Voronoi method with code ATOMSK \ref{}, and resulting in the arbitrary shape and orientation of the grains.
+The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{}, and resulting in the arbitrary shape and orientation of the grains.
 Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model.
 The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig.
-\ref{}.
+\cite{}.
 The intergranular spherical void was at the center of the simulation cell, as shown in Fig.
-\ref{}.
+\cite{}.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/pf_model_labeled}
+	\caption{Simulation box}
+
+	%\label{Simulation box}
+\end{figure}
 
@@
 The interaction of particle in the material is determined by interatomic potential.
-Many reported examples of crack propagation in metal materials were performed with embedded atomic method, due to is better accuracy in metal lattice compare with F-S and L/J \ref{compare LJ and other}.
-The embedded atom method (MEAM) potential developed by Zope and Mishin by \ref{} was used in the study, which is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \ref{}.
+Many reported examples of crack propagation in metal materials were performed with embedded atomic method, due to is better accuracy in metal lattice compare with F-S and L/J \cite{compare LJ and other}.
+The embedded atom method (MEAM) potential developed by Zope and Mishin by \cite{} was used in the study, which is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{}.
 We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation.
@@
 \paragraph{Cen}
-In view of the fact that dislocations cannot be easily spotted in a three-dimensional crystal, a centrosymmetry parameter \ref{C.L.
-Kelchner, S.J.
-Plimpton, J.C.
-Hamilton, Phys.
-Rev.
-B 58 (1998) 11085–11088.
-[27]} is used to identify the nucleation and propagation of dislocations.
+In view of the fact that dislocations cannot be easily spotted in a three-dimensional crystal, a centrosymmetry parameter \cite{C.L.
+Kelchner1998} is used to identify the nucleation and propagation of dislocations.
 The said centrosymmetry parameter is defined as follow:
@@
 $$\sigma_t(i)= $$
+\section{Molecular dynamics simulation}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{img/process-ia}
+	\label{fig:process.ia}
+	\caption{Fracture process of specimem with void in $\alpha$ pahse}
+\end{figure}
 
@@
 The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
-Detailed observation of specimen with void inside the grain is shown in Figure ~\ref{fig:strline}.
+Detailed observation of specimen with void inside the grain is shown in Figure ~\cite{fig:processia}.
 1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
@@
 3.Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
+
 \subsection{Decrease of Strength}
 \section{Conclusion}
-%\section*{References}
-\bibliography{/home/alex/Documents/Bibtex/VIOLET-ref.bib}
-Fig.\ref{fig:stress}.
+
+\bibliographystyle{elsarticle-num.bst}
+\section*{References}
+\bibliography{/ref/VIOLET-ref}
+%Fig.\cite{fig:stress}.
 \end{document}

### 2018-08-06 draft/draft.tex
ref linked

--- 2018-08-06 draft/bkp/scpt.tex
@@
-\documentclass[review]{elsarticle}
 %\documentclass[review]{elsarticle}
+\documentclass[final,5p,times,twocolumn]{elsarticle}
 
-%\documentclass[final,5p,times,twocolumn]{elsarticle}
-%\documentclass[final,5p,times,twocolumn]{elsarticle}
-\usepackage[labelfont=bf,justification=raggedright]{caption}
-\captionsetup[figure]{name=Fig. ,labelsep=period,singlelinecheck=true,skip=5pt}
-%\captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
-%reviewc
-%final,5p,times,twocolumn
 	\usepackage{lineno,hyperref}
-\usepackage{float}
-%\usepackage{cite}
+	\modulolinenumbers[5]
+
+	\journal{Journal of \LaTeX\ Templates}
+
+	%%%%%%%%%%%%%%%%%%%%%%%
+	%% Elsevier bibliography styles
+	%%%%%%%%%%%%%%%%%%%%%%%
+	%% To change the style, put a % in front of the second line of the current style and
+	%% remove the % from the second line of the style you would like to use.
+	%%%%%%%%%%%%%%%%%%%%%%%
+
+	%% Numbered
+	%\bibliographystyle{model1-num-names}
+
+	%% Numbered without titles
+	%\bibliographystyle{model1a-num-names}
+
+	%% Harvard
+	\bibliographystyle{elsarticle-num.bst}
 \modulolinenumbers[5]
@@
 \subsection{Model creation of nanocrystalline}
-$\gamma  TiAl$ has a fcc-centered tetragonal with an $\L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cell are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}.
+$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cell are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}.
 The simulation cells of two phase poly crystal with an initially spherical void at different position are shown in figure \cite{}.
@@
 The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
-Detailed observation of specimen with void inside the grain is shown in Figure ~\cite{fig:processia}.
+Detailed observation of specimen with void inside the grain is shown in Figure \cite{}.
 1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
@@
 
-\bibliographystyle{elsarticle-num.bst}
-\section*{References}
-\bibliography{/ref/VIOLET-ref}
+%\bibliographystyle{elsarticle-num.bst}
+\bibliography{ref/VIOLET-ref}
 %Fig.\cite{fig:stress}.

### 2018-08-06 draft/draft.tex
env is ok :)

@@
 The interaction of particle in the material is determined by interatomic potential.
-Many reported examples of crack propagation in metal materials were performed with embedded atomic method, due to is better accuracy in metal lattice compare with F-S and L/J \cite{compare LJ and other}.
+Many reported examples of crack propagation in metal materials were performed with embedded atomic method, due to is better accuracy in metal lattice compare with F-S and L/J \cite{}.
 The embedded atom method (MEAM) potential developed by Zope and Mishin by \cite{} was used in the study, which is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{}.
@@
 \paragraph{Cen}
-In view of the fact that dislocations cannot be easily spotted in a three-dimensional crystal, a centrosymmetry parameter \cite{C.L.
-Kelchner1998} is used to identify the nucleation and propagation of dislocations.
+In view of the fact that dislocations cannot be easily spotted in a three-dimensional crystal, a centrosymmetry parameter \cite{} is used to identify the nucleation and propagation of dislocations.
 The said centrosymmetry parameter is defined as follow:
@@
 \subsection{Decrease of Strength}
-\section{Conclusion}
 

### 2018-08-06 draft/draft.tex
add lattice parameter

@@
 \subsection{Model creation of nanocrystalline}
+
+\begin{table}[h]
+	\centering
+	\caption{Parameters of  Nanocrystallin}
+	\begin{tabular}{l*{6}{c}r}
+			\hline
+			Phase			& Space group		& Designation		& Lattice parameters \\
+			\hline
+			$\alpha_2$		& $\rm P6_3/mmc$ 	& $\rm 0_{19}$ 		& a=0.5765 c=0.46833  \\
+			$\gamma$		& $\rm tP4$ 		& $\rm L1_0$			& a = 0.3997 c=0.4062 \\
+			\hline
+	\end{tabular}
+	\label{Tab:model-parameter}
+	\end{table}
+
 $\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cell are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}.

### 2018-08-07 draft/draft.tex
table corrected

@@
-%\documentclass[review]{elsarticle}
-\documentclass[final,5p,times,twocolumn]{elsarticle}
-
+\documentclass[final,5p,times]{elsarticle}
+%\documentclass[final,5p,times,twocolumn]{elsarticle}
+	\setlength{\mathindent}{3cm}
 	\usepackage{lineno,hyperref}
@@
 
-	\journal{Journal of \LaTeX\ Templates}
+	\journal{Computational Materaials Science}
 
@@
 However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{intro-structure}.
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{img/cell}
-	%\label{fig:cell}
-	\caption{units cell}
-\end{figure}
-\subsection{Model creation of nanocrystalline}
+
+\section{Molecular Dynamics Simulation }
+\subsection{Model Creation of Crystalline}
 
@@
 	\centering
-	\caption{Parameters of  Nanocrystallin}
-	\begin{tabular}{l*{6}{c}r}
+	\begin{tabular}{l c c l}
 			\hline
-			Phase			& Space group		& Designation		& Lattice parameters \\
+			Phase			& Space group		& Designation		& Parameters \\
 			\hline
-			$\alpha_2$		& $\rm P6_3/mmc$ 	& $\rm 0_{19}$ 		& a=0.5765 c=0.46833  \\
-			$\gamma$		& $\rm tP4$ 		& $\rm L1_0$			& a = 0.3997 c=0.4062 \\
+			$\alpha_2$		& $\rm P6_3/mmc$ 	& $\rm 0_{19}$ 		& $a$ = 0.5765 \\
+							&					&					& $c$ = 0.46833 \\
+			$\gamma$		& $\rm tP4$ 		& $\rm L1_0$		& $a$ = 0.3997 \\
+			 				&					&					& $c$ = 0.4062 \\			
 			\hline
 	\end{tabular}
+	\caption{Parameters of  Nanocrystallin}
 	\label{Tab:model-parameter}
@@
 \cite{}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{img/cell}
+	%\label{fig:cell}
+	\caption{units cell}
+\end{figure}
+
 \begin{figure}
@@
 The said centrosymmetry parameter is defined as follow:
-$$P = \displaystyle\sum_{i=1}^{6}|\vec{R_i}+\vec{R_{i+6}}|^2$$
+
 where $\vec{R_i}$ and $\vec{R_{i+6}}$ are the vectors corresponding to the six pairs of opposite nearest neighbors in the fcc lattice.
-The centrosymmetry parameter is zero for atoms in a perfect lattice.
+The centrosymmetry parameter(CSP) defined by \ref{eq:csp} is zero for atoms in a perfect lattice.
 In other words, if the lattice is distorted the value of P will not be zero.
 Instead, the parameter will have a value within the range corresponding to a particular defect.
-By removing all the perfect and surface atoms within the bulk, the existence of dislocation atoms become visible.<Details>
+By removing all the perfect and surface atoms within the bulk, the existence of dislocation atoms become visible.<Details> It is shown as follows:
+
+\begin{equation} \label{eq:csp} 
+	P = \displaystyle\sum_{i=1}^{6}|\vec{R_i}+\vec{R_{i+6}}|^2
+	\end{equation}
+
 \paragraph{stress}
@@
 $$\sigma_t(i)= $$
-\section{Molecular dynamics simulation}
 

### 2018-08-07 draft/draft.tex
formated

@@
-\documentclass[final,5p,times]{elsarticle}
+\documentclass[final,5p,times,twocolumn]{elsarticle}
+\usepackage[labelfont=bf,justification=raggedright]{caption}
+\captionsetup[figure]{name=Fig. ,labelsep=period,singlelinecheck=true,skip=5pt}
+\captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
 %\documentclass[final,5p,times,twocolumn]{elsarticle}
@@
 	\centering
+	\caption{Parameters of  nanocrystalline}
+
 	\begin{tabular}{l c c l}
@@
 	\end{tabular}
-	\caption{Parameters of  Nanocrystallin}
 	\label{Tab:model-parameter}
@@
 
-\subsection{data Analysis method}
-\paragraph{Cen}
+\subsection{Analysis method}
+\paragraph{CSP}
 In view of the fact that dislocations cannot be easily spotted in a three-dimensional crystal, a centrosymmetry parameter \cite{} is used to identify the nucleation and propagation of dislocations.
 The said centrosymmetry parameter is defined as follow:
-
-where $\vec{R_i}$ and $\vec{R_{i+6}}$ are the vectors corresponding to the six pairs of opposite nearest neighbors in the fcc lattice.
-The centrosymmetry parameter(CSP) defined by \ref{eq:csp} is zero for atoms in a perfect lattice.
-In other words, if the lattice is distorted the value of P will not be zero.
-Instead, the parameter will have a value within the range corresponding to a particular defect.
-By removing all the perfect and surface atoms within the bulk, the existence of dislocation atoms become visible.<Details> It is shown as follows:
 
@@
 
-\paragraph{stress}
+where $\vec{R_i}$ and $\vec{R_{i+6}}$ are the vectors corresponding to the six pairs of opposite nearest neighbors in the fcc lattice.
+The centrosymmetry parameter(CSP) is zero for atoms in a perfect lattice.
+In other words, if the lattice is distorted the value of P will not be zero.
+Instead, the parameter will have a value within the range corresponding to a particular defect.
+By removing all the perfect and surface atoms within the bulk, the existence of dislocation atoms become visible.
+
+\paragraph{Virial Stress}
 The atomic stress is calculated using the virial definition :
@@
 	\label{fig:process.ia}
-	\caption{Fracture process of specimem with void in $\alpha$ pahse}
+	\caption{Fracture process of specimen with void in $\alpha$ phase}
 \end{figure}

### 2018-08-08 draft/draft.tex
add figs

@@
 \section{Molecular Dynamics Simulation }
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{img/cell}
+	%\label{fig:cell}
+	\caption{units cell}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/pf_model_labeled}
+	\caption{Simulation box}
+
 \subsection{Model Creation of Crystalline}
+
+	%\label{Simulation box}
+\end{figure}
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{img/cell}
-	%\label{fig:cell}
-	\caption{units cell}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{img/pf_model_labeled}
-	\caption{Simulation box}
-
-	%\label{Simulation box}
-\end{figure}
-
 \subsection{Atomic potential}
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{img/process-ia}
-	\label{fig:process.ia}
-	\caption{Fracture process of specimen with void in $\alpha$ phase}
-\end{figure}
-
-\section{Results and Discussion}
-\subsection{The influence of void on strength of TiAl alloy}
 The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{img/allline}
+	\label{fig:allline}
+	\caption{Fracture process of specimen with void in $\alpha$ phase}
+\end{figure}
+
+\section{Results and Discussion}
+\subsection{The influence of void on strength of TiAl alloy}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{img/ialine}
+	\label{fig:ialine}
+	\caption{stress-strain curve}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{img/agline}
+	\label{fig:agline}
+	\caption{stress-strain curve}
+\end{figure}
+
+\subsection{Fracture Process}
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{img/crack_surf}
+	\label{fig:agline}
+	\caption{stress-strain curve}
+\end{figure}
+
 %\bibliographystyle{elsarticle-num.bst}
@@
 %Fig.\cite{fig:stress}.
+
 \end{document}

### 2018-08-08 code/LinePlt.py

@@ -2,6 +2,8 @@
 import os
 import matplotlib.pyplot as plt
 import pandas as pd
+#csfont = {'fontname':'Times New Roman'}
+plt.rcParams["font.family"] = "Times New Roman"
 
 # pre-set head name
 prop = ['step', 'strain', 'stress', 'energy']
@@ -19,7 +21,11 @@ p4 = plt.plot(ds4.step, ds4.stress, label='ia')
 
 plt.title('stress-strain curve')
 plt.xlabel('Step')
+plt.xlim(xmax=3e5)
 plt.ylabel('Stress (GPa)')
-plt.legend()
+plt.legend(frameon=False)
+plt.savefig('/home/alex/violet/draft/img/allline.pdf')
 plt.show()
-
+#/home/alex/violet/all.line.pdf
+#/home/alex/violet/code/pict/area.png
+#/home/alex/violet/draft/img/ag.png

### 2018-08-08 code/agline.py

@@ -1,0 +1,30 @@
+# 读取输出文件，绘制应力应变曲线
+import os
+import matplotlib.pyplot as plt
+import pandas as pd
+#import matplotlib.pyplot as pltplt.rc('font',family='Times New Roman') 
+#import matplotlib as pltplt.get_cachedir() 
+csfont = {'fontname':'Times New Roman'}
+
+# pre-set head name
+prop = ['step', 'strain', 'stress', 'energy']
+# import data from .csv file:
+ds1 = pd.read_csv('~/violet/code/data/stress_strain/ag.csv', sep=' ', skiprows=1, names=prop)
+
+# plot lines
+p1 = plt.plot(ds1.step, ds1.stress, label='ag')
+
+# config title and label
+
+plt.title('stress-strain curve')
+plt.xlabel('Step')
+plt.ylabel('Stress (GPa)')
+plt.xlim(1e5,2e5)
+
+#plt.lim(-6,6)
+#plt.legend()
+plt.savefig('/home/alex/violet/draft/img/agline.pdf')
+#plt.show()
+#/home/alex/violet/all.line.pdf
+#/home/alex/violet/code/pict/area.png
+#/home/alex/violet/draft/img/ag.png

### 2018-08-08 code/cracksurf.py

@@ -1,0 +1,24 @@
+
+import numpy as np
+
+import matplotlib.pyplot as plt
+#import matplotlib.pyplot as plt.rc('font',family='Times New Roman')
+#/home/alex/violet/code/data/crack_surf
+ag = np.loadtxt('/home/alex/violet/code/data/crack_surf/ag_10.txt')
+ia = np.loadtxt('/home/alex/violet/code/data/crack_surf/ia_10.txt')
+ig = np.loadtxt('/home/alex/violet/code/data/crack_surf/ig_10.txt')
+pf = np.loadtxt('/home/alex/violet/code/data/crack_surf/pf_10.txt')
+imglist = [ag, ia, ig, pf]
+for img in imglist:
+    pxx = range(len(img))
+    plt.plot(pxx, img)
+plt.title('Growth of Crack')
+plt.xlabel('strain')
+plt.ylabel('area of crack surface')
+plt.legend(["ag", "ia", "ig", "pf"],frameon=False)
+plt.savefig('/home/alex/violet/draft/img/crack_surf.pdf')
+
+plt.show()
+
+
+

### 2018-08-08 code/ialine.py

@@ -1,0 +1,28 @@
+# 读取输出文件，绘制应力应变曲线
+import os
+import matplotlib.pyplot as plt
+import pandas as pd
+csfont = {'fontname':'Times New Roman'}
+
+# pre-set head name
+prop = ['step', 'strain', 'stress', 'energy']
+# import data from .csv file:
+ds1 = pd.read_csv('~/violet/code/data/stress_strain/ia.csv', sep=' ', skiprows=1, names=prop)
+
+# plot lines
+p1 = plt.plot(ds1.step, ds1.stress, label='ia')
+
+# config title and label
+
+plt.title('stress-strain curve')
+plt.xlabel('Step')
+plt.ylabel('Stress (GPa)')
+plt.xlim(1e5,2e5)
+
+#plt.lim(-6,6)
+#plt.legend()
+plt.savefig('/home/alex/violet/draft/img/ialine.pdf')
+#plt.show()
+#/home/alex/violet/all.line.pdf
+#/home/alex/violet/code/pict/area.png
+#/home/alex/violet/draft/img/ag.png

### 2018-08-08 code/maplot.py

@@ -1,0 +1,28 @@
+import os
+import matplotlib.pyplot as plt
+import pandas as pd
+
+def mplt(pos):
+    plt.title('stress-strain curve')
+    plt.xlabel('Step')
+    plt.ylabel('Stress (GPa)')
+    plt.xlim(xmax=2.5e5)
+    plt.plot(pos.step, pos.stress, label='%s' %pos)
+    plt.savefig('/home/alex/violet/draft/img/%sline.pdf' %pos)
+    #plt.cla()
+    #plt.show()
+
+# pre-set head name
+prop = ['step', 'strain', 'stress', 'energy']
+# import data from .csv file:
+d_aa = pd.read_csv('~/violet/code/data/stress_strain/aa.csv', sep=' ', skiprows=1, names=prop)
+d_ag = pd.read_csv('~/violet/code/data/stress_strain/ag.csv', sep=' ', skiprows=1, names=prop)
+d_pf = pd.read_csv('~/violet/code/data/stress_strain/pf.csv', sep=' ', skiprows=1, names=prop)
+d_ia = pd.read_csv('~/violet/code/data/stress_strain/ia.csv', sep=' ', skiprows=1, names=prop)
+
+pos = [d_aa, d_ag, d_pf, d_ia]
+
+
+map(mplt(pos),pos)
+    #plt.savefig('/home/alex/HDD/str-pict/frame%s.png' % frame)
+    

### 2018-08-08 code/agline.py
add path

@@ -1,15 +1,19 @@
 # 读取输出文件，绘制应力应变曲线
 import os
+import os.path
 import matplotlib.pyplot as plt
 import pandas as pd
-#import matplotlib.pyplot as pltplt.rc('font',family='Times New Roman') 
-#import matplotlib as pltplt.get_cachedir() 
-csfont = {'fontname':'Times New Roman'}
+
+WDIR = os.getcwd()
+loadpath = os.path.join(WDIR,'code','data','stress_strain')
+writepath = os.path.join(WDIR,'draft','img')
+
+
 
 # pre-set head name
 prop = ['step', 'strain', 'stress', 'energy']
 # import data from .csv file:
-ds1 = pd.read_csv('~/violet/code/data/stress_strain/ag.csv', sep=' ', skiprows=1, names=prop)
+ds1 = pd.read_csv(os.path.join(loadpath,'ag.csv'), sep=' ', skiprows=1, names=prop)
 
 # plot lines
 p1 = plt.plot(ds1.step, ds1.stress, label='ag')
@@ -21,10 +25,6 @@ plt.xlabel('Step')
 plt.ylabel('Stress (GPa)')
 plt.xlim(1e5,2e5)
 
-#plt.lim(-6,6)
-#plt.legend()
-plt.savefig('/home/alex/violet/draft/img/agline.pdf')
-#plt.show()
-#/home/alex/violet/all.line.pdf
-#/home/alex/violet/code/pict/area.png
-#/home/alex/violet/draft/img/ag.png
+
+plt.savefig(os.path.join(writepath,'agline.pdf'))
+plt.show()

### 2018-08-08 code/allline.py

@@ -1,17 +1,20 @@
 # 读取输出文件，绘制应力应变曲线
 import os
+import os.path
 import matplotlib.pyplot as plt
 import pandas as pd
 #csfont = {'fontname':'Times New Roman'}
-plt.rcParams["font.family"] = "Times New Roman"
-
+#plt.rcParams["font.family"] = "Times New Roman"
+WDIR = os.getcwd()
+loadpath = os.path.join(WDIR,'code','data','stress_strain')
+writepath = os.path.join(WDIR,'draft','img')
 # pre-set head name
 prop = ['step', 'strain', 'stress', 'energy']
 # import data from .csv file:
-ds1 = pd.read_csv('~/violet/code/data/stress_strain/aa.csv', sep=' ', skiprows=1, names=prop)
-ds2 = pd.read_csv('~/violet/code/data/stress_strain/ag.csv', sep=' ', skiprows=1, names=prop)
-ds3 = pd.read_csv('~/violet/code/data/stress_strain/pf.csv', sep=' ', skiprows=1, names=prop)
-ds4 = pd.read_csv('~/violet/code/data/stress_strain/ia.csv', sep=' ', skiprows=1, names=prop)
+ds1 = pd.read_csv(os.path.join(loadpath,'aa.csv'), sep=' ', skiprows=1, names=prop)
+ds2 = pd.read_csv(os.path.join(loadpath,'ag.csv'), sep=' ', skiprows=1, names=prop)
+ds3 = pd.read_csv(os.path.join(loadpath,'pf.csv'), sep=' ', skiprows=1, names=prop)
+ds4 = pd.read_csv(os.path.join(loadpath,'ia.csv'), sep=' ', skiprows=1, names=prop)
 # plot lines
 p1 = plt.plot(ds1.step, ds1.stress, label='aa')
 p2 = plt.plot(ds2.step, ds2.stress, label='ag')
@@ -24,8 +27,8 @@ plt.xlabel('Step')
 plt.xlim(xmax=3e5)
 plt.ylabel('Stress (GPa)')
 plt.legend(frameon=False)
-plt.savefig('/home/alex/violet/draft/img/allline.pdf')
-plt.show()
+plt.savefig(os.path.join(writepath,'allline.pdf'))
+#plt.show()
 #/home/alex/violet/all.line.pdf
 #/home/alex/violet/code/pict/area.png
 #/home/alex/violet/draft/img/ag.png

### 2018-08-08 code/cracksurf.py

@@ -1,24 +1,0 @@
-
-import numpy as np
-
-import matplotlib.pyplot as plt
-#import matplotlib.pyplot as plt.rc('font',family='Times New Roman')
-#/home/alex/violet/code/data/crack_surf
-ag = np.loadtxt('/home/alex/violet/code/data/crack_surf/ag_10.txt')
-ia = np.loadtxt('/home/alex/violet/code/data/crack_surf/ia_10.txt')
-ig = np.loadtxt('/home/alex/violet/code/data/crack_surf/ig_10.txt')
-pf = np.loadtxt('/home/alex/violet/code/data/crack_surf/pf_10.txt')
-imglist = [ag, ia, ig, pf]
-for img in imglist:
-    pxx = range(len(img))
-    plt.plot(pxx, img)
-plt.title('Growth of Crack')
-plt.xlabel('strain')
-plt.ylabel('area of crack surface')
-plt.legend(["ag", "ia", "ig", "pf"],frameon=False)
-plt.savefig('/home/alex/violet/draft/img/crack_surf.pdf')
-
-plt.show()
-
-
-

### 2018-08-08 code/ialine.py

@@ -2,12 +2,14 @@
 import os
 import matplotlib.pyplot as plt
 import pandas as pd
-csfont = {'fontname':'Times New Roman'}
-
+#csfont = {'fontname':'Times New Roman'}
+WDIR = os.getcwd()
+loadpath = os.path.join(WDIR,'code','data','stress_strain')
+writepath = os.path.join(WDIR,'draft','img')
 # pre-set head name
 prop = ['step', 'strain', 'stress', 'energy']
 # import data from .csv file:
-ds1 = pd.read_csv('~/violet/code/data/stress_strain/ia.csv', sep=' ', skiprows=1, names=prop)
+ds1 = pd.read_csv(os.path.join(loadpath,'ia.csv'), sep=' ', skiprows=1, names=prop)
 
 # plot lines
 p1 = plt.plot(ds1.step, ds1.stress, label='ia')
@@ -21,7 +23,7 @@ plt.xlim(1e5,2e5)
 
 #plt.lim(-6,6)
 #plt.legend()
-plt.savefig('/home/alex/violet/draft/img/ialine.pdf')
+plt.savefig(os.path.join(writepath,'ialine.pdf'))
 #plt.show()
 #/home/alex/violet/all.line.pdf
 #/home/alex/violet/code/pict/area.png

### 2018-08-08 code/surfidt.py

@@ -1,0 +1,28 @@
+
+import os
+import os.path
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+WDIR = os.getcwd()
+loadpath = os.path.join(WDIR,'code','data','surf')
+#plt.savefig(os.path.join(WDIR,'draft','img','surf.pdf'))
+#loadpath = os.path.join(WDIR,'code','data','surf')
+ag = np.loadtxt(os.path.join(loadpath,'surf_ag.txt'))
+ia = np.loadtxt(os.path.join(loadpath,'surf_ia.txt'))
+ig = np.loadtxt(os.path.join(loadpath,'surf_ig.txt'))
+pf = np.loadtxt(os.path.join(loadpath,'surf_pf.txt'))
+
+imglist = [ag, ia, ig, pf]
+for img in imglist:
+    pxx = range(len(img))
+    plt.plot(pxx, img)
+plt.title('Growth of Crack')
+plt.xlabel('strain')
+plt.ylabel('area of crack surface')
+plt.legend(["ag", "ia", "ig", "pf"],frameon=False)
+plt.savefig(os.path.join(WDIR,'draft','img','surf.pdf'))
+#plt.show()
+
+

### 2018-08-08 draft/draft.tex
fig label modified
add eam blank

@@
-\documentclass[final,5p,times,twocolumn]{elsarticle}
+\documentclass[final,5p,times,onecolumn]{elsarticle}
+%\documentclass[]{elsarticle}
 \usepackage[labelfont=bf,justification=raggedright]{caption}
@@
 \setlength{\mathindent}{3cm}
+%Function format
 \usepackage{lineno,hyperref}
@@
 
+\subsection{Model Creation of Crystalline}
+
 \begin{figure}
@@
 	\includegraphics[width=1\linewidth]{img/cell}
-	%\label{fig:cell}
-	\caption{units cell}
+	\caption{unit cell}
+	\label{fig:unit_cell}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{img/pf_model_labeled}
+	\includegraphics[width=1\linewidth]{img/pf_model_labeled}
 	\caption{Simulation box}
-
-\subsection{Model Creation of Crystalline}
-
-	%\label{Simulation box}
+	\label{fig:simulation_box}
 \end{figure}
@@
 	\end{tabular}
-	\label{Tab:model-parameter}
+	\label{tab:lattice_parameter}
 	\end{table}
@@
 We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation.
-
+\begin{equation} \label{eq:eam} 
+	E= \displaystyle\sum
+\end{equation}
 \subsection{Analysis method}
@@
 
+\subsection{Decrease of Strength}
+
 The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
@@
 Reorientation of slip is always required at the $\alpha_{2} / \gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree ref{}.
-2.
+
 The core of  a dislocation intersecting an interface often needs to be transformed.
@@
 These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
-3.Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
 
-\subsection{Decrease of Strength}
+Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
 
@@
 	\includegraphics[width=1\linewidth]{img/allline}
-	\label{fig:allline}
 	\caption{Fracture process of specimen with void in $\alpha$ phase}
+	\label{fig:all_line}
 \end{figure}
@@
 	\includegraphics[width=1\linewidth]{img/ialine}
-	\label{fig:ialine}
 	\caption{stress-strain curve}
+	\label{fig:ia_line}
 \end{figure}
@@
 	\includegraphics[width=1\linewidth]{img/agline}
-	\label{fig:agline}
+	\caption{stress-strain curve}
+	\label{fig:ag_line}
+\end{figure}
+
+\subsection{Fracture Process}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{img/crack_surf}
+	\label{fig:surf}
 	\caption{stress-strain curve}
@@
 
-\subsection{Fracture Process}
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{img/crack_surf}
-	\label{fig:agline}
-	\caption{stress-strain curve}
-\end{figure}
+\section{Conclusion}
+%\bibliographystyle{elsarticle-num.bst}
 
-%\bibliographystyle{elsarticle-num.bst}
 \bibliography{ref/VIOLET-ref}
-%Fig.\cite{fig:stress}.
 

### 2018-08-08 draft/draft.tex
str modified

@@
 We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation.
+
 \begin{equation} \label{eq:eam} 
@@
 \end{equation}
+
 \subsection{Analysis method}
@@
 
-\subsection{Decrease of Strength}
-
-The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
-Detailed observation of specimen with void inside the grain is shown in Figure \cite{}.
-1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
-This may significantly reduce the Schmid factor and thus impede slip transfer.
-At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
-Reorientation of slip is always required at the $\alpha_{2} / \gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree ref{}.
-
-The core of  a dislocation intersecting an interface often needs to be transformed.
-For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
-At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
-These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
-
-Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
-
 \begin{figure}
@@
 \section{Results and Discussion}
-\subsection{The influence of void on strength of TiAl alloy}
+%\subsection{The influence of void on strength of TiAl alloy}
+\subsection{Decrease of Strength}
+
+The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
+Detailed observation of specimen with void inside the grain is shown in Figure \cite{}.
+1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
+This may significantly reduce the Schmid factor and thus impede slip transfer.
+At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
+Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
+
+The core of  a dislocation intersecting an interface often needs to be transformed.
+For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
+At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
+These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
+
+Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
 

### 2018-08-08 draft/fmt.tex
simplify format

--- 2018-08-08 draft/draft.tex
@@
-\documentclass[final,5p,times,onecolumn]{elsarticle}
-%\documentclass[]{elsarticle}
-\usepackage[labelfont=bf,justification=raggedright]{caption}
-\captionsetup[figure]{name=Fig. ,labelsep=period,singlelinecheck=true,skip=5pt}
-\captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
-%\documentclass[final,5p,times,twocolumn]{elsarticle}
-\setlength{\mathindent}{3cm}
-%Function format
+\documentclass[preview,times]{elsarticle}
 \usepackage{lineno,hyperref}
 \modulolinenumbers[5]
+%\usepackage[labelfont=bf,justification=raggedright]{caption}
+%\captionsetup[figure]{name=Fig. ,labelsep=period,singlelinecheck=true,skip=5pt}
+%\captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
+\linenumbers
+
+%\documentclass[final,5p,times,twocolumn]{elsarticle}
+%\setlength{\mathindent}{3cm}
+%Function format
+%\usepackage{lineno,hyperref}
+%\modulolinenumbers[5]
 
@@
 \bibliographystyle{elsarticle-num.bst}
-\modulolinenumbers[5]
+%\modulolinenumbers[5]
 \journal{Materials and Design}
@@
 \end{frontmatter}
-\linenumbers
+%\linenumbers
 
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \centering
@@
 
-\subsection{Atomic potential}
+\subsection{Atomic Potential}
 The interaction of particle in the material is determined by interatomic potential.
-Many reported examples of crack propagation in metal materials were performed with embedded atomic method, due to is better accuracy in metal lattice compare with F-S and L/J \cite{}.
-The embedded atom method (MEAM) potential developed by Zope and Mishin by \cite{} was used in the study, which is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{}.
+Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to is better accuracy in metal lattice compare with F-S and L/J \cite{}.
+The embedded atom method (MEAM) potential developed by Zope and Mishin by \cite{} was used in the study.
+The simulation is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{}.
 We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation.

### 2018-08-09 draft/draft.tex
move to desktop

@@
-\documentclass[final,5p,times,onecolumn]{elsarticle}
+\documentclass[review]{elsarticle}
 %\documentclass[]{elsarticle}
@@
 %\documentclass[final,5p,times,twocolumn]{elsarticle}
-\setlength{\mathindent}{3cm}
+%\setlength{\mathindent}{3cm}
 %Function format
@@
 However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{intro-structure}.
+
+Two phase titanium aluminide alloys exhibit a much better mechanical performance than their monolithic
+constituents $\gamma$(TiAl) and $\alpha_2$ (Ti3Al), provided that the phase distribution and grain size are suitably controlled.
+Two-phase titantium aliuminde alloys with proper phase distribution and grain size exhibit better mechanicalperformance compared with monolithicconstituents gamma and alpha[].
+Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine andcombustion generator.
+[R].Defects such as dislocation, void and segregation plays an significant role in the process of fracture[R].In order to understanding the mechanism of brittle fracture, multiscale methods from micro to marco scale have been applied to investigate the behavior of fracture.
+It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
+A previous study on void growth in gamma-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength [R].
+Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nano-
+scale[R].
+The fracture mechanisms in the duplex micro-structure are plasticity-induced grain boundary de- cohesion
+and cleavage, while those in the lamellar microstructure are interface delamination and crack- ing across the
+lamellae[R].
 

### 2018-08-09 draft/draft.tex
add fig:1st div

@@
 Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
+The results show that voids located at the $\alpha$/$\gamma$ phase boundary have significant detract to strength of Ti-Al polycrystalline.
 \end{abstract}
@@
 \section{Introduction}
-TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{Xiong2015}.
-However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{intro-structure}.
+TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{}.
+However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{}.
 
@@
 
-\subsection{Fracture Process}
+%\subsection{Fracture Process with Integranular Void }
+
+%\subsection{Fracture Process with Intergranular Void }
+
+\subsection{Evolution of spherical boid in the simulation with intragranular spherical voids}
+A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{fig:}.
+A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{fig:}.
+If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to
 
@@
 	\includegraphics[width=1\linewidth]{img/crack_surf}
+	\label{fig:surf}
+	\caption{stress-strain curve}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{img/1stdiv}
 	\label{fig:surf}

### 2018-08-09 code/surf_div.py

@@ -1,0 +1,35 @@
+
+import os
+import os.path
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+WDIR = os.getcwd()
+loadpath = os.path.join(WDIR,'code','data','surf')
+writepath = os.path.join(WDIR,'draft','img')
+
+#plt.savefig(os.path.join(WDIR,'draft','img','surf.pdf'))
+#loadpath = os.path.join(WDIR,'code','data','surf')
+ag =np.loadtxt(os.path.join(loadpath,'surf_ag.txt'))
+ia =np.loadtxt(os.path.join(loadpath,'surf_ia.txt'))
+ig =np.loadtxt(os.path.join(loadpath,'surf_ig.txt'))
+pf =np.loadtxt(os.path.join(loadpath,'surf_pf.txt'))
+#d_pf = np.gradient(pf)
+imglist = ([ag, ia,  ig, pf])
+dv1st = list(map(np.gradient,imglist))
+for img in dv1st:
+    pxx = range(len(img))
+    plt.plot(pxx, img)
+plt.title('1st Deviation of Area of Surface of Crack')
+plt.xlabel('strain')
+plt.ylabel('area of crack surface')
+plt.xlim(xmax=70)
+plt.legend(["ag", "ia", "ig", "pf"],frameon=False)
+plt.savefig(os.path.join(writepath,'1stdiv.pdf'))
+
+plt.show()
+plt.cla
+plt.clf()
+
+

### 2018-09-04 draft/draft.tex
add picture

@@
-\documentclass[review]{elsarticle}
+\documentclass[times]{elsarticle}
 %\documentclass[]{elsarticle}
@@
 
-	%% Numbered without titles
+	%% Numbered without titles2
 	%\bibliographystyle{model1a-num-names}
@@
 \end{abstract}
+
 \begin{keyword}
@@
 \end{keyword}
+
 \end{frontmatter}
@@
 
+\subsection{Atomic Potential}
+The interaction of particle in the material is determined by interatomic potential.
+Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to is better accuracy in metal lattice compare with F-S and L/J \cite{}.
+The embedded atom method (MEAM) potential developed by Zope and Mishin by \cite{} was used in the study.
+The simulation is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{}.
+We performed constant-pressure and constant-temperature (NPT) molecular dynamics simulation.
+
+\begin{equation} \label{eq:eam} 
+	E= \displaystyle\sum
+\end{equation}
+
 \subsection{Model Creation of Crystalline}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{img/cell}
-	\caption{unit cell}
-	\label{fig:unit_cell}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{img/pf_model_labeled}
-	\caption{Simulation box}
-	\label{fig:simulation_box}
-\end{figure}
+$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}.
+The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \cite{}.
+Periodic boundary conditions (PBC)are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
+The initial dimension of simulation cell is  $L_x = $ nm, $L_y = $ nm, $L_z = $ nm, and each model contains about 4.6 million atoms.
+The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{}, and resulting in the arbitrary shape and orientation of the grains.
+Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model.
+The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig.
+\cite{}.
+The intergranular spherical void was at the center of the simulation cell, as shown in Fig.
+\cite{}.
 
@@
 
-$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cell are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}.
-The simulation cells of two phase poly crystal with an initially spherical void at different position are shown in figure \cite{}.
-Periodic boundary conditions are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
-Each cuboidal model, containing about 4.6 million atoms,The initial dimension of simulation cell is  $L_x = nm$, $L_y =  nm$, $L_z =  nm$.
-The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{}, and resulting in the arbitrary shape and orientation of the grains.
-Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model.
-The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig.
-\cite{}.
-The intergranular spherical void was at the center of the simulation cell, as shown in Fig.
-\cite{}.
-
-\subsection{Atomic Potential}
-The interaction of particle in the material is determined by interatomic potential.
-Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to is better accuracy in metal lattice compare with F-S and L/J \cite{}.
-The embedded atom method (MEAM) potential developed by Zope and Mishin by \cite{} was used in the study.
-The simulation is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{}.
-We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation.
-
-\begin{equation} \label{eq:eam} 
-	E= \displaystyle\sum
-\end{equation}
-
 \subsection{Analysis method}
 \paragraph{CSP}
-In view of the fact that dislocations cannot be easily spotted in a three-dimensional crystal, a centrosymmetry parameter \cite{} is used to identify the nucleation and propagation of dislocations.
-The said centrosymmetry parameter is defined as follow:
-
+The centrosymmetry parameter is defined as follow:
 \begin{equation} \label{eq:csp} 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{img/allline}
-	\caption{Fracture process of specimen with void in $\alpha$ phase}
-	\label{fig:all_line}
-\end{figure}
-
-\section{Results and Discussion}
-%\subsection{The influence of void on strength of TiAl alloy}
-\subsection{Decrease of Strength}
-
+\subsection{Fracture Process}
+\paragraph{initiation of crack}
+\paragraph{fracture process}
 The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{img/ialine}
-	\caption{stress-strain curve}
-	\label{fig:ia_line}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{img/agline}
-	\caption{stress-strain curve}
-	\label{fig:ag_line}
-\end{figure}
-
 %\subsection{Fracture Process with Integranular Void }
@@
 	\centering
-	\includegraphics[width=1\linewidth]{img/crack_surf}
-	\label{fig:surf}
-	\caption{stress-strain curve}
+	\includegraphics[width=0.7\linewidth]{img/cell}
+	\caption{unit cell}
+	\label{fig:unit_cell}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{img/1stdiv}
+	\includegraphics[width=0.7\linewidth]{img/pf_model_labeled}
+	\caption{Simulation box}
+	\label{fig:simulation_box}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/allline}
+	\caption{Fracture process of specimen with void in $\alpha$ phase}
+	\label{fig:all_line}
+\end{figure}
+
+\section{Results and Discussion}
+%\subsection{The influence of void on strength of TiAl alloy}
+\subsection{Effect of Void Size}
+\paragraph{size}
+\paragraph{position}
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{"img/fracture process"}
+	\caption{}
+	\label{fig:fracture-process}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/effect_of_vol}
+	\caption{}
+	\label{fig:effectofvol}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/ialine}
+	\caption{stress-strain curve}
+	\label{fig:ia_line}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/agline}
+	\caption{stress-strain curve}
+	\label{fig:ag_line}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/1stdiv}
 	\label{fig:surf}

### 2018-09-04 code/data/size/size_summary.py

@@ -14,7 +14,7 @@ violet
 '''
 import os
 import matplotlib.pyplot as plt
-plt.rcParams["font.family"] = 'Times New Roman'
+# plt.rcParams["font.family"] = 'Times New Roman'
 
 WDIR = os.path.dirname(__file__)
 writepath = os.path.join(WDIR,'..','..','..','draft','img')

### 2018-09-04 code/surf_div.py

@@ -18,20 +18,26 @@ ia =np.loadtxt(os.path.join(loadpath,'surf_ia.txt'))
 ig =np.loadtxt(os.path.join(loadpath,'surf_ig.txt'))
 pf =np.loadtxt(os.path.join(loadpath,'surf_pf.txt'))
 #d_pf = np.gradient(pf)
-imglist = ([ag, ia,  ig, pf])
+imglist =[ag, ig, pf]
 dv1st = list(map(np.gradient,imglist))
+#colorlist = ['g','b','r']
+# markerlist = ['s','^','o']
+max = list(map(np.max,dv1st))
+min = np.min(np.abs(ag))
 for img in dv1st:
-    pxx = range(len(img))
-    plt.plot(pxx, img)
-plt.title('1st Deviation of Area of Surface of Crack')
-plt.xlabel('strain')
-plt.ylabel('area of crack surface')
-plt.xlim(xmax=50)
-plt.legend(["ag", "ia", "ig", "pf"],frameon=False)
+    pxx = np.linspace(0,np.dot(0.005,len(img)),len(img))
+    plt.plot(pxx, img/np.max(max))
+# plt.title('1st Deviation of Area of Surface of Crack')
+plt.xlabel('Strain')
+plt.ylabel('Relative Crack Propagation Indicator')
+plt.xlim(xmax=0.3)
+plt.legend(["ag","ig", "pf"],frameon=False)
+# plt.legend()
 plt.savefig(os.path.join(writepath,'1stdiv.pdf'))
 
 plt.show()
 plt.cla
 plt.clf()
+
 
 

### 2018-09-09 draft/draft.tex
no

@@
 Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine andcombustion generator.
-[R].Defects such as dislocation, void and segregation plays an significant role in the process of fracture[R].In order to understanding the mechanism of brittle fracture, multiscale methods from micro to marco scale have been applied to investigate the behavior of fracture.
+[R].Defects such as dislocation, void and segregation plays an significant role in the process of fracture[R].In order to understanding the mechanism of brittle fracture, multi-scale methods from micro to marco scale have been applied to investigate the behavior of fracture.
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
@@
 
-Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamellae, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
+Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamella, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
 
@@
 
-\subsection{Evolution of spherical boid in the simulation with intragranular spherical voids}
+\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
 A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{fig:}.

### 2018-09-11 draft/draft.tex
no

@@
 
+\section{Results and Discussion}
+
 \subsection{Fracture Process}
@@
 
-\section{Results and Discussion}
 %\subsection{The influence of void on strength of TiAl alloy}
+
+\begin{figure}
+	\centering
+ 	\includegraphics[width=0.7\linewidth]{img/effect_of_vol}
+	\caption{}
+	\label{fig:voleff}
+\end{figure}
+
 \subsection{Effect of Void Size}
 \paragraph{size}
-\paragraph{position}
+Voids with different size: 2A, 5A, 10A, 15A were placed into the model respectively.
+It has been observed that  voids detracts the strengths of the material.
+The max stress stress of the simulation cell decreases as the volume of voids are lareger.
+From Fig \ref{fig:voleff}, there is a critical value of void radius about 15A, the void greater than 15A cause serious detraction of strength of material.
+Engineering stress is calculated
+$$ \sigma = S/A$$
+The rate of decrease of loading area are smaller comparing with the detraction of strength, so it can be assumed that the yield yield behaviour and strength is much more related with local behaviour of grain boundaries and void.
+
+Grain and phase boundaris are obstancles to deformation process, thus the stability of boundaries have great impact on the strength of materials.
+Interactive between grainboundary and void determins the fracture mode of the TiAl alloy.
+
+According to Schmid's law:
+$$\tau = \sigma*m$$
+where m is the Schmid factor :
+$$ m = cos(\phi)cos(\lambda)$$
+
+\paragraph{position}critical void 
+The location of void affects strength of material. Comparing with the model with integranular void, the model with intergranular voids is weaker. atomic stress is calculated
+
 \begin{figure}
@@
 	\label{fig:fracture-process}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{img/effect_of_vol}
-	\caption{}
-	\label{fig:effectofvol}
 \end{figure}

### 2018-09-12 draft/draft.tex
add a subsection

@@
 
+\subsection{Deformation Mechanisms in Two-Phase Alloys}
+Deformation phenomena in TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
+The literature data covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
+Much of the work has been performed on single phase $\gamma$ alloys and PST crystals.
+However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in two - phase alloys.
+Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
+
 \subsection{Fracture Process}

### 2018-09-12 draft/draft.tex
add intro

@@
 \documentclass[times]{elsarticle}
+\usepackage[margin=2.5cm]{geometry}
 %\documentclass[]{elsarticle}
@@
 
-Two phase titanium aluminide alloys exhibit a much better mechanical performance than their monolithic
-constituents $\gamma$(TiAl) and $\alpha_2$ (Ti3Al), provided that the phase distribution and grain size are suitably controlled.
+The failure modes of materials have significant influence on the design of material properties in materials science.
+Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions [1].These defects are known to play a fundamental role in the deformation of the material.
+Nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important.
+Therefore, it is necessary to study the deformation response of porous materials with the consideration of microstructure evolution.
+
+Two phase titanium aluminide alloys exhibit a much better mechanical performance than their monolithic constituents $\gamma$(TiAl) and $\alpha_2$ (Ti3Al), provided that the phase distribution and grain size are suitably controlled.
 Two-phase titantium aliuminde alloys with proper phase distribution and grain size exhibit better mechanicalperformance compared with monolithicconstituents gamma and alpha[].

### 2018-09-13 draft/draft.tex
edited

@@
 \documentclass[times]{elsarticle}
-\usepackage[margin=2.5cm]{geometry}
+\usepackage[margin=2cm]{geometry}
 %\documentclass[]{elsarticle}
@@
 \begin{abstract}
- The fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects.
+Fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects.
 Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
@@
 \section{Introduction}
-TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{}.
-However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{}.
+\paragraph{Material}
+TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{vu2013}.However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{}.
+
+\paragraph{Void}
+Two phase titanium aluminide alloys exhibit a much better mechanical performance than their monolithic constituents $\gamma$(TiAl) and $\alpha_2$ (Ti3Al), provided that the phase distribution and grain size are suitably controlled.
+Two-phase titantium aliuminde alloys with proper phase distribution and grain size exhibit better mechanicalperformance compared with monolithicconstituents gamma and alpha[].
+Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine andcombustion generator.
 
@@
 Two-phase titantium aliuminde alloys with proper phase distribution and grain size exhibit better mechanicalperformance compared with monolithicconstituents gamma and alpha[].
-Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine andcombustion generator.
-[R].Defects such as dislocation, void and segregation plays an significant role in the process of fracture[R].In order to understanding the mechanism of brittle fracture, multi-scale methods from micro to marco scale have been applied to investigate the behavior of fracture.
+Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine andcombustion generator[].Defects such as dislocation, void and segregation plays an significant role in the process of fracture[].In order to understanding the mechanism of brittle fracture, multi-scale methods from micro to marco scale have been applied to investigate the behavior of fracture.
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
-A previous study on void growth in gamma-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength [R].
+A previous study on void growth in gamma-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength [].
 Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nano-
-scale[R].
+scale[].
 The fracture mechanisms in the duplex micro-structure are plasticity-induced grain boundary de- cohesion
 and cleavage, while those in the lamellar microstructure are interface delamination and crack- ing across the
-lamellae[R].
+lamellae[].
 

### 2018-09-18 draft/draft.tex
add pict
add more

--- 2018-09-12 draft/draft.tex
@@
 \title{Effect of Nanovoid on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy}
-%\tnotetext[mytitlenote]{*** \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
+%\tnotetext[mytitlenote]{*** \href{http: //www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
 %% Group authors per affiliation:
@@
 \section{Introduction}
-TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{}.
-However, single phase $\gamma-\rm TiAl$ generally brittle at room temperatures and this limits their use in many other fields.Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{}.
+\paragraph{Material}
+TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{vu2013}.
+Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{}.
+Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator.
 
 The failure modes of materials have significant influence on the design of material properties in materials science.
-Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions [1].These defects are known to play a fundamental role in the deformation of the material.
+Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{}.
+These defects are known to play a fundamental role in the deformation of the material.
 Nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important.
@@
 
-Two phase titanium aluminide alloys exhibit a much better mechanical performance than their monolithic constituents $\gamma$(TiAl) and $\alpha_2$ (Ti3Al), provided that the phase distribution and grain size are suitably controlled.
-Two-phase titantium aliuminde alloys with proper phase distribution and grain size exhibit better mechanicalperformance compared with monolithicconstituents gamma and alpha[].
-Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine andcombustion generator.
-[R].Defects such as dislocation, void and segregation plays an significant role in the process of fracture[R].In order to understanding the mechanism of brittle fracture, multi-scale methods from micro to marco scale have been applied to investigate the behavior of fracture.
-It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
-A previous study on void growth in gamma-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength [R].
-Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nano-
-scale[R].
-The fracture mechanisms in the duplex micro-structure are plasticity-induced grain boundary de- cohesion
-and cleavage, while those in the lamellar microstructure are interface delamination and crack- ing across the
-lamellae[R].
+Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine andcombustion generator[].Defects such as grainboundary, void and segregation plays an significant role in the process of fracture[].In order to understanding the mechanism of brittle fracture, multi-scale methods from micro to marco scale have been applied to investigate the behavior of fracture.
+It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.A previous study on void growth in gamma-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength \cite{}.Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nanoscale \cite{}.
+The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar microstructure are interface delamination and cracking across the lamellae \cite{}.
 
@@
 \begin{equation} \label{eq:eam} 
-	E= \displaystyle\sum
+	E_{total}= \displaystyle\sum F_i(\rho_{h,i})+\frac{1}{2}\sum_i\sum_{j(\neq1)}\phi_{ij}(R_{ij})
+\end{equation}
+
+where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system,$F_i(\rho)$ is the energy for embedding atom i into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ is the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$.
+It can be noted that $F_i$ only depends on the element of atom $i$ and $\phi_{ij}$ only depends on the elements of atoms $i$ and $j$.
+The electron density is, as stated above, approximated by the superposition of atomic densities, namely
+
+\begin{equation} \label{eq:eam} 
+\rho_{h,i}=\sum_{j(\neq1)} \rho_i(R_{ij})
 \end{equation}
@@
 \end{table}
+
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[width=0.7\linewidth]{img/cell}
+% 	\caption{unit cell}
+% 	\label{fig:unit_cell}
+% \end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{img/models}
+	\caption{models}
+	\label{fig:simulation_box}
+\end{figure}
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{img/cell}
-	\caption{unit cell}
-	\label{fig:unit_cell}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{img/pf_model_labeled}
-	\caption{Simulation box}
-	\label{fig:simulation_box}
-\end{figure}
-
-\begin{figure}
+\begin{figure}[h]
 	\centering
@@
 	\caption{Fracture process of specimen with void in $\alpha$ phase}
-	\label{fig:all_line}
-\end{figure}
-
-%\subsection{The influence of void on strength of TiAl alloy}
-
-\begin{figure}
-	\centering
- 	\includegraphics[width=0.7\linewidth]{img/effect_of_vol}
-	\caption{}
-	\label{fig:voleff}
+	\label{ }
 \end{figure}
@@
 \paragraph{size}
+
+\begin{figure}[h]
+	\centering
+ 	\includegraphics[width=0.7\linewidth]{img/effect_of_vol}
+	\caption{Effect of Void}
+	\label{fig:voleff}
+\end{figure}
+
 Voids with different size: 2A, 5A, 10A, 15A were placed into the model respectively.
@@
 $$ m = cos(\phi)cos(\lambda)$$
+%\subsection{The influence of void on strength of TiAl alloy}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/frame2}
+	\caption{stress-$\sigma$=0}
+	\label{ }
+\end{figure}
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/frame150}
+	\caption{stress-$\sigma$=0.15}
+	\label{ }
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/frame160}
+	\caption{stress-$\sigma$=0.16}
+	\label{ }
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/frame170}
+	\caption{stress-$\sigma$=0.17}
+	\label{ }
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{img/frame180}
+	\caption{stress-$\sigma$=0.18}
+	\label{ }
+\end{figure}
 \paragraph{position}critical void 
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
-	\includegraphics[width=1\linewidth]{"img/fracture process"}
-	\caption{}
+	\includegraphics[width=1\linewidth]{"img/fracture3"}
+	\caption{Fracture Process}
 	\label{fig:fracture-process}
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{img/ialine}
-	\caption{stress-strain curve}
-	\label{fig:ia_line}
-\end{figure}
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[width=0.7\linewidth]{img/ialine}
+% 	\caption{stress-strain curve}
+% 	\label{fig:ia_line}
+% \end{figure}
+% 
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[width=0.7\linewidth]{img/agline}
+% 	\caption{stress-strain curve}
+% 	\label{fig:ag_line}
+% \end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{img/agline}
-	\caption{stress-strain curve}
-	\label{fig:ag_line}
-\end{figure}
-
-\begin{figure}
+\begin{figure}[h]
 	\centering

### 2018-09-18 draft/draft.tex
no

@@
 \modulolinenumbers[5]
-
-	\journal{Computational Materaials Science}
-
-	%%%%%%%%%%%%%%%%%%%%%%%
-	%% Elsevier bibliography styles
-	%%%%%%%%%%%%%%%%%%%%%%%
-	%% To change the style, put a % in front of the second line of the current style and
-	%% remove the % from the second line of the style you would like to use.
-	%%%%%%%%%%%%%%%%%%%%%%%
-
-	%% Numbered
-	%\bibliographystyle{model1-num-names}
-
-	%% Numbered without titles2
-	%\bibliographystyle{model1a-num-names}
-
-	%% Harvard
+\journal{Materials and Design}
 \bibliographystyle{elsarticle-num.bst}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
+
 \begin{frontmatter}
 \title{Effect of Nanovoid on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy}
-%\tnotetext[mytitlenote]{*** \href{http: //www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
-%% Group authors per affiliation:
-%\author{Maomao Wang\fnref{myfootnote}}
+\address[mymainaddress]{School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China}
 
-\address[mymainaddress]{School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China}
 \begin{abstract}
@@
 \subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
-A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{fig:}.
-A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{fig:}.
+A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}.
+A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}.
 If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to

### 2018-09-26 draft/draft.tex
add par

@@
-\documentclass[times]{elsarticle}
+\documentclass[times,12pt]{elsarticle}
 \usepackage[margin=2.5cm]{geometry}
@@
 \usepackage{lineno,hyperref}
-\modulolinenumbers[5]
+%\modulolinenumbers[5]
 \journal{Materials and Design}
 \bibliographystyle{elsarticle-num.bst}
-\modulolinenumbers[5]
-\journal{Materials and Design}
+\journal{}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{frontmatter}
-\linenumbers
 
@@
 	\includegraphics[width=1\linewidth]{img/models}
-	\caption{models}
-	\label{fig:simulation_box}
+	\caption{Overview of model creation}
+	\label{fig:model-creation}
 \end{figure}
@@
 \section{Results and Discussion}
+\subsection{The effect of void on the strength of material}
+The strength of materails with void in different size and at different position is shown in \ref{}.
+The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
+Detailed observation of specimen with void inside the grain is shown in Figure \cite{}.It's an expectable that the existence of voids detracts the strength of the materials, however it has been observed in the simulation that there is a critical value about 15A for voids at different position.
+The voids larger than 15 A have dramatic detraction to the strength of the material.
+It can be also found that the location of void affects strength of material.
+Comparing with the model with integranularvoid, the model with innergranular voids is weaker.
+The strength calculated with continous theory is as follow:
+
+\begin{equation} \label{eq:section} 
+\sigma^* = \sigma_0 \cdot \frac{A^*}{A_0}
+\end{equation}
+where $\sigma_0$ is the strength of the model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = a\times b = 36000 A^2$, $A^* $ is section area in consider of the subsection that results from the voids.
+Comparing with the strength determined by molecular dynamics simulation and the resuts calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behaciour of the materials, thus revolution of defects should be examined carefully.
+
+\subsection{Effect of Void Size}
+\paragraph{size}
+
+\begin{figure}[h]
+	\centering
+	\begin{minipage}{0.495\textwidth}
+		\includegraphics[width=1\linewidth]{img/allline}
+		\centering
+		\caption{Stress-Strain}
+		\label{fig:stress&strain}
+	\end{minipage}
+	%\hspace{0.1cm} 
+	\hfill
+	\begin{minipage}{0.495\textwidth}		
+		\includegraphics[width=1\linewidth]{img/effect_of_vol}
+		\centering
+		\caption{Strength of model with different voids}
+		\label{fig:strength}
+
+	\end{minipage}
+
+\end{figure}
 
 \subsection{Deformation Mechanisms in Two-Phase Alloys}
+
 Deformation phenomena in TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
@@
 Much of the work has been performed on single phase $\gamma$ alloys and PST crystals.
-However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in two - phase alloys.
+However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in twophase alloys.
 Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
+
+Basic deformationg mechanism of $\alpha$ phase
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.7\linewidth]{img/allline}
-	\caption{Fracture process of specimen with void in $\alpha$ phase}
-	\label{ }
-\end{figure}
-
-\subsection{Effect of Void Size}
-\paragraph{size}
-
-\begin{figure}[h]
-	\centering
- 	\includegraphics[width=0.7\linewidth]{img/effect_of_vol}
-	\caption{Effect of Void}
-	\label{fig:voleff}
-\end{figure}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=0.7\linewidth]{img/allline}
+%	\caption{Fracture process of specimen with void in $\alpha$ phase}
+%	\label{ }
+%\end{figure}
+%
 

### 2018-09-26 code/allline.py

@@ -20,7 +20,8 @@ from os import listdir
 import matplotlib.pyplot as plt
 import pandas as pd
 plt.rcParams["font.family"] = 'Times New Roman'
-
+import matplotlib.pyplot as plt
+plt.rcParams.update({'font.size': 12})
 #csfont = {'fontname':'Times New Roman'}
 #plt.rcParams["font.family"] = "Times New Roman"
 WDIR = os.path.dirname(__file__)
@@ -29,20 +30,26 @@ writepath = os.path.join(WDIR,'..','draft','img')
 # pre-set head name
 prop = ['step', 'strain', 'stress', 'energy']
 # import data from .csv file:
-ds1 = pd.read_csv(os.path.join(loadpath,'aa.csv'), sep=' ', skiprows=1, names=prop)
+#ds1 = pd.read_csv(os.path.join(loadpath,'aa.csv'), sep=' ', skiprows=1, names=prop)
 ds2 = pd.read_csv(os.path.join(loadpath,'ag.csv'), sep=' ', skiprows=1, names=prop)
 ds3 = pd.read_csv(os.path.join(loadpath,'pf.csv'), sep=' ', skiprows=1, names=prop)
 ds4 = pd.read_csv(os.path.join(loadpath,'ia.csv'), sep=' ', skiprows=1, names=prop)
+fct = 10e6
+px2=ds2.step/fct
+px3=ds3.step/fct
+px4=ds4.step/fct
+
 # plot lines
-p1 = plt.plot(ds1.step, ds1.stress, label='aa')
-p2 = plt.plot(ds2.step, ds2.stress, label='ag')
-p3 = plt.plot(ds3.step, ds3.stress, label='pf')
-p4 = plt.plot(ds4.step, ds4.stress, label='ia')
+#p1 = plt.plot(ds1.step, ds1.stress, label='aa')
+p2 = plt.plot(px2, ds2.stress, label='ag')
+p3 = plt.plot(px3, ds3.stress, label='pf')
+p4 = plt.plot(px4, ds4.stress, label='ia')
 # config title and label
 
-plt.title('stress-strain curve')
-plt.xlabel('Step')
-plt.xlim(xmax=3e5)
+#plt.title('stress-strain curve')
+plt.xlabel('Strain')
+plt.xlim(xmax=0.035)
+plt.ylim(ymax=6)
 plt.ylabel('Stress (GPa)')
 plt.legend(frameon=False)
 plt.savefig(os.path.join(writepath, 'allline.pdf'))

### 2018-09-26 code/data/size/size_summary.py

@@ -14,20 +14,26 @@ violet
 '''
 import os
 import matplotlib.pyplot as plt
+import numpy as np
+import matplotlib.pyplot as plt
+plt.rcParams.update({'font.size': 12})
 # plt.rcParams["font.family"] = 'Times New Roman'
 
 WDIR = os.path.dirname(__file__)
 writepath = os.path.join(WDIR,'..','..','..','draft','img')
 
-size = [0, 2, 5, 10, 15, 20]
-iamax = [5.2, 5.16, 5.27, 5.22, 5.19, 4.96]
-agmax = [5.2, 5.19, 5.10, 5.11, 5.09, 4.87]
+size = np.array([0, 2, 5, 10, 15, 20])
+iamax = np.array([5.26, 5.25, 5.25, 5.22, 5.19, 4.96])
+agmax = np.array([5.26, 5.25, 5.17, 5.11, 5.09, 4.87])
+fac = (1-np.pi*(size/2)**2/(200*180))*iamax[0]
 
-plt.plot(size, iamax, linestyle='--', marker='s', color='darkorange')
-plt.plot(size, agmax, linestyle='--', marker='^', color='steelblue')
-
-plt.legend(['ia', 'ag'], frameon=False)
-# plt.ylim(ymin=0)
+plt.plot(size, iamax, linestyle='--', marker='s')
+# color='darkorange'
+# color='steelblue'
+plt.plot(size, agmax, linestyle='--', marker='^')
+plt.plot(size, fac, linestyle='--',marker='o')
+plt.legend(['ia', 'ag','Calculated'], frameon=False)
+plt.ylim(4.75,5.35)
 plt.xlabel('Radius of Void/A')
 plt.ylabel('Strength/GPa')
 plt.savefig(os.path.join(writepath,'effect_of_vol.pdf'))

### 2018-09-26 draft/draft.tex
update

@@
 \begin{frontmatter}
-\title{Effect of Nanovoid on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy}
+\title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
 \address[mymainaddress]{School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China}
@@
 \begin{equation} \label{eq:csp} 
-	P = \displaystyle\sum_{i=1}^{6}|\vec{R_i}+\vec{R_{i+6}}|^2
+	P = \displaystyle\sum_{i=1}^{6}|\vec{R_i}+{\vec{R}}_{i+6}|^2
 \end{equation}
 
-where $\vec{R_i}$ and $\vec{R_{i+6}}$ are the vectors corresponding to the six pairs of opposite nearest neighbors in the fcc lattice.
+where $\vec{R_i}$ and ${\vec{R}}_{i+6}$ are the vectors corresponding to the six pairs of opposite nearest neighbors in the fcc lattice.
 The centrosymmetry parameter(CSP) is zero for atoms in a perfect lattice.
@@
 \subsection{The effect of void on the strength of material}
-The strength of materails with void in different size and at different position is shown in \ref{}.
-The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
-Detailed observation of specimen with void inside the grain is shown in Figure \cite{}.It's an expectable that the existence of voids detracts the strength of the materials, however it has been observed in the simulation that there is a critical value about 15A for voids at different position.
+\paragraph{position} Void of R=10$\AA$ was placed at phase boundary, inside $\alpha$ phase grain respectively.
+Effect of void at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}.
+The strength of materails with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
+The results show that the model without void defect has best stength, while the void loacted inside $\alpha$ phase detracts the strength of the material most, and the void at the phase boundary have less impact on the strength.
+
+\paragraph{size} The effect of siz is expectable that the greater voids detracts the strength of the materials more, however, it has been observed in the simulation that there is a critical value about 15A for voids at different position.
 The voids larger than 15 A have dramatic detraction to the strength of the material.
-It can be also found that the location of void affects strength of material.
-Comparing with the model with integranularvoid, the model with innergranular voids is weaker.
-The strength calculated with continous theory is as follow:
+Conventional definition of strength of materails with geometry substraction was applied to the model, and theroticial strength of the models was calculated by formulation \ref{eq:section}:
 
@@
 \end{equation}
+
 where $\sigma_0$ is the strength of the model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = a\times b = 36000 A^2$, $A^* $ is section area in consider of the subsection that results from the voids.
 Comparing with the strength determined by molecular dynamics simulation and the resuts calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behaciour of the materials, thus revolution of defects should be examined carefully.
-
-\subsection{Effect of Void Size}
-\paragraph{size}
 
@@
 	\end{minipage}	
-	%\hspace{0.1cm} 
 	\hfill
@@
 		\label{fig:strength}
-
 	\end{minipage}
-
 \end{figure}
@@
 \subsection{Deformation Mechanisms in Two-Phase Alloys}
-
 Deformation phenomena in TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
@@
 
-\subsection{Fracture Process}
-\paragraph{initiation of crack}
-\paragraph{fracture process}
-The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material.
-Detailed observation of specimen with void inside the grain is shown in Figure \cite{}.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{"img/fracture3"}
+	\caption{Yield process of the models}
+	\label{fig:yield}
+\end{figure}
+
 1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/fracture3"}
-	\caption{Fracture Process}
-	\label{fig:fracture-process}
-\end{figure}
-
 % \begin{figure}[h]

### 2018-09-26 code/allline.py

@@ -57,4 +57,4 @@ plt.savefig(os.path.join(writepath, 'allline.pdf'))
 plt.show()
 # /home/alex/violet/all.line.pdf
 # /home/alex/violet/code/pict/area.png
-# /home/alex/violet/draft/img/ag.png
+# /home/alex/violet/draft/img/ag.pngf

### 2018-09-26 code/data/size/size_summary.py

@@ -17,7 +17,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import matplotlib.pyplot as plt
 plt.rcParams.update({'font.size': 12})
-# plt.rcParams["font.family"] = 'Times New Roman'
+plt.rcParams["font.family"] = 'Times New Roman'
 
 WDIR = os.path.dirname(__file__)
 writepath = os.path.join(WDIR,'..','..','..','draft','img')
@@ -27,13 +27,14 @@ iamax = np.array([5.26, 5.25, 5.25, 5.22, 5.19, 4.96])
 agmax = np.array([5.26, 5.25, 5.17, 5.11, 5.09, 4.87])
 fac = (1-np.pi*(size/2)**2/(200*180))*iamax[0]
 
-plt.plot(size, iamax, linestyle='--', marker='s')
+plt.plot(size, iamax,marker='s')
+plt.plot(size, agmax, marker='^')
+plt.plot(size, fac, marker='o',linestyle='--'
+                                         '')
 # color='darkorange'
 # color='steelblue'
-plt.plot(size, agmax, linestyle='--', marker='^')
-plt.plot(size, fac, linestyle='--',marker='o')
 plt.legend(['ia', 'ag','Calculated'], frameon=False)
-plt.ylim(4.75,5.35)
+plt.ylim(4.8,5.35)
 plt.xlabel('Radius of Void/A')
 plt.ylabel('Strength/GPa')
 plt.savefig(os.path.join(writepath,'effect_of_vol.pdf'))

### 2018-09-26 code/surf_div.py

@@ -3,6 +3,7 @@ import os
 import os.path
 import numpy as np
 import matplotlib.pyplot as plt
+plt.rcParams.update({'font.size': 12})
 
 
 #WDIR = os.getcwd()
@@ -25,12 +26,12 @@ dv1st = list(map(np.gradient,imglist))
 max = list(map(np.max,dv1st))
 min = np.min(np.abs(ag))
 for img in dv1st:
-    pxx = np.linspace(0,np.dot(0.005,len(img)),len(img))
+    pxx = np.linspace(0,np.dot(0.005,len(img)),len(img))/10
     plt.plot(pxx, img/np.max(max))
 # plt.title('1st Deviation of Area of Surface of Crack')
 plt.xlabel('Strain')
 plt.ylabel('Relative Crack Propagation Indicator')
-plt.xlim(xmax=0.3)
+plt.xlim(xmax=0.03)
 plt.legend(["ag","ig", "pf"],frameon=False)
 # plt.legend()
 plt.savefig(os.path.join(writepath,'1stdiv.pdf'))

### 2018-09-27 draft/alexpub.tex
add

--- 2018-09-26 draft/draft.tex
@@
-\documentclass[times,12pt]{elsarticle}
-\usepackage[margin=2.5cm]{geometry}
-%\documentclass[]{elsarticle}
-\usepackage[labelfont=bf,justification=raggedright]{caption}
-\captionsetup[figure]{name=Fig. ,labelsep=period,singlelinecheck=true,skip=5pt}
-\captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
-%\documentclass[final,5p,times,twocolumn]{elsarticle}
-%\setlength{\mathindent}{3cm}
-%Function format
-\usepackage{lineno,hyperref}
-%\modulolinenumbers[5]
-\journal{Materials and Design}
-\bibliographystyle{elsarticle-num.bst}
-\journal{}
-%%%%%%%%%%%%%%%%%%%%%%%
+%=================================================================
+\documentclass[journal,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi}
 
+\firstpage{1} 
+\makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother
+\pubvolume{xx}
+\issuenum{1}
+\articlenumber{5}
+\pubyear{2018}
+\copyrightyear{2018}
+%\externaleditor{Academic Editor: name}
+\history{Received: date; Accepted: date; Published: date}
+
+% Full title of the paper (Capitalized)
+\Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
+
+% Author Orchid ID: enter ID or remove command
+\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
+%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name
+
+% Authors, for the paper (add full first names)
+\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
+
+% Authors, for metadata in PDF
+\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China; e-mail@e-mail.com\\
+$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
+
+% Contact information of the corresponding author
+\corres{Correspondence: e-mail@e-mail.com; Tel.: +x-xxx-xxx-xxxx}
+
+% Current address and/or shared authorship
+\firstnote{Current address: Affiliation 3} 
+\secondnote{These authors contributed equally to this work.}
+% The commands \thirdnote{} till \eighthnote{} are available for further notes
+
+%\simplesumm{} % Simple summary
+
+%\conference{} % An extended version of a conference paper
+
+% Abstract (Do not insert blank lines, i.e. \\) 
+\abstract{Fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects.
+Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
+The results show that voids located at the $\alpha$/$\gamma$ phase boundary have significant detract to strength of Ti-Al polycrystalline.}
+
+% Keywords
+\keyword{$\alpha$ + $\gamma$ two phase TiAl alloy; void; molecular dynamics}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
-
-\begin{frontmatter}
-\title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
-\address[mymainaddress]{School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China}
-
-\begin{abstract}
-Fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects.
-Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
-The results show that voids located at the $\alpha$/$\gamma$ phase boundary have significant detract to strength of Ti-Al polycrystalline.
-\end{abstract}
-
-\begin{keyword}
-$\alpha$+$\gamma$ two phase TiAl alloy; void; molecular dynamics
-\end{keyword}
-
-\end{frontmatter}
-
 \section{Introduction}
@@
 \subsection{Atomic Potential}
+
 The interaction of particle in the material is determined by interatomic potential.
@@
 	\section{Results and Discussion}
+%	/home/alex/Documents/violet/draft/img/perfect-line.pdf
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=1\linewidth]{img/perfect-line2-2}
+		\caption{perfect-line2-2}
+		\label{fig:perfect-line2-2}
+	\end{figure}
+
+\subsection{Deformation Mechanisms in Two-Phase Alloys}
+Deformation phenomena in TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
+The literature data covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
+Much of the work has been performed on single phase $\gamma$ alloys and PST crystals.
+However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in twophase alloys.
+Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
+\begin{figure}[h]
+		\centering
+		\includegraphics[width=1\linewidth]{img/def-gamma}
+		\label{fig:def-gamma}
+		\caption{$\gamma$ phase deformation}
+\end{figure}
+The configure of atoms is shown in Fig.\ref{fig:yield}, it can be seen that dislication emission initiate in $\gamma$ pahse in XXX ps, and the deformation canbe mainly confied to the majority $\gamma$ pahse.
+$\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2<110] and superdislocations with the Burgers vectors b=<101] and $b=1/2<11\overline{2}]$.
+The other potential deformation mode is mechanical twinning along $1/6<11\overline{2}]{111}$.
+From Fig.\ref{fig:yield}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
+A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
+TEM examinations performed on tensile  tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3<11\overline{2}0>$ prism planes\ref{fig:yield}, which is by far the easiest slip system in $\alpha_2$ single crystals.
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=1\linewidth]{img/def-alpha}
+		\label{fig:def-alpha}
+		\caption{$\alpha$ phase deformation}
+	\end{figure}
+Basic deformationg mechanism of $\alpha$ phase
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=1\linewidth]{"img/fracture3"}
+		\caption{Yield process of the models}
+		\label{fig:yield}
+	\end{figure}
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=1\linewidth]{"img/disl-gamma"}
+		\caption{Disloaction in $\gamma$}
+		\label{fig:dis-alpha}
+	\end{figure}
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=1\linewidth]{img/disl2-gamma}
+		\label{fig:surf}
+		\caption{stress-strain curve}
+	\end{figure}
+1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
+This may significantly reduce the Schmid factor and thus impede slip transfer.
+At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
+Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
+
+The core of  a dislocation intersecting an interface often needs to be transformed.
+For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
+At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
+These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
+
+Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamella, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
+
+	%\subsection{Fracture Process with Integranular Void }
+
+	%\subsection{Fracture Process with Intergranular Void }
+
+\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
+A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}.
+A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}.
+If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to
+
 \subsection{The effect of void on the strength of material}
@@
 			\centering
-		\caption{Strength of model with different voids}
+			\caption{Strength of models}
 			\label{fig:strength}
@@
 	\end{figure}
-
-\subsection{Deformation Mechanisms in Two-Phase Alloys}
-Deformation phenomena in TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
-The literature data covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
-Much of the work has been performed on single phase $\gamma$ alloys and PST crystals.
-However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in twophase alloys.
-Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
-
-Basic deformationg mechanism of $\alpha$ phase
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/fracture3"}
-	\caption{Yield process of the models}
-	\label{fig:yield}
-\end{figure}
-
-1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
-This may significantly reduce the Schmid factor and thus impede slip transfer.
-At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
-Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
-
-The core of  a dislocation intersecting an interface often needs to be transformed.
-For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
-At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
-These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
-
-Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamella, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
-
-%\subsection{Fracture Process with Integranular Void }
-
-%\subsection{Fracture Process with Intergranular Void }
-
-\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
-A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}.
-A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}.
-If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to
 

### 2018-09-27 draft/draft (copy).tex
add

--- 2018-09-26 draft/draft.tex
@@
 
+The configure of atoms is shown in Fig.\ref{fig:yield}, it can be seen that dislication emission initiate in $\gamma$ pahse in XXX ps, and the deformation canbe mainly confied to the majority $\gamma$ pahse.
+$\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2<110] and superdislocations with the Burgers vectors b=<101] and $b=1/2<11\overline{2}]$.
+The other potential deformation mode is mechanical twinning along $1/6<11\overline{2}]{111}$.
+From Fig.\ref{fig:yield}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
+A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
+TEM examinations performed on tensile  tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3<11\overline{2}0>$ prism planes\ref{fig:yield}, which is by far the easiest slip system in $\alpha_2$ single crystals.
+
 Basic deformationg mechanism of $\alpha$ phase

### 2018-09-27 draft/draft.tex
add

@@
 \section{Results and Discussion}
+
+\subsection{Deformation Mechanisms in Two-Phase Alloys}
+Deformation phenomena in TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
+The literature data covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
+Much of the work has been performed on single phase $\gamma$ alloys and PST crystals.
+However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in twophase alloys.
+Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{img/def-gamma}
+	\label{fig:def-gamma}
+	\caption{$\gamma$ phase deformation}
+\end{figure}
+The configure of atoms is shown in Fig.\ref{fig:yield}, it can be seen that dislication emission initiate in $\gamma$ pahse in XXX ps, and the deformation canbe mainly confied to the majority $\gamma$ pahse.
+$\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2<110] and superdislocations with the Burgers vectors b=<101] and $b=1/2<11\overline{2}]$.
+The other potential deformation mode is mechanical twinning along $1/6<11\overline{2}]{111}$.
+From Fig.\ref{fig:yield}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
+A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
+TEM examinations performed on tensile  tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3<11\overline{2}0>$ prism planes\ref{fig:yield}, which is by far the easiest slip system in $\alpha_2$ single crystals.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{img/def-alpha}
+	\label{fig:def-alpha}
+	\caption{$\alpha$ phase deformation}
+\end{figure}
+Basic deformationg mechanism of $\alpha$ phase
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{"img/fracture3"}
+	\caption{Yield process of the models}
+	\label{fig:yield}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{"img/disl-gamma"}
+	\caption{Disloaction in $\gamma$}
+	\label{fig:dis-alpha}
+\end{figure}
+
+1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
+This may significantly reduce the Schmid factor and thus impede slip transfer.
+At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
+Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
+
+The core of  a dislocation intersecting an interface often needs to be transformed.
+For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
+At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
+These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
+
+Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamella, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
+
+%\subsection{Fracture Process with Integranular Void }
+
+%\subsection{Fracture Process with Intergranular Void }
+
+\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
+A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}.
+A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}.
+If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to
+
 \subsection{The effect of void on the strength of material}
@@
 \end{figure}
-
-\subsection{Deformation Mechanisms in Two-Phase Alloys}
-Deformation phenomena in TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
-The literature data covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
-Much of the work has been performed on single phase $\gamma$ alloys and PST crystals.
-However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in twophase alloys.
-Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
-
-Basic deformationg mechanism of $\alpha$ phase
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/fracture3"}
-	\caption{Yield process of the models}
-	\label{fig:yield}
-\end{figure}
-
-1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
-This may significantly reduce the Schmid factor and thus impede slip transfer.
-At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
-Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
-
-The core of  a dislocation intersecting an interface often needs to be transformed.
-For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
-At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
-These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
-
-Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamella, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
-
-%\subsection{Fracture Process with Integranular Void }
-
-%\subsection{Fracture Process with Intergranular Void }
-
-\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
-A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}.
-A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}.
-If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to
 

### 2018-09-27 code/data/size/size_summary.py

@@ -23,9 +23,9 @@ WDIR = os.path.dirname(__file__)
 writepath = os.path.join(WDIR,'..','..','..','draft','img')
 
 size = np.array([0, 2, 5, 10, 15, 20])
-iamax = np.array([5.26, 5.25, 5.25, 5.22, 5.19, 4.96])
-agmax = np.array([5.26, 5.25, 5.17, 5.11, 5.09, 4.87])
-fac = (1-np.pi*(size/2)**2/(200*180))*iamax[0]
+iamax = np.array([5.3, 5.26, 5.25, 5.22, 5.19, 4.96])
+agmax = np.array([5.3, 5.25, 5.17, 5.11, 5.09, 4.87])
+fac = (1-(np.pi*(size/2)**2)/(200*180))*iamax[0]
 
 plt.plot(size, iamax,marker='s')
 plt.plot(size, agmax, marker='^')

### 2018-09-27 code/ialine.py

@@ -1,34 +1,31 @@
 # 读取输出文件，绘制应力应变曲线
 import os
+import os.path
 import matplotlib.pyplot as plt
 import pandas as pd
-#csfont = {'fontname':'Times New Roman'}
-#WDIR = os.getcwd()
-#loadpath = os.path.join(WDIR,'code','data','stress_strain')
-#writepath = os.path.join(WDIR,'draft','img')
+from os import listdir
+plt.rcParams.update({'font.size': 12})
 
 WDIR = os.path.dirname(__file__)
-loadpath = os.path.join(WDIR,'data','stress_strain')
+loadpath = os.path.join(WDIR,'data')
 writepath = os.path.join(WDIR,'..','draft','img')
 # pre-set head name
 prop = ['step', 'strain', 'stress', 'energy']
 # import data from .csv file:
-ds1 = pd.read_csv(os.path.join(loadpath,'ia.csv'), sep=' ', skiprows=1, names=prop)
-
+ds1 = pd.read_csv(os.path.join(loadpath,'pfct.txt'), sep=' ', skiprows=1, names=prop)
+plt.figure(figsize=(8.5,2.5))
 # plot lines
-p1 = plt.plot(ds1.step, ds1.stress, label='ia')
-
+p1 = plt.plot(ds1.strain, ds1.stress, label='ag')
+vlinex = [130000, 130000]
+vliney = [4, 6]
+# p2 = plt.plot(vlinex,vliney)
 # config title and label
 
-plt.title('stress-strain curve')
-plt.xlabel('Step')
+#plt.title('stress-strain curve')
+plt.xlabel('Strain')
 plt.ylabel('Stress (GPa)')
-plt.xlim(1e5,2e5)
+#plt.xlim(0,2e5)
 
-#plt.lim(-6,6)
-#plt.legend()
-plt.savefig(os.path.join(writepath,'ialine.pdf'))
+
+plt.savefig(os.path.join(writepath,'perfect-line.pdf'))
 plt.show()
-#/home/alex/violet/all.line.pdf
-#/home/alex/violet/code/pict/area.png
-#/home/alex/violet/draft/img/ag.png

### 2018-09-27 code/pict/pfctline.py

@@ -1,0 +1,34 @@
+# 读取输出文件，绘制应力应变曲线
+import os
+import matplotlib.pyplot as plt
+import pandas as pd
+#csfont = {'fontname':'Times New Roman'}
+#WDIR = os.getcwd()
+#loadpath = os.path.join(WDIR,'code','data','stress_strain')
+#writepath = os.path.join(WDIR,'draft','img')
+
+WDIR = os.path.dirname(__file__)
+loadpath = os.path.join(WDIR,'data','stress_strain')
+writepath = os.path.join(WDIR,'..','draft','img')
+# pre-set head name
+prop = ['step', 'strain', 'stress', 'energy']
+# import data from .csv file:
+ds1 = pd.read_csv(os.path.join(loadpath,'ia.csv'), sep=' ', skiprows=1, names=prop)
+
+# plot lines
+p1 = plt.plot(ds1.step, ds1.stress, label='ia')
+
+# config title and label
+
+plt.title('stress-strain curve')
+plt.xlabel('Step')
+plt.ylabel('Stress (GPa)')
+plt.xlim(1e5,2e5)
+
+#plt.lim(-6,6)
+#plt.legend()
+plt.savefig(os.path.join(writepath,'ialine.pdf'))
+plt.show()
+#/home/alex/violet/all.line.pdf
+#/home/alex/violet/code/pict/area.png
+#/home/alex/violet/draft/img/ag.png

### 2018-10-02 draft/alexpub.tex
add subsect

@@
 % Full title of the paper (Capitalized)
-\Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
-
+% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
+\Title{On the Cold Deformation Behaviour of Two Phase TiAl Alloy with and without Void Defects}
 % Author Orchid ID: enter ID or remove command
@@
 \begin{document}
+\bibliography{ref/VIOLET-ref.bib}
+
 \section{Introduction}
-\paragraph{Material}
 TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{vu2013}.
-Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{}.
+Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}.
 Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator.
 
-The failure modes of materials have significant influence on the design of material properties in materials science.
+Deformation phenomena in TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
+The literature data covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
+Much of the work has been performed on single phase $\gamma$ alloys and PST crystals.
+% The failure modes of materials have significant influence on the design of material properties in materials science. 
 Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{}.
@@
 The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar microstructure are interface delamination and cracking across the lamellae \cite{}.
+
+MD simulations has reveals that existence of voids alone may contribute to strain hardening because theyare barriers to dislocation movement \cite{Xiong2015}
 
@@
 
-	\begin{equation} \label{eq:eam} 
-	\rho_{h,i}=\sum_{j(\neq1)} \rho_i(R_{ij})
-	\end{equation}
+%	\begin{equation} \label{eq:eam} 
+%	\rho_{h,i}=\sum_{j(\neq1)} \rho_i(R_{ij})
+%	\end{equation}
+%	
+\subsection{Model Creation of Crystalline}
 
-\subsection{Model Creation of Crystalline}
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{img/models}
+	\caption{Overview of model creation}
+	\label{fig:model-creation}
+\end{figure}
+
+\cite{}
 $\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}.
@@
 
-	\begin{table}[h]
+\begin{table}[ht]
+	\caption{Parameters of  nanocrystalline}
 	\centering
-		\caption{Parameters of  nanocrystalline}
-
 	\begin{tabular}{l c c l}
-			\hline
-			Phase			& Space group		& Designation		& Parameters \\
-			\hline
+	\toprule
+	\textbf{Phase}			& \textbf{Space group}		& \textbf{Designation} 		& \textbf{Parameters} \\
+	\midrule
 		$\alpha_2$		& $\rm P6_3/mmc$ 	& $\rm 0_{19}$ 		& $a$ = 0.5765 \\
@@
 		&					&					& $c$ = 0.4062 \\			
-			\hline
+	\bottomrule
 	\end{tabular} 
@@
 
-	% \begin{figure}[h]
+	% \begin{figure}[ht]
 	% 	\centering  
@@
 
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=1\linewidth]{img/models}
-		\caption{Overview of model creation}
-		\label{fig:model-creation}
-	\end{figure}
-
 	\subsection{Analysis method}
-	\paragraph{CSP}
 	The centrosymmetry parameter is defined as follow:
@@
 
-	\paragraph{Virial Stress}
-	The atomic stress is calculated using the virial definition :
-	$$\sigma_t(i)=-$$
-	$$\sigma_t(i)= $$
+	% \paragraph{Virial Stress}
+	% The atomic stress is calculated using the virial definition :
+	% $$\sigma_t(i)=-$$
+	% $$\sigma_t(i)= $$
 
@@
 
-	\begin{figure}[h]
+	\begin{figure}[ht]
 		\centering
@@
 
-\subsection{Deformation Mechanisms in Two-Phase Alloys}
-Deformation phenomena in TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
-The literature data covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
-Much of the work has been performed on single phase $\gamma$ alloys and PST crystals.
+	\begin{table}[ht]
+		\caption{Key point during tensile process}
+		\centering
+		\begin{tabular}{l c c c c c c c c c c}
+		\toprule
+		 \textbf{Key Number} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{9} & \textbf{10}\\
+		\midrule
+		Time/ps	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.20 & 0.21 & 0.22 & 0.23 \\
+		\midrule
+		Strain	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.20 & 0.21 & 0.22 & 0.23 \\
+		\bottomrule
+		\end{tabular} 
+		\label{tab:key-pint}
+	\end{table}
+
+\subsection{Deformation Behaviour of Two Phase Alloys without Void Defects}
 However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in twophase alloys.
 Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
-\begin{figure}[h]
+\begin{figure}[ht]
 		\centering
@@
 TEM examinations performed on tensile  tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3<11\overline{2}0>$ prism planes\ref{fig:yield}, which is by far the easiest slip system in $\alpha_2$ single crystals.
-	\begin{figure}[h]
+	\begin{figure}[ht]
 		\centering
@@
 \subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{"img/dis-void"}
+	\caption{Dislocation around void}
+	\label{fig:dis-void}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{"img/orowan"}
+	\caption{orowan}
+	\label{fig:dis-void}
+\end{figure}
+
 A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}.
@@
 \subsection{The effect of void on the strength of material}
-\paragraph{position} Void of R=10$\AA$ was placed at phase boundary, inside $\alpha$ phase grain respectively.
+
+Void of R=10$\AA$ was placed at phase boundary, inside $\alpha$ phase grain respectively.
 Effect of void at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}.
@@
 
-\paragraph{size} The effect of siz is expectable that the greater voids detracts the strength of the materials more, however, it has been observed in the simulation that there is a critical value about 15A for voids at different position.
+The effect of siz is expectable that the greater voids detracts the strength of the materials more, however, it has been observed in the simulation that there is a critical value about 15A for voids at different position.
 The voids larger than 15 A have dramatic detraction to the strength of the material.
@@
 
-	%\begin{figure}[h]
+	%\begin{figure}[ht]
 	%	\centering
@@
 The max stress stress of the simulation cell decreases as the volume of voids are lareger.
-From Fig \ref{fig:voleff}, there is a critical value of void radius about 15A, the void greater than 15A cause serious detraction of strength of material.
+From Fig \ref{}, there is a critical value of void radius about 15A, the void greater than 15A cause serious detraction of strength of material.
 Engineering stress is calculated
@@
 	%\subsection{The influence of void on strength of TiAl alloy}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.7\linewidth]{img/frame2}
-		\caption{stress-$\sigma$=0}
-		\label{ }
-	\end{figure}
-
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.7\linewidth]{img/frame150}
-		\caption{stress-$\sigma$=0.15}
-		\label{ }
-	\end{figure}
-
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.7\linewidth]{img/frame160}
-		\caption{stress-$\sigma$=0.16}
-		\label{ }
-	\end{figure}
-
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.7\linewidth]{img/frame170}
-		\caption{stress-$\sigma$=0.17}
-		\label{ }
-	\end{figure}
-
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.7\linewidth]{img/frame180}
-		\caption{stress-$\sigma$=0.18}
-		\label{ }
-	\end{figure}
-	\paragraph{position}critical void 
-The location of void affects strength of material. Comparing with the model with integranular void, the model with intergranular voids is weaker. atomic stress is calculated
-
-	% \begin{figure}[h]
+%	\begin{figure}[ht]
 %		\centering
-	% 	\includegraphics[width=0.7\linewidth]{img/ialine}
-	% 	\caption{stress-strain curve}
-	% 	\label{fig:ia_line}
+%		\includegraphics[width=0.7\linewidth]{img/frame2}
+%		\caption{stress-$\sigma$=0}
+%		\label{ }
 %	\end{figure}
 %	
-	% \begin{figure}[h]
+%	\begin{figure}[ht]
 %		\centering
-	% 	\includegraphics[width=0.7\linewidth]{img/agline}
+%		\includegraphics[width=0.7\linewidth]{img/frame150}
+%		\caption{stress-$\sigma$=0.15}
+%		\label{ }
+%	\end{figure}
+%	
+%	\begin{figure}[ht]
+%		\centering
+%		\includegraphics[width=0.7\linewidth]{img/frame160}
+%		\caption{stress-$\sigma$=0.16}
+%		\label{ }
+%	\end{figure}
+%	
+%	\begin{figure}[ht]
+%		\centering
+%		\includegraphics[width=0.7\linewidth]{img/frame170}
+%		\caption{stress-$\sigma$=0.17}
+%		\label{ }
+%	\end{figure}
+%	
+%	
+%	\begin{figure}[ht]
+%		\centering
+%		\includegraphics[width=0.7\linewidth]{img/frame180}
+%		\caption{stress-$\sigma$=0.18}
+%		\label{ }
+%	\end{figure}
+%The location of void affects strength of material. Comparing with the model with integranular void, the model with %intergranular voids is weaker. atomic stress is calculated 
+%	
+%	
+%	
+%	
+%	
+%	% \begin{figure}[ht]
+%	% 	\centering
+%	% 	\includegraphics[width=0.7\linewidth]{img/ialine}
+%	% 	\caption{stress-strain curve}
+%	% 	\label{fig:ia_line}
+%	% \end{figure}
+%	% 
+%	% \begin{figure}[ht]
+%	% 	\centering
+%	% 	\includegraphics[width=0.7\linewidth]{img/agline}
+%	% 	\caption{stress-strain curve}
+%	% 	\label{fig:ag_line}
+%	% \end{figure}
+%	
+%	
+%	\begin{figure}[ht]
+%		\centering
+%		\includegraphics[width=0.7\linewidth]{img/1stdiv}
+%		\label{fig:surf}
 %		\caption{stress-strain curve}
-	% 	\label{fig:ag_line}
 %	\end{figure}
-
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.7\linewidth]{img/1stdiv}
-		\label{fig:surf}
-		\caption{stress-strain curve}
-	\end{figure}
-
-	\section{Conclusion}
-	%\bibliographystyle{elsarticle-num.bst}
-
-	\bibliography{ref/VIOLET-ref}
+%	
+%	
+%	\section{Conclusion}
+%	%\bibliographystyle{elsarticle-num.bst}
+%
 

### 2018-10-02 draft/ed3.tex
add subsect

--- 2018-10-02 draft/alexpub.tex
@@
 % \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
-\Title{On the Cold Deformation Behaviour of Two Phase TiAl Alloy with and without Void Defects}
+\Title{On the Cold Deformation Behavior of Two Phase TiAl Alloy with and without Void Defects}
 % Author Orchid ID: enter ID or remove command
@@
 \begin{document}
-\bibliography{ref/VIOLET-ref.bib}
-
 \section{Introduction}
@@
 The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar microstructure are interface delamination and cracking across the lamellae \cite{}.
-
-MD simulations has reveals that existence of voids alone may contribute to strain hardening because theyare barriers to dislocation movement \cite{Xiong2015}
 
@@
 
-\cite{}
 $\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}.
@@
 \subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/dis-void"}
-	\caption{Dislocation around void}
-	\label{fig:dis-void}
-\end{figure}
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/orowan"}
-	\caption{orowan}
-	\label{fig:dis-void}
-\end{figure}
-
 A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}.
@@
 	%\subsection{The influence of void on strength of TiAl alloy}
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[width=0.7\linewidth]{img/frame2}
+		\caption{stress-$\sigma$=0}
+		\label{ }
+	\end{figure}
+
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[width=0.7\linewidth]{img/frame150}
+		\caption{stress-$\sigma$=0.15}
+		\label{ }
+	\end{figure}
+
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[width=0.7\linewidth]{img/frame160}
+		\caption{stress-$\sigma$=0.16}
+		\label{ }
+	\end{figure}
+
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[width=0.7\linewidth]{img/frame170}
+		\caption{stress-$\sigma$=0.17}
+		\label{ }
+	\end{figure}
+
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[width=0.7\linewidth]{img/frame180}
+		\caption{stress-$\sigma$=0.18}
+		\label{ }
+	\end{figure}
+The location of void affects strength of material. Comparing with the model with integranular void, the model with intergranular voids is weaker. atomic stress is calculated
+
 	% \begin{figure}[ht]
 	% 	\centering
-%		\includegraphics[width=0.7\linewidth]{img/frame2}
-%		\caption{stress-$\sigma$=0}
-%		\label{ }
+	% 	\includegraphics[width=0.7\linewidth]{img/ialine}
+	% 	\caption{stress-strain curve}
+	% 	\label{fig:ia_line}
 	% \end{figure}
@@
 	% 	\centering
-%		\includegraphics[width=0.7\linewidth]{img/frame150}
-%		\caption{stress-$\sigma$=0.15}
-%		\label{ }
+	% 	\includegraphics[width=0.7\linewidth]{img/agline}
+	% 	\caption{stress-strain curve}
+	% 	\label{fig:ag_line}
 	% \end{figure}
-%	
-%	\begin{figure}[ht]
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{img/frame160}
-%		\caption{stress-$\sigma$=0.16}
-%		\label{ }
-%	\end{figure}
-%	
-%	\begin{figure}[ht]
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{img/frame170}
-%		\caption{stress-$\sigma$=0.17}
-%		\label{ }
-%	\end{figure}
-%	
-%	
-%	\begin{figure}[ht]
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{img/frame180}
-%		\caption{stress-$\sigma$=0.18}
-%		\label{ }
-%	\end{figure}
-%The location of void affects strength of material. Comparing with the model with integranular void, the model with %intergranular voids is weaker. atomic stress is calculated 
-%	
-%	
-%	
-%	
-%	
-%	% \begin{figure}[ht]
-%	% 	\centering
-%	% 	\includegraphics[width=0.7\linewidth]{img/ialine}
-%	% 	\caption{stress-strain curve}
-%	% 	\label{fig:ia_line}
-%	% \end{figure}
-%	% 
-%	% \begin{figure}[ht]
-%	% 	\centering
-%	% 	\includegraphics[width=0.7\linewidth]{img/agline}
-%	% 	\caption{stress-strain curve}
-%	% 	\label{fig:ag_line}
-%	% \end{figure}
-%	
-%	
-%	\begin{figure}[ht]
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{img/1stdiv}
-%		\label{fig:surf}
-%		\caption{stress-strain curve}
-%	\end{figure}
-%	
-%	
-%	\section{Conclusion}
-%	%\bibliographystyle{elsarticle-num.bst}
-%
+
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[width=0.7\linewidth]{img/1stdiv}
+		\label{fig:surf}
+		\caption{stress-strain curve}
+	\end{figure}
+
+	\section{Conclusion}
+	%\bibliographystyle{elsarticle-num.bst}
+
+	\bibliography{ref/VIOLET-ref}
 

### 2018-10-02 code/SigLinePlt.py

@@ -4,15 +4,17 @@ import matplotlib.pyplot as plt
 file_path = os.path.join('data', 'inflammation-01.csv')
 # pre-set head name
 
-wdir = os.path.abspath('.')
-pyy = np.loadtxt("wdir/code/data/crack_surf/ig_10.txt")
+#wdir = os.path.abspath('.')
+pyy = np.loadtxt("/home/alex/Documents/str.txt")
+
+# pyy = np.loadtxt("wdir/code/data/crack_surf/ig_10.txt")
 pxx = np.linspace(0, 0.4, (len(pyy)))
 
 plt.plot(pxx, pyy)
 plt.title('Area of Crack Surface')
 plt.xlabel('strain')
 plt.ylabel('Area/A2')
-plt.savefig('area.png')
+#plt.savefig('area.png')
 plt.show()
 #plt.savefig()
 

### 2018-10-02 draft/alexpub.tex
add subsection

@@
 \subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
+The volume defects considered pertain to three-dimensional objects contained within a matrix. Three-dimensional structures composed of zero-, one- or two-dimensional defects are not considered here.
+Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, more or less (as possibly associated with
+the occurrence of incoherent or coherent interfaces; see Sect.
+5.3), the long-range translation symmetry of the matrix.
+They may induce considerable misfit-stress fields and thus can influence material properties pronouncedly.
+Such stress fields surrounding the second-phase particles can be due to misfit between the volume occupied by the second-phase particle when unconstrained and the space (“hole”) put at its disposal by the matrix.
+Such misfit can arise due to specific volume differences induced by precipitation or by different thermal expansion or shrinkage upon heating
+or cooling the specimen.
+A possibly favourable effect of second-phase particles is a contribution to the enhancement of mechanical strength.
+Considering yielding of a material as related to glide of dislocations (Sect.
+5.2.5), any mechanism obstructing dislocation glide improves the mechanical strength.
+In the discussion of the Frank–Read source for dislocation (-line) production (Sect.
+5.2.6) it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of “antagonistic” nature and “block” propagation of the stress field of a migrating dislocation: the second-phase particle acts as “pinning point”.
+It was already indicated that in order that a dislocation can pass two pinning points (A and B in Fig.
+5.13; see Sect.
+5.2.6) a critical shear stress is needed
+that depends on the distance between the obstacles (which can be second-phase particles):
+
+\begin{equation} \label{eq:orowan} 
+\tau_0 = Gb/d
+\end{equation}
+
+where d represents the distance between A and B and thus reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution.
+This mechanism for hardening is designated as the Orowan process (with $\tau_0$ as the Orowan
+(shear) stress ; see also Sect.
+11.14.4).
+As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles (see Fig.
+5.27).
+Consequently, the effective average distance between the second-phase particles has decreased to d which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide (cf.
+(5.10)).
+A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}.
+A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}.
+If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to
+
 \begin{figure}[ht]
@@
 \end{figure}
-
-A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}.
-A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}.
-If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to
 

### 2018-10-04 draft/alexpub.tex
no

@@
 % \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
-\Title{On the Cold Deformation Behaviour of Two Phase TiAl Alloy with and without Void Defects}
+\Title{The Effect of Void on the}
 % Author Orchid ID: enter ID or remove command
@@
 		\centering
-		\includegraphics[width=1\linewidth]{"img/fracture3"}
-		\caption{Yield process of the models}
-		\label{fig:yield}
-	\end{figure}
-
-	\begin{figure}[ht]
-		\centering
 		\includegraphics[width=1\linewidth]{"img/disl-gamma"}
@@
 
-	\begin{figure}[ht]
-		\centering
-		\includegraphics[width=1\linewidth]{img/disl2-gamma}
-		\label{fig:surf}
-		\caption{stress-strain curve}
-	\end{figure}
+%	\begin{figure}[ht]
+%		\centering
+%		\includegraphics[width=1\linewidth]{img/disl2-gamma}
+%		\label{fig:surf}
+%		\caption{stress-strain curve}
+%	\end{figure}
 1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
@@
 Comparing with the strength determined by molecular dynamics simulation and the resuts calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behaciour of the materials, thus revolution of defects should be examined carefully.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{"img/fracture3"}
+	\caption{Yield process of the models}
+	\label{fig:yield}
+\end{figure}
 

### 2018-10-04 draft/alexpub.tex
add ref
add no
delete blank line
delet 1 line

@@
 \begin{document}
-\bibliography{ref/VIOLET-ref.bib}
 
@@
 The centrosymmetry parameter is defined as follow:
+
 	\begin{equation} \label{eq:csp} 
@@
 %	/home/alex/Documents/violet/draft/img/perfect-line.pdf
-
+The model without and type of void defect was regarded as benchmark of other simulation, deformation mechanisms was chose to .
+In order to examine deforamtion behaviour carefully, the whole tension process was sliced into four stages.
+Stage 1 is typical elasttic stage of the model, which is originate from strain $\epsilon = 0$ to $\epsilon = 0.09$.
+Stage 2 is yield stage of the model range from $\epsilon = 0.09$ to $\epsilon = $.
+stage 3.cracking stage and 4.
+Fracture stage.
+More specificially, a greater number of moments was snaped in stage 2 and stage 3.
 	\begin{figure}[ht]
@@
 that depends on the distance between the obstacles (which can be second-phase particles):
-
 \begin{equation} \label{eq:orowan} 
@@
 This mechanism for hardening is designated as the Orowan process (with $\tau_0$ as the Orowan
-(shear) stress ; see also Sect.
+(shear) stress ; sgitee also Sect.
 11.14.4).
@@
 	%\begin{figure}[ht]
-	%	\centering
+	%	\centeringT
 	%	\includegraphics[width=0.7\linewidth]{img/allline}
@@
 %	
-
+\reftitle{References}
+\bibliography{ref/VIOLET-ref.bib}
 \end{document}

### 2018-10-04 draft/alexpub.tex
add new

--- 2018-10-04 draft/alexpub.tex
@@
 % Full title of the paper (Capitalized)
-% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
+% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
 \Title{The Effect of Void on the}
@@
 \abstract{Fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects.
-Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
-The results show that voids located at the $\alpha$/$\gamma$ phase boundary have significant detract to strength of Ti-Al polycrystalline.}
+Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha_2$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
+The results show that voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detract to strength of Ti-Al polycrystalline.}
 
 % Keywords
-\keyword{$\alpha$ + $\gamma$ two phase TiAl alloy; void; molecular dynamics}
+\keyword{$\alpha_2$ + $\gamma$ two phase TiAl alloy; void; molecular dynamics}
 
@@
 \cite{}
-$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}.
+$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha_2 TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}.
 The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \cite{}.
@@
 %	/home/alex/Documents/violet/draft/img/perfect-line.pdf
+In order to examine deforamtion behaviour carefully, tensile loading was applied to the model without any types of void defect.
+The whole tension process was saperated into four stages: Stage-1 is typical elasttic part of the deformation, which is originated from $\epsilon = 0$ to $\epsilon = 0.092$, includeing key point 1.
+Stage-2 is yield stage ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6.
+In stage-2, the stress decreased slightly along with the increasing of strain.
+Stage-3 is cracking stage and in this stage the strength of the model have beeen was detracted sharply, we can confine that the structure almost fail after the stage-3.
+Snapshots of atoms configuration are labeled with key points number from 1 to 10, specific list of key points numbers were shown in Table.\ref{tab:key-point}.
+Deformation beaviour of the $\alpha_2$ phase had $\gamma$ phase were discussed in the folling subsection respectively.
 
@@
 		\includegraphics[width=1\linewidth]{img/perfect-line2-2}
-		\caption{perfect-line2-2}
-		\label{fig:perfect-line2-2}
+		\caption{Deformation process of the model without void defect}
+		\label{fig:deformation-pf}
 	\end{figure}
@@
 		\midrule
-		Strain	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.20 & 0.21 & 0.22 & 0.23 \\
+		Strain	& 0 & 0.092 & 0.094 & 0.096 & 0.099 & 0.101 & 0.104 & 0.107 & 0.110 & 0.112 \\
 		\bottomrule
 		\end{tabular} 
-		\label{tab:key-pint}
+		\label{tab:key-point}
 	\end{table}
@@
 		\includegraphics[width=1\linewidth]{img/def-alpha}
-		\label{fig:def-alpha}
-		\caption{$\alpha$ phase deformation}
+		\label{fig:def-alpha_2}
+		\caption{$\alpha_2$ phase deformation}
 	\end{figure}
-Basic deformationg mechanism of $\alpha$ phase
+Basic deformationg mechanism of $\alpha_2$ phase
 
@@
 		\caption{Disloaction in $\gamma$}
-		\label{fig:dis-alpha}
+		\label{fig:dis-alpha_2}
 	\end{figure}
@@
 For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
-At the $\alpha/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
+At the $\alpha_2/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
 These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
@@
 
-Void of R=10$\AA$ was placed at phase boundary, inside $\alpha$ phase grain respectively.
+Void of R=10$\AA$ was placed at phase boundary, inside $\alpha_2$ phase grain respectively.
 Effect of void at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}.
 The strength of materails with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
-The results show that the model without void defect has best stength, while the void loacted inside $\alpha$ phase detracts the strength of the material most, and the void at the phase boundary have less impact on the strength.
+The results show that the model without void defect has best stength, while the void loacted inside $\alpha_2$ phase detracts the strength of the material most, and the void at the phase boundary have less impact on the strength.
 
@@
 	%\begin{figure}[ht]
-	%	\centering
+	%	\centeringT
 	%	\includegraphics[width=0.7\linewidth]{img/allline}
-	%	\caption{Fracture process of specimen with void in $\alpha$ phase}
+	%	\caption{Fracture process of specimen with void in $\alpha_2$ phase}
 	%	\label{ }

### 2018-10-07 draft/alexpub.tex
no

@@
 % \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
-\Title{The Effect of Void on the}
+\Title{The Effect of Void on the Cold Deformation Behaviour of $\alpha_2+\gamma$ Two Phase Ti-Al Alloy}
 % Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorA}{0000-0001-8385-4439} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0002-9582-6301} % Add \orcidB{} behind the author's name
 
 % Authors, for the paper (add full first names)
-\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
+\Author{Ruicheng Feng $^{1,2}$\orcidA{}, Maomao Wang $^{1}$\orcidB{}}
 
 % Authors, for metadata in PDF
-\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
+%\AuthorNames{Maomao Wang $^{1,\dagger,\ddagger}$\orcidB{}, Firstname Lastname and Firstname Lastname}
 
@@
 \address{%
-$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China; e-mail@e-mail.com\\
-$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
-
+$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com (R.F.); 15620864891@163.com (M.W.)\\
+% $^{2}$ \quad Key Laboratory of Digital Manufacturing Technology and Application, Ministry of Education, Lanzhou University of Technology, Lanzhou 730050, China
+%*; e-mail@e-mail.com}
+$^{2}$ \quad State Key Laboratory of Advanced Processing and Recycling of Non-ferrous Metals, Lanzhou University of Technology, Lanzhou 730050, China}
 % Contact information of the corresponding author
@@
 % Current address and/or shared authorship
-\firstnote{Current address: Affiliation 3} 
-\secondnote{These authors contributed equally to this work.}
+%\firstnote{Current address: Affiliation 3} 
+%\secondnote{These authors contributed equally to this work.}
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
@@
 Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator.
-
-Deformation phenomena in TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
-The literature data covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
-Much of the work has been performed on single phase $\gamma$ alloys and PST crystals.
+Deformation phenomena of TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
+A great number of literature covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
+Much of the work has been performed on single phase $\gamma$ alloys and PST crystals[].
 % The failure modes of materials have significant influence on the design of material properties in materials science. 
 Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{}.
+
+The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study of detailed mechanisms of defromation and cracking.
+
 These defects are known to play a fundamental role in the deformation of the material.

### 2018-10-08 draft/alexpub.tex
add bib

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects.
-Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha_2$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
+\abstract{Fracture processes of nanocrystalline metallic materia is affected by dislocation, nano void and other defects.
+Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nano void in $\alpha_2$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
 The results show that voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detract to strength of Ti-Al polycrystalline.}
@@
 % Keywords
-\keyword{$\alpha_2$ + $\gamma$ two phase TiAl alloy; void; molecular dynamics}
+\keyword{$\alpha_2+\gamma$ two phase TiAl alloy; void; molecular dynamics}
 
@@
 \section{Introduction}
-TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{vu2013}.
+Brittle fracture in Ti-Al alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator \cite{Munz2017}.
 Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}.
-Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator.
 Deformation phenomena of TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
 A great number of literature covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
-Much of the work has been performed on single phase $\gamma$ alloys and PST crystals[].
+Much of the work has been performed on single phase $\gamma$ alloys and PST crystals\cite{Appel2016}.
 % The failure modes of materials have significant influence on the design of material properties in materials science. 
-Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{}.
-
-The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study of detailed mechanisms of defromation and cracking.
-
+Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{Tang2014}.
+The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study of detailed mechanisms of deformation and cracking.
 These defects are known to play a fundamental role in the deformation of the material.
-Nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important.
+Nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
 Therefore, it is necessary to study the deformation response of porous materials with the consideration of microstructure evolution.
 
-Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine andcombustion generator[].Defects such as grainboundary, void and segregation plays an significant role in the process of fracture[].In order to understanding the mechanism of brittle fracture, multi-scale methods from micro to marco scale have been applied to investigate the behavior of fracture.
-It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.A previous study on void growth in gamma-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength \cite{}.Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nanoscale \cite{}.
-The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar microstructure are interface delamination and cracking across the lamellae \cite{}.
+Defects such as grain boundary, void and segregation plays an significant role in the process of fracture \cite{Larsen2016}.
+In order to understanding the mechanism of brittle fracture, multi-scale methods from micro to marco scale have been applied to investigate the behavior of fracture.
+It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
+A previous study on void growth in gamma-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength \cite{Tang2014}.Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nanoscale \cite{Jing2018a,Elkhateeb2018,Tang2014}.
+The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{}.
 
@@
 The interaction of particle in the material is determined by interatomic potential.
-Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to is better accuracy in metal lattice compare with F-S and L/J \cite{}.
-The embedded atom method (MEAM) potential developed by Zope and Mishin by \cite{} was used in the study.
-The simulation is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{}.
+Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to is better accuracy in metal lattice compare with F-S and L/J \cite{Goes1998}.
+The embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study.
+The simulation is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}.
 We performed constant-pressure and constant-temperature (NPT) molecular dynamics simulation.
@@
 It can be noted that $F_i$ only depends on the element of atom $i$ and $\phi_{ij}$ only depends on the elements of atoms $i$ and $j$.
-The electron density is, as stated above, approximated by the superposition of atomic densities, namely
+The electron density is, as stated above, approximated by the superposition of atomic densities.
 
@@
 \end{figure}
-
 \cite{}
@@
 or cooling the specimen.
-A possibly favourable effect of second-phase particles is a contribution to the enhancement of mechanical strength.
+A possibly favorable effect of second-phase particles is a contribution to the enhancement of mechanical strength.
 Considering yielding of a material as related to glide of dislocations (Sect.
@@
 (5.10)).
-A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}.
-A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}.
-If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to
+A step, of the width of a burgers vector, will be generated at both sidesof a crystal along the direction of the burgers vector after dislocation traversing the entire crystal, as is shown in \ref{}.
+A small tep will be formed at spherical void surface toward the void interiorafter dislocation absorption at spherical void surfaces, as is shown in \ref{}.
+If a great number of dislocation slip along their respective systemstowards the spherical nano void in all directions, and are absorbed at fhe spherical void surfaces, the spherical nano void will eventually shrink from the dash circle to
 
@@
 	\includegraphics[width=1\linewidth]{"img/dis-void"}
-	\caption{Dislocation around void}
+	\caption{Atoms configuration around void ($\alpha$ phase atoms have been removed)}
 	\label{fig:dis-void}
@@
 	\includegraphics[width=1\linewidth]{"img/orowan"}
-	\caption{orowan}
+	\caption{Schematic of Orowan process}
 	\label{fig:dis-void}
@@
 
-Void of R=10$\AA$ was placed at phase boundary, inside $\alpha_2$ phase grain respectively.
+Void of R=10 \AA\ was placed at phase boundary, inside $\alpha_2$ phase grain respectively.
 Effect of void at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}.
 The strength of materails with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
-The results show that the model without void defect has best stength, while the void loacted inside $\alpha_2$ phase detracts the strength of the material most, and the void at the phase boundary have less impact on the strength.
+The results show that the model without void defect has best strength, while the void located inside $\alpha_2$ phase detracts the strength of the material most, and the void at phase boundary have less impact on the strength.
 
-The effect of siz is expectable that the greater voids detracts the strength of the materials more, however, it has been observed in the simulation that there is a critical value about 15A for voids at different position.
+The effect of size is expectable that the greater voids detracts the strength of the materials more, however, it has been observed in the simulation that there is a critical value about 15A for voids at different position.
 The voids larger than 15 A have dramatic detraction to the strength of the material.
-Conventional definition of strength of materails with geometry substraction was applied to the model, and theroticial strength of the models was calculated by formulation \ref{eq:section}:
+Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by formulation \ref{eq:section}:
 
@@
 
-where $\sigma_0$ is the strength of the model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = a\times b = 36000 A^2$, $A^* $ is section area in consider of the subsection that results from the voids.
-Comparing with the strength determined by molecular dynamics simulation and the resuts calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behaciour of the materials, thus revolution of defects should be examined carefully.
+where $\sigma_0$ is the strength of the model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = 36000 {AA}^2$, $A^* $ is section area in consider of the subsection that results from the voids.
+Comparing with the strength determined by molecular dynamics simulation and the results calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behaviour of the materials, thus revolution of defects should be examined carefully.
 

### 2018-10-09 draft/alexpub.tex
midified

@@
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
-A previous study on void growth in gamma-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength \cite{Tang2014}.Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nanoscale \cite{Jing2018a,Elkhateeb2018,Tang2014}.
-The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{}.
+A previous study on void growth in $\gamma$-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength \cite{Tang2014}.Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nanoscale \cite{Jing2018a,Elkhateeb2018,Tang2014}.
+The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang20}.
 
@@
 The interaction of particle in the material is determined by interatomic potential.
-Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to is better accuracy in metal lattice compare with F-S and L/J \cite{Goes1998}.
+Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to is better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015}.
 The embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study.
@@
 We performed constant-pressure and constant-temperature (NPT) molecular dynamics simulation.
+The definitnion of potential is as following:
 
@@
 
-where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system,$F_i(\rho)$ is the energy for embedding atom i into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ is the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$.
+where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system,$F_i(\rho)$ is the energy for embedding atom $i$ into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ is the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$.
 It can be noted that $F_i$ only depends on the element of atom $i$ and $\phi_{ij}$ only depends on the elements of atoms $i$ and $j$.
@@
 \end{figure}
-\cite{}
-$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha_2 TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}.
+
+$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure, and $\alpha_2 -\rm TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\ref{}, and the constructing parameters are givin by Table.
+\ref{tab:lattice_parameter}.
 The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \cite{}.
 Periodic boundary conditions (PBC)are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
-The initial dimension of simulation cell is  $L_x = $ nm, $L_y = $ nm, $L_z = $ nm, and each model contains about 4.6 million atoms.
+The initial dimension of simulation cell is  $L_x =20$ nm, $L_y = $18nm, $L_z = 21$ nm, and each model contains about 4.6 million atoms.
 The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{}, and resulting in the arbitrary shape and orientation of the grains.
@@
 \end{table}
-
-	% \begin{figure}[ht]
-	% 	\centering  
-	% 	\includegraphics[width=0.7\linewidth]{img/cell}
-	% 	\caption{unit cell}
-	% 	\label{fig:unit_cell}
-	% \end{figure}
 
@@
 \subsection{Deformation Behaviour of Two Phase Alloys without Void Defects}
-However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in twophase alloys.
+However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in twophase alloys.
 Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
+
 \begin{figure}[ht]
@@
 		\label{fig:def-gamma}
-		\caption{$\gamma$ phase deformation}
+		\caption{Defect evolution in $\gamma$ phase (perfect atoms of $\alpha$ phase have been removed)}
 \end{figure}
+
 The configure of atoms is shown in Fig.\ref{fig:yield}, it can be seen that dislication emission initiate in $\gamma$ pahse in XXX ps, and the deformation canbe mainly confied to the majority $\gamma$ pahse.
-$\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2<110] and superdislocations with the Burgers vectors b=<101] and $b=1/2<11\overline{2}]$.
+$\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2<110] and superdislocations with the Burgers vectors $b=<101]$ and $b=1/2<11\overline{2}]$.
 The other potential deformation mode is mechanical twinning along $1/6<11\overline{2}]{111}$.
+
 From Fig.\ref{fig:yield}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
@@
 TEM examinations performed on tensile  tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3<11\overline{2}0>$ prism planes\ref{fig:yield}, which is by far the easiest slip system in $\alpha_2$ single crystals.
+
 \begin{figure}[ht]
@@
 		\label{fig:def-alpha_2}
-		\caption{$\alpha_2$ phase deformation}
+		\caption{Defect evolution in $\alpha_2$-phase (perfect atoms in $\alpha_2$ phase have been removed)}
 	\end{figure}
-Basic deformationg mechanism of $\alpha_2$ phase
 
@@
 
-%	\begin{figure}[ht]
-%		\centering
-%		\includegraphics[width=1\linewidth]{img/disl2-gamma}
-%		\label{fig:surf}
-%		\caption{stress-strain curve}
-%	\end{figure}
-1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
+In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
 This may significantly reduce the Schmid factor and thus impede slip transfer.
 At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
-Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
+Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1}_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
 
 The core of  a dislocation intersecting an interface often needs to be transformed.
-For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
+For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a $<101]$ super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
 At the $\alpha_2/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
@@
 
-	%\subsection{Fracture Process with Integranular Void }
-
-	%\subsection{Fracture Process with Intergranular Void }
-
 \subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
-The volume defects considered pertain to three-dimensional objects contained within a matrix. Three-dimensional structures composed of zero-, one- or two-dimensional defects are not considered here.
-Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, more or less (as possibly associated with
-the occurrence of incoherent or coherent interfaces; see Sect.
+The volume defects considered pertain to three-dimensional objects contained within a matrix.
+Three-dimensional structures composed of zero-, one- or two-dimensional defects are not considered here.
+Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, more or less (as possibly associated with the occurrence of incoherent or coherent interfaces; see Sect.
 5.3), the long-range translation symmetry of the matrix.
@@
 Such stress fields surrounding the second-phase particles can be due to misfit between the volume occupied by the second-phase particle when unconstrained and the space (“hole”) put at its disposal by the matrix.
-Such misfit can arise due to specific volume differences induced by precipitation or by different thermal expansion or shrinkage upon heating
-or cooling the specimen.
+Such misfit can arise due to specific volume differences induced by precipitation or by different thermal expansion or shrinkage upon heating or cooling the specimen.
 A possibly favorable effect of second-phase particles is a contribution to the enhancement of mechanical strength.
@@
 	\centering
-	\includegraphics[width=1\linewidth]{"img/dis-void"}
-	\caption{Atoms configuration around void ($\alpha$ phase atoms have been removed)}
-	\label{fig:dis-void}
-\end{figure}
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/orowan"}
-	\caption{Schematic of Orowan process}
+	\includegraphics[width=1\linewidth]{"img/dis-void2"}
+	\caption{Orowan process in $\alpha$-phase ($\alpha$ phase atoms have been removed)}
 	\label{fig:dis-void}
@@
 
-	%\begin{figure}[ht]
-	%	\centeringT
-	%	\includegraphics[width=0.7\linewidth]{img/allline}
-	%	\caption{Fracture process of specimen with void in $\alpha_2$ phase}
-	%	\label{ }
-	%\end{figure}
-	%
-
 Voids with different size: 2A, 5A, 10A, 15A were placed into the model respectively.
@@
 	$$ m = cos(\phi)cos(\lambda)$$
-	%\subsection{The influence of void on strength of TiAl alloy}
-%	\begin{figure}[ht]
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{img/frame2}
-%		\caption{stress-$\sigma$=0}
-%		\label{ }
-%	\end{figure}
-%	
-%	\begin{figure}[ht]
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{img/frame150}
-%		\caption{stress-$\sigma$=0.15}
-%		\label{ }
-%	\end{figure}
-%	
-%	\begin{figure}[ht]
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{img/frame160}
-%		\caption{stress-$\sigma$=0.16}
-%		\label{ }
-%	\end{figure}
-%	
-%	\begin{figure}[ht]
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{img/frame170}
-%		\caption{stress-$\sigma$=0.17}
-%		\label{ }
-%	\end{figure}
-%	
-%	
-%	\begin{figure}[ht]
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{img/frame180}
-%		\caption{stress-$\sigma$=0.18}
-%		\label{ }
-%	\end{figure}
-%The location of void affects strength of material. Comparing with the model with integranular void, the model with %intergranular voids is weaker. atomic stress is calculated 
-%	
-%	
-%	
-%	
-%	
-%	% \begin{figure}[ht]
-%	% 	\centering
-%	% 	\includegraphics[width=0.7\linewidth]{img/ialine}
-%	% 	\caption{stress-strain curve}
-%	% 	\label{fig:ia_line}
-%	% \end{figure}
-%	% 
-%	% \begin{figure}[ht]
-%	% 	\centering
-%	% 	\includegraphics[width=0.7\linewidth]{img/agline}
-%	% 	\caption{stress-strain curve}
-%	% 	\label{fig:ag_line}
-%	% \end{figure}
-%	
-%	
-%	\begin{figure}[ht]
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{img/1stdiv}
-%		\label{fig:surf}
-%		\caption{stress-strain curve}
-%	\end{figure}
-%	
-%	
-%	\section{Conclusion}
-%	%\bibliographystyle{elsarticle-num.bst}
-%	
+
 \reftitle{References}

### 2018-10-17 draft/alexpub.tex
edited

@@
 %=================================================================
-\documentclass[journal,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi}
-
+\documentclass[materials,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi} 
+\usepackage{siunitx}
+\preto{\abstractkeywords}{\nolinenumbers}
 \firstpage{1} 
@@
 % \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
-\Title{The Effect of Void on the Cold Deformation Behaviour of $\alpha_2+\gamma$ Two Phase Ti-Al Alloy}
+\Title{Atomic Investigation on Cold Deformation Behavior of Two Phase TiAl Polycrystalline with and without Void Defect}
 % Author Orchid ID: enter ID or remove command
@@
 % Authors, for the paper (add full first names)
-\Author{Ruicheng Feng $^{1,2}$\orcidA{}, Maomao Wang $^{1}$\orcidB{}}
+\Author{Author \orcidA{}}
+%\Author{Ruicheng Feng $^{1,2}$\orcidA{}, Maomao Wang $^{1}$\orcidB{}}
 
@@
 \address{%
-$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com (R.F.); 15620864891@163.com (M.W.)\\
+% $^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com (R.F.); 15620864891@163.com (M.W.)\\
+$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China;\\
 % $^{2}$ \quad Key Laboratory of Digital Manufacturing Technology and Application, Ministry of Education, Lanzhou University of Technology, Lanzhou 730050, China
@@
 \section{Introduction}
-Brittle fracture in Ti-Al alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator \cite{Munz2017}.
-Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}.
+Ductility at room temperature  and brittle rapture failure in Ti-Al alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator \cite{Munz2017}.
 Deformation phenomena of TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
-A great number of literature covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
 Much of the work has been performed on single phase $\gamma$ alloys and PST crystals\cite{Appel2016}.
-% The failure modes of materials have significant influence on the design of material properties in materials science. 
 Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{Tang2014}.
@@
 These defects are known to play a fundamental role in the deformation of the material.
-Nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
-Therefore, it is necessary to study the deformation response of porous materials with the consideration of microstructure evolution.
-
+It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
+Therefore, it is necessary to study the deformation response of intermetallic structural materials with the consideration of microstructure evolution.
+A great number of literature covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
+Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}.
 Defects such as grain boundary, void and segregation plays an significant role in the process of fracture \cite{Larsen2016}.
@@
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
-A previous study on void growth in $\gamma$-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength \cite{Tang2014}.Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nanoscale \cite{Jing2018a,Elkhateeb2018,Tang2014}.
-The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang20}.
+A previous study on void growth in $\gamma$-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength \cite{Tang2014}.
+Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nanoscale \cite{Jing2018a,Elkhateeb2018,Tang2014}.
+The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang2014}.
 
@@
 \subsection{Model Creation of Crystalline}
-
 \begin{figure}[ht]
 	\centering
-	\includegraphics[width=1\linewidth]{img/models}
-	\caption{Overview of model creation}
-	\label{fig:model-creation}
+	\includegraphics[width=1\linewidth]{img/tial-cell}
+	\caption{Unit cell of \rm{TiAl} (a) and $\rm{Ti_3Al}$ (b)}
+	\label{fig:tial-cell}
 \end{figure}
-
-$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure, and $\alpha_2 -\rm TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\ref{}, and the constructing parameters are givin by Table.
-\ref{tab:lattice_parameter}.
-The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \cite{}.
-Periodic boundary conditions (PBC)are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
-The initial dimension of simulation cell is  $L_x =20$ nm, $L_y = $18nm, $L_z = 21$ nm, and each model contains about 4.6 million atoms.
-The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{}, and resulting in the arbitrary shape and orientation of the grains.
-Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model.
-The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig.
-\cite{}.
-The intergranular spherical void was at the center of the simulation cell, as shown in Fig.
-\cite{}.
 
@@
 	\centering
-	\begin{tabular}{l c c l}
+	\begin{tabular}{c c c l}
 	\toprule
@@
 	\midrule
-		$\alpha_2$		& $\rm P6_3/mmc$ 	& $\rm 0_{19}$ 		& $a$ = 0.5765 \\
+	$\alpha_2$ - $\rm{Ti_3Al}$		& $\rm P6_3/mmc$ 	& $\rm 0_{19}$ 		& $a$ = 0.5765 \\
 		&					&					& $c$ = 0.46833 \\
-		$\gamma$		& $\rm tP4$ 		& $\rm L1_0$		& $a$ = 0.3997 \\
+	$\gamma$ - $\rm{TiAl}$ 		& $\rm tP4$ 		& $\rm L1_0$		& $a$ = 0.3997 \\
 		&					&					& $c$ = 0.4062 \\			
@@
 \end{table}
+
+$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure, and $\alpha_2 -\rm TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.
+\ref{fig:unit-cell}, and the constructing parameters are givin by Table.
+\ref{tab:lattice_parameter}.
+The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \ref{fig:model-creation}.
+Periodic boundary conditions (PBC)are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
+The initial dimension of simulation cell is $L_x =20$ \si{\angstrom}, $L_y = $18\si{\angstrom}, $L_z = 21$ \si{\angstrom}, and each model contains about 4.6 million atoms.
+The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{Hirel2015}, and resulting in the arbitrary shape and orientation of the grains.
+Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model.
+The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig.
+\ref{fig:model-creation}(b).
+The intergranular spherical void was at the center of the simulation cell, as shown in Fig.
+\ref{fig:model-creation}(d).
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{img/models}
+	\caption{Model creation: without void defect(b);with intergranular void(c), with inergranular void(d) }
+	\label{fig:model-creation}
+\end{figure}
 
@@
 In order to examine deforamtion behaviour carefully, tensile loading was applied to the model without any types of void defect.
-The whole tension process was saperated into four stages: Stage-1 is typical elasttic part of the deformation, which is originated from $\epsilon = 0$ to $\epsilon = 0.092$, includeing key point 1.
-Stage-2 is yield stage ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6.
-In stage-2, the stress decreased slightly along with the increasing of strain.
-Stage-3 is cracking stage and in this stage the strength of the model have beeen was detracted sharply, we can confine that the structure almost fail after the stage-3.
-Snapshots of atoms configuration are labeled with key points number from 1 to 10, specific list of key points numbers were shown in Table.\ref{tab:key-point}.
+The whole tension process was saperated into four stages: Stage-\uppercase\expandafter{\romannumeral1} is typical elasttic part of the deformation, which is originated from $\epsilon = 0$ to $\epsilon = 0.092$, includeing key point 1.
+Stage-\uppercase\expandafter{\romannumeral2} is yield stage ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6.
+In stage-\uppercase\expandafter{\romannumeral2}, the stress decreased slightly along with the increasing of strain.
+Stage-\uppercase\expandafter{\romannumeral3} is cracking stage and in this stage the strength of the model have beeen was detracted sharply, we can confine that the structure almost fail after the Stage-\uppercase\expandafter{\romannumeral3}.
+Snapshots of atoms configuration are labeled with key points number from 1 to 10, specific list of key points numbers were shown in Table.
+\ref{tab:key-point}.
 Deformation beaviour of the $\alpha_2$ phase had $\gamma$ phase were discussed in the folling subsection respectively.
@@
 
-From Fig.\ref{fig:yield}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
+From Fig.
+\ref{fig:yield}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
 A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
 TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3<11\overline{2}0>$ prism planes\ref{fig:yield}, which is by far the easiest slip system in $\alpha_2$ single crystals.
+
+\subsection{Model Creation of Crystalline}
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{img/plane}
+	\caption{close packed plane of $\gamma\ \rm{phase}\ (\rm{TiAl})$ and $\alpha (\rm{Ti_3Al})$ phase }
+	\label{fig:unit-cell}
+\end{figure}
 
@@
 \subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
+
 The volume defects considered pertain to three-dimensional objects contained within a matrix.
@@
 (5.10)).
-A step, of the width of a burgers vector, will be generated at both sidesof a crystal along the direction of the burgers vector after dislocation traversing the entire crystal, as is shown in \ref{}.
-A small tep will be formed at spherical void surface toward the void interiorafter dislocation absorption at spherical void surfaces, as is shown in \ref{}.
+A step, of the width of a burgers vector, will be generated at both sidesof a crystal along the direction of the burgers vector after dislocation traversing the entire crystal, as is shown in \ref{fig:orowan}.
+A small tep will be formed at spherical void surface toward the void interiorafter dislocation absorption at spherical void surfaces.
 If a great number of dislocation slip along their respective systemstowards the spherical nano void in all directions, and are absorbed at fhe spherical void surfaces, the spherical nano void will eventually shrink from the dash circle to
@@
 	\caption{Orowan process in $\alpha$-phase ($\alpha$ phase atoms have been removed)}
-	\label{fig:dis-void}
+	\label{fig:orowan}
 \end{figure}
@@
 The max stress stress of the simulation cell decreases as the volume of voids are lareger.
-From Fig \ref{}, there is a critical value of void radius about 15A, the void greater than 15A cause serious detraction of strength of material.
+From Fig \ref{fig:stress&strain}, there is a critical value of void radius about 15A, the void greater than 15A cause serious detraction of strength of material.
 Engineering stress is calculated

### 2018-10-20 draft/alexpub.tex
add new

@@
 \usepackage{siunitx}
+\usepackage{multirow}
 \preto{\abstractkeywords}{\nolinenumbers}
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Fracture processes of nanocrystalline metallic materia is affected by dislocation, nano void and other defects.
-Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nano void in $\alpha_2$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
-The results show that voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detract to strength of Ti-Al polycrystalline.}
-
+\abstract{Cold deformation behavior of polycrystalline metallic materia is affected by dislocation, nano void and other defects.
+Existing studies on two phase TiAl alloy covers about deformation behavior mainly on marco scale.
+This paper mainly concern about cold deforamtion mechanism of the two phase TiAl ally at atomic scale, and  the role of void defect in deformation process.
+Molecular dynamics simulation was performed to study the evolution of a spherical nano void in $\alpha_2$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
+Simulation cases of model with different size and position of void were performed.
+The results show that i) $\gamma$ phase is the major deformation source of the two phase alloy; ii) Voids defect detracts the strength of the two phase alloy, however the position of void affect the degree of this substraction: voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detract to strength.}
 % Keywords
@@
 \section{Introduction}
-Ductility at room temperature  and brittle rapture failure in Ti-Al alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator \cite{Munz2017}.
+% and brittle rapture failure 
+Poor Ductility at room temperature in Ti-Al alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator \cite{Munz2017}.
 Deformation phenomena of TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
@@
 Therefore, it is necessary to study the deformation response of intermetallic structural materials with the consideration of microstructure evolution.
+
 A great number of literature covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
 Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}.
+Due to difficulties in observing the dynamic process during deformation wit expeiments, MD simulation has become a effective method to investigate micro deformation mechanism.
 Defects such as grain boundary, void and segregation plays an significant role in the process of fracture \cite{Larsen2016}.
@@
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
-A previous study on void growth in $\gamma$-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength \cite{Tang2014}.
-Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nanoscale \cite{Jing2018a,Elkhateeb2018,Tang2014}.
-The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang2014}.
+The effect of void defect is another great concern about properties of deformation mechanism about of TiAl alloy.
+A previous study on void growth in $\gamma$-TiAl single crystal has reveals that void with high volume fraction detracts yield strength, and emission of dislocation \cite{Tang2014,Xu2015}.
+Evolution of void in ductile polycrystalline was studied in nanoscale with MD simulations.
+\cite{Jing2018a,Elkhateeb2018}.
+The deformation and fracture mechanisms in the duplex microstructure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang2014}.
+It has reveals that existence of voids alone may contribute to strain hardening because theyare barriers to dislocation movement \cite{Xiong2015}.
 
-MD simulations has reveals that existence of voids alone may contribute to strain hardening because theyare barriers to dislocation movement \cite{Xiong2015}
+However, few literatures covers about deformation mechanism of two phase TiAl alloy and the role of void in atomic scale.
+This paper focus on the evolution of microstructure, tend to find out the connection between microstructure and cold deformation behaviour of two phase TiAl alloy.
+MD simulaiton including model creation and analysis method is given in Section \ref{section:method}; Results and discussion are in Section \ref{section:RD}.
 
-\section{Molecular Dynamics Simulation }
-
+\section{Molecular Dynamics Simulation }\label{section:method}
 \subsection{Atomic Potential}
@@
 We performed constant-pressure and constant-temperature (NPT) molecular dynamics simulation.
-The definitnion of potential is as following:
+The definition of potential is as following:
 
@@
 	\toprule
-	\textbf{Phase}			& \textbf{Space group}		& \textbf{Designation} 		& \textbf{Parameters} \\
+	\textbf{Phase}			& {Space group}		& {Designation} 		& {Parameters} \\
 	\midrule
@@
 
-$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure, and $\alpha_2 -\rm TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.
+$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure, and $\alpha_2 -\rm Ti_3Al$ has hcp structure, the two types of initial cells are shown in Fig.
 \ref{fig:unit-cell}, and the constructing parameters are givin by Table.
-\ref{tab:lattice_parameter}.
-The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \ref{fig:model-creation}.
-Periodic boundary conditions (PBC)are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
+In order to study the deformation mechanism of the two phase alloy and the effect of void defect, three types of models were created: Type-1.model without any void defect; Type-2.
+models with different size void inside $\alpha_2$ phase; Type-3.
+models with void at $\alpha_2-\gamma$ interface.
+\ref{tab:lattice_parameter}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \ref{fig:model-creation}. 
+Periodic boundary conditions (PBC) are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
 The initial dimension of simulation cell is $L_x =20$ \si{\angstrom}, $L_y = $18\si{\angstrom}, $L_z = 21$ \si{\angstrom}, and each model contains about 4.6 million atoms.
 The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{Hirel2015}, and resulting in the arbitrary shape and orientation of the grains.
-Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model.
-The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig.
-\ref{fig:model-creation}(b).
-The intergranular spherical void was at the center of the simulation cell, as shown in Fig.
-\ref{fig:model-creation}(d).
+Unixial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$.
 
@@
 	\includegraphics[width=1\linewidth]{img/models}
-	\caption{Model creation: without void defect(b);with intergranular void(c), with inergranular void(d) }
+	\caption{ Model with no void defect (b), with void inside $\alpha_2$ phase (c) with void at $\alpha_2-\gamma$ interface (d)}
 	\label{fig:model-creation}
@@
 \subsection{Analysis method}
-The centrosymmetry parameter is defined as follow:
+In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010a}.Dislocation is visualized by DXA method, and Centrossymmetry parameter(CSP) is used to tell grain boundary from  $\alpha_2$ phase and $\gamma$ phase.
+The definition of CSP is as following:
 
@@
 
-	% \paragraph{Virial Stress}
-	% The atomic stress is calculated using the virial definition :
-	% $$\sigma_t(i)=-$$
-	% $$\sigma_t(i)= $$
+\section{Results and Discussion}\label{section:RD}
+%	/home/alex/Documents/violet/draft/img/perfect-line.pdf
 
-\section{Results and Discussion}
-%	/home/alex/Documents/violet/draft/img/perfect-line.pdf
-In order to examine deforamtion behaviour carefully, tensile loading was applied to the model without any types of void defect.
+In order to examine deformation behavior carefully, tensile loading was applied to the model without any types of void defect.
 The whole tension process was saperated into four stages: Stage-\uppercase\expandafter{\romannumeral1} is typical elasttic part of the deformation, which is originated from $\epsilon = 0$ to $\epsilon = 0.092$, includeing key point 1.
@@
 \ref{tab:key-point}.
-Deformation beaviour of the $\alpha_2$ phase had $\gamma$ phase were discussed in the folling subsection respectively.
+% Deformation beaviour of the $\alpha_2$ phase had $\gamma$ phase were discussed in the following subsection respectively.
 
@@
 		\toprule
-		 \textbf{Key Number} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{9} & \textbf{10}\\
+		\textbf{Key Number} & {1} & {2} & {3} & {4} & {5} & {6} & {7} & {8} & {9} & {10}\\		 \midrule
+		\textbf{Stage} &\uppercase\expandafter{\romannumeral1} &\uppercase\expandafter{\romannumeral1} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3}\\
+
 		\midrule
-		Time/ps	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.20 & 0.21 & 0.22 & 0.23 \\
-		\midrule
-		Strain	& 0 & 0.092 & 0.094 & 0.096 & 0.099 & 0.101 & 0.104 & 0.107 & 0.110 & 0.112 \\
+		% Time/ps	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.20 & 0.21 & 0.22 & 0.23 \\
+		% \midule
+		\textbf{Strain}	& 0 & 0.092 & 0.094 & 0.096 & 0.099 & 0.101 & 0.104 & 0.107 & 0.110 & 0.112 \\
 		\bottomrule
@@
 
-\subsection{Deformation Behaviour of Two Phase Alloys without Void Defects}
-However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in twophase alloys.
-Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
+% Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
+\subsection{Deformation Mechanism of Two Phase TiAl Alloy without Void Defects}
+Deformation process of model without void under uniaxial load is shown by stress-strain curve: Fig.
+\ref{fig:deformation-pf} and snapshots of atom configuration at 10 key points in Fig.
+\ref{fig:Defect}.
+In Fig.\ref{fig:Defect}(a), ordered atoms in $\gamma$ phase grains have been removed, defects inside grains have been left.
+Similarly, the defect of $\alpha_2$ phase has been left.
+Following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in two phase alloys.
+The results show that, at elastic stage(stage 1), the structure of model have little change but the size of simulation box enlarged due to the loading.
+Emission of dislocation and evolution of defects initiated at the end of elastic stage (key point 2).
+A  great number of dislocation emitted inside $\gamma$ phase stage 2, however,  the dislocation inside $\gamma$ phase was emitted after key point 6 in Fig.
+\ref{fig:Defect}(b).
+$\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2[110] and superdislocations with the Burgers vectors $b=[101]$ and $b=1/2[11\overline{2}]$.
+The other potential deformation mode is mechanical twinning along $1/6[11\overline{2}]{111}$.
+
+The orientation of slip is changed because the crystallographically available slip and directions are not continuous across the interface.
+This may significantly reduce the Schmid factor and thus impede slip transfer.
+At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
+Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1}_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
+From Fig.
+\ref{fig:Defect}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
+A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
+TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of [a]-type dislocations with the Burgers vector $b=1/3[11\overline{2}0]$ prism planes\ref{fig:Defect}, which is by far the easiest slip system in $\alpha_2$ single crystals.
 
@@
 	\centering
-		\includegraphics[width=1\linewidth]{img/def-gamma}
-		\label{fig:def-gamma}
-		\caption{Defect evolution in $\gamma$ phase (perfect atoms of $\alpha$ phase have been removed)}
+	\includegraphics[width=1\linewidth]{img/def}
+	\caption{Defect evolution}
+	\label{fig:Defect}
 \end{figure}
 
-The configure of atoms is shown in Fig.\ref{fig:yield}, it can be seen that dislication emission initiate in $\gamma$ pahse in XXX ps, and the deformation canbe mainly confied to the majority $\gamma$ pahse.
-$\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2<110] and superdislocations with the Burgers vectors $b=<101]$ and $b=1/2<11\overline{2}]$.
-The other potential deformation mode is mechanical twinning along $1/6<11\overline{2}]{111}$.
-
-From Fig.
-\ref{fig:yield}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
-A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
-TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3<11\overline{2}0>$ prism planes\ref{fig:yield}, which is by far the easiest slip system in $\alpha_2$ single crystals.
-
-\subsection{Model Creation of Crystalline}
 \begin{figure}[ht]
@@
 		\centering
-		\includegraphics[width=1\linewidth]{img/def-alpha}
-		\label{fig:def-alpha_2}
-		\caption{Defect evolution in $\alpha_2$-phase (perfect atoms in $\alpha_2$ phase have been removed)}
-	\end{figure}
-
-	\begin{figure}[ht]
-		\centering
 		\includegraphics[width=1\linewidth]{"img/disl-gamma"}
@@
 
-In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface.
-This may significantly reduce the Schmid factor and thus impede slip transfer.
-At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
-Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1}_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
-
 The core of a dislocation intersecting an interface often needs to be transformed.
-For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a $<101]$ super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
+For example, an ordinary 1/2[110] dislocation gliding in one $\gamma$ grain has to be converted in to a $[101]$ super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
 At the $\alpha_2/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
@@
 
-Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamella, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
+Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamealla, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
 
@@
 
-The volume defects considered pertain to three-dimensional objects contained within a matrix.
-Three-dimensional structures composed of zero-, one- or two-dimensional defects are not considered here.
-Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, more or less (as possibly associated with the occurrence of incoherent or coherent interfaces; see Sect.
-5.3), the long-range translation symmetry of the matrix.
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{"img/dis-void2"}
+	\caption{Orowan process in $\alpha$-phase ($\alpha$ phase atoms have been removed)}
+	\label{fig:orowan}
+\end{figure}
+
+The role of void can be concluded as two main parts: source of dislocation and obstacles to dislocations.
+Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, more or less (as possibly associated with the occurrence of incoherent or coherent interfaces;the long-range translation symmetry of the matrix.
 They may induce considerable misfit-stress fields and thus can influence material properties pronouncedly.
@@
 A possibly favorable effect of second-phase particles is a contribution to the enhancement of mechanical strength.
-Considering yielding of a material as related to glide of dislocations (Sect.
-5.2.5), any mechanism obstructing dislocation glide improves the mechanical strength.
-In the discussion of the Frank–Read source for dislocation (-line) production (Sect.
-5.2.6) it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of “antagonistic” nature and “block” propagation of the stress field of a migrating dislocation: the second-phase particle acts as “pinning point”.
-It was already indicated that in order that a dislocation can pass two pinning points (A and B in Fig.
-5.13; see Sect.
-5.2.6) a critical shear stress is needed
-that depends on the distance between the obstacles (which can be second-phase particles):
+Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength.
+In the discussion of the Frank–Read source for dislocation (-line) production  it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of “antagonistic” nature and “block” propagation of the stress field of a migrating dislocation: the second-phase particle acts as “pinning point”.
+It was already indicated that in order that a dislocation can pass two pinning points a critical shear stress is needed that depends on the distance between the obstacles (which can be second-phase particles):
 \begin{equation} \label{eq:orowan} 
@@
 
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/dis-void2"}
-	\caption{Orowan process in $\alpha$-phase ($\alpha$ phase atoms have been removed)}
-	\label{fig:orowan}
-\end{figure}
-
 \subsection{The effect of void on the strength of material}
-
-Void of R=10 \AA\ was placed at phase boundary, inside $\alpha_2$ phase grain respectively.
-Effect of void at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}.
-The strength of materails with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
-The results show that the model without void defect has best strength, while the void located inside $\alpha_2$ phase detracts the strength of the material most, and the void at phase boundary have less impact on the strength.
-
-The effect of size is expectable that the greater voids detracts the strength of the materials more, however, it has been observed in the simulation that there is a critical value about 15A for voids at different position.
-The voids larger than 15 A have dramatic detraction to the strength of the material.
-Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by formulation \ref{eq:section}:
-
-	\begin{equation} \label{eq:section} 
-	\sigma^* = \sigma_0 \cdot \frac{A^*}{A_0}
-	\end{equation}
-
-where $\sigma_0$ is the strength of the model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = 36000 {AA}^2$, $A^* $ is section area in consider of the subsection that results from the voids.
-Comparing with the strength determined by molecular dynamics simulation and the results calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behaviour of the materials, thus revolution of defects should be examined carefully.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/fracture3"}
-	\caption{Yield process of the models}
-	\label{fig:yield}
-\end{figure}
 
@@
 
+Void of R=10 \AA\ was placed at phase boundary, inside $\alpha_2$ phase grain respectively.
+Effect of void at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}.
+The strength of materails with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
+The results show that the model without void defect has best strength, while the void located inside $\alpha_2$ phase detracts the strength of the material most, and the void at phase boundary have less impact on the strength.
+
+The effect of size is expectable that the greater voids detracts the strength of the materials more, however, it has been observed in the simulation that there is a critical value about 15A for voids at different position.
+The voids larger than 15 A have dramatic detraction to the strength of the material.
+Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by formulation \ref{eq:section}:
+
+	\begin{equation} \label{eq:section} 
+	\sigma^* = \sigma_0 \cdot \frac{A^*}{A_0}
+	\end{equation}
+
+where $\sigma_0$ is the strength of the model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = 36000 {AA}^2$, $A^* $ is section area in consider of the subsection that results from the voids.
+Comparing with the strength determined by molecular dynamics simulation and the results calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behaviour of the materials, thus revolution of defects should be examined carefully.
+
+%%%	
+%\begin{figure}[ht]
+%%	\includegraphics[width=1\linewidth]{"img/fracture3"}
+%	\caption{Yield process of the models}
+%	\label{fig:yield}
+%\end{figure}
+
 Voids with different size: 2A, 5A, 10A, 15A were placed into the model respectively.
@@
 	$$ \sigma = S/A$$
-The rate of decrease of loading area are smaller comparing with the detraction of strength, so it can be assumed that the yield yield behaviour and strength is much more related with local behaviour of grain boundaries and void.
+The rate of decrease of loading area are smaller comparing with the detraction of strength, so it can be assumed that the yield yield behavior and strength is much more related with local behaviour of grain boundaries and void.
 
@@
 \bibliography{ref/VIOLET-ref.bib}
+\funding{This research was funded by the National Natural Science Fundation of China (No.
+51665030) and the Program for Changjiang Scholars and Innovative Research Team in Universities of the Ministry of Education of China (No.
+IRT-15R30) and the Doctoral Research Foundation of Lanzhou University of Technology.}
 \end{document}

### 2018-10-25 draft/alexpub.tex
add new

@@
 	\includegraphics[width=1\linewidth]{img/tial-cell}
-	\caption{Unit cell of \rm{TiAl} (a) and $\rm{Ti_3Al}$ (b)}
+	\caption{Unit cell of \rm{TiAl} \ref (a) and $\rm{Ti_3Al}$ (b)}
 	\label{fig:tial-cell}
@@
 In order to examine deformation behavior carefully, tensile loading was applied to the model without any types of void defect.
-The whole tension process was saperated into four stages: Stage-\uppercase\expandafter{\romannumeral1} is typical elasttic part of the deformation, which is originated from $\epsilon = 0$ to $\epsilon = 0.092$, includeing key point 1.
-Stage-\uppercase\expandafter{\romannumeral2} is yield stage ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6.
+The whole tension process can be divided into four stages: Stage-\uppercase\expandafter{\romannumeral1} , the elastic stage, ranging from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1; Stage-\uppercase\expandafter{\romannumeral2}, the yield stage ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6.
 In stage-\uppercase\expandafter{\romannumeral2}, the stress decreased slightly along with the increasing of strain.
-Stage-\uppercase\expandafter{\romannumeral3} is cracking stage and in this stage the strength of the model have beeen was detracted sharply, we can confine that the structure almost fail after the Stage-\uppercase\expandafter{\romannumeral3}.
+Stage-\uppercase\expandafter{\romannumeral3} is cracking stage and in this stage the strength of the model have been was detracted sharply, we can confine that the structure almost fail after the Stage-\uppercase\expandafter{\romannumeral3}.
 Snapshots of atoms configuration are labeled with key points number from 1 to 10, specific list of key points numbers were shown in Table.
@@
 \end{table}
-
 % Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
@@
 \ref{fig:Defect}.
-In Fig.\ref{fig:Defect}(a), ordered atoms in $\gamma$ phase grains have been removed, defects inside grains have been left.
+In Fig.\ref{fig:Defect}a, ordered atoms in $\gamma$ phase grains have been removed, defects inside grains have been left.
 Similarly, the defect of $\alpha_2$ phase has been left.
-Following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in two phase alloys.
+Following discussion concentrates on deformation phenomena that rely on the elastoplastic co-deformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in two phase alloys.
 The results show that, at elastic stage(stage 1), the structure of model have little change but the size of simulation box enlarged due to the loading.
@@
 A  great number of dislocation emitted inside $\gamma$ phase stage 2, however,  the dislocation inside $\gamma$ phase was emitted after key point 6 in Fig.
-\ref{fig:Defect}(b).
+\ref{fig:Defect}b.
 $\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2[110] and superdislocations with the Burgers vectors $b=[101]$ and $b=1/2[11\overline{2}]$.
 The other potential deformation mode is mechanical twinning along $1/6[11\overline{2}]{111}$.
+
+\begin{equation}\label{eq:dis1}
+	[\ 0\ 1\ \overline{1}\ ] \to 1/2 [\ 1\ 1\ \overline{2}\ ]+1/2[\ \overline{1}\ 1\ 0\ ]
+\end{equation}
 
@@
 		\includegraphics[width=1\linewidth]{"img/disl-gamma"}
-		\caption{Disloaction in $\gamma$}
+		\caption{Dislocation in $\gamma$}
 		\label{fig:dis-alpha_2}
@@
 These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
-
+\begin{equation}
+u = sin(v)
+\end{equation}	
 Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamealla, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
@@
 	$$\tau = \sigma*m$$
-where m is the Schmid factor :
+where m is the Schmid factor :Science China MaterialsScience China Materials - Springer - Springer
 	$$ m = cos(\phi)cos(\lambda)$$
@@
 \bibliography{ref/VIOLET-ref.bib}
-\funding{This research was funded by the National Natural Science Fundation of China (No.
+\funding{This research was funded by the National Natural Science Foundation of China (No.
 51665030) and the Program for Changjiang Scholars and Innovative Research Team in Universities of the Ministry of Education of China (No.

### 2018-10-30 draft/alexpub.tex
添加结论

--- 2018-10-20 draft/alexpub.tex
@@
  %=================================================================
-\documentclass[materials,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi} 
+\documentclass[metals,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi} 
 \usepackage{siunitx}
@@
 $\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure, and $\alpha_2 -\rm Ti_3Al$ has hcp structure, the two types of initial cells are shown in Fig.
-\ref{fig:unit-cell}, and the constructing parameters are givin by Table.
+\ref{fig:tial-cell}, and the constructing parameters are givin by Table \ref{tab:lattice_parameter}.
 In order to study the deformation mechanism of the two phase alloy and the effect of void defect, three types of models were created: Type-1.model without any void defect; Type-2.
@@
 Periodic boundary conditions (PBC) are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
-The initial dimension of simulation cell is $L_x =20$ \si{\angstrom}, $L_y = $18\si{\angstrom}, $L_z = 21$ \si{\angstrom}, and each model contains about 4.6 million atoms.
+The initial dimension of simulation cell is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model contains about 4.6 million atoms.
 The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{Hirel2015}, and resulting in the arbitrary shape and orientation of the grains.
@@
 %	/home/alex/Documents/violet/draft/img/perfect-line.pdf
-
-In order to examine deformation behavior carefully, tensile loading was applied to the model without any types of void defect.
-The whole tension process was saperated into four stages: Stage-\uppercase\expandafter{\romannumeral1} is typical elasttic part of the deformation, which is originated from $\epsilon = 0$ to $\epsilon = 0.092$, includeing key point 1.
-Stage-\uppercase\expandafter{\romannumeral2} is yield stage ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6.
-In stage-\uppercase\expandafter{\romannumeral2}, the stress decreased slightly along with the increasing of strain.
-Stage-\uppercase\expandafter{\romannumeral3} is cracking stage and in this stage the strength of the model have beeen was detracted sharply, we can confine that the structure almost fail after the Stage-\uppercase\expandafter{\romannumeral3}.
-Snapshots of atoms configuration are labeled with key points number from 1 to 10, specific list of key points numbers were shown in Table.
-\ref{tab:key-point}.
-% Deformation beaviour of the $\alpha_2$ phase had $\gamma$ phase were discussed in the following subsection respectively.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{img/perfect-line2-2}
-	\caption{Deformation process of the model without void defect}
-	\label{fig:deformation-pf}
-\end{figure}
+Deformation process of the model witout void defect is shown in Fig.
+\ref{fig:deformation-pf}.
+The streng of the model without void defect is 5.3 Gpa.
+According to stress response under constan rate of strain rate, the whole tensile process can be divided into four stages:
+Stage - \uppercase\expandafter{\romannumeral1}: elasetic stage,ranging from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1;
+Stage - \uppercase\expandafter{\romannumeral2}: yield stage, ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6;
+Stage - \uppercase\expandafter{\romannumeral3}: cracking stage, ranging from $\epsilon = 0.101$ to $\epsilon = 0.112$, including key pint 7 to 10;
+Stage - \uppercase\expandafter{\romannumeral4}: fracture stage.
+Following discussion concentrates on deformation phenomena that rely on the elastoplastic co-deformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in two phase alloys.
 
@@
 		\midrule
-		% Time/ps	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.20 & 0.21 & 0.22 & 0.23 \\
+		% Time/ps	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.Fu = sin20 & 0.21 & 0.22 & 0.23 \\
 		% \midule
-		\textbf{Strain}	& 0 & 0.092 & 0.094 & 0.096 & 0.099 & 0.101 & 0.104 & 0.107 & 0.110 & 0.112 \\
+		\textbf{Strain}	& 0.05 &  0.092 & 0.092 & 0.096 & 0.099 & 0.101 & 0.104 & 0.107 & 0.110 & 0.112 \\
 		\bottomrule
@@
 
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{img/perfect-line2-2}
+	\caption{Deformation process of the model without void defect}
+	\label{fig:deformation-pf}
+\end{figure}
+
 % Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
 \subsection{Deformation Mechanism of Two Phase TiAl Alloy without Void Defects}
-Deformation process of model without void under uniaxial load is shown by stress-strain curve: Fig.
-\ref{fig:deformation-pf} and snapshots of atom configuration at 10 key points in Fig.
+
+\begin{figure}[ht] 
+	\centering
+	\includegraphics[width=1\linewidth]{img/def}
+	\caption{Microstrucutre evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) at key point 1 to 10}
+	\label{fig:Defect}
+\end{figure}
+
+Deformation process of model without void under uniaxial load is shown by stress-strain curve Fig.
+\ref{fig:deformation-pf} and snapshots of atom configuration at the 10 key points in Fig.
 \ref{fig:Defect}.
-In Fig.\ref{fig:Defect}(a), ordered atoms in $\gamma$ phase grains have been removed, defects inside grains have been left.
-Similarly, the defect of $\alpha_2$ phase has been left.
-Following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in two phase alloys.
-The results show that, at elastic stage(stage 1), the structure of model have little change but the size of simulation box enlarged due to the loading.
+Atoms with ordered orientation  of $\gamma$ phase grains have been removed in Fig.\ref{fig:Defect}a,\ $\alpha_2$ phase and defects inside grains have been left.
+Similarly, $\gamma$ phase grain have been removed in Fig.
+\ref{fig:Defect}b, the defect of $\alpha_2$ phase has been left.
+
+The results show that, at elastic stage(stage\uppercase\expandafter{\romannumeral1}), the structure of model have little change but the size of simulation box enlarged due to the loading, the deformation of the two phase are compatible.
 Emission of dislocation and evolution of defects initiated at the end of elastic stage (key point 2).
 A  great number of dislocation emitted inside $\gamma$ phase stage 2, however, the dislocation inside $\gamma$ phase was emitted after key point 6 in Fig.
-\ref{fig:Defect}(b).
-$\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2[110] and superdislocations with the Burgers vectors $b=[101]$ and $b=1/2[11\overline{2}]$.
-The other potential deformation mode is mechanical twinning along $1/6[11\overline{2}]{111}$.
+\ref{fig:Defect}b.
+The deformation of $\alpha_2$ phase is even more earlier than $\gamma$ phase druing yied stage, thus local displacement of two phase are incompatible during yield stage.
+$\gamma$ phase (TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2[110] and super dislocations with the Burgers vectors $b=[101]$ and $b=1/2[11\overline{2}]$.
+The other potential deformation mode is mechanical twinning have been repored along $1/6[11\overline{2}]{111}$, have not been observed in the simulation because of room temperature cannot offer enough energy for dislocation nucleation.
+
+\begin{equation}\label{eq:dis1}
+	[\ 0\ 1\ \overline{1}\ ] \to 1/2 [\ 1\ 1\ \overline{2}\ ]+1/2[\ \overline{1}\ 1\ 0\ ]
+\end{equation}
+The velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it can be written as
+
+\begin{equation}\label{eq:temp-dis}
+v = v_0 \exp(-\Delta H(\tau^*)/kT)
+\end{equation}
+
+where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions.
+The effect of temperature on the mobility can be obtained under different loading conditions, thus  $\Delta H(\tau^*)$ are different.
+We choose cases with different loading condition$\Delta H(\tau^*)$  , normalized velocity can be  case 1 to case 3  in a increse order of $\Delta H(\tau^*)$.
+t
 
@@
 
+%\begin{figure}[ht]
+%	\centering
+%	\includegraphics[width=1\linewidth]{img/plane}
+%	\caption{close packed plane of $\gamma\ \rm{phase}\ (\rm{TiAl})$ and $\alpha (\rm{Ti_3Al})$ phase }
+%	\label{fig:unit-cell}
+%\end{figure}
+
 	\begin{figure}[ht]
 		\centering
-	\includegraphics[width=1\linewidth]{img/def}
-	\caption{Defect evolution}
-	\label{fig:Defect}
+		\includegraphics[width=1\linewidth]{"img/disl-gamma"}
+		\caption{Dislocation in $\gamma$}
+		\label{fig:dis-alpha_2}
 	\end{figure}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{img/plane}
-	\caption{close packed plane of $\gamma\ \rm{phase}\ (\rm{TiAl})$ and $\alpha (\rm{Ti_3Al})$ phase }
-	\label{fig:unit-cell}
-\end{figure}
-
-	\begin{figure}[ht]
+	\begin{minipage}{0.495\textwidth}
+		\includegraphics[width=1\linewidth]{img/temp}
 		\centering
-		\includegraphics[width=1\linewidth]{"img/disl-gamma"}
-		\caption{Disloaction in $\gamma$}
-		\label{fig:dis-alpha_2}
+		\caption{Mobility of dislocation\\
+		}
+		\label{fig:temp}
+	\end{minipage}	
+	\hfill
+	\begin{minipage}{0.495\textwidth}		
+		\includegraphics[width=1\linewidth]{img/disum}
+		\centering
+		\caption{Strength of models}
+		\label{fig:disum}
+	\end{minipage}
 \end{figure}
@@
 
-\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/dis-void2"}
-	\caption{Orowan process in $\alpha$-phase ($\alpha$ phase atoms have been removed)}
-	\label{fig:orowan}
-\end{figure}
-
-The role of void can be concluded as two main parts: source of dislocation and obstacles to dislocations.
-Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, more or less (as possibly associated with the occurrence of incoherent or coherent interfaces;the long-range translation symmetry of the matrix.
-They may induce considerable misfit-stress fields and thus can influence material properties pronouncedly.
-Such stress fields surrounding the second-phase particles can be due to misfit between the volume occupied by the second-phase particle when unconstrained and the space (“hole”) put at its disposal by the matrix.
-Such misfit can arise due to specific volume differences induced by precipitation or by different thermal expansion or shrinkage upon heating or cooling the specimen.
-A possibly favorable effect of second-phase particles is a contribution to the enhancement of mechanical strength.
-Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength.
-In the discussion of the Frank–Read source for dislocation (-line) production  it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of “antagonistic” nature and “block” propagation of the stress field of a migrating dislocation: the second-phase particle acts as “pinning point”.
-It was already indicated that in order that a dislocation can pass two pinning points a critical shear stress is needed that depends on the distance between the obstacles (which can be second-phase particles):
-\begin{equation} \label{eq:orowan} 
-\tau_0 = Gb/d
-\end{equation}
-
-where d represents the distance between A and B and thus reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution.
-This mechanism for hardening is designated as the Orowan process (with $\tau_0$ as the Orowan
-(shear) stress ; sgitee also Sect.
-11.14.4).
-As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles (see Fig.
-5.27).
-Consequently, the effective average distance between the second-phase particles has decreased to d which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide (cf.
-(5.10)).
-A step, of the width of a burgers vector, will be generated at both sidesof a crystal along the direction of the burgers vector after dislocation traversing the entire crystal, as is shown in \ref{fig:orowan}.
-A small tep will be formed at spherical void surface toward the void interiorafter dislocation absorption at spherical void surfaces.
-If a great number of dislocation slip along their respective systemstowards the spherical nano void in all directions, and are absorbed at fhe spherical void surfaces, the spherical nano void will eventually shrink from the dash circle to
-
 \subsection{The effect of void on the strength of material}
-
 \begin{figure}[ht]
@@
 
-According to Schmid's law:
-	$$\tau = \sigma*m$$
-where m is the Schmid factor :
-	$$ m = cos(\phi)cos(\lambda)$$
+\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{"img/dis-void2"}
+	\caption{Orowan process in $\alpha$-phase ($\alpha$ phase atoms have been removed)}
+	\label{fig:orowan}
+\end{figure}
+
+The role of void can be concluded as two main parts: source of dislocation and obstacles to dislocations.
+Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, more or less (as possibly associated with the occurrence of incoherent or coherent interfaces;the long-range translation symmetry of the matrix.
+They may induce considerable misfit-stress fields and thus can influence material properties pronouncedly.
+Such stress fields surrounding the second-phase particles can be due to misfit between the volume occupied by the second-phase particle when unconstrained and the space (“hole”) put at its disposal by the matrix.
+Such misfit can arise due to specific volume differences induced by precipitation or by different thermal expansion or shrinkage upon heating or cooling the specimen.
+A possibly favorable effect of second-phase particles is a contribution to the enhancement of mechanical strength.
+Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength.
+In the discussion of the Frank–Read source for dislocation (-line) production  it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of “antagonistic” nature and “block” propagation of the stress field of a migrating dislocation: the second-phase particle acts as “pinning point”.
+It was already indicated that in order that a dislocation can pass two pinning points a critical shear stress is needed that depends on the distance between the obstacles (which can be second-phase particles):
+\begin{equation} \label{eq:orowan} 
+\tau_0 = Gb/d
+\end{equation}
+
+where d represents the distance between A and B and thus reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution.
+This mechanism for hardening is designated as the Orowan process (with $\tau_0$ as the Orowan
+(shear) stress ; sgitee also Sect.
+11.14.4).
+As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles (see Fig.
+5.27).
+Consequently, the effective average distance between the second-phase particles has decreased to d which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide (cf.
+(5.10)).
+A step, of the width of a burgers vector, will be generated at both sidesof a crystal along the direction of the burgers vector after dislocation traversing the entire crystal, as is shown in \ref{fig:orowan}.
+A small tep will be formed at spherical void surface toward the void interiorafter dislocation absorption at spherical void surfaces.
+If a great number of dislocation slip along their respective systemstowards the spherical nano void in all directions, and are absorbed at fhe spherical void surfaces, the spherical nano void will eventually shrink from the dash circle to
+\section{conclusion}
+In this paper, annealing processes of $\gamma$-TiAl alloy after introducing residual stress into prepressing are simulated, and the dynamic evolution process of microdefects and the distribution of residual stress before and after annealing are investigated.
+The conclusions are as follows:
+
+(1) In the cold defromation processs of two phase TiAl alloy, $\gamma$ phase is the major deforamtion components of the alloy. The typical deformation mechanism of the gamma phase in tial
+
+(2)
 
@@
 \bibliography{ref/VIOLET-ref.bib}
-\funding{This research was funded by the National Natural Science Fundation of China (No.
+\funding{This research was funded by the National Natural Science Foundation of China (No.
 51665030) and the Program for Changjiang Scholars and Innovative Research Team in Universities of the Ministry of Education of China (No.
 IRT-15R30) and the Doctoral Research Foundation of Lanzhou University of Technology.}
+
 \end{document}

### 2018-10-30 code/Temp.py

@@ -1,0 +1,32 @@
+import os
+import os.path
+
+#plt.rcParams["font.family"] = 'Times New Roman'
+import matplotlib.pyplot as plt
+plt.rcParams.update({'font.size': 12})
+#csfont = {'fontname':'Times New Roman'}
+#plt.rcParams["font.family"] = "Times New Roman"
+WDIR = os.path.dirname(__file__)
+# loadpath = os.path.join(WDIR,'data','stress_strain')
+writepath = os.path.join(WDIR,'..','draft','img')
+import numpy as np
+import matplotlib.pyplot as plt
+
+T = np.linspace(0,1200,1500)
+key = 20*np.e**(-150/298)/20
+key1=[298,298]
+key2=[0,1]
+u = 20*np.e**(-300/T)/20
+v = 20*np.e**(-350/T)/20
+w = 20*np.e**(-450/T)/20
+plt.xlabel('Temperature / K')
+plt.ylabel('Mobility of Dislocation')
+plt.ylim(ymax=1)
+plt.plot(key1,key2)
+plt.plot(T,u,label='Case 1')
+plt.plot(T,v,label='Case 2')
+plt.plot(T,w,label='Case 3')
+plt.legend(frameon=False)
+plt.savefig(os.path.join(writepath, 'temp.pdf'))
+
+plt.show()

### 2018-10-30 code/dissum.py

@@ -1,0 +1,61 @@
+
+import os
+import os.path
+
+#plt.rcParams["font.family"] = 'Times New Roman'
+import matplotlib.pyplot as plt
+plt.rcParams.update({'font.size': 12})
+#csfont = {'fontname':'Times New Roman'}
+#plt.rcParams["font.family"] = "Times New Roman"
+WDIR = os.path.dirname(__file__)
+# loadpath = os.path.join(WDIR,'data','stress_strain')
+writepath = os.path.join(WDIR,'..','draft','img')
+import numpy as np
+import matplotlib.pyplot as plt
+
+pf = [744, 290, 212, 530]
+shockley = [1343, 1470, 3581, 4367]
+stair_rode = [0, 123, 259, 295]
+hirth = [0, 407, 1100, 557]
+frank = [0, 375, 211, 500]
+
+
+# data to plot
+n_groups = 4
+
+# create plot
+fig, ax = plt.subplots()
+index = np.arange(n_groups)
+bar_width = 0.22
+opacity = 0.8
+
+rects1 = plt.bar(index, pf, bar_width,
+                 alpha=opacity,
+                # color='b',
+                 label='Perfect')
+
+rects2 = plt.bar(index + bar_width, shockley, bar_width,
+                 alpha=opacity,
+                 #color='g',
+                 label='Shockley')
+
+rects3 = plt.bar(index + 2*bar_width, stair_rode, bar_width,
+                 alpha=opacity,
+                 #color='b',
+                 label='Stair-rod')
+
+rects4 = plt.bar(index + 3*bar_width, frank, bar_width,
+                 alpha=opacity,
+                 #color='g',
+                 label='Frank')
+
+plt.xlabel('Stage')
+plt.ylabel('Dislocation length / A')
+# plt.title('Scores by person')
+plt.xticks(index + bar_width, ('Initial', 'Before yield', 'After yield', 'Cracked'))
+plt.legend(frameon = False)
+
+plt.savefig(os.path.join(writepath, 'disum.pdf'))
+
+#plt.tight_layout()
+plt.show()

### 2018-10-30 code/exp.py

@@ -1,0 +1,60 @@
+# 读取输出文件，绘制应力应变曲线
+'''
+violet
+├── code
+│   ├── data
+│   │   ├── size
+│   │   ├── stress_strain
+│   │   └── surf
+│   └── pict
+└── draft
+    ├── bkp
+    ├── img
+    ├── material
+    └── ref
+'''
+
+import os
+import os.path
+from os import listdir
+import matplotlib.pyplot as plt
+import pandas as pd
+plt.rcParams["font.family"] = 'Times New Roman'
+import matplotlib.pyplot as plt
+plt.rcParams.update({'font.size': 12})
+#csfont = {'fontname':'Times New Roman'}
+#plt.rcParams["font.family"] = "Times New Roman"
+WDIR = os.path.dirname(__file__)
+loadpath = os.path.join(WDIR,'data','stress_strain')
+writepath = os.path.join(WDIR,'..','draft','img')
+# pre-set head name
+prop = ['step', 'strain', 'stress', 'energy']
+# import data from .csv file:
+#ds1 = pd.read_csv(os.path.join(loadpath,'aa.csv'), sep=' ', skiprows=1, names=prop)
+ds2 = pd.read_csv(os.path.join(loadpath,'ag.csv'), sep=' ', skiprows=1, names=prop)
+ds3 = pd.read_csv(os.path.join(loadpath,'pf.csv'), sep=' ', skiprows=1, names=prop)
+ds4 = pd.read_csv(os.path.join(loadpath,'ia.csv'), sep=' ', skiprows=1, names=prop)
+fct = 10e6
+px2=ds2.step/fct
+px3=ds3.step/fct
+px4=ds4.step/fct
+
+# plot lines
+#p1 = plt.plot(ds1.step, ds1.stress, label='aa')
+p2 = plt.plot(px2, ds2.stress, label='ag')
+p3 = plt.plot(px3, ds3.stress, label='pf')
+p4 = plt.plot(px4, ds4.stress, label='ia')
+# config title and label
+
+#plt.title('stress-strain curve')
+plt.xlabel('Strain')
+plt.xlim(xmax=0.035)
+plt.ylim(ymax=6)
+plt.ylabel('Stress (GPa)')
+plt.legend(frameon=False)
+plt.savefig(os.path.join(writepath, 'allline.pdf'))
+
+plt.show()
+# /home/alex/violet/all.line.pdf
+# /home/alex/violet/code/pict/area.png
+# /home/alex/violet/draft/img/ag.pngf

### 2018-10-30 code/temp.py

@@ -1,0 +1,16 @@
+import numpy as np
+import matplotlib.pyplot as plt 
+T = np.linspace(0,1000,1500)
+key = 20*np.e**(-150/298)/20
+key1=[298,298]
+key2=[0,key]
+u = 20*np.e**(-150/T)/20
+v = 20*np.e**(-250/T)/20
+w = 20*np.e**(-100/T)/20
+plt.xlabel('Temperature/K')
+plt.ylabel('Normalized Velocity of Dislocation')
+plt.plot(key1,key2)
+plt.plot(T,u,label='T1')
+plt.plot(T,v,label='T2')
+plt.plot(T,w,label='T3')
+plt.show()

### 2018-11-01 draft/alexpub.tex
add new

@@
 % Keywords
-\keyword{$\alpha_2+\gamma$ two phase TiAl alloy; void; molecular dynamics}
+\keyword{two phase TiAl alloy; void; molecular dynamics}
 
@@
 	\centering
-	\includegraphics[width=1\linewidth]{img/tial-cell}
+	\includegraphics[width=1\linewidth]{img/tial-cell2}
 	\caption{Unit cell of \rm{TiAl} (a) and $\rm{Ti_3Al}$ (b)}
@@
 models with void at $\alpha_2-\gamma$ interface.
-\ref{tab:lattice_parameter}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \ref{fig:model-creation}. 
+\ref{tab:lattice_parameter}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure . 
 Periodic boundary conditions (PBC) are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
@@
 Unixial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{img/models}
-	\caption{ Model with no void defect (b), with void inside $\alpha_2$ phase (c) with void at $\alpha_2-\gamma$ interface (d)}
-	\label{fig:model-creation}
-\end{figure}
 
@@
 \section{Results and Discussion}\label{section:RD}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{img/perfect-line2-2}
+	\caption{Deformation process of the model without void defect}
+	\label{fig:deformation-pf}
+\end{figure}
+
 %	/home/alex/Documents/violet/draft/img/perfect-line.pdf
@@
 
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{img/perfect-line2-2}
-	\caption{Deformation process of the model without void defect}
-	\label{fig:deformation-pf}
-\end{figure}
-
 % Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
@@
 	\centering
-	\includegraphics[width=1\linewidth]{img/def}
+	\includegraphics[width=1\linewidth]{img/def2}
 	\caption{Microstrucutre evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) at key point 1 to 10}
@@
 \subsection{The effect of void on the strength of material}
+
 \begin{figure}[ht]
 	\centering
-	\begin{minipage}{0.495\textwidth}
-		\includegraphics[width=1\linewidth]{img/allline}
-		\centering
-		\caption{Stress-Strain}
-		\label{fig:stress&strain}
-	\end{minipage}	
-	\hfill
-	\begin{minipage}{0.495\textwidth}		
-		\includegraphics[width=1\linewidth]{img/effect_of_vol}
-		\centering
-		\caption{Strength of models}
-		\label{fig:strength}
-	\end{minipage}
+	\includegraphics[width=1\linewidth]{img/models}
+	\caption{ Model with no void defect (b), with void inside $\alpha_2$ phase (c) with void at $\alpha_2-\gamma$ interface (d)}
+	\label{fig:model-creation}
 \end{figure}
@@
 Comparing with the strength determined by molecular dynamics simulation and the results calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behaviour of the materials, thus revolution of defects should be examined carefully.
+
+\begin{figure}[ht]
+	\centering
+	\begin{minipage}{0.495\textwidth}
+		\includegraphics[width=1\linewidth]{img/allline}
+		\centering
+		\caption{Stress-Strain}
+		\label{fig:stress&strain}
+	\end{minipage}	
+	\hfill
+	\begin{minipage}{0.495\textwidth}		
+		\includegraphics[width=1\linewidth]{img/effect_of_vol}
+		\centering
+		\caption{Strength of models}
+		\label{fig:strength}
+	\end{minipage}
+\end{figure}
 
@@
 where d represents the distance between A and B and thus reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution.
-This mechanism for hardening is designated as the Orowan process (with $\tau_0$ as the Orowan
-(shear) stress ; sgitee also Sect.
-11.14.4).
-As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles (see Fig.
-5.27).
-Consequently, the effective average distance between the second-phase particles has decreased to d which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide (cf.
-(5.10)).
-A step, of the width of a burgers vector, will be generated at both sidesof a crystal along the direction of the burgers vector after dislocation traversing the entire crystal, as is shown in \ref{fig:orowan}.
+This mechanism for hardening is designated as the Orowan process (with $\tau_0$ as the Orowan (shear) stress.
+As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles.
+Consequently, the effective average distance between the second-phase particles has decreased to d which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide.
+The width of a burgers vector, will be generated at both sidesof a crystal along the direction of the burgers vector after dislocation traversing the entire crystal, as is shown in \ref{fig:orowan}.
 A small tep will be formed at spherical void surface toward the void interiorafter dislocation absorption at spherical void surfaces.
-If a great number of dislocation slip along their respective systemstowards the spherical nano void in all directions, and are absorbed at fhe spherical void surfaces, the spherical nano void will eventually shrink from the dash circle to
+If a great number of dislocation slip along their respective systemstowards the spherical nano void in all directions, and are absorbed at fhe spherical void surfaces, the spherical nano void will eventually shrink from the dash circle
 \section{conclusion}
@@
 
-(1) In the cold defromation processs of two phase TiAl alloy, $\gamma$ phase is the major deforamtion components of the alloy. The typical deformation mechanism of the gamma phase in tial
+(1) .
 
-(2)
+(2) .
 

### 2018-11-01 draft/alexpub.tex
add mark
add introduction

@@
 Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{Tang2014}.
-The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study of detailed mechanisms of deformation and cracking.
-These defects are known to play a fundamental role in the deformation of the material.
-It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
-Therefore, it is necessary to study the deformation response of intermetallic structural materials with the consideration of microstructure evolution.
 
@@
 Defects such as grain boundary, void and segregation plays an significant role in the process of fracture \cite{Larsen2016}.
-In order to understanding the mechanism of brittle fracture, multi-scale methods from micro to marco scale have been applied to investigate the behavior of fracture.
+Multiscale method have been applied to study deformation behavior polycrystalline with single aluminum element \cite{Groh2009} and single titanium element \cite{Liu2018}.
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
+
+The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study of detailed mechanisms of deformation and cracking.
+These defects are known to play a fundamental role in the deformation of the material.
+It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
+Therefore, it is necessary to study the deformation response of intermetallic structural materials with the consideration of microstructure evolution.
 The effect of void defect is another great concern about properties of deformation mechanism about of TiAl alloy.
 A previous study on void growth in $\gamma$-TiAl single crystal has reveals that void with high volume fraction detracts yield strength, and emission of dislocation \cite{Tang2014,Xu2015}.
-Evolution of void in ductile polycrystalline was studied in nanoscale with MD simulations.
+Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations.
 \cite{Jing2018a,Elkhateeb2018}.
@@
 However, few literatures covers about deformation mechanism of two phase TiAl alloy and the role of void in atomic scale.
+
+Apart from the difficulty in component manufacturing, defects will form inevitably, e.g.
+as micro-pores and loosens from casting, surface scratches from machining, and surface indentation from mishandling, and the component reliability can be influenced greatly by these defects.
+
+Regarding the effects of various defects on the behavior of different materials, a lot of investigations have been carried out which show that point defects may affect the properties of materials greatly.
+The strength of irradiated copper was controlled by dislocation–irradiation defect interactions[10].
+Both polycrystals and single crystals of Fe–40 at.
+Al displayed a rapid initial increase in yield stress with increasing vacancy concentration, followed by a much slower increase at high vacancy concentrations[11].
+TiAl, as a relatively brittle material, may be more sensitive to these defects, but the mechanistic study of how different defects influence their properties is limited.
+It has been shown that artificial rectangular micro-slots in the midsection of Ti–48Al–2Cr–2Nb specimens would decrease its fatigue limit[12].
+The high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy could also be lowered by surface defects such as small notches[13].
+The resis- tance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was markedly reduced due to earlier crack initiation.
+The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small micro-cracks in the damaged zone.
+The principal effect of foreign-object damage in
+
+[11] D. Kiener, P. Hosemann, S.A. Maloy, A.M. Minor, Nat. Mater. 10 (2011) 608–613.
+[12] Y. Yang, I. Baker, Intermetallics 6 (1998) 167–175.
+[13] M. Filippini, S. Beretta, L. Patriarca, G. Pasquero, S. Sabbadini, 11th International Conference on the Mechanical Behavior of Materials (Icm11), 10 (2011) 3677–3682.
+[14] M. Nazmy, M. Staubli, G. Onofrio, V. Lupinc, Scripta Mater. 45 (2001) 787–792.
+
 This paper focus on the evolution of microstructure, tend to find out the connection between microstructure and cold deformation behaviour of two phase TiAl alloy.
@@
 A small tep will be formed at spherical void surface toward the void interiorafter dislocation absorption at spherical void surfaces.
-If a great number of dislocation slip along their respective systemstowards the spherical nano void in all directions, and are absorbed at fhe spherical void surfaces, the spherical nano void will eventually shrink from the dash circle
+If a great number of dislocation slip along their respective systemstowards the spherical nano void in all directions, and are absorbed at spherical void surfaces, the spherical nano void will eventually shrink from the dash circle
 \section{conclusion}
-In this paper, annealing processes of $\gamma$-TiAl alloy after introducing residual stress into prepressing are simulated, and the dynamic evolution process of microdefects and the distribution of residual stress before and after annealing are investigated.
+In this paper, deformation behavior of two phase TiAl alloy under tensile loading was simulated with MD method.
+The mechanism of deformation was investigated under atomic scale, and the effect of void defect on the properties of two phase TiAl alloy was also studied.
 The conclusions are as follows:
 
-(1) .
+(1) The major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha$ phase is harder to be deformed, this inhomogene results in cracks at interface of the two phase.
 
-(2) .
+(2) The effect of the void defect on the strength of the two phase alloy is sensitive to the location of the void.
+The void located inside the grain decrease the strength to the material because this type defect weaken the grain thus caused even more serious stress concentration, and the void at phase boundary have less impact on the strength of the material because this type void help to release of local stress at grain boundary.
 
@@
 IRT-15R30) and the Doctoral Research Foundation of Lanzhou University of Technology.}
-
+mark
 \end{document}

### 2018-11-04 draft/alexpub.tex
add intro

@@
 The effect of void defect is another great concern about properties of deformation mechanism about of TiAl alloy.
-A previous study on void growth in $\gamma$-TiAl single crystal has reveals that void with high volume fraction detracts yield strength, and emission of dislocation \cite{Tang2014,Xu2015}.
+A previous study on void growth in $\gamma$-TiAl single crystal has reveals that void with high volume fraction detracts yield strength, and emission of dislocation \cite{Tang2014, Xu2011}.
 Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations.
@@
 It has reveals that existence of voids alone may contribute to strain hardening because theyare barriers to dislocation movement \cite{Xiong2015}.
-
 However, few literatures covers about deformation mechanism of two phase TiAl alloy and the role of void in atomic scale.
-
-Apart from the difficulty in component manufacturing, defects will form inevitably, e.g.
-as micro-pores and loosens from casting, surface scratches from machining, and surface indentation from mishandling, and the component reliability can be influenced greatly by these defects.
-
-Regarding the effects of various defects on the behavior of different materials, a lot of investigations have been carried out which show that point defects may affect the properties of materials greatly.
-The strength of irradiated copper was controlled by dislocation–irradiation defect interactions[10].
-Both polycrystals and single crystals of Fe–40 at.
-Al displayed a rapid initial increase in yield stress with increasing vacancy concentration, followed by a much slower increase at high vacancy concentrations[11].
-TiAl, as a relatively brittle material, may be more sensitive to these defects, but the mechanistic study of how different defects influence their properties is limited.
-It has been shown that artificial rectangular micro-slots in the midsection of Ti–48Al–2Cr–2Nb specimens would decrease its fatigue limit[12].
-The high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy could also be lowered by surface defects such as small notches[13].
-The resis- tance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was markedly reduced due to earlier crack initiation.
+Defects are inevitable as micro-pores and loosen from casting, and in the actual work environment with radiation.
+A lot work carried out on the the effect of various defects on the behavior of different materials, show that point defects may affect the properties of materials greatly.
+The mechanical properties of irradiated copper is affected by the interaction between irradiation and dislocation \cite{Kiener2011}.
+Vacancy concentration in single crystal and polycrystal Fe–40 at.
+Al bulk results in an increase of strength \cite{Yang1998}.
+Ti-Al alloy is a type of typical brittle material, thus it can be assumed that its properties are seneitive to the existence of void defect.
+Surface defect such as small notches can caused lower high ccle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$ - TiAl is also also lowered by point defect \cite{Wu2016}.
+The resistance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was markedly reduced due to earlier crack initiation.
 The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small micro-cracks in the damaged zone.
-The principal effect of foreign-object damage in
-
-[11] D. Kiener, P. Hosemann, S.A. Maloy, A.M. Minor, Nat. Mater. 10 (2011) 608–613.
-[12] Y. Yang, I. Baker, Intermetallics 6 (1998) 167–175.
-[13] M. Filippini, S. Beretta, L. Patriarca, G. Pasquero, S. Sabbadini, 11th International Conference on the Mechanical Behavior of Materials (Icm11), 10 (2011) 3677–3682.
-[14] M. Nazmy, M. Staubli, G. Onofrio, V. Lupinc, Scripta Mater. 45 (2001) 787–792.
 

### 2018-11-06 draft/alexpub.tex
edited

@@
 % \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
-\Title{Atomic Investigation on Cold Deformation Behavior of Two Phase TiAl Polycrystalline with and without Void Defect}
+\Title{Atomic Investigation on Cold Deformation Behavior of Two Phase TiAl Polycrystal with and without Void Defect}
 % Author Orchid ID: enter ID or remove command
@@
 Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}.
-Due to difficulties in observing the dynamic process during deformation wit expeiments, MD simulation has become a effective method to investigate micro deformation mechanism.
+Due to difficulties in observing the dynamic process during deformation wit experiments, MD simulation has become a effective method to investigate micro deformation mechanism.
 Defects such as grain boundary, void and segregation plays an significant role in the process of fracture \cite{Larsen2016}.
-Multiscale method have been applied to study deformation behavior polycrystalline with single aluminum element \cite{Groh2009} and single titanium element \cite{Liu2018}.
+Multiscale method have been applied to study deformation behavior polycrystal with single aluminum element \cite{Groh2009} and single titanium element \cite{Liu2018}.
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
@@
 It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
-Therefore, it is necessary to study the deformation response of intermetallic structural materials with the consideration of microstructure evolution.
+Therefore, it is necessary to study the deformation response of intermetallics structural materials with the consideration of microstructure evolution.
 The effect of void defect is another great concern about properties of deformation mechanism about of TiAl alloy.
@@
 The deformation and fracture mechanisms in the duplex microstructure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang2014}.
-It has reveals that existence of voids alone may contribute to strain hardening because theyare barriers to dislocation movement \cite{Xiong2015}.
+It has reveals that existence of voids alone may contribute to strain hardening because they are barriers to dislocation movement \cite{Xiong2015}.
 However, few literatures covers about deformation mechanism of two phase TiAl alloy and the role of void in atomic scale.
@@
 Al bulk results in an increase of strength \cite{Yang1998}.
-Ti-Al alloy is a type of typical brittle material, thus it can be assumed that its properties are seneitive to the existence of void defect.
-Surface defect such as small notches can caused lower high ccle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$ - TiAl is also also lowered by point defect \cite{Wu2016}.
+Ti-Al alloy is a type of typical brittle material, thus it can be assumed that its properties are sensitive to the existence of void defect.
+Surface defect such as small notches can caused lower high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$ - TiAl is also also lowered by point defect \cite{Wu2016}.
 The resistance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was markedly reduced due to earlier crack initiation.
@@
 
-This paper focus on the evolution of microstructure, tend to find out the connection between microstructure and cold deformation behaviour of two phase TiAl alloy.
-MD simulaiton including model creation and analysis method is given in Section \ref{section:method}; Results and discussion are in Section \ref{section:RD}.
+This paper focus on the evolution of microstructure, tend to find out the connection between microstructure and cold deformation behavior of two phase TiAl alloy.
+MD simulation including model creation and analysis method is given in Section \ref{section:method}; Results and discussion are in Section \ref{section:RD}.
 
@@
 The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{Hirel2015}, and resulting in the arbitrary shape and orientation of the grains.
-Unixial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$.
+Uniaxial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$.
 
 \subsection{Analysis method}
-In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010a}.Dislocation is visualized by DXA method, and Centrossymmetry parameter(CSP) is used to tell grain boundary from  $\alpha_2$ phase and $\gamma$ phase.
+In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010a}.Dislocation is visualized by DXA method, and Centro-symmetry parameter(CSP) is used to tell grain boundary from  $\alpha_2$ phase and $\gamma$ phase.
 The definition of CSP is as following:
@@
 where $\vec{R_i}$ and ${\vec{R}}_{i+6}$ are the vectors corresponding to the six pairs of opposite nearest neighbors in the fcc lattice.
-The centrosymmetry parameter(CSP) is zero for atoms in a perfect lattice.
+The centro-symmetry parameter(CSP) is zero for atoms in a perfect lattice.
 In other words, if the lattice is distorted the value of P will not be zero.
@@
 %	/home/alex/Documents/violet/draft/img/perfect-line.pdf
-Deformation process of the model witout void defect is shown in Fig.
+Deformation process of the model without void defect is shown in Fig.
 \ref{fig:deformation-pf}.
-The streng of the model without void defect is 5.3 Gpa.
-According to stress response under constan rate of strain rate, the whole tensile process can be divided into four stages:
-Stage - \uppercase\expandafter{\romannumeral1}: elasetic stage,ranging from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1;
+The strength of the model without void defect is 5.3 GPa.
+According to stress response under constant rate of strain rate, the whole tensile process can be divided into four stages:
+Stage - \uppercase\expandafter{\romannumeral1}: elastic stage,ranging from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1;
 Stage - \uppercase\expandafter{\romannumeral2}: yield stage, ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6;
@@
 Stage - \uppercase\expandafter{\romannumeral4}: fracture stage.
-Following discussion concentrates on deformation phenomena that rely on the elastoplastic co-deformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in two phase alloys.
+Following discussion concentrates on deformation phenomena that rely on the elastro-plastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in two phase alloys.
 
@@
 	\includegraphics[width=1\linewidth]{img/def2}
-	\caption{Microstrucutre evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) at key point 1 to 10}
+	\caption{Microstructure evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) at key point 1 to 10}
 	\label{fig:Defect}
@@
 Similarly, $\gamma$ phase grain have been removed in Fig.
-\ref{fig:Defect}b, the defect of $\alpha_2$ phase has been left.
+\ref{fig:Defect}b, the defects of $\alpha_2$ phase have been left.
 
@@
 \ref{fig:Defect}b.
-The deformation of $\alpha_2$ phase is even more earlier than $\gamma$ phase druing yied stage, thus local displacement of two phase are incompatible during yield stage.
+The deformation of $\alpha_2$ phase is even more earlier than $\gamma$ phase during yield stage, thus local displacement of two phase are incompatible during yield stage.
 $\gamma$ phase (TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2[110] and super dislocations with the Burgers vectors $b=[101]$ and $b=1/2[11\overline{2}]$.
-The other potential deformation mode is mechanical twinning have been repored along $1/6[11\overline{2}]{111}$, have not been observed in the simulation because of room temperature cannot offer enough energy for dislocation nucleation.
+The other potential deformation mode is mechanical twinning have been reported along $1/6[11\overline{2}]{111}$, have not been observed in the simulation because of room temperature cannot offer enough energy for dislocation nucleation.
 
@@
 
-where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions.
+where the pre factor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions.
 The effect of temperature on the mobility can be obtained under different loading conditions, thus  $\Delta H(\tau^*)$ are different.
-We choose cases with different loading condition$\Delta H(\tau^*)$  , normalized velocity can be  case 1 to case 3  in a increse order of $\Delta H(\tau^*)$.
-t
+We choose cases with different loading condition$\Delta H(\tau^*)$  , normalized velocity can be  case 1 to case 3  in a increase order of $\Delta H(\tau^*)$.
 
@@
 
-Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamealla, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
+Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamella, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
 
@@
 Effect of void at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}.
-The strength of materails with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
+The strength of materials with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
 The results show that the model without void defect has best strength, while the void located inside $\alpha_2$ phase detracts the strength of the material most, and the void at phase boundary have less impact on the strength.
@@
 where $\sigma_0$ is the strength of the model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = 36000 {AA}^2$, $A^* $ is section area in consider of the subsection that results from the voids.
-Comparing with the strength determined by molecular dynamics simulation and the results calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behaviour of the materials, thus revolution of defects should be examined carefully.
+Comparing with the strength determined by molecular dynamics simulation and the results calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.
 
@@
 It has been observed that voids detracts the strengths of the material.
-The max stress stress of the simulation cell decreases as the volume of voids are lareger.
+The max stress stress of the simulation cell decreases as the volume of voids are larger.
 From Fig \ref{fig:stress&strain}, there is a critical value of void radius about 15A, the void greater than 15A cause serious detraction of strength of material.
@@
 	$$ \sigma = S/A$$
-The rate of decrease of loading area are smaller comparing with the detraction of strength, so it can be assumed that the yield yield behavior and strength is much more related with local behaviour of grain boundaries and void.
+The rate of decrease of loading area are smaller comparing with the detraction of strength, so it can be assumed that the yield yield behavior and strength is much more related with local behavior of grain boundaries and void.
 
-Grain and phase boundaris are obstancles to deformation process, thus the stability of boundaries have great impact on the strength of materials.
-Interactive between grainboundary and void determins the fracture mode of the TiAl alloy.
+Grain and phase boundaries are obstacles to deformation process, thus the stability of boundaries have great impact on the strength of materials.
+Interactive between grain boundary and void determines the fracture mode of the TiAl alloy.
 
@@
 Consequently, the effective average distance between the second-phase particles has decreased to d which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide.
-The width of a burgers vector, will be generated at both sidesof a crystal along the direction of the burgers vector after dislocation traversing the entire crystal, as is shown in \ref{fig:orowan}.
-A small tep will be formed at spherical void surface toward the void interiorafter dislocation absorption at spherical void surfaces.
-If a great number of dislocation slip along their respective systemstowards the spherical nano void in all directions, and are absorbed at spherical void surfaces, the spherical nano void will eventually shrink from the dash circle
+The width of a burgers vector, will be generated at both sides of a crystal along the direction of the burgers vector after dislocation traversing the entire crystal, as is shown in \ref{fig:orowan}.
+A small tep will be formed at spherical void surface toward the void interior after dislocation absorption at spherical void surfaces.
+If a great number of dislocation slip along their respective systems towards the spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from the dash circle
 \section{conclusion}
@@
 
-(1) The major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha$ phase is harder to be deformed, this inhomogene results in cracks at interface of the two phase.
+(1) The major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha$ phase is harder to be deformed, this inhomogeneity results in cracks at interface of the two phase.
 

### 2018-11-09 draft/alexpub.tex
edited

@@
 \ref{fig:Defect}.
-Atoms with ordered orientation  of $\gamma$ phase grains have been removed in Fig.\ref{fig:Defect}a,\ $\alpha_2$ phase and defects inside grains have been left.
+Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig.\ref{fig:Defect}a,\ $\alpha_2$ phase and defects inside grains have been left.
 Similarly, $\gamma$ phase grain have been removed in Fig.
@@
 
-The results show that, at elastic stage(stage\uppercase\expandafter{\romannumeral1}), the structure of model have little change but the size of simulation box enlarged due to the loading, the deformation of the two phase are compatible.
-Emission of dislocation and evolution of defects initiated at the end of elastic stage (key point 2).
-A  great number of dislocation emitted inside $\gamma$ phase stage 2, however, the dislocation inside $\gamma$ phase was emitted after key point 6 in Fig.
+The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of the model is under typical elastic deformation and the size of simulation box enlarged due to the loading, the deformation of the two phase are compatible.
+Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}.
+A  great number of dislocation emitted inside $\gamma$ phase at stage 2, however, the dislocation inside $\gamma$ phase was emitted after key point 6 shown by Fig.
 \ref{fig:Defect}b.
@@
 $\gamma$ phase (TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2[110] and super dislocations with the Burgers vectors $b=[101]$ and $b=1/2[11\overline{2}]$.
-The other potential deformation mode is mechanical twinning have been reported along $1/6[11\overline{2}]{111}$, have not been observed in the simulation because of room temperature cannot offer enough energy for dislocation nucleation.
+% The other potential deformation mode is mechanical twinning have been reported along $1/6[11\overline{2}]{111}$, have not been observed in the simulation because of room temperature cannot offer enough energy for dislocation nucleation.
 
@@
 \end{equation}
-The velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it can be written as
-
-\begin{equation}\label{eq:temp-dis}
-v = v_0 \exp(-\Delta H(\tau^*)/kT)
-\end{equation}
-
-where the pre factor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions.
-The effect of temperature on the mobility can be obtained under different loading conditions, thus  $\Delta H(\tau^*)$ are different.
-We choose cases with different loading condition$\Delta H(\tau^*)$  , normalized velocity can be  case 1 to case 3  in a increase order of $\Delta H(\tau^*)$.
-
-The orientation of slip is changed because the crystallographically available slip and directions are not continuous across the interface.
-This may significantly reduce the Schmid factor and thus impede slip transfer.
-At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
-Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1}_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
-From Fig.
-\ref{fig:Defect}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
-A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
-TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of [a]-type dislocations with the Burgers vector $b=1/3[11\overline{2}0]$ prism planes\ref{fig:Defect}, which is by far the easiest slip system in $\alpha_2$ single crystals.
-
-%\begin{figure}[ht]
-%	\centering
-%	\includegraphics[width=1\linewidth]{img/plane}
-%	\caption{close packed plane of $\gamma\ \rm{phase}\ (\rm{TiAl})$ and $\alpha (\rm{Ti_3Al})$ phase }
-%	\label{fig:unit-cell}
-%\end{figure}
 
@@
 \end{figure}
+
+The mobility of dislocation is affected by structure of crystal, loading condition and temperature, and experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature\cite{Stein1960}.
+The brittleness of the two phase Ti-Al alloy attributed to the poor mobility of dislocation at room temperature.
+The velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it can be written as
+
+\begin{equation}\label{eq:temp-dis}
+v = v_0 \exp(-\Delta H(\tau^*)/kT)
+\end{equation}
+
+where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions.
+The effect of temperature on the mobility can be obtained under different loading conditions, we chose  $$\Delta H(\tau_1^*) > \Delta H(\tau_2^*) > \Delta H(\tau_3^*)$$, thus  $\Delta H(\tau^*)$ are different.
+We choose cases with different loading condition$\Delta H(\tau^*)$  , normalized velocity can be  case 1 to case 3  in a increase order of $\Delta H(\tau^*)$.
 
@@
 \end{figure}
+
+The orientation of slip is changed because the crystallographically available slip and directions are not continuous across the interface.
+This may significantly reduce the Schmid factor and thus impede slip transfer.
+At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
+Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1}_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
+From Fig.
+\ref{fig:Defect}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
+A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
+TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of [a]-type dislocations with the Burgers vector $b=1/3[11\overline{2}0]$ prism planes\ref{fig:Defect}, which is by far the easiest slip system in $\alpha_2$ single crystals.
+
+%\begin{figure}[ht]
+%	\centering
+%	\includegraphics[width=1\linewidth]{img/plane}
+%	\caption{close packed plane of $\gamma\ \rm{phase}\ (\rm{TiAl})$ and $\alpha (\rm{Ti_3Al})$ phase }
+%	\label{fig:unit-cell}
+%\end{figure}
 

### 2018-11-10 draft/alexpub.tex
change figure

@@
 % and brittle rapture failure 
-Poor Ductility at room temperature in Ti-Al alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator \cite{Munz2017}.
+Poor Ductility at room temperature in Ti-Al alloy strongly affects the safety of fracture of structures like turbo of aircraft engine and combustion generator \cite{Munz2017}.
 Deformation phenomena of TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
@@
 where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions.
-The effect of temperature on the mobility can be obtained under different loading conditions, we chose  $$\Delta H(\tau_1^*) > \Delta H(\tau_2^*) > \Delta H(\tau_3^*)$$, thus  $\Delta H(\tau^*)$ are different.
-We choose cases with different loading condition$\Delta H(\tau^*)$  , normalized velocity can be  case 1 to case 3  in a increase order of $\Delta H(\tau^*)$.
+The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\Delta H(\tau_1^*) > \Delta H(\tau_2^*) > \Delta H(\tau_3^*)$ in formula \ref{eq:temp-dis}, normalized velocity is shown in fig \ref{fig:temp}.
+The relative velocity  of dislocation rise along with increase of  stress, the speed of dislocation
 
@@
 		\centering
-		\caption{Mobility of dislocation\\
-		}
+		\caption{Mobility of dislocation}
 		\label{fig:temp}
@@
 		\centering
-		\caption{Strength of models}
+		\caption{Dislocation length during different stages}
 		\label{fig:disum}
@@
 
-Void of R=10 \AA\ was placed at phase boundary, inside $\alpha_2$ phase grain respectively.
-Effect of void at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}.
+Void with different sizes was placed at $\alpha_2-\gamma$ phase boundary, inside $\gamma$ phase respectively.
+Effect of void on the strength at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}.
 The strength of materials with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
-The results show that the model without void defect has best strength, while the void located inside $\alpha_2$ phase detracts the strength of the material most, and the void at phase boundary have less impact on the strength.
+The existence of void have little impact on the elastic properties of the material, and the model without void defect has best strength 5.3 GPa, the yield stress of model with void is smaller.
+located inside $\alpha_2$ phase detracts the strength of the material most, and the void at phase boundary have less impact on the strength.
 
@@
 where $\sigma_0$ is the strength of the model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = 36000 {AA}^2$, $A^* $ is section area in consider of the subsection that results from the voids.
-Comparing with the strength determined by molecular dynamics simulation and the results calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.
+Comparing with the strength determined by molecular dynamics simulation and the result4s calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.
 

### 2018-11-10 code/allline.py

@@ -19,7 +19,7 @@ import os.path
 from os import listdir
 import matplotlib.pyplot as plt
 import pandas as pd
-plt.rcParams["font.family"] = 'Times New Roman'
+# plt.rcParams["font.family"] = 'Times New Roman'
 import matplotlib.pyplot as plt
 plt.rcParams.update({'font.size': 12})
 #csfont = {'fontname':'Times New Roman'}
@@ -41,9 +41,9 @@ px4=ds4.step/fct
 
 # plot lines
 #p1 = plt.plot(ds1.step, ds1.stress, label='aa')
-p2 = plt.plot(px2, ds2.stress, label='ag')
-p3 = plt.plot(px3, ds3.stress, label='pf')
-p4 = plt.plot(px4, ds4.stress, label='ia')
+p2 = plt.plot(px2, ds2.stress, label='ia', color = 'G')
+p3 = plt.plot(px3, ds3.stress, label='pf', color = 'R')
+p4 = plt.plot(px4, ds4.stress, label='ag', color = 'B')
 # config title and label
 
 #plt.title('stress-strain curve')

### 2018-11-10 code/data/size/size_summary.py

@@ -18,7 +18,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 from scipy.optimize import curve_fit as fit
 plt.rcParams.update({'font.size': 12})
-plt.rcParams["font.family"] = 'Times New Roman'
+# plt.rcParams["font.family"] = 'Times New Roman'
 
 WDIR = os.path.dirname(__file__)
 writepath = os.path.join(WDIR,'..','..','..','draft','img')
@@ -28,9 +28,9 @@ iamax = np.array([5.3, 5.26, 5.25, 5.22, 5.19, 4.96])
 agmax = np.array([5.3, 5.25, 5.17, 5.11, 5.09, 4.87])
 fac = (1-(np.pi*(size/2)**2)/(210*180))*iamax[0]
 # pia = fit.gaussian(size,iamax)
-plt.plot(size, iamax,marker='s')
-plt.plot(size, agmax, marker='^')
-plt.plot(size, fac, marker='o',linestyle='--')
+plt.plot(size, iamax,marker='s',color='G')
+plt.plot(size, agmax, marker='^',color='B')
+plt.plot(size, fac, marker='o',linestyle='--',color='black')
 # color='darkorange'
 # color='steelblue'
 plt.legend(['ia', 'ag','Calculated'], frameon=False)

### 2018-11-10 code/Temp.py
fig modified

@@ -3,7 +3,9 @@ import os.path
 
 #plt.rcParams["font.family"] = 'Times New Roman'
 import matplotlib.pyplot as plt
-plt.rcParams.update({'font.size': 12})
+plt.rcParams.update({'font.size': 14})
+from matplotlib import rc
+rc('text', usetex=True)
 #csfont = {'fontname':'Times New Roman'}
 #plt.rcParams["font.family"] = "Times New Roman"
 WDIR = os.path.dirname(__file__)
@@ -22,11 +24,14 @@ w = 20*np.e**(-450/T)/20
 plt.xlabel('Temperature / K')
 plt.ylabel('Mobility of Dislocation')
 plt.ylim(ymax=1)
-plt.plot(key1,key2)
-plt.plot(T,u,label='Case 1')
-plt.plot(T,v,label='Case 2')
-plt.plot(T,w,label='Case 3')
-plt.legend(frameon=False)
+plt.plot(T,u)
+plt.plot(T,v)
+plt.plot(T,w)
+plt.legend([r'$\Delta H(\tau_1^*)$', r'$\Delta H(\tau_2^*)$',r'$\Delta H(\tau_3^*)$'], frameon=False,loc='best')
+plt.text(450,0.85,r'$\Delta H(\tau_1^*) > \Delta H(\tau_2^*) > \Delta H(\tau_3^*)$')
+plt.annotate('298 K',xy=(290,0.35),xytext=(80,0.45),arrowprops=dict(arrowstyle="->",connectionstyle="arc3"))
+plt.plot(key1,key2,linestyle='--',color='black')
+
 plt.savefig(os.path.join(writepath, 'temp.pdf'))
 
 plt.show()

### 2018-11-10 code/allline.py

@@ -21,13 +21,18 @@ import matplotlib.pyplot as plt
 import pandas as pd
 # plt.rcParams["font.family"] = 'Times New Roman'
 import matplotlib.pyplot as plt
-plt.rcParams.update({'font.size': 12})
+plt.rcParams.update({'font.size': 14})
+from matplotlib import rc
+rc('text', usetex=True)
 #csfont = {'fontname':'Times New Roman'}
 #plt.rcParams["font.family"] = "Times New Roman"
 WDIR = os.path.dirname(__file__)
 loadpath = os.path.join(WDIR,'data','stress_strain')
 writepath = os.path.join(WDIR,'..','draft','img')
 # pre-set head name
+
+
+
 prop = ['step', 'strain', 'stress', 'energy']
 # import data from .csv file:
 #ds1 = pd.read_csv(os.path.join(loadpath,'aa.csv'), sep=' ', skiprows=1, names=prop)
@@ -41,19 +46,20 @@ px4=ds4.step/fct
 
 # plot lines
 #p1 = plt.plot(ds1.step, ds1.stress, label='aa')
-p2 = plt.plot(px2, ds2.stress, label='ia', color = 'G')
-p3 = plt.plot(px3, ds3.stress, label='pf', color = 'R')
-p4 = plt.plot(px4, ds4.stress, label='ag', color = 'B')
+p3 = plt.plot(px3, ds3.stress, color = 'R')
+p2 = plt.plot(px2, ds2.stress, color = 'G')
+p4 = plt.plot(px4, ds4.stress, color = 'B')
+
+plt.legend([ 'no void',r'void inside $\alpha$ phase',r'void at \textbf{$\alpha$-$\gamma$} phase boundary'], frameon=False)
+
 # config title and label
 
 #plt.title('stress-strain curve')
 plt.xlabel('Strain')
 plt.xlim(xmax=0.035)
 plt.ylim(ymax=6)
-plt.ylabel('Stress (GPa)')
-plt.legend(frameon=False)
+plt.ylabel('Stress / GPa')
 plt.savefig(os.path.join(writepath, 'allline.pdf'))
-
 plt.show()
 # /home/alex/violet/all.line.pdf
 # /home/alex/violet/code/pict/area.png

### 2018-11-10 code/data/size/size_summary.py

@@ -17,7 +17,10 @@ import matplotlib.pyplot as plt
 import numpy as np
 import matplotlib.pyplot as plt
 from scipy.optimize import curve_fit as fit
-plt.rcParams.update({'font.size': 12})
+plt.rcParams.update({'font.size': 14})
+from matplotlib import rc
+rc('text', usetex=True)
+
 # plt.rcParams["font.family"] = 'Times New Roman'
 
 WDIR = os.path.dirname(__file__)
@@ -30,16 +33,18 @@ fac = (1-(np.pi*(size/2)**2)/(210*180))*iamax[0]
 # pia = fit.gaussian(size,iamax)
 plt.plot(size, iamax,marker='s',color='G')
 plt.plot(size, agmax, marker='^',color='B')
-plt.plot(size, fac, marker='o',linestyle='--',color='black')
+plt.plot(size, fac, marker='o',linestyle='--',color='orange')
 # color='darkorange'
 # color='steelblue'
-plt.legend(['ia', 'ag','Calculated'], frameon=False)
+plt.legend([r'void inside $\alpha$ phase', r'void at \textbf{$\alpha$-$\gamma$} phase boundary','calculated value'], frameon=False)
 plt.ylim(4.8,5.35)
-plt.xlabel('Radius of Void/A')
+plt.xlabel(r'Radius of Void/ \AA')
 plt.ylabel('Strength/GPa')
 plt.savefig(os.path.join(writepath,'effect_of_vol.pdf'))
 plt.show()
 
+# import matplotlib as plt
+# print(plt.get_cachedir())
 # comments
 
 '''

### 2018-11-10 code/dissum.py

@@ -4,15 +4,18 @@ import os.path
 
 #plt.rcParams["font.family"] = 'Times New Roman'
 import matplotlib.pyplot as plt
-plt.rcParams.update({'font.size': 12})
+
 #csfont = {'fontname':'Times New Roman'}
 #plt.rcParams["font.family"] = "Times New Roman"
+
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import rc
+rc('text', usetex=True)
+plt.rcParams.update({'font.size': 14})
 WDIR = os.path.dirname(__file__)
 # loadpath = os.path.join(WDIR,'data','stress_strain')
 writepath = os.path.join(WDIR,'..','draft','img')
-import numpy as np
-import matplotlib.pyplot as plt
-
 pf = [744, 290, 212, 530]
 shockley = [1343, 1470, 3581, 4367]
 stair_rode = [0, 123, 259, 295]
@@ -50,7 +53,7 @@ rects4 = plt.bar(index + 3*bar_width, frank, bar_width,
                  label='Frank')
 
 plt.xlabel('Stage')
-plt.ylabel('Dislocation length / A')
+plt.ylabel(r'Dislocation length / \AA')
 # plt.title('Scores by person')
 plt.xticks(index + bar_width, ('Initial', 'Before yield', 'After yield', 'Cracked'))
 plt.legend(frameon = False)

### 2018-11-10 code/temp.py

@@ -1,5 +1,8 @@
 import numpy as np
-import matplotlib.pyplot as plt 
+import matplotlib.pyplot as plt
+WDIR = os.path.dirname(__file__)
+# loadpath = os.path.join(WDIR,'data','stress_strain')
+writepath = os.path.join(WDIR,'..','draft','img')
 T = np.linspace(0,1000,1500)
 key = 20*np.e**(-150/298)/20
 key1=[298,298]

### 2018-11-11 draft/alexpub.tex
pict

@@
 % \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
-\Title{Atomic Investigation on Cold Deformation Behavior of Two Phase TiAl Polycrystal with and without Void Defect}
+\Title{Atomic Investigation on Cold Deformation Behavior of Two Phase Ti-Al Polycrystal with and without Void Defect}
 % Author Orchid ID: enter ID or remove command
@@
 \abstract{Cold deformation behavior of polycrystalline metallic materia is affected by dislocation, nano void and other defects.
-Existing studies on two phase TiAl alloy covers about deformation behavior mainly on marco scale.
-This paper mainly concern about cold deforamtion mechanism of the two phase TiAl ally at atomic scale, and  the role of void defect in deformation process.
-Molecular dynamics simulation was performed to study the evolution of a spherical nano void in $\alpha_2$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
-Simulation cases of model with different size and position of void were performed.
+Existing studies on $\alpha_2(\rm{Ti_3Al})$+$\gamma(\rm{TiAl})$  two phase Ti-Al alloy covers about deformation behavior mainly on marco scale.
+This paper focus on the cold deformation mechanism of two phase Ti-Al alloy at micro scale, and  the role of void defect in deformation process.
+Molecular dynamics simulations were performed to study the evolution of microstructure in the model under uniaxial tension.
+Interaction between spherical nano void with different size and position was also examined in the simulation.
 The results show that i) $\gamma$ phase is the major deformation source of the two phase alloy; ii) Voids defect detracts the strength of the two phase alloy, however the position of void affect the degree of this substraction: voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detract to strength.}
 % Keywords
-\keyword{two phase TiAl alloy; void; molecular dynamics}
+\keyword{two phase Ti-Al alloy; void defect; molecular dynamics}
 
@@
 % and brittle rapture failure 
-Poor Ductility at room temperature in Ti-Al alloy strongly affects the safety of fracture of structures like turbo of aircraft engine and combustion generator \cite{Munz2017}.
-Deformation phenomena of TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
+The light weight intermeatlic alloy Ti-Al alloys are promising high temperatture structural materials because of their great corrison resistance at high temperature.
+Comparing with nickle based alloy, titanium based aluminide alloys have lower density and are pron to be utilized in combustionnor, turbine, and other components work at high temperature ranging from 500 degree to 900 degree.
+The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20 as a results of the weight of components decreased 30\%~40\%.
+With the advancement of non-ferrous metallurgy, titanium aluminide based components has better economical efficiency than ever before.
+, TiAl based alloys have good prospects for applications in aero- space and automobile industry, e.g.
+as turbine blades and valves[4–7].
+Poor ductility of Ti-Al alloy  at room temperature strongly affects the safety structures like turbo of aircraft engine and combustion generator \cite{Munz2017}.
+Deformation phenomena of Ti-Al alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
 Much of the work has been performed on single phase $\gamma$ alloys and PST crystals\cite{Appel2016}.
@@
 \ref{fig:tial-cell}, and the constructing parameters are givin by Table \ref{tab:lattice_parameter}.
-In order to study the deformation mechanism of the two phase alloy and the effect of void defect, three types of models were created: Type-1.model without any void defect; Type-2.
-models with different size void inside $\alpha_2$ phase; Type-3.
-models with void at $\alpha_2-\gamma$ interface.
-\ref{tab:lattice_parameter}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure . 
 Periodic boundary conditions (PBC) are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
@@
 Uniaxial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$.
-
+% In order to study the deformation mechanism of the two phase alloy and the effect of void defect, three types of models were created: Type-1.model without any void defect; Type-2.
+models with different size void inside $\alpha_2$ phase; Type-3.
+models with void at $\alpha_2-\gamma$ interface.
+\ref{tab:lattice_parameter}.
+The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure .
 \subsection{Analysis method}
@@
 \begin{table}[ht]
-	\caption{Key point during tensile process}
+	\caption{Key points during tensile process}
 	\centering
@@
 
-\begin{figure}[ht] 
-	\centering
-	\includegraphics[width=1\linewidth]{img/def2}
-	\caption{Microstructure evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) at key point 1 to 10}
-	\label{fig:Defect}
-\end{figure}
-
-Deformation process of model without void under uniaxial load is shown by stress-strain curve Fig.
-\ref{fig:deformation-pf} and snapshots of atom configuration at the 10 key points in Fig.
-\ref{fig:Defect}.
-Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig.\ref{fig:Defect}a,\ $\alpha_2$ phase and defects inside grains have been left.
-Similarly, $\gamma$ phase grain have been removed in Fig.
-\ref{fig:Defect}b, the defects of $\alpha_2$ phase have been left.
-
-The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of the model is under typical elastic deformation and the size of simulation box enlarged due to the loading, the deformation of the two phase are compatible.
-Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}.
-A  great number of dislocation emitted inside $\gamma$ phase at stage 2, however, the dislocation inside $\gamma$ phase was emitted after key point 6 shown by Fig.
-\ref{fig:Defect}b.
-The deformation of $\alpha_2$ phase is even more earlier than $\gamma$ phase during yield stage, thus local displacement of two phase are incompatible during yield stage.
-$\gamma$ phase (TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2[110] and super dislocations with the Burgers vectors $b=[101]$ and $b=1/2[11\overline{2}]$.
-% The other potential deformation mode is mechanical twinning have been reported along $1/6[11\overline{2}]{111}$, have not been observed in the simulation because of room temperature cannot offer enough energy for dislocation nucleation.
-
-\begin{equation}\label{eq:dis1}
-	[\ 0\ 1\ \overline{1}\ ] \to 1/2 [\ 1\ 1\ \overline{2}\ ]+1/2[\ \overline{1}\ 1\ 0\ ]
-\end{equation}
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/disl-gamma"}
-	\caption{Dislocation in $\gamma$}
-	\label{fig:dis-alpha_2}
-\end{figure}
-
 The mobility of dislocation is affected by structure of crystal, loading condition and temperature, and experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature\cite{Stein1960}.
@@
 where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions.
-The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\Delta H(\tau_1^*) > \Delta H(\tau_2^*) > \Delta H(\tau_3^*)$ in formula \ref{eq:temp-dis}, normalized velocity is shown in fig \ref{fig:temp}.
-The relative velocity  of dislocation rise along with increase of  stress, the speed of dislocation
+The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\tau_1^*>\tau_2^*>\tau_3^*$ in formulation \ref{eq:temp-dis}, normalized velocity is shown in Fig \ref{fig:temp}.
+The relative velocity  of dislocation rise along with increase of  stress, the speed of dislocation is relatively low at room temperature, and it is more sensitive to temperature than shear stress.
 
@@
 		\centering
-		\caption{Dislocation length during different stages}
+		\caption{Dislocation length}
 		\label{fig:disum}
@@
 
-The orientation of slip is changed because the crystallographically available slip and directions are not continuous across the interface.
+In Fig.
+\ref{fig:disum}, length of different types of dislocation are plotted at four stages.
+Dislocations are recognized and identified using the dislocation analysis (DXA) ofOVITO.
+$\gamma$ phase (TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2[110] and super dislocations with the Burgers vectors $b=[101]$ and $b=1/2[11\overline{2}]$
+
+\begin{equation}\label{eq:dis1}
+[\ 0\ 1\ \overline{1}\ ] \to 1/2 [\ 1\ 1\ \overline{2}\ ]+1/2[\ \overline{1}\ 1\ 0\ ]
+\end{equation}
+
+The length of Shorckley dislocation with Burgers vector $1/6[1 1 2]$ increase sharply during yield stage of the deformation process in Fig.
+\ref{fig:disum}, but the length of perfect dislocation fluctuate at a low level.
+That is mainly because decomposition of the perfect  dislocations which is given by formulation \ref{eq:dis2}, and the structure spontaneously transform into intrinsic stacking fault in Fig.
+\ref{fig:dis-alpha_2}.
+
+\begin{equation}\label{eq:dis2}
+1/2 [\ 1\ \overline { 1 }\ 2\ ] \rightarrow 1/6 [\ 1\ \overline { 1 }\ 2\ ]  + 1/3 [\ 1\ \overline { 1 }\ 2\ ]
+\end{equation}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{"img/disl-gamma"}
+	\caption{Dislocation in $\gamma$}
+	\label{fig:dis-alpha_2}
+\end{figure}
+
+% Deformation process of model without void under uniaxial load is shown by stress-strain curve Fig. \ref{fig:deformation-pf} and
+Snapshots of atom configuration at the 5 of 10 key points are shown by Fig.
+\ref{fig:Defect}.
+Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig.\ref{fig:Defect}a,\ $\alpha_2$ phase and defects inside grains have been left.
+Similarly, $\gamma$ phase grain have been removed in Fig.
+\ref{fig:Defect}b, the defects of $\alpha_2$ phase have been left.
+The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of the model is under typical elastic deformation and the size of simulation box enlarged due to the loading, the deformation of the two phase are compatible.
+Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}.
+A  great number of dislocation emitted inside $\gamma$ phase at stage 2, however, the dislocation inside $\gamma$ phase was emitted after key point 6 shown by Fig.
+\ref{fig:Defect}b.
+The deformation of $\alpha_2$ phase is even more earlier than $\gamma$ phase during yield stage, thus local displacement of two phase are incompatible during yield stage.
+
+\begin{figure}[ht] 
+	\centering
+	\includegraphics[width=1\linewidth]{img/def2}
+	\caption{Microstructure evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) at key point 1 to 10}
+	\label{fig:Defect}
+\end{figure}
+
+The orientation of slip is changed in Fig.
+\ref{fig:Defect}, because the crystallographically available slip and directions are not continuous across the interface.
 This may significantly reduce the Schmid factor and thus impede slip transfer.
 At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
-Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1}_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
+Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1}_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{intro-structure}.
 From Fig.
@@
 A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
-TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of [a]-type dislocations with the Burgers vector $b=1/3[11\overline{2}0]$ prism planes\ref{fig:Defect}, which is by far the easiest slip system in $\alpha_2$ single crystals.
-
-%\begin{figure}[ht]
-%	\centering
-%	\includegraphics[width=1\linewidth]{img/plane}
-%	\caption{close packed plane of $\gamma\ \rm{phase}\ (\rm{TiAl})$ and $\alpha (\rm{Ti_3Al})$ phase }
-%	\label{fig:unit-cell}
-%\end{figure}
-
+TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of [a]-type dislocations with the Burgers vector $b=1/3[11\overline{2}0]$ prism planes shown by Fig.
+\ref{fig:Defect}, which is by far the easiest slip system in $\alpha_2$ single crystals.
 The core of a dislocation intersecting an interface often needs to be transformed.
@@
 These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
-
 Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamella, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
@@
 
-Void with different sizes was placed at $\alpha_2-\gamma$ phase boundary, inside $\gamma$ phase respectively.
-Effect of void on the strength at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}.
+In Fig.
+\ref{fig:model-creation}, voids with different size: 2A, 5A, 10A, 15A were placed  at $\alpha_2-\gamma$ phase boundary, inside $\gamma$ phase respectively.
 The strength of materials with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
@@
 The effect of size is expectable that the greater voids detracts the strength of the materials more, however, it has been observed in the simulation that there is a critical value about 15A for voids at different position.
-The voids larger than 15 A have dramatic detraction to the strength of the material.
+The voids larger than 15 \AA\ have dramatic detraction to the strength of the material.
 Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by formulation \ref{eq:section}:
@@
 
-Voids with different size: 2A, 5A, 10A, 15A were placed into the model respectively.
-It has been observed that voids detracts the strengths of the material.
+In Fig.
+\ref{fig:strength} It has been observed that voids detracts the strengths of the material.
 The max stress stress of the simulation cell decreases as the volume of voids are larger.
 From Fig \ref{fig:stress&strain}, there is a critical value of void radius about 15A, the void greater than 15A cause serious detraction of strength of material.
-Engineering stress is calculated
-	$$ \sigma = S/A$$
 The rate of decrease of loading area are smaller comparing with the detraction of strength, so it can be assumed that the yield yield behavior and strength is much more related with local behavior of grain boundaries and void.
-
 Grain and phase boundaries are obstacles to deformation process, thus the stability of boundaries have great impact on the strength of materials.
@@
 The role of void can be concluded as two main parts: source of dislocation and obstacles to dislocations.
-Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, more or less (as possibly associated with the occurrence of incoherent or coherent interfaces;the long-range translation symmetry of the matrix.
+Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, associated with the occurrence of incoherent or coherent interfaces;the long-range translation symmetry of the matrix.
 They may induce considerable misfit-stress fields and thus can influence material properties pronouncedly.
@@
 This mechanism for hardening is designated as the Orowan process (with $\tau_0$ as the Orowan (shear) stress.
+
 As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles.
@@
 IRT-15R30) and the Doctoral Research Foundation of Lanzhou University of Technology.}
-mark
+
 \end{document}

### 2018-11-11 code/Temp.py

@@ -14,24 +14,28 @@ writepath = os.path.join(WDIR,'..','draft','img')
 import numpy as np
 import matplotlib.pyplot as plt
 
-T = np.linspace(0,1200,1500)
+T = np.linspace(0,1100,100)
 key = 20*np.e**(-150/298)/20
 key1=[298,298]
 key2=[0,1]
-u = 20*np.e**(-300/T)/20
-v = 20*np.e**(-350/T)/20
+# u = 20*np.e**(-300/T)/20
+# v = 20*np.e**(-350/T)/20
+# w = 20*np.e**(-450/T)/20
+u = 20*np.e**(-350/T)/20
+v = 20*np.e**(-400/T)/20
 w = 20*np.e**(-450/T)/20
 plt.xlabel('Temperature / K')
 plt.ylabel('Mobility of Dislocation')
 plt.ylim(ymax=1)
-plt.plot(T,u)
-plt.plot(T,v)
-plt.plot(T,w)
-plt.legend([r'$\Delta H(\tau_1^*)$', r'$\Delta H(\tau_2^*)$',r'$\Delta H(\tau_3^*)$'], frameon=False,loc='best')
-plt.text(450,0.85,r'$\Delta H(\tau_1^*) > \Delta H(\tau_2^*) > \Delta H(\tau_3^*)$')
+plt.plot(T,u, color='R')
+plt.plot(T,v, color='G')
+plt.plot(T,w, color='B')
+plt.legend([r'$v_1 (\tau_1^*)$', r'$v_2 (\tau_2^*)$',r'$v_3 (\tau_3^*)$'], frameon=False,loc='best')
+plt.text(450,0.85,r'$\tau_1^*>\tau_2^*>\tau_3^*$')
 plt.annotate('298 K',xy=(290,0.35),xytext=(80,0.45),arrowprops=dict(arrowstyle="->",connectionstyle="arc3"))
 plt.plot(key1,key2,linestyle='--',color='black')
 
 plt.savefig(os.path.join(writepath, 'temp.pdf'))
 
 plt.show()
+

### 2018-11-11 code/data/size/size_summary.py

@@ -33,11 +33,11 @@ fac = (1-(np.pi*(size/2)**2)/(210*180))*iamax[0]
 # pia = fit.gaussian(size,iamax)
 plt.plot(size, iamax,marker='s',color='G')
 plt.plot(size, agmax, marker='^',color='B')
-plt.plot(size, fac, marker='o',linestyle='--',color='orange')
+plt.plot(size, fac, marker='o',linestyle='--',color='R')
 # color='darkorange'
 # color='steelblue'
 plt.legend([r'void inside $\alpha$ phase', r'void at \textbf{$\alpha$-$\gamma$} phase boundary','calculated value'], frameon=False)
-plt.ylim(4.8,5.35)
+plt.ylim(4.8,5.5)
 plt.xlabel(r'Radius of Void/ \AA')
 plt.ylabel('Strength/GPa')
 plt.savefig(os.path.join(writepath,'effect_of_vol.pdf'))

### 2018-11-11 code/dissum.py

@@ -34,26 +34,27 @@ opacity = 0.8
 
 rects1 = plt.bar(index, pf, bar_width,
                  alpha=opacity,
-                # color='b',
+                 color='R',
                  label='Perfect')
 
 rects2 = plt.bar(index + bar_width, shockley, bar_width,
                  alpha=opacity,
-                 #color='g',
+                 color='B',
                  label='Shockley')
 
 rects3 = plt.bar(index + 2*bar_width, stair_rode, bar_width,
                  alpha=opacity,
-                 #color='b',
+                 color='G',
                  label='Stair-rod')
 
 rects4 = plt.bar(index + 3*bar_width, frank, bar_width,
                  alpha=opacity,
-                 #color='g',
+                 color='black',
                  label='Frank')
 
 plt.xlabel('Stage')
 plt.ylabel(r'Dislocation length / \AA')
+plt.ylim(ymax=5000)
 # plt.title('Scores by person')
 plt.xticks(index + bar_width, ('Initial', 'Before yield', 'After yield', 'Cracked'))
 plt.legend(frameon = False)

### 2018-11-11 draft/alexpub.tex
add new

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Cold deformation behavior of polycrystalline metallic materia is affected by dislocation, nano void and other defects.
-Existing studies on $\alpha_2(\rm{Ti_3Al})$+$\gamma(\rm{TiAl})$  two phase Ti-Al alloy covers about deformation behavior mainly on marco scale.
+\abstract{Cold deformation behavior of poly crystalline metallic material is affected intrinsic defects such as dislocation, etc.
+Existing studies on $\alpha_2(\rm{Ti_3Al})$+$\gamma(\rm{TiAl})$  two phase Ti-Al alloy covers about deformation behavior mainly on macro scale.
 This paper focus on the cold deformation mechanism of two phase Ti-Al alloy at micro scale, and  the role of void defect in deformation process.
-Molecular dynamics simulations were performed to study the evolution of microstructure in the model under uniaxial tension.
+Molecular dynamics simulations were performed to study the evolution of micro structure in the model under uniaxial tension.
 Interaction between spherical nano void with different size and position was also examined in the simulation.
-The results show that i) $\gamma$ phase is the major deformation source of the two phase alloy; ii) Voids defect detracts the strength of the two phase alloy, however the position of void affect the degree of this substraction: voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detract to strength.}
+The results show that i) $\gamma$ phase is the major deformation source of the two phase alloy; ii) Voids defect detracts the strength of the two phase alloy, however the position of void affect the degree of this subtraction: voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detract to strength.}
 % Keywords
@@
 % and brittle rapture failure 
-The light weight intermeatlic alloy Ti-Al alloys are promising high temperatture structural materials because of their great corrison resistance at high temperature.
-Comparing with nickle based alloy, titanium based aluminide alloys have lower density and are pron to be utilized in combustionnor, turbine, and other components work at high temperature ranging from 500 degree to 900 degree.
-The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20 as a results of the weight of components decreased 30\%~40\%.
-With the advancement of non-ferrous metallurgy, titanium aluminide based components has better economical efficiency than ever before.
-, TiAl based alloys have good prospects for applications in aero- space and automobile industry, e.g.
-as turbine blades and valves[4–7].
+The titanium  aluminum based intermetallic alloys are promising high temperature structural materials because of their great corrosion resistance at high temperature.
+Comparing with nickle based alloy,  alloys have lower density and are pron to be utilized in combustion engine, turbine, and other components work at high temperature ranging from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius}.
+The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20\% because the weight of components decreased 30\%~40\%.
+With the advancement of non-ferrous metallurgy, Ti-Al based components has better economic efficiency than ever before.
+Thus, Ti-Al based alloys have good prospects for applications in aerospace and automobile industry.
 Poor ductility of Ti-Al alloy  at room temperature strongly affects the safety structures like turbo of aircraft engine and combustion generator \cite{Munz2017}.
 Deformation phenomena of Ti-Al alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
-Much of the work has been performed on single phase $\gamma$ alloys and PST crystals\cite{Appel2016}.
-Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{Tang2014}.
-
+Much of the work has been performed on single phase $\gamma$ alloys and polysynthetically twinned crystals\cite{Appel2016}.
+Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially easily formed in the casting process, such as voids and inclusions \cite{Tang2014}.
 A great number of literature covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
 Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}.
-Due to difficulties in observing the dynamic process during deformation wit experiments, MD simulation has become a effective method to investigate micro deformation mechanism.
-Defects such as grain boundary, void and segregation plays an significant role in the process of fracture \cite{Larsen2016}.
-Multiscale method have been applied to study deformation behavior polycrystal with single aluminum element \cite{Groh2009} and single titanium element \cite{Liu2018}.
+Due to difficulties in observing the dynamic process during deformation wit experiments, MD simulation has become an effective method to investigate micro deformation mechanism.
+Defects such as grain boundary, void and segregation plays a significant role in the process of fracture \cite{Larsen2016}.
+Multiscale method have been applied to study deformation behavior polycrystal with single aluminum \cite{Groh2009} and titanium element \cite{Liu2018}.
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
 
-The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study of detailed mechanisms of deformation and cracking.
-These defects are known to play a fundamental role in the deformation of the material.
+The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study of detailed mechanisms of deformation and cracking, these defects are known to play a fundamental role in the deformation of materials.
 It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
@@
 A previous study on void growth in $\gamma$-TiAl single crystal has reveals that void with high volume fraction detracts yield strength, and emission of dislocation \cite{Tang2014, Xu2011}.
-Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations.
-\cite{Jing2018a,Elkhateeb2018}.
+Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations \cite{Jing2018a,Elkhateeb2018}.
 The deformation and fracture mechanisms in the duplex microstructure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang2014}.
-It has reveals that existence of voids alone may contribute to strain hardening because they are barriers to dislocation movement \cite{Xiong2015}.
-However, few literatures covers about deformation mechanism of two phase TiAl alloy and the role of void in atomic scale.
+It reveals that existence of voids alone may contribute to strain hardening because they are barriers to dislocation movement \cite{Xiong2015}.
+However, few literature covers about deformation mechanism of two phase Ti-Al alloy and the role of void in atomic scale.
 Defects are inevitable as micro-pores and loosen from casting, and in the actual work environment with radiation.
-A lot work carried out on the the effect of various defects on the behavior of different materials, show that point defects may affect the properties of materials greatly.
-The mechanical properties of irradiated copper is affected by the interaction between irradiation and dislocation \cite{Kiener2011}.
+A lot of work carried out on the  effect of various defects on the behavior of different materials, show that point defects may affect the properties of materials greatly.
+The mechanical performance of irradiated copper is affected by the interaction between irradiation and dislocation \cite{Kiener2011}.
 Vacancy concentration in single crystal and polycrystal Fe–40 at.
@@
 Ti-Al alloy is a type of typical brittle material, thus it can be assumed that its properties are sensitive to the existence of void defect.
-Surface defect such as small notches can caused lower high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$ - TiAl is also also lowered by point defect \cite{Wu2016}.
+Surface defects such as small notches can caused lower high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$  TiAl is also lowered by point defect \cite{Wu2016}.
 The resistance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was markedly reduced due to earlier crack initiation.
-The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small micro-cracks in the damaged zone.
-
-This paper focus on the evolution of microstructure, tend to find out the connection between microstructure and cold deformation behavior of two phase TiAl alloy.
+The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small micro-cracks in the damaged zone.This paper focus on the evolution of microstructure, tend to find out it connection to cold deformation behavior of two phase TiAl alloy.
 MD simulation including model creation and analysis method is given in Section \ref{section:method}; Results and discussion are in Section \ref{section:RD}.
@@
 
-$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure, and $\alpha_2 -\rm Ti_3Al$ has hcp structure, the two types of initial cells are shown in Fig.
-\ref{fig:tial-cell}, and the constructing parameters are givin by Table \ref{tab:lattice_parameter}.
+$\gamma $ TiAl has a fcc type cell with an $L1_0$ structure, and $\alpha_2 -\rm Ti_3Al$ has a hcp structure, the two types of initial cells are shown in Fig.
+\ref{fig:tial-cell}, and the constructing parameters are given by Table \ref{tab:lattice_parameter}.
 Periodic boundary conditions (PBC) are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
 The initial dimension of simulation cell is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model contains about 4.6 million atoms.
-The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{Hirel2015}, and resulting in the arbitrary shape and orientation of the grains.
+The grain orientation and size were randomly created with Voronoi method by code ATOMSK \cite{Hirel2015}, and resulting in the arbitrary shape and orientation of the grains.
 Uniaxial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$.
@@
 \subsection{Deformation Mechanism of Two Phase TiAl Alloy without Void Defects}
+Snapshots of atom configuration at the 5 of 10 key points are shown by Fig.
+\ref{fig:Defect}.
+Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig.\ref{fig:Defect}a,\ $\alpha_2$ phase and defects inside grains have been left.
+Similarly, $\gamma$ phase grain have been removed in Fig.
+\ref{fig:Defect}b, the defects of $\alpha_2$ phase have been left.
+The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of the model is under typical elastic deformation and the size of simulation box enlarged due to the loading, deformation of the two phase are compatible.
+Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}.
+A  great number of dislocation emitted inside $\gamma$ phase at stage 2, however, the dislocation inside $\gamma$ phase was emitted after key point 5 shown by Fig.
+\ref{fig:Defect}b.
+The deformation of $\alpha_2$ phase is earlier than $\gamma$ phase during yield stage, thus local displacement of two phase are incompatible during yield stage.
+
+\begin{figure}[ht] 
+	\centering
+	\includegraphics[width=1\linewidth]{img/def2}
+	\caption{Microstructure evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) at key point 1 to 10}
+	\label{fig:Defect}
+\end{figure}
 
 The mobility of dislocation is affected by structure of crystal, loading condition and temperature, and experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature\cite{Stein1960}.
-The brittleness of the two phase Ti-Al alloy attributed to the poor mobility of dislocation at room temperature.
-The velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it can be written as
-
+The brittleness of two phase Ti-Al alloy attributed to the poor mobility of dislocation at room temperature.
+Velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it can be written as:
 \begin{equation}\label{eq:temp-dis}
@@
 \end{equation}
-
 where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions.
 The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\tau_1^*>\tau_2^*>\tau_3^*$ in formulation \ref{eq:temp-dis}, normalized velocity is shown in Fig \ref{fig:temp}.
-The relative velocity  of dislocation rise along with increase of  stress, the speed of dislocation is relatively low at room temperature, and it is more sensitive to temperature than shear stress.
+The  velocity  of dislocation movement rise along with increase of  stress, the speed of dislocation is relatively low at 298 K, and it is more sensitive to temperature than shear stress.
 
@@
 In Fig.
-\ref{fig:disum}, length of different types of dislocation are plotted at four stages.
-Dislocations are recognized and identified using the dislocation analysis (DXA) ofOVITO.
-$\gamma$ phase (TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2[110] and super dislocations with the Burgers vectors $b=[101]$ and $b=1/2[11\overline{2}]$
-
-\begin{equation}\label{eq:dis1}
-[\ 0\ 1\ \overline{1}\ ] \to 1/2 [\ 1\ 1\ \overline{2}\ ]+1/2[\ \overline{1}\ 1\ 0\ ]
-\end{equation}
-
+\ref{fig:disum}, length of different type dislocation are given at four stages.
+Dislocations are recognized and identified using the dislocation analysis (DXA) of OVITO.
 The length of Shorckley dislocation with Burgers vector $1/6[1 1 2]$ increase sharply during yield stage of the deformation process in Fig.
 \ref{fig:disum}, but the length of perfect dislocation fluctuate at a low level.
-That is mainly because decomposition of the perfect  dislocations which is given by formulation \ref{eq:dis2}, and the structure spontaneously transform into intrinsic stacking fault in Fig.
-\ref{fig:dis-alpha_2}.
+Decomposition of the perfect  dislocations split into Shockley partial dislocations as formulation \ref{eq:dis-1},ref{eq:dis-2}, and the structure spontaneously transform into intrinsic stacking fault, it can be observed in Fig.
+\ref{fig:Defect}a.
 
-\begin{equation}\label{eq:dis2}
-1/2 [\ 1\ \overline { 1 }\ 2\ ] \rightarrow 1/6 [\ 1\ \overline { 1 }\ 2\ ]  + 1/3 [\ 1\ \overline { 1 }\ 2\ ]
+%\begin{equation}\label{eq:dis-1}
+%[\ 0\ 1\ \overline{1}\ ] \to 1/2 [\ 1\ 1\ \overline{2}\ ]+1/2[\ \overline{1}\ 1\ 0\ ]\\
+%\end{equation}
+
+\begin{equation}\label{eq:dis-1}
+1/2 [\ 0\ 1\ 1\ ] \to 1/6[\ 1\ 1\ 2\ ]+1/6[\ \overline{1}\ 2\ 1\ ]
 \end{equation}
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/disl-gamma"}
-	\caption{Dislocation in $\gamma$}
-	\label{fig:dis-alpha_2}
-\end{figure}
-
-% Deformation process of model without void under uniaxial load is shown by stress-strain curve Fig. \ref{fig:deformation-pf} and
-Snapshots of atom configuration at the 5 of 10 key points are shown by Fig.
-\ref{fig:Defect}.
-Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig.\ref{fig:Defect}a,\ $\alpha_2$ phase and defects inside grains have been left.
-Similarly, $\gamma$ phase grain have been removed in Fig.
-\ref{fig:Defect}b, the defects of $\alpha_2$ phase have been left.
-The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of the model is under typical elastic deformation and the size of simulation box enlarged due to the loading, the deformation of the two phase are compatible.
-Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}.
-A  great number of dislocation emitted inside $\gamma$ phase at stage 2, however, the dislocation inside $\gamma$ phase was emitted after key point 6 shown by Fig.
-\ref{fig:Defect}b.
-The deformation of $\alpha_2$ phase is even more earlier than $\gamma$ phase during yield stage, thus local displacement of two phase are incompatible during yield stage.
-
-\begin{figure}[ht] 
-	\centering
-	\includegraphics[width=1\linewidth]{img/def2}
-	\caption{Microstructure evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) at key point 1 to 10}
-	\label{fig:Defect}
-\end{figure}
+\begin{equation}\label{eq:dis-2}
+1/2 [\ 1\ 0\ \overline{1}\ ] \to 1/6 [\ 1\ 1\ \overline{2}\ ] + 1/6[\ 2\ \overline{1}\ \overline{1}\ ]
+\end{equation}
+Interaction between dislocation with Burgers vector of $1/6 [112] $ and $ 1/6 [11\overline{2}]$ follows the decomposition of perfect dislocation.
+The process produce leading dislocation and a trailing dislocation, when the two leading Shockley partials combine, they form Lomer–Cottrell junction, a separate dislocation.
+It's sessile and immobile in the slip plane,plays a role of barrier against other dislocations in the plane.
+The process is as follow :
+\begin{equation}\label{eq:dis-3}
+1/6 [\ 1\ 1\ 2\ ] + 1/6 [\ 1\ 1\  \overline{2}\ ] \to 1/3 [\ 1\ 1\ 0\ ]
+\end{equation}
 
@@
 This may significantly reduce the Schmid factor and thus impede slip transfer.
-At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree.
+At the $\gamma/\gamma$ interfaces, the orientation of slip plan could change through a relevantly large angle of about 90 degree.
 Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1}_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{intro-structure}.
@@
 A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
-TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of [a]-type dislocations with the Burgers vector $b=1/3[11\overline{2}0]$ prism planes shown by Fig.
+TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3[11\overline{2}0]$ prism planes shown by Fig.
 \ref{fig:Defect}, which is by far the easiest slip system in $\alpha_2$ single crystals.
@@
 For example, an ordinary 1/2[110] dislocation gliding in one $\gamma$ grain has to be converted in to a $[101]$ super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
-At the $\alpha_2/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
-These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.
-Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocations, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When the slip is forced to cross $\alpha_2$ lamella, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
+At the $\alpha_2/\gamma$ interface, dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
+These core transformations are associated with a change of the dislocation line energy because the lengths of Burgers vectors and the shear module are different.
+Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocation, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When slip is forced to cross $\alpha_2$ phase, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
 
@@
 In Fig.
-\ref{fig:model-creation}, voids with different size: 2A, 5A, 10A, 15A were placed  at $\alpha_2-\gamma$ phase boundary, inside $\gamma$ phase respectively.
+\ref{fig:model-creation}, voids with different size: 2\AA, 5\AA, 10\AA, 15\AA were placed  at $\alpha_2-\gamma$ phase boundary, inside $\gamma$ phase respectively.
 The strength of materials with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
-The existence of void have little impact on the elastic properties of the material, and the model without void defect has best strength 5.3 GPa, the yield stress of model with void is smaller.
-located inside $\alpha_2$ phase detracts the strength of the material most, and the void at phase boundary have less impact on the strength.
-
-The effect of size is expectable that the greater voids detracts the strength of the materials more, however, it has been observed in the simulation that there is a critical value about 15A for voids at different position.
-The voids larger than 15 \AA\ have dramatic detraction to the strength of the material.
-Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by formulation \ref{eq:section}:
-
+The existence of void have little impact on the elastic properties of the material, and the model without void defect has the best strength 5.3 GPa, the yield stress of model with void is smaller.
+Void at $\alpha_2$-$\gamma$ phase boundary  detracts the strength of  material most, and the void inside $\alpha_2$ phase  have less impact on the strength.
+The effect of void size can be generally calculated by means of classical method proposed by 
 \begin{equation} \label{eq:section} 
@@
 \end{equation}
+It  the greater voids detracts the strength of the materials more, however, it has been observed in the simulation that there is a critical value larger than 10 \AA for voids at different position.
+The voids larger than 10 \AA\ have dramatic detraction to the strength of two phase Ti-Al alloy.
+Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by formulation :
 
-where $\sigma_0$ is the strength of the model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = 36000 {AA}^2$, $A^* $ is section area in consider of the subsection that results from the voids.
+where $\sigma_0$ is the strength of model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = 36000 {AA}^2$, $A^* $ is section area in consider of the subsection that results from the voids.
 Comparing with the strength determined by molecular dynamics simulation and the result4s calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.
@@
 In Fig.
-\ref{fig:strength} It has been observed that voids detracts the strengths of the material.
-The max stress stress of the simulation cell decreases as the volume of voids are larger.
+\ref{fig:strength} It has been observed that voids detracts the strengths of  material.
+The max stress  of the simulation cell decreases as the volume of voids are larger.
 From Fig \ref{fig:stress&strain}, there is a critical value of void radius about 15A, the void greater than 15A cause serious detraction of strength of material.
-The rate of decrease of loading area are smaller comparing with the detraction of strength, so it can be assumed that the yield yield behavior and strength is much more related with local behavior of grain boundaries and void.
+The decrease rate of loading area are smaller comparing with the detraction of strength, so it can be assumed that the  yield behavior and strength is much more related with local behavior of grain boundaries and void.
 Grain and phase boundaries are obstacles to deformation process, thus the stability of boundaries have great impact on the strength of materials.
@@
 Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength.
-In the discussion of the Frank–Read source for dislocation (-line) production  it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of “antagonistic” nature and “block” propagation of the stress field of a migrating dislocation: the second-phase particle acts as “pinning point”.
-It was already indicated that in order that a dislocation can pass two pinning points a critical shear stress is needed that depends on the distance between the obstacles (which can be second-phase particles):
+In the discussion of the Frank–Read source for dislocation production  it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of “antagonistic” nature and “block” propagation of the stress field of a migrating dislocation: the second-phase particle acts as “pinning point”.
+It was already indicated that in order that a dislocation can pass two pinning points a critical shear stress is needed that depends on the distance between  obstacles, which can be regarded as second-phase particles:
 \begin{equation} \label{eq:orowan} 

### 2018-11-12 draft/alexpub.tex
Edt-1

@@
 % \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
-\Title{Atomic Investigation on Cold Deformation Behavior of Two Phase Ti-Al Polycrystal with and without Void Defect}
+\Title{Micromechanism of  Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with and without Void Defect}
 % Author Orchid ID: enter ID or remove command
@@
 Interaction between spherical nano void with different size and position was also examined in the simulation.
-The results show that i) $\gamma$ phase is the major deformation source of the two phase alloy; ii) Voids defect detracts the strength of the two phase alloy, however the position of void affect the degree of this subtraction: voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detract to strength.}
+The results show that i) $\gamma$ phase is the major deformation source of the two phase alloy; ii) Voids defect detracts the strength of the two phase alloy, however the position of void affect the degree of this subtraction: voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detraction to strength.}
 % Keywords
@@
 The titanium  aluminum based intermetallic alloys are promising high temperature structural materials because of their great corrosion resistance at high temperature.
-Comparing with nickle based alloy,  alloys have lower density and are pron to be utilized in combustion engine, turbine, and other components work at high temperature ranging from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius}.
-The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20\% because the weight of components decreased 30\%~40\%.
+Comparing with nickle based alloy,  alloys have lower density and are pron to be utilized in combustion engine, turbine, and other components work at high temperature ranging from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius} \cite{Clemens2016}.
+The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20\% because the weight of components decreased 30\%~40\% \cite{Bewlay2016}.
 With the advancement of non-ferrous metallurgy, Ti-Al based components has better economic efficiency than ever before.
@@
 
-$\gamma $ TiAl has a fcc type cell with an $L1_0$ structure, and $\alpha_2 -\rm Ti_3Al$ has a hcp structure, the two types of initial cells are shown in Fig.
+$\gamma $ TiAl has a fcc type cell with an $L1_0$ structure, and $\alpha_2 -\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Fig.
 \ref{fig:tial-cell}, and the constructing parameters are given by Table \ref{tab:lattice_parameter}.
@@
 	\includegraphics[width=1\linewidth]{img/def2}
-	\caption{Microstructure evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) at key point 1 to 10}
+	\caption{Microstructure evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) during yield stage}
 	\label{fig:Defect}
@@
 		\centering
-		\caption{Mobility of dislocation}
+		\caption{Mobility of dislocation under stress}
 		\label{fig:temp}
@@
 		\centering
-		\caption{Dislocation length}
+		\caption{Dislocation length at different stage }
 		\label{fig:disum}
@@
 \ref{fig:disum}, but the length of perfect dislocation fluctuate at a low level.
-Decomposition of the perfect  dislocations split into Shockley partial dislocations as formulation \ref{eq:dis-1},ref{eq:dis-2}, and the structure spontaneously transform into intrinsic stacking fault, it can be observed in Fig.
+Decomposition of the perfect  dislocations split into Shockley partial dislocations as formulation \ref{eq:dis-1} and \ref{eq:dis-2}.
+The structure spontaneously transform into intrinsic stacking fault (ISF), it can be observed in Fig.
 \ref{fig:Defect}a.
@@
 \ref{fig:Defect}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
+
 A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
@@
 Void at $\alpha_2$-$\gamma$ phase boundary  detracts the strength of  material most, and the void inside $\alpha_2$ phase  have less impact on the strength.
-The effect of void size can be generally calculated by means of classical method proposed by 
+Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by
 \begin{equation} \label{eq:section} 
@@
 \end{equation}
-It  the greater voids detracts the strength of the materials more, however, it has been observed in the simulation that there is a critical value larger than 10 \AA for voids at different position.
-The voids larger than 10 \AA\ have dramatic detraction to the strength of two phase Ti-Al alloy.
-Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by formulation :
-
-where $\sigma_0$ is the strength of model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = 36000 {AA}^2$, $A^* $ is section area in consider of the subsection that results from the voids.
+where $\sigma_0$ is the strength of model without void defects 5.26 Gpa, and $A_0$ is initial section area,  $A^*$ is effective section area.
+In classic theory, the relationship between void size and strength of the model is linear.
+However, simulation results reveals that two phase Ti-Al alloy is sensitive to existence of void defect.
 Comparing with the strength determined by molecular dynamics simulation and the result4s calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.
@@
 The max stress  of the simulation cell decreases as the volume of voids are larger.
-From Fig \ref{fig:stress&strain}, there is a critical value of void radius about 15A, the void greater than 15A cause serious detraction of strength of material.
+From Fig \ref{fig:stress&strain}, there is a critical value of void radius about 15 \AA, the void greater than 15 \AA cause serious detraction of strength of material.
 The decrease rate of loading area are smaller comparing with the detraction of strength, so it can be assumed that the  yield behavior and strength is much more related with local behavior of grain boundaries and void.
@@
 Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength.
-In the discussion of the Frank–Read source for dislocation production  it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of “antagonistic” nature and “block” propagation of the stress field of a migrating dislocation: the second-phase particle acts as “pinning point”.
+In the discussion of the Frank–Read source for dislocation production  it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of block propagation of the stress field of a migrating dislocation: the second-phase particle acts as pinning point.
 It was already indicated that in order that a dislocation can pass two pinning points a critical shear stress is needed that depends on the distance between  obstacles, which can be regarded as second-phase particles:
@@
 \end{equation}
-
-where d represents the distance between A and B and thus reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution.
-This mechanism for hardening is designated as the Orowan process (with $\tau_0$ as the Orowan (shear) stress.
+where $d$ represents the distance between obstancle A and B , reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution.
+This mechanism for hardening is designated as the Orowan process with $\tau_0$ as the Orowan (shear) stress.
 

### 2018-11-16 draft/MDPI_template/temp.tex
CLEAR
cleared files

%  LaTeX support: latex@mdpi.com 
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.

%=================================================================
\documentclass[journal,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi}

% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g. \documentclass[preprints,article,accept,moreauthors,pdftex,10pt,a4paper]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%
%--------------------
% Class Options:
%--------------------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, ceramics, challenges, chemengineering, chemosensors, children, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cybersecurity, data, dentistry, designs, diagnostics, dairy, diseases, diversity, drones, econometrics, economies, education, electrochem, electrochemistry, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, ijtpp, inventions, j, jcdd, jcm, jcs, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmmp, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, medsci, medicina, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, neonatalscreening, neuroglia, nitrogen, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, plasma, polymers, polysaccharides, proceedings, processes, proteomes, publications, quaternary, qubs, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, sinusitis, smartcities, socsci, societies, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj
%---------
% article
%---------
% The default type of manuscript is article, but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferenceproceedings, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, opinion, obituary, projectreport, reply, reprint, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials
% protocol: If you are preparing a "Protocol" paper, please refer to http://www.mdpi.com/journal/mps/instructions for details on its expected structure and content.
%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g. the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2018}
\copyrightyear{2018}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
%\updates{yes} % If there is an update available, un-comment this line

%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
%\continuouspages{yes}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

% Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: +x-xxx-xxx-xxxx}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for the journal Gels: Please place the Experimental Section after the Conclusions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}
The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g. the positioning of the Materials and Methods section). Please check the instructions for authors page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}
The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. And now citing a book reference \cite{ref-book}. Please use the command \citep{ref-journal} for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Languages, Laws, Religions, Risks, Social Sciences.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\begin{quote}
This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Subsection}

\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}[leftmargin=*,labelsep=5.8mm]
\item	First bullet
\item	Second bullet
\item	Third bullet
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}[leftmargin=*,labelsep=4.9mm]
\item	First item 
\item	Second item
\item	Third item
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure 1, Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=2 cm]{Definitions/logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

Text

Text

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
entry 1		& data			& data\\
entry 2		& data			& data\\
\bottomrule
\end{tabular}
\end{table}

Text

Text

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\textwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\textwidth}{1pt}
%\end{listing}

\subsection{Formatting of Mathematical Components}

This is an example of an equation:

\begin{equation}
a + b = c
\end{equation}
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}
This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used “conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing—original draft preparation, X.X.; writing—review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.”, please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work reported.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g. materials used for experiments).}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & linear dichroism
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixsections{multiple} %Leave argument "multiple" if there are multiple sections. Then a counter is printed ("Appendix A"). If there is only one appendix section then change the argument to "one" and no counter is printed ("Appendix").
\appendix
\section{}
\subsection{}
The appendix is an optional section that can contain details and data supplemental to the main text. For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data. Mathematical proofs of results not central to the paper can be added as an appendix.

\section{}
All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: internal bibliography
%=====================================
\reftitle{References}
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149, doi:xxxxx.
% Reference 2
\bibitem[Author2(year)]{ref-book}
Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58, ISBN.
\end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%=====================================
% References, variant B: external bibliography
%=====================================
%\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds ...... are available from the authors.}

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2018-11-16 draft/alexpub.tex
add mark
CLEAR
cleared files

@@
 % \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
-\Title{Micromechanism of  Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with and without Void Defect}
+\Title{Micromechanism of  Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with Void Defect}
 % Author Orchid ID: enter ID or remove command
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Cold deformation behavior of poly crystalline metallic material is affected intrinsic defects such as dislocation, etc.
+\abstract{Cold deformation behavior of poly crystalline metallic material is affected by intrinsic defects such as dislocation, etc.
 Existing studies on $\alpha_2(\rm{Ti_3Al})$+$\gamma(\rm{TiAl})$  two phase Ti-Al alloy covers about deformation behavior mainly on macro scale.
 This paper focus on the cold deformation mechanism of two phase Ti-Al alloy at micro scale, and  the role of void defect in deformation process.
-Molecular dynamics simulations were performed to study the evolution of micro structure in the model under uniaxial tension.
+Molecular dynamics simulations were performed to study the evolution of micro structure in the material under uniaxial tension.
 Interaction between spherical nano void with different size and position was also examined in the simulation.
-The results show that i) $\gamma$ phase is the major deformation source of the two phase alloy; ii) Voids defect detracts the strength of the two phase alloy, however the position of void affect the degree of this subtraction: voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detraction to strength.}
+The results show that i) $\gamma$ phase is the major deformation source of the two phase alloy; ii) Voids defect detracts the strength of the two phase alloy, however the position of void affect the degree of this subtraction, voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detraction to strength.}
 % Keywords
-\keyword{two phase Ti-Al alloy; void defect; molecular dynamics}
+\keyword{two phase Ti-Al alloy, void, molecular dynamics, cold deformation}
 
@@
 Comparing with nickle based alloy,  alloys have lower density and are pron to be utilized in combustion engine, turbine, and other components work at high temperature ranging from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius} \cite{Clemens2016}.
-The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20\% because the weight of components decreased 30\%~40\% \cite{Bewlay2016}.
+The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20\% because the weight of components decreased from 30\% to 40\% \cite{Bewlay2016}.
 With the advancement of non-ferrous metallurgy, Ti-Al based components has better economic efficiency than ever before.
@@
 Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially easily formed in the casting process, such as voids and inclusions \cite{Tang2014}.
-A great number of literature covers a wide range of parameters such as alloy composition, microstructure and deformation temperature.
+A great number of literature covers a wide range of factors such as alloy composition, microstructure and deformation temperature.
 Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}.
 Due to difficulties in observing the dynamic process during deformation wit experiments, MD simulation has become an effective method to investigate micro deformation mechanism.
-Defects such as grain boundary, void and segregation plays a significant role in the process of fracture \cite{Larsen2016}.
-Multiscale method have been applied to study deformation behavior polycrystal with single aluminum \cite{Groh2009} and titanium element \cite{Liu2018}.
+Defects such as grain boundary, void and segregation play a significant role in the process of fracture \cite{Larsen2016}.
+Multiscale method have been applied to study deformation behavior of polycrystal with single aluminum \cite{Groh2009} and titanium element respectively \cite{Liu2018}.
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
 
-The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study of detailed mechanisms of deformation and cracking, these defects are known to play a fundamental role in the deformation of materials.
+The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study about  mechanisms of deformation and cracking, these defects are known to play a fundamental role in the deformation of materials.
 It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
 Therefore, it is necessary to study the deformation response of intermetallics structural materials with the consideration of microstructure evolution.
-The effect of void defect is another great concern about properties of deformation mechanism about of TiAl alloy.
-A previous study on void growth in $\gamma$-TiAl single crystal has reveals that void with high volume fraction detracts yield strength, and emission of dislocation \cite{Tang2014, Xu2011}.
+The effect of void defect is another great concern about properties and deformation mechanism  of TiAl alloy.
+A previous study on void growth in single crystal $\gamma$-TiAl reveals that void with high volume fraction detracts yield strength, and emission of dislocation \cite{Tang2014, Xu2011}.
 Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations \cite{Jing2018a,Elkhateeb2018}.
@@
 Ti-Al alloy is a type of typical brittle material, thus it can be assumed that its properties are sensitive to the existence of void defect.
-Surface defects such as small notches can caused lower high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$  TiAl is also lowered by point defect \cite{Wu2016}.
+Surface defects such as small notches can caused low and high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$  TiAl is also lowered by point defect \cite{Wu2016}.
 The resistance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was markedly reduced due to earlier crack initiation.
-The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small micro-cracks in the damaged zone.This paper focus on the evolution of microstructure, tend to find out it connection to cold deformation behavior of two phase TiAl alloy.
-MD simulation including model creation and analysis method is given in Section \ref{section:method}; Results and discussion are in Section \ref{section:RD}.
+The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small micro-cracks in the damaged zone.This paper focus on the evolution of microstructure, tend to find out its connection to cold deformation behavior of two phase TiAl alloy.
+MD simulation including model creation and analysis method is given in Section \ref{section:method}, Results and discussion are in Section \ref{section:RD}.
 
@@
 The interaction of particle in the material is determined by interatomic potential.
-Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to is better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015}.
+Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to its better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015}.
 The embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study.
@@
 
-where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system,$F_i(\rho)$ is the energy for embedding atom $i$ into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ is the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$.
+where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system,$F_i(\rho)$ represents the energy for embedding atom $i$ into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ give the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$.
 It can be noted that $F_i$ only depends on the element of atom $i$ and $\phi_{ij}$ only depends on the elements of atoms $i$ and $j$.
@@
 	\centering
-	\includegraphics[width=1\linewidth]{img/tial-cell2}
+	\includegraphics[width=1\linewidth]{img/modeling}
 	\caption{Unit cell of \rm{TiAl} (a) and $\rm{Ti_3Al}$ (b)}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{img/perfect-line2-2}
+	\includegraphics[width=1\linewidth]{img/tens}
 	\caption{Deformation process of the model without void defect}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{img/def2}
+	\includegraphics[width=1\linewidth]{img/def-box}
 	\caption{Microstructure evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) during yield stage}
@@
 	\begin{minipage}{0.495\textwidth}		
-		\includegraphics[width=1\linewidth]{img/disum}
+		\includegraphics[width=1\linewidth]{img/dis-summary}
 		\centering
@@
 The length of Shorckley dislocation with Burgers vector $1/6[1 1 2]$ increase sharply during yield stage of the deformation process in Fig.
-\ref{fig:disum}, but the length of perfect dislocation fluctuate at a low level.
+\ref{fig:dis-summary}, but the length of perfect dislocation fluctuate at a low level.
 Decomposition of the perfect  dislocations split into Shockley partial dislocations as formulation \ref{eq:dis-1} and \ref{eq:dis-2}.
@@
 	\centering
-	\includegraphics[width=1\linewidth]{img/models}
+	\includegraphics[width=1\linewidth]{img/slice-view}
 	\caption{ Model with no void defect (b), with void inside $\alpha_2$ phase (c) with void at $\alpha_2-\gamma$ interface (d)}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{"img/dis-void2"}
+	\includegraphics[width=1\linewidth]{"img/orowan"}
 	\caption{Orowan process in $\alpha$-phase ($\alpha$ phase atoms have been removed)}

### 2018-11-16 code/SigLinePlt.py

@@ -1,22 +1,0 @@
-import os
-import numpy as np
-import matplotlib.pyplot as plt
-file_path = os.path.join('data', 'inflammation-01.csv')
-# pre-set head name
-
-#wdir = os.path.abspath('.')
-pyy = np.loadtxt("/home/alex/Documents/str.txt")
-
-# pyy = np.loadtxt("wdir/code/data/crack_surf/ig_10.txt")
-pxx = np.linspace(0, 0.4, (len(pyy)))
-
-plt.plot(pxx, pyy)
-plt.title('Area of Crack Surface')
-plt.xlabel('strain')
-plt.ylabel('Area/A2')
-#plt.savefig('area.png')
-plt.show()
-#plt.savefig()
-
-
-

### 2018-11-16 code/agline.py

@@ -1,28 +1,0 @@
-# 读取输出文件，绘制应力应变曲线
-import os
-import os.path
-import matplotlib.pyplot as plt
-import pandas as pd
-from os import listdir
-
-WDIR = os.path.dirname(__file__)
-loadpath = os.path.join(WDIR,'data','stress_strain')
-writepath = os.path.join(WDIR,'..','draft','img')
-# pre-set head name
-prop = ['step', 'strain', 'stress', 'energy']
-# import data from .csv file:
-ds1 = pd.read_csv(os.path.join(loadpath,'ag.csv'), sep=' ', skiprows=1, names=prop)
-
-# plot lines
-p1 = plt.plot(ds1.step, ds1.stress, label='ag')
-
-# config title and label
-
-plt.title('stress-strain curve')
-plt.xlabel('Step')
-plt.ylabel('Stress (GPa)')
-plt.xlim(1e5,2e5)
-
-
-plt.savefig(os.path.join(writepath,'agline.pdf'))
-plt.show()

### 2018-11-16 code/dissum.py

@@ -59,7 +59,7 @@ plt.ylim(ymax=5000)
 plt.xticks(index + bar_width, ('Initial', 'Before yield', 'After yield', 'Cracked'))
 plt.legend(frameon = False)
 
-plt.savefig(os.path.join(writepath, 'disum.pdf'))
+plt.savefig(os.path.join(writepath, 'dis-summary.pdf'))
 
 #plt.tight_layout()
 plt.show()

### 2018-11-16 code/exp.py

@@ -1,60 +1,0 @@
-# 读取输出文件，绘制应力应变曲线
-'''
-violet
-├── code
-│   ├── data
-│   │   ├── size
-│   │   ├── stress_strain
-│   │   └── surf
-│   └── pict
-└── draft
-    ├── bkp
-    ├── img
-    ├── material
-    └── ref
-'''
-
-import os
-import os.path
-from os import listdir
-import matplotlib.pyplot as plt
-import pandas as pd
-plt.rcParams["font.family"] = 'Times New Roman'
-import matplotlib.pyplot as plt
-plt.rcParams.update({'font.size': 12})
-#csfont = {'fontname':'Times New Roman'}
-#plt.rcParams["font.family"] = "Times New Roman"
-WDIR = os.path.dirname(__file__)
-loadpath = os.path.join(WDIR,'data','stress_strain')
-writepath = os.path.join(WDIR,'..','draft','img')
-# pre-set head name
-prop = ['step', 'strain', 'stress', 'energy']
-# import data from .csv file:
-#ds1 = pd.read_csv(os.path.join(loadpath,'aa.csv'), sep=' ', skiprows=1, names=prop)
-ds2 = pd.read_csv(os.path.join(loadpath,'ag.csv'), sep=' ', skiprows=1, names=prop)
-ds3 = pd.read_csv(os.path.join(loadpath,'pf.csv'), sep=' ', skiprows=1, names=prop)
-ds4 = pd.read_csv(os.path.join(loadpath,'ia.csv'), sep=' ', skiprows=1, names=prop)
-fct = 10e6
-px2=ds2.step/fct
-px3=ds3.step/fct
-px4=ds4.step/fct
-
-# plot lines
-#p1 = plt.plot(ds1.step, ds1.stress, label='aa')
-p2 = plt.plot(px2, ds2.stress, label='ag')
-p3 = plt.plot(px3, ds3.stress, label='pf')
-p4 = plt.plot(px4, ds4.stress, label='ia')
-# config title and label
-
-#plt.title('stress-strain curve')
-plt.xlabel('Strain')
-plt.xlim(xmax=0.035)
-plt.ylim(ymax=6)
-plt.ylabel('Stress (GPa)')
-plt.legend(frameon=False)
-plt.savefig(os.path.join(writepath, 'allline.pdf'))
-
-plt.show()
-# /home/alex/violet/all.line.pdf
-# /home/alex/violet/code/pict/area.png
-# /home/alex/violet/draft/img/ag.pngf

### 2018-11-16 code/ialine.py

@@ -1,31 +1,0 @@
-# 读取输出文件，绘制应力应变曲线
-import os
-import os.path
-import matplotlib.pyplot as plt
-import pandas as pd
-from os import listdir
-plt.rcParams.update({'font.size': 12})
-
-WDIR = os.path.dirname(__file__)
-loadpath = os.path.join(WDIR,'data')
-writepath = os.path.join(WDIR,'..','draft','img')
-# pre-set head name
-prop = ['step', 'strain', 'stress', 'energy']
-# import data from .csv file:
-ds1 = pd.read_csv(os.path.join(loadpath,'pfct.txt'), sep=' ', skiprows=1, names=prop)
-plt.figure(figsize=(8.5,2.5))
-# plot lines
-p1 = plt.plot(ds1.strain, ds1.stress, label='ag')
-vlinex = [130000, 130000]
-vliney = [4, 6]
-# p2 = plt.plot(vlinex,vliney)
-# config title and label
-
-#plt.title('stress-strain curve')
-plt.xlabel('Strain')
-plt.ylabel('Stress (GPa)')
-#plt.xlim(0,2e5)
-
-
-plt.savefig(os.path.join(writepath,'perfect-line.pdf'))
-plt.show()

### 2018-11-16 code/maplot.py

@@ -1,28 +1,0 @@
-import os
-import matplotlib.pyplot as plt
-import pandas as pd
-
-def mplt(pos):
-    plt.title('stress-strain curve')
-    plt.xlabel('Step')
-    plt.ylabel('Stress (GPa)')
-    plt.xlim(xmax=2.5e5)
-    plt.plot(pos.step, pos.stress, label='%s' %pos)
-    plt.savefig('/home/alex/violet/draft/img/%sline.pdf' %pos)
-    #plt.cla()
-    #plt.show()
-
-# pre-set head name
-prop = ['step', 'strain', 'stress', 'energy']
-# import data from .csv file:
-d_aa = pd.read_csv('~/violet/code/data/stress_strain/aa.csv', sep=' ', skiprows=1, names=prop)
-d_ag = pd.read_csv('~/violet/code/data/stress_strain/ag.csv', sep=' ', skiprows=1, names=prop)
-d_pf = pd.read_csv('~/violet/code/data/stress_strain/pf.csv', sep=' ', skiprows=1, names=prop)
-d_ia = pd.read_csv('~/violet/code/data/stress_strain/ia.csv', sep=' ', skiprows=1, names=prop)
-
-pos = [d_aa, d_ag, d_pf, d_ia]
-
-
-map(mplt(pos),pos)
-    #plt.savefig('/home/alex/HDD/str-pict/frame%s.png' % frame)
-    

### 2018-11-16 code/pict/pfctline.py

@@ -1,34 +1,0 @@
-# 读取输出文件，绘制应力应变曲线
-import os
-import matplotlib.pyplot as plt
-import pandas as pd
-#csfont = {'fontname':'Times New Roman'}
-#WDIR = os.getcwd()
-#loadpath = os.path.join(WDIR,'code','data','stress_strain')
-#writepath = os.path.join(WDIR,'draft','img')
-
-WDIR = os.path.dirname(__file__)
-loadpath = os.path.join(WDIR,'data','stress_strain')
-writepath = os.path.join(WDIR,'..','draft','img')
-# pre-set head name
-prop = ['step', 'strain', 'stress', 'energy']
-# import data from .csv file:
-ds1 = pd.read_csv('/home/alex/Documents/violet/code/data/stress_strain/pf.csv', sep=' ', skiprows=1, names=prop)
-# /home/alex/Documents/violet/code/data/stress_strain/pf.csv
-# plot lines
-p1 = plt.plot(ds1.strain, ds1.stress, label='ia')
-
-# config title and label
-
-plt.title('stress-strain curve')
-plt.xlabel('Step')
-plt.ylabel('Stress (GPa)')
-#plt.xlim(1e5,2e5)
-
-#plt.lim(-6,6)
-#plt.legend()
-plt.savefig('pfline.pdf')
-plt.show()
-#/home/alex/violet/all.line.pdf
-#/home/alex/violet/code/pict/area.png
-#/home/alex/violet/draft/img/ag.png

### 2018-11-16 code/surf_div.py

@@ -1,44 +1,0 @@
-
-import os
-import os.path
-import numpy as np
-import matplotlib.pyplot as plt
-plt.rcParams.update({'font.size': 12})
-
-
-#WDIR = os.getcwd()
-WDIR = os.path.dirname(__file__)
-loadpath = os.path.join(WDIR,'data','surf')
-#writepath = os.path.join(WDIR,'draft','img')
-writepath = os.path.join(WDIR,'..','draft','img')
-
-#plt.savefig(os.path.join(WDIR,'draft','img','surf.pdf'))
-#loadpath = os.path.join(WDIR,'code','data','surf')
-ag =np.loadtxt(os.path.join(loadpath,'surf_ag.txt'))
-ia =np.loadtxt(os.path.join(loadpath,'surf_ia.txt'))
-ig =np.loadtxt(os.path.join(loadpath,'surf_ig.txt'))
-pf =np.loadtxt(os.path.join(loadpath,'surf_pf.txt'))
-#d_pf = np.gradient(pf)
-imglist =[ag, ig, pf]
-dv1st = list(map(np.gradient,imglist))
-#colorlist = ['g','b','r']
-# markerlist = ['s','^','o']
-max = list(map(np.max,dv1st))
-min = np.min(np.abs(ag))
-for img in dv1st:
-    pxx = np.linspace(0,np.dot(0.005,len(img)),len(img))/10
-    plt.plot(pxx, img/np.max(max))
-# plt.title('1st Deviation of Area of Surface of Crack')
-plt.xlabel('Strain')
-plt.ylabel('Relative Crack Propagation Indicator')
-plt.xlim(xmax=0.03)
-plt.legend(["ag","ig", "pf"],frameon=False)
-# plt.legend()
-plt.savefig(os.path.join(writepath,'1stdiv.pdf'))
-
-plt.show()
-plt.cla
-plt.clf()
-
-
-

### 2018-11-16 code/surfidt.py

@@ -1,29 +1,0 @@
-
-import os
-import os.path
-import numpy as np
-import matplotlib.pyplot as plt
-
-
-WDIR = os.path.dirname(__file__)
-loadpath = os.path.join(WDIR,'data','surf')
-writepath = os.path.join(WDIR,'..','draft','img')
-#plt.savefig(os.path.join(WDIR,'draft','img','surf.pdf'))
-#loadpath = os.path.join(WDIR,'code','data','surf')
-ag = np.loadtxt(os.path.join(loadpath,'surf_ag.txt'))
-ia = np.loadtxt(os.path.join(loadpath,'surf_ia.txt'))
-ig = np.loadtxt(os.path.join(loadpath,'surf_ig.txt'))
-pf = np.loadtxt(os.path.join(loadpath,'surf_pf.txt'))
-
-imglist = [ag, ia, ig, pf]
-for img in imglist:
-    pxx = range(len(img))
-    plt.plot(pxx, img)
-plt.title('Growth of Crack')
-plt.xlabel('strain')
-plt.ylabel('area of crack surface')
-plt.legend(["ag", "ia", "ig", "pf"],frameon=False)
-plt.savefig(os.path.join(writepath,'surf.pdf'))
-plt.show()
-
-

### 2018-11-16 code/temp.py

@@ -1,19 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-WDIR = os.path.dirname(__file__)
-# loadpath = os.path.join(WDIR,'data','stress_strain')
-writepath = os.path.join(WDIR,'..','draft','img')
-T = np.linspace(0,1000,1500)
-key = 20*np.e**(-150/298)/20
-key1=[298,298]
-key2=[0,key]
-u = 20*np.e**(-150/T)/20
-v = 20*np.e**(-250/T)/20
-w = 20*np.e**(-100/T)/20
-plt.xlabel('Temperature/K')
-plt.ylabel('Normalized Velocity of Dislocation')
-plt.plot(key1,key2)
-plt.plot(T,u,label='T1')
-plt.plot(T,v,label='T2')
-plt.plot(T,w,label='T3')
-plt.show()

### 2018-11-17 code/Temp.py
参照冯老师的意见修改
1. 修改了插图字体，标注 
2. 改正了正文的若干错误

@@ -7,7 +7,7 @@ plt.rcParams.update({'font.size': 14})
 from matplotlib import rc
 rc('text', usetex=True)
 #csfont = {'fontname':'Times New Roman'}
-#plt.rcParams["font.family"] = "Times New Roman"
+plt.rcParams["font.family"] = "Times New Roman"
 WDIR = os.path.dirname(__file__)
 # loadpath = os.path.join(WDIR,'data','stress_strain')
 writepath = os.path.join(WDIR,'..','draft','img')

### 2018-11-17 code/dissum.py

@@ -6,8 +6,7 @@ import os.path
 import matplotlib.pyplot as plt
 
 #csfont = {'fontname':'Times New Roman'}
-#plt.rcParams["font.family"] = "Times New Roman"
-
+plt.rcParams["font.family"] = 'Times New Roman'
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import rc

### 2018-11-17 draft/alexpub.tex
1 .修改了插图字体，标注 2. 改正了正文的若干错误

@@
 
-where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system,$F_i(\rho)$ represents the energy for embedding atom $i$ into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ give the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$.
+where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system,$F_i(\rho)$ represents the energy for embedding atom $i$ into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ gives the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$.
 It can be noted that $F_i$ only depends on the element of atom $i$ and $\phi_{ij}$ only depends on the elements of atoms $i$ and $j$.
@@
 	\includegraphics[width=1\linewidth]{img/modeling}
-	\caption{Unit cell of \rm{TiAl} (a) and $\rm{Ti_3Al}$ (b)}
+	\caption{Unit cell of \rm{TiAl} (a), $\rm{Ti_3Al}$ (b) and two phase Ti-Al model (c)}
 	\label{fig:tial-cell}
@@
 According to stress response under constant rate of strain rate, the whole tensile process can be divided into four stages:
-Stage - \uppercase\expandafter{\romannumeral1}: elastic stage,ranging from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1;
-Stage - \uppercase\expandafter{\romannumeral2}: yield stage, ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6;
-Stage - \uppercase\expandafter{\romannumeral3}: cracking stage, ranging from $\epsilon = 0.101$ to $\epsilon = 0.112$, including key pint 7 to 10;
+Stage - \uppercase\expandafter{\romannumeral1}: elastic stage,ranging from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1,
+Stage - \uppercase\expandafter{\romannumeral2}: yield stage, ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6,
+Stage - \uppercase\expandafter{\romannumeral3}: cracking stage, ranging from $\epsilon = 0.101$ to $\epsilon = 0.112$, including key pint 7 to 10,
 Stage - \uppercase\expandafter{\romannumeral4}: fracture stage.
@@
 		% \midule
-		\textbf{Strain}	& 0.05 &  0.092 & 0.092 & 0.096 & 0.099 & 0.101 & 0.104 & 0.107 & 0.110 & 0.112 \\
+		\textbf{Strain}	& 0.05 &  0.088 & 0.092 & 0.096 & 0.099 & 0.101 & 0.104 & 0.107 & 0.110 & 0.112 \\
 		\bottomrule
@@
 \ref{fig:Defect}.
-Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig.\ref{fig:Defect}a,\ $\alpha_2$ phase and defects inside grains have been left.
+Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig.
+\ref{fig:Defect}(a),\ $\alpha_2$ phase and defects inside grains have been left.
 Similarly, $\gamma$ phase grain have been removed in Fig.
-\ref{fig:Defect}b, the defects of $\alpha_2$ phase have been left.
+\ref{fig:Defect}(b), the defects of $\alpha_2$ phase have been left.
 The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of the model is under typical elastic deformation and the size of simulation box enlarged due to the loading, deformation of the two phase are compatible.
 Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}.
-A  great number of dislocation emitted inside $\gamma$ phase at stage 2, however, the dislocation inside $\gamma$ phase was emitted after key point 5 shown by Fig.
-\ref{fig:Defect}b.
+A  great number of dislocation emitted inside $\gamma$ phase at stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\gamma$ phase was emitted after key point 5 shown by Fig.
+\ref{fig:Defect}(b).
 The deformation of $\alpha_2$ phase is earlier than $\gamma$ phase during yield stage, thus local displacement of two phase are incompatible during yield stage.
@@
 \end{equation}
-where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions.
-The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\tau_1^*>\tau_2^*>\tau_3^*$ in formulation \ref{eq:temp-dis}, normalized velocity is shown in Fig \ref{fig:temp}.
+where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ represents the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions.
+The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\tau_1^*>\tau_2^*>\tau_3^*$ in formulation (\ref{eq:temp-dis}), normalized velocity is shown in Fig.
+\ref{fig:temp}.
 The  velocity  of dislocation movement rise along with increase of  stress, the speed of dislocation is relatively low at 298 K, and it is more sensitive to temperature than shear stress.
@@
 \ref{fig:dis-summary}, but the length of perfect dislocation fluctuate at a low level.
-Decomposition of the perfect  dislocations split into Shockley partial dislocations as formulation \ref{eq:dis-1} and \ref{eq:dis-2}.
+Decomposition of the perfect  dislocations split into Shockley partial dislocations as formulation (\ref{eq:dis-1}) and (\ref{eq:dis-2}).
 The structure spontaneously transform into intrinsic stacking fault (ISF), it can be observed in Fig.
-\ref{fig:Defect}a.
+\ref{fig:Defect}(a).
 
@@
 \begin{figure}[ht]
-	\centering
+	\centeringz
 	\includegraphics[width=1\linewidth]{img/slice-view}
@@
 
-\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
+\subsection{Evolution of spherical void}
 

### 2018-11-17 code/allline.py

@@ -19,7 +19,7 @@ import os.path
 from os import listdir
 import matplotlib.pyplot as plt
 import pandas as pd
-# plt.rcParams["font.family"] = 'Times New Roman'
+plt.rcParams["font.family"] = 'Times New Roman'
 import matplotlib.pyplot as plt
 plt.rcParams.update({'font.size': 14})
 from matplotlib import rc

### 2018-11-17 code/data/size/size_summary.py

@@ -21,7 +21,7 @@ plt.rcParams.update({'font.size': 14})
 from matplotlib import rc
 rc('text', usetex=True)
 
-# plt.rcParams["font.family"] = 'Times New Roman'
+plt.rcParams["font.family"] = 'TimesNewRoman'
 
 WDIR = os.path.dirname(__file__)
 writepath = os.path.join(WDIR,'..','..','..','draft','img')
@@ -31,9 +31,10 @@ iamax = np.array([5.3, 5.26, 5.25, 5.22, 5.19, 4.96])
 agmax = np.array([5.3, 5.25, 5.17, 5.11, 5.09, 4.87])
 fac = (1-(np.pi*(size/2)**2)/(210*180))*iamax[0]
 # pia = fit.gaussian(size,iamax)
+plt.plot(size, fac, marker='o',linestyle='--',color='R')
 plt.plot(size, iamax,marker='s',color='G')
 plt.plot(size, agmax, marker='^',color='B')
-plt.plot(size, fac, marker='o',linestyle='--',color='R')
+
 # color='darkorange'
 # color='steelblue'
 plt.legend([r'void inside $\alpha$ phase', r'void at \textbf{$\alpha$-$\gamma$} phase boundary','calculated value'], frameon=False)

### 2018-11-17 draft/alexpub.tex
修改了图片 改正了些许文字错误

@@
 
-$\gamma $ TiAl has a fcc type cell with an $L1_0$ structure, and $\alpha_2 -\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Fig.
+$\gamma $ TiAl has a fcc type cell with an $L1_0$ structure, and $\alpha_2$-$\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Fig.
 \ref{fig:tial-cell}, and the constructing parameters are given by Table \ref{tab:lattice_parameter}.
-Periodic boundary conditions (PBC) are applied along all three directions, that makes poly crystal with periodic nanovoid structures.
-The initial dimension of simulation cell is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model contains about 4.6 million atoms.
+Periodic boundary conditions (PBC) are applied along all three directions, that makes polycrystal with periodic nanovoid structures.
+The initial dimension of simulation cell is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model contains about 460,000 atoms.
 The grain orientation and size were randomly created with Voronoi method by code ATOMSK \cite{Hirel2015}, and resulting in the arbitrary shape and orientation of the grains.
@@
 The centro-symmetry parameter(CSP) is zero for atoms in a perfect lattice.
-In other words, if the lattice is distorted the value of P will not be zero.
+In other words, if the lattice is distorted, the value of P will not be zero.
 Instead, the parameter will have a value within the range corresponding to a particular defect.
-By removing all the perfect and surface atoms within the bulk, the existence of dislocation atoms become visible.
+By removing all the perfect and surface atoms within the bulk, atoms around dislocation zone are visualized.
 
@@
 The core of a dislocation intersecting an interface often needs to be transformed.
-For example, an ordinary 1/2[110] dislocation gliding in one $\gamma$ grain has to be converted in to a $[101]$ super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
-At the $\alpha_2/\gamma$ interface, dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure.
+For example, an ordinary 1/2 [110] dislocation gliding in one $\gamma$ grain has to be converted into a $[101]$ super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
+At the $\alpha_2/\gamma$ interface, dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $\rm{L1_0}$ structure.
 These core transformations are associated with a change of the dislocation line energy because the lengths of Burgers vectors and the shear module are different.
@@
 In Fig.
-\ref{fig:model-creation}, voids with different size: 2\AA, 5\AA, 10\AA, 15\AA were placed  at $\alpha_2-\gamma$ phase boundary, inside $\gamma$ phase respectively.
+\ref{fig:model-creation}, voids with different size: 2\AA, 5\AA, 10\AA, 15\AA\ were placed  at $\alpha_2-\gamma$ phase boundary, inside $\gamma$ phase respectively.
 The strength of materials with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
@@
 
-In Fig.
-\ref{fig:strength} It has been observed that voids detracts the strengths of  material.
+It has been observed in Fig.
+\ref{fig:strength} that voids detracts the strengths of  material.
 The max stress  of the simulation cell decreases as the volume of voids are larger.
-From Fig \ref{fig:stress&strain}, there is a critical value of void radius about 15 \AA, the void greater than 15 \AA cause serious detraction of strength of material.
+From Fig.
+\ref{fig:stress&strain}, there is a critical value of void radius about 15 \AA, the void greater than 15 \AA\ cause serious detraction of strength of material.
 The decrease rate of loading area are smaller comparing with the detraction of strength, so it can be assumed that the  yield behavior and strength is much more related with local behavior of grain boundaries and void.
@@
 The role of void can be concluded as two main parts: source of dislocation and obstacles to dislocations.
-Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, associated with the occurrence of incoherent or coherent interfaces;the long-range translation symmetry of the matrix.
+Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, associated with the occurrence of incoherent or coherent interfaces, the long-range translation symmetry of the matrix.
 They may induce considerable misfit-stress fields and thus can influence material properties pronouncedly.

### 2018-11-17 code/allline.py

@@ -19,11 +19,14 @@ import os.path
 from os import listdir
 import matplotlib.pyplot as plt
 import pandas as pd
-plt.rcParams["font.family"] = 'Times New Roman'
+from matplotlib import rc
 import matplotlib.pyplot as plt
 plt.rcParams.update({'font.size': 14})
-from matplotlib import rc
+plt.rcParams["font.family"] = 'Times New Roman'
+
 rc('text', usetex=True)
+
+# rc('text', usetex=True)
 #csfont = {'fontname':'Times New Roman'}
 #plt.rcParams["font.family"] = "Times New Roman"
 WDIR = os.path.dirname(__file__)
@@ -39,16 +42,16 @@ prop = ['step', 'strain', 'stress', 'energy']
 ds2 = pd.read_csv(os.path.join(loadpath,'ag.csv'), sep=' ', skiprows=1, names=prop)
 ds3 = pd.read_csv(os.path.join(loadpath,'pf.csv'), sep=' ', skiprows=1, names=prop)
 ds4 = pd.read_csv(os.path.join(loadpath,'ia.csv'), sep=' ', skiprows=1, names=prop)
-fct = 10e6
+fct = 10e6*0.75
 px2=ds2.step/fct
 px3=ds3.step/fct
 px4=ds4.step/fct
 
 # plot lines
 #p1 = plt.plot(ds1.step, ds1.stress, label='aa')
-p3 = plt.plot(px3, ds3.stress, color = 'R')
-p2 = plt.plot(px2, ds2.stress, color = 'G')
-p4 = plt.plot(px4, ds4.stress, color = 'B')
+p3 = plt.plot((ds3.strain-0.015)*1.2, ds3.stress, color = 'R')
+p2 = plt.plot((ds2.strain-0.015)*1.2, ds2.stress, color = 'G')
+p4 = plt.plot((ds4.strain-0.015)*1.2, ds4.stress, color = 'B')
 
 plt.legend([ 'no void',r'void inside $\alpha$ phase',r'void at \textbf{$\alpha$-$\gamma$} phase boundary'], frameon=False)
 
@@ -56,9 +59,9 @@ plt.legend([ 'no void',r'void inside $\alpha$ phase',r'void at \textbf{$\alpha$-
 
 #plt.title('stress-strain curve')
 plt.xlabel('Strain')
-plt.xlim(xmax=0.035)
-plt.ylim(ymax=6)
[…]

### 2018-11-17 code/data/size/size_summary.py

@@ -20,8 +20,7 @@ from scipy.optimize import curve_fit as fit
 plt.rcParams.update({'font.size': 14})
 from matplotlib import rc
 rc('text', usetex=True)
-
-plt.rcParams["font.family"] = 'TimesNewRoman'
+plt.rcParams["font.family"] = 'Times New Roman'
 
 WDIR = os.path.dirname(__file__)
 writepath = os.path.join(WDIR,'..','..','..','draft','img')
@@ -37,7 +36,7 @@ plt.plot(size, agmax, marker='^',color='B')
 
 # color='darkorange'
 # color='steelblue'
-plt.legend([r'void inside $\alpha$ phase', r'void at \textbf{$\alpha$-$\gamma$} phase boundary','calculated value'], frameon=False)
+plt.legend(['calculated value',r'void inside $\alpha$ phase', r'void at \textbf{$\alpha$-$\gamma$} phase boundary'], frameon=False)
 plt.ylim(4.8,5.5)
 plt.xlabel(r'Radius of Void/ \AA')
 plt.ylabel('Strength/GPa')

### 2018-11-17 draft/alexpub.tex
修改图片格式

@@
 In Fig.
-\ref{fig:model-creation}, voids with different size: 2\AA, 5\AA, 10\AA, 15\AA\ were placed  at $\alpha_2-\gamma$ phase boundary, inside $\gamma$ phase respectively.
+\ref{fig:model-creation}, voids with different size: 2\AA, 5\AA, 10\AA, 15\AA\ were placed  at $\alpha_2$/$\gamma$ phase boundary, inside $\gamma$ phase respectively.
 The strength of materials with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.

### 2018-11-19 draft/alexpub.tex
增加了小插图

@@
  %=================================================================
-\documentclass[metals,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi} 
+\documentclass[Unknown,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi} 
 \usepackage{siunitx}
@@
 
+Void defect can arise due to specific volume differences induced by precipitation or by different thermal expansion or shrinkage upon heating or cooling the specimen.
+It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
 The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study about  mechanisms of deformation and cracking, these defects are known to play a fundamental role in the deformation of materials.
-It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
 Therefore, it is necessary to study the deformation response of intermetallics structural materials with the consideration of microstructure evolution.
@@
 Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig.
-\ref{fig:Defect}(a),\ $\alpha_2$ phase and defects inside grains have been left.
+\ref{fig:Defect}(a) and (b),\ $\alpha_2$ phase and defects inside grains have been left.
 Similarly, $\gamma$ phase grain have been removed in Fig.
-\ref{fig:Defect}(b), the defects of $\alpha_2$ phase have been left.
-The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of the model is under typical elastic deformation and the size of simulation box enlarged due to the loading, deformation of the two phase are compatible.
+\ref{fig:Defect}(b) and (c), the defects of $\alpha_2$ phase have been left.
+The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of material is under typical elastic deformation and the size of simulation box enlarged due to the loading, deformation of the two phase are compatible.
 Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}.
-A  great number of dislocation emitted inside $\gamma$ phase at stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\gamma$ phase was emitted after key point 5 shown by Fig.
-\ref{fig:Defect}(b).
-The deformation of $\alpha_2$ phase is earlier than $\gamma$ phase during yield stage, thus local displacement of two phase are incompatible during yield stage.
-
+A  great number of dislocation emitted inside $\gamma$ phase at beginning of stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\alpha_2$ phase was emitted at the end of stage \uppercase\expandafter{\romannumeral2} shown by Fig.
+\ref{fig:Defect}(c).
+The deformation of $\alpha_2$ phase is earlier than $\gamma$ phase during yield stage, thus local displacement of two phases are incompatible during yield stage.
+The mobility of dislocation is affected by structure of crystal, loading condition and temperature.
+$\alpha_2$ phase is made up of hcp  structured grain, grain with this type of structure possess less slip system compering with grain with fcc structure \cite{Zhu2012}, thus $\alpha_2$ phase is difficult do be deformed under uniaxial tensile loading.
 \begin{figure}[ht] 
@@
 	\includegraphics[width=1\linewidth]{img/def-box}
-	\caption{Microstructure evolution inside $\gamma$ phase(a), $\alpha_2$ phase(b) during yield stage}
+	\caption{Microstructure evolution inside $\gamma$ phase(a,b), $\alpha_2$ phase(c,d) during yield stage}
 	\label{fig:Defect}
@@
 
-The mobility of dislocation is affected by structure of crystal, loading condition and temperature, and experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature\cite{Stein1960}.
+Experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature\cite{Stein1960}.
 The brittleness of two phase Ti-Al alloy attributed to the poor mobility of dislocation at room temperature.
@@
 where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ represents the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions.
-The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\tau_1^*>\tau_2^*>\tau_3^*$ in formulation (\ref{eq:temp-dis}), normalized velocity is shown in Fig.
+The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\tau_1^*>\tau_2^*>\tau_3^*$ in formulation (\ref{eq:temp-dis}), normalized velocity of dislocation motion is shown by Fig.
 \ref{fig:temp}.
-The  velocity  of dislocation movement rise along with increase of  stress, the speed of dislocation is relatively low at 298 K, and it is more sensitive to temperature than shear stress.
+The  velocity  of dislocation movement rise along with increase of  stress, the mobility  of dislocation is relatively poor at room temperature 298 K.
+Due to motion of dislocation is inactive inside $alpha_2$ phase, piling up of dislocations, the typical strengthening mechanism closely related with interaction between grain boundary and dislocation was not observed in Fig.
+\ref{fig:Defect}.
 
@@
 		\centering
-		\caption{Mobility of dislocation under stress}
+		\caption{Normalized velocity of dislocation motion under different loading conditions}
 		\label{fig:temp}
@@
 		\centering
-		\caption{Dislocation length at different stage }
+		\caption{Dislocation length under differentstrain }
 		\label{fig:disum}
@@
 
-In Fig.
-\ref{fig:disum}, length of different type dislocation are given at four stages.
+Length of different types of dislocations are given at four stages in Fig.
+\ref{fig:disum}.
 Dislocations are recognized and identified using the dislocation analysis (DXA) of OVITO.
 The length of Shorckley dislocation with Burgers vector $1/6[1 1 2]$ increase sharply during yield stage of the deformation process in Fig.
-\ref{fig:dis-summary}, but the length of perfect dislocation fluctuate at a low level.
+\ref{fig:disum}, but the length of perfect dislocation fluctuate at a low level.
 Decomposition of the perfect  dislocations split into Shockley partial dislocations as formulation (\ref{eq:dis-1}) and (\ref{eq:dis-2}).
@@
 The process produce leading dislocation and a trailing dislocation, when the two leading Shockley partials combine, they form Lomer–Cottrell junction, a separate dislocation.
-It's sessile and immobile in the slip plane,plays a role of barrier against other dislocations in the plane.
+It's sessile and immobile in the slip plane, plays a role of barrier against other dislocations in the plane.
 The process is as follow :
@@
 \end{equation}
-
 The orientation of slip is changed in Fig.
@@
 TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3[11\overline{2}0]$ prism planes shown by Fig.
-\ref{fig:Defect}, which is by far the easiest slip system in $\alpha_2$ single crystals.
+\ref{fig:Defect}(b), which is by far the easiest slip system in $\alpha_2$ single crystals.
 The core of a dislocation intersecting an interface often needs to be transformed.
@@
 These core transformations are associated with a change of the dislocation line energy because the lengths of Burgers vectors and the shear module are different.
-Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocation, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.When slip is forced to cross $\alpha_2$ phase, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
+Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocation, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.
+When slip is forced to cross $\alpha_2$ phase, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
 
@@
 \end{equation}
-where $\sigma_0$ is the strength of model without void defects 5.26 Gpa, and $A_0$ is initial section area,  $A^*$ is effective section area.
+where $\sigma_0$ is the strength of model without void defects 5.3 Gpa, and $A_0$ is initial section area,  $A^*$ is effective section area.
 In classic theory, the relationship between void size and strength of the model is linear.
 However, simulation results reveals that two phase Ti-Al alloy is sensitive to existence of void defect.
-Comparing with the strength determined by molecular dynamics simulation and the result4s calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.
+Comparing with the strength determined by molecular dynamics simulation and the result4s calculated with formulation (\ref{eq:section}), it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.
 
@@
 		\centering
-		\caption{Stress-Strain}
+		\caption{Stress-strain response of models}
 		\label{fig:stress&strain}
@@
 		\centering
-		\caption{Strength of models}
+		\caption{Yield strength of material with void}
 		\label{fig:strength}
@@
 
+The role of void can be concluded as two main parts: source and obstacles to dislocations, and which part is dominant depends on the location of void.
+Void inside $\alpha$ phase plays a role of second phase particles, in other words, this type of void possess similar properties as second phase particles.
+Void at $\alpha/\gamma$ boundary act as source of dislocation.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{"img/void-gb"}
+	\caption{(a) Fracture mode of two types of model  (b)Evolution of void at  phase boundary}
+	\label{fig:void-gb}
+\end{figure}
+
+Void at $\alpha_2/\gamma$ phase boundary lowered yield strength of the material down to 5.1 Gpa, and caused fracture along the phase boundary.
+
+Void inside $\alpha_2$ phase induce considerable misfit-stress fields and thus can influence material properties pronouncedly.
+Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and 'free' atoms surounded the void.Is a possibly favorable effect of second-phase particles that void defect contribution to the enhancement of mechanical strength.
+The strengthening effect of the particle inside single phase TiAl alloy have been verified by experiment \cite{Zghal1998}.
+Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength.
+
 \begin{figure}[ht]
@@
 
-The role of void can be concluded as two main parts: source of dislocation and obstacles to dislocations.
-Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, associated with the occurrence of incoherent or coherent interfaces, the long-range translation symmetry of the matrix.
-They may induce considerable misfit-stress fields and thus can influence material properties pronouncedly.
-Such stress fields surrounding the second-phase particles can be due to misfit between the volume occupied by the second-phase particle when unconstrained and the space (“hole”) put at its disposal by the matrix.
-Such misfit can arise due to specific volume differences induced by precipitation or by different thermal expansion or shrinkage upon heating or cooling the specimen.
-A possibly favorable effect of second-phase particles is a contribution to the enhancement of mechanical strength.
-Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength.
-In the discussion of the Frank–Read source for dislocation production  it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of block propagation of the stress field of a migrating dislocation: the second-phase particle acts as pinning point.
-It was already indicated that in order that a dislocation can pass two pinning points a critical shear stress is needed that depends on the distance between  obstacles, which can be regarded as second-phase particles:
+The defect evolution neighboring the void during yield stage is given by Fig.
+\ref{fig:orowan}(a), the role of void is similar to second-phase particles.
+It can serve as obstacles for dislocation migration which is shown by Fig.
+\ref{fig:orowan}(b): the stress fields surrounding the second-phase particles can be of block propagation of the stress field of a migrating dislocation, the void particle acts as pinning point.
+It was already indicated that a dislocation can pass two pinning points a critical shear stress is needed that depends on the distance between  obstacles, which can be regarded as second-phase particles\cite{Xiong2015}:
 \begin{equation} \label{eq:orowan} 
@@
 \end{equation}
-where $d$ represents the distance between obstancle A and B , reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution.
+where $d$ represents the distance between two obstacle A and B in , reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution.
 This mechanism for hardening is designated as the Orowan process with $\tau_0$ as the Orowan (shear) stress.
@@
 If a great number of dislocation slip along their respective systems towards the spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from the dash circle
+
 \section{conclusion}
@@
 The mechanism of deformation was investigated under atomic scale, and the effect of void defect on the properties of two phase TiAl alloy was also studied.
-The conclusions are as follows:
-
-(1) The major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha$ phase is harder to be deformed, this inhomogeneity results in cracks at interface of the two phase.
-
+The conclusions are as follows:\\
+(1) The major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha$ phase is harder to be deformed, this inhomogeneity results in cracks at interface of the two phase. \\
 (2) The effect of the void defect on the strength of the two phase alloy is sensitive to the location of the void.

### 2018-11-19 code/Temp.py

@@ -25,7 +25,7 @@ u = 20*np.e**(-350/T)/20
 v = 20*np.e**(-400/T)/20
 w = 20*np.e**(-450/T)/20
 plt.xlabel('Temperature / K')
-plt.ylabel('Mobility of Dislocation')
+plt.ylabel('Normalized velocity of dislocation motion')
 plt.ylim(ymax=1)
 plt.plot(T,u, color='R')
 plt.plot(T,v, color='G')

### 2018-11-19 code/data/size/size_summary.py

@@ -39,7 +39,7 @@ plt.plot(size, agmax, marker='^',color='B')
 plt.legend(['calculated value',r'void inside $\alpha$ phase', r'void at \textbf{$\alpha$-$\gamma$} phase boundary'], frameon=False)
 plt.ylim(4.8,5.5)
 plt.xlabel(r'Radius of Void/ \AA')
-plt.ylabel('Strength/GPa')
+plt.ylabel('Yield strength/GPa')
 plt.savefig(os.path.join(writepath,'effect_of_vol.pdf'))
 plt.show()
 

### 2018-11-19 code/dissum.py

@@ -51,12 +51,12 @@ rects4 = plt.bar(index + 3*bar_width, frank, bar_width,
                  color='black',
                  label='Frank')
 
-plt.xlabel('Stage')
+plt.xlabel('Strain')
 plt.ylabel(r'Dislocation length / \AA')
 plt.ylim(ymax=5000)
 # plt.title('Scores by person')
-plt.xticks(index + bar_width, ('Initial', 'Before yield', 'After yield', 'Cracked'))
-plt.legend(frameon = False)
+plt.xticks(index + bar_width, ('0.005','0.092','0.101','0.112'))
+plt.legend(frameon = False,title='Type of dislocation')
 
 plt.savefig(os.path.join(writepath, 'dis-summary.pdf'))
 

### 2018-11-23 draft/alexpub.tex
祁永年改

@@
 Interaction between spherical nano void with different size and position was also examined in the simulation.
-The results show that i) $\gamma$ phase is the major deformation source of the two phase alloy; ii) Voids defect detracts the strength of the two phase alloy, however the position of void affect the degree of this subtraction, voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detraction to strength.}
+The results show that (1) $\gamma$ phase is the major deformation source of the two phase alloy; (2) Void defect detracts the strength of the two phase alloy, however the position of void affect the degree of this subtraction, voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detraction to strength.}
 % Keywords
@@
 % and brittle rapture failure 
-The titanium  aluminum based intermetallic alloys are promising high temperature structural materials because of their great corrosion resistance at high temperature.
-Comparing with nickle based alloy,  alloys have lower density and are pron to be utilized in combustion engine, turbine, and other components work at high temperature ranging from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius} \cite{Clemens2016}.
+Titanium  aluminum based intermetallic alloys are promising high temperature structural materials because of their great corrosion resistance and strength at high temperature.
+Comparing with nickle based alloy,  Ti-Al based alloys have lower density and are pron to be utilized in combustion engine, turbine, and other components work at high temperature ranging from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius} \cite{Clemens2016}.
 The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20\% because the weight of components decreased from 30\% to 40\% \cite{Bewlay2016}.
-With the advancement of non-ferrous metallurgy, Ti-Al based components has better economic efficiency than ever before.
-Thus, Ti-Al based alloys have good prospects for applications in aerospace and automobile industry.
-Poor ductility of Ti-Al alloy  at room temperature strongly affects the safety structures like turbo of aircraft engine and combustion generator \cite{Munz2017}.
+With the advancement of non-ferrous metallurgy, Ti-Al based alloy components has better economic efficiency than ever before.
+Ti-Al based alloys have good prospects for applications in aerospace and automobile industry.
+Poor ductility of Ti-Al alloy  at room temperature strongly affects the safety of structures like turbo of aircraft engine and combustion generator \cite{Munz2017}.
 Deformation phenomena of Ti-Al alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
-Much of the work has been performed on single phase $\gamma$ alloys and polysynthetically twinned crystals\cite{Appel2016}.
-Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially easily formed in the casting process, such as voids and inclusions \cite{Tang2014}.
-A great number of literature covers a wide range of factors such as alloy composition, microstructure and deformation temperature.
-Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}.
-Due to difficulties in observing the dynamic process during deformation wit experiments, MD simulation has become an effective method to investigate micro deformation mechanism.
-Defects such as grain boundary, void and segregation play a significant role in the process of fracture \cite{Larsen2016}.
-Multiscale method have been applied to study deformation behavior of polycrystal with single aluminum \cite{Groh2009} and titanium element respectively \cite{Liu2018}.
-It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
-
+Much of the work has been performed on single phase $\gamma$-TiAl alloys and polysynthetically twinned crystals(PTC)\cite{Appel2016}.
+Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially easily formed in the casting process, such as voids and inclusions \cite{Tang2014}.
+A great number of literatures cover a wide range of factors such as alloy composition, microstructure and deformation temperature,some reports come up with idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}.
 Void defect can arise due to specific volume differences induced by precipitation or by different thermal expansion or shrinkage upon heating or cooling the specimen.
@@
 The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study about  mechanisms of deformation and cracking, these defects are known to play a fundamental role in the deformation of materials.
+Multiscale method have been applied to study deformation behavior of polycrystal with single aluminum \cite{Groh2009} and titanium element respectively \cite{Liu2018}.
+It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
+The effect of void defect is another great concern about properties and deformation mechanism  of TiAl alloy.
 Therefore, it is necessary to study the deformation response of intermetallics structural materials with the consideration of microstructure evolution.
-The effect of void defect is another great concern about properties and deformation mechanism  of TiAl alloy.
-A previous study on void growth in single crystal $\gamma$-TiAl reveals that void with high volume fraction detracts yield strength, and emission of dislocation \cite{Tang2014, Xu2011}.
-Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations \cite{Jing2018a,Elkhateeb2018}.
+Previous study on void growth in single crystal $\gamma$-TiAl reveals that void with high volume fraction detracts yield strength, and emission of dislocation \cite{Tang2014, Xu2011}.
+Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations, \cite{Jing2018a,Elkhateeb2018}, voids inside material are soures of dislocation and affects the properties of materials differently because of difference in size and position.
 The deformation and fracture mechanisms in the duplex microstructure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang2014}.
-It reveals that existence of voids alone may contribute to strain hardening because they are barriers to dislocation movement \cite{Xiong2015}.
+It reveals that existence of voids alone may contribute to strain hardening because they are barriers to dislocation movement in ductile fcc structure metal\cite{Xiong2015}.
 However, few literature covers about deformation mechanism of two phase Ti-Al alloy and the role of void in atomic scale.
@@
 Ti-Al alloy is a type of typical brittle material, thus it can be assumed that its properties are sensitive to the existence of void defect.
-Surface defects such as small notches can caused low and high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$  TiAl is also lowered by point defect \cite{Wu2016}.
+Surface defects such as small notches can caused low and high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$-TiAl is also lowered by point defect \cite{Wu2016}.
 The resistance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was markedly reduced due to earlier crack initiation.
-The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small micro-cracks in the damaged zone.This paper focus on the evolution of microstructure, tend to find out its connection to cold deformation behavior of two phase TiAl alloy.
+The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small micro-cracks in the damaged zone.
+Due to difficulties in observing the dynamic process during deformation wit experiments, MD simulation has become an effective method to investigate micro deformation mechanism.
+Defects such as grain boundary, void and segregation play a significant role in the process of fracture \cite{Larsen2016}.
+This paper focus on the evolution of microstructure, tend to find out its connection to cold deformation behavior of two phase TiAl alloy.
 MD simulation including model creation and analysis method is given in Section \ref{section:method}, Results and discussion are in Section \ref{section:RD}.
@@
 The interaction of particle in the material is determined by interatomic potential.
-Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to its better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015}.
-The embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study.
+Many reported simulation cases of deform and crack propagation in metal materials were performed with embedded atomic method due to its better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015,Zepeda-Ruiz2017,Fan2018a}.
+Embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study.
 The simulation is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}.
-We performed constant-pressure and constant-temperature (NPT) molecular dynamics simulation.
+We performed constant-pressure and constant-temperature (NPT) molecular dynamics simulation at room temperature (298K).
 The definition of potential is as following:
@@
 \end{equation}
+where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system, $F_i(\rho)$ represents the energy for embedding atom $i$ into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ gives the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$.
+It can be noted that $F_i$ only depends on the element of atom $i$ and $\phi_{ij}$ only depends on the elements of atoms $i$ and $j$.
 
-where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system,$F_i(\rho)$ represents the energy for embedding atom $i$ into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ gives the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$.
-It can be noted that $F_i$ only depends on the element of atom $i$ and $\phi_{ij}$ only depends on the elements of atoms $i$ and $j$.
-The electron density is, as stated above, approximated by the superposition of atomic densities.
-
-%	\begin{equation} \label{eq:eam} 
-%	\rho_{h,i}=\sum_{j(\neq1)} \rho_i(R_{ij})
-%	\end{equation}
-%	
 \subsection{Model Creation of Crystalline}
@@
 
-$\gamma $ TiAl has a fcc type cell with an $L1_0$ structure, and $\alpha_2$-$\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Fig.
-\ref{fig:tial-cell}, and the constructing parameters are given by Table \ref{tab:lattice_parameter}.
+Two phase Ti-Al alloy is composed of $\gamma $-TiAl and $\alpha_2$-$\rm Ti_3Al$ has a fcc type cell with an $L1_0$ structure, and $\alpha_2$-$\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Fig.
+\ref{fig:tial-cell}, constructing parameters of the two type of unit cell are given by table \ref{tab:lattice_parameter}.
 Periodic boundary conditions (PBC) are applied along all three directions, that makes polycrystal with periodic nanovoid structures.
@@
 Instead, the parameter will have a value within the range corresponding to a particular defect.
-By removing all the perfect and surface atoms within the bulk, atoms around dislocation zone are visualized.
+By removing all the perfect and surface atoms within the bulk, atoms around defected zone are visualized.
 
@@
 According to stress response under constant rate of strain rate, the whole tensile process can be divided into four stages:
-Stage - \uppercase\expandafter{\romannumeral1}: elastic stage,ranging from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1,
-Stage - \uppercase\expandafter{\romannumeral2}: yield stage, ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6,
-Stage - \uppercase\expandafter{\romannumeral3}: cracking stage, ranging from $\epsilon = 0.101$ to $\epsilon = 0.112$, including key pint 7 to 10,
-Stage - \uppercase\expandafter{\romannumeral4}: fracture stage.
+stage - \uppercase\expandafter{\romannumeral1}: elastic stage, ranging from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1,
+stage - \uppercase\expandafter{\romannumeral2}: yield stage, ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6,
+stage - \uppercase\expandafter{\romannumeral3}: cracking stage, ranging from $\epsilon = 0.101$ to $\epsilon = 0.112$, including key pint 7 to 10,
+stage - \uppercase\expandafter{\romannumeral4}: fracture stage.
 Following discussion concentrates on deformation phenomena that rely on the elastro-plastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in two phase alloys.
@@
 		\toprule
-		\textbf{Key Number} & {1} & {2} & {3} & {4} & {5} & {6} & {7} & {8} & {9} & {10}\\		 \midrule
-		\textbf{Stage} &\uppercase\expandafter{\romannumeral1} &\uppercase\expandafter{\romannumeral1} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3}\\
-
+		\textbf{Number} &1 &2 &3 &4 &5 &6 &7 &8 &9 &10\\		 
+		\midrule
+		\textbf{Stage} &\uppercase\expandafter{\romannumeral1} &\uppercase\expandafter{\romannumeral1} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3}	 \\
 		\midrule
@@
 \subsection{Deformation Mechanism of Two Phase TiAl Alloy without Void Defects}
-Snapshots of atom configuration at the 5 of 10 key points are shown by Fig.
+Snapshots of atom configuration at the 3 of 10 key points are shown by Fig.
 \ref{fig:Defect}.
@@
 Similarly, $\gamma$ phase grain have been removed in Fig.
-\ref{fig:Defect}(b) and (c), the defects of $\alpha_2$ phase have been left.
+\ref{fig:Defect}(c) and (d), the defects of $\alpha_2$ phase have been left.
 The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of material is under typical elastic deformation and the size of simulation box enlarged due to the loading, deformation of the two phase are compatible.
 Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}.
-A  great number of dislocation emitted inside $\gamma$ phase at beginning of stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\alpha_2$ phase was emitted at the end of stage \uppercase\expandafter{\romannumeral2} shown by Fig.
+A  great number of dislocation emitted inside $\gamma$ phase at earlier part of stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\alpha_2$ phase was emitted at the end of stage \uppercase\expandafter{\romannumeral2} shown by Fig.
 \ref{fig:Defect}(c).
-The deformation of $\alpha_2$ phase is earlier than $\gamma$ phase during yield stage, thus local displacement of two phases are incompatible during yield stage.
-The mobility of dislocation is affected by structure of crystal, loading condition and temperature.
-$\alpha_2$ phase is made up of hcp  structured grain, grain with this type of structure possess less slip system compering with grain with fcc structure \cite{Zhu2012}, thus $\alpha_2$ phase is difficult do be deformed under uniaxial tensile loading.
 \begin{figure}[ht] 
@@
 \end{figure}
-
 Experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature\cite{Stein1960}.
@@
 \begin{equation}\label{eq:temp-dis}
-v = v_0 \exp(-\Delta H(\tau^*)/kT)
+v = v_0\ e^{-\Delta H(\tau^*)/kT}
 \end{equation}
@@
 \ref{fig:temp}.
-The  velocity  of dislocation movement rise along with increase of  stress, the mobility  of dislocation is relatively poor at room temperature 298 K.
-Due to motion of dislocation is inactive inside $alpha_2$ phase, piling up of dislocations, the typical strengthening mechanism closely related with interaction between grain boundary and dislocation was not observed in Fig.
-\ref{fig:Defect}.
-
+The  velocity  of dislocation movement rise along with increase of  stress, the mobility  of dislocation is relatively poor at 298 K.
+Due to motion of dislocation is inactive inside $\alpha_2$ phase, piling up of dislocations, the typical strengthening mechanism closely related with interaction between grain boundary and dislocation can not be dramatic at room temperature.
+That is in good agreement with simulation results shown by in Fig.
+\ref{fig:Defect}, there was few dislocation piling up at near boundaries.
 \begin{figure}[ht]
@@
 It's sessile and immobile in the slip plane, plays a role of barrier against other dislocations in the plane.
-The process is as follow :
+This process can be given by :
 \begin{equation}\label{eq:dis-3}
@@
 \end{equation}
-The orientation of slip is changed in Fig.
-\ref{fig:Defect}, because the crystallographically available slip and directions are not continuous across the interface.
-This may significantly reduce the Schmid factor and thus impede slip transfer.
-At the $\gamma/\gamma$ interfaces, the orientation of slip plan could change through a relevantly large angle of about 90 degree.
-Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1}_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{intro-structure}.
-From Fig.
-\ref{fig:Defect}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform.
+According to results calculated by first principle, the stacking faulting energy for TiAl is much smaller than $\rm{Ti_3Al}$, as a consequence calculated shear strength of TiAl and $Ti_3Al$is 4.1 Gpa and 2.86 Gpa along their easy slip plane respectively\cite{Liu2007}.
+This calculation reveals that tensile behaviour in single crystal is mainly controlled by the type of the structure.
+However, in two phase Ti-Al alloy, deformation of $\alpha_2$ phase is earlier than $\gamma$ phase during yield stage, thus local displacement of two phases are incompatible during yield stage.
+Mobility of dislocation is affected by structure of crystal, loading condition and temperature.
+$\alpha_2$ phase is made up of hcp  structured grain, grain with this type of structure possess less slip system compering with grain with fcc structure \cite{Zhu2012}, thus $\alpha_2$ phase is difficult do be deformed under uniaxial tensile loading.
 
-A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
-TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3[11\overline{2}0]$ prism planes shown by Fig.
+Main reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
+TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3[11\overline{2}0]$ prism planes shown by Fig.
 \ref{fig:Defect}(b), which is by far the easiest slip system in $\alpha_2$ single crystals.
@@
 \begin{figure}[ht]
-	\centeringz
+	\centering
 	\includegraphics[width=1\linewidth]{img/slice-view}
@@
 The existence of void have little impact on the elastic properties of the material, and the model without void defect has the best strength 5.3 GPa, the yield stress of model with void is smaller.
-Void at $\alpha_2$-$\gamma$ phase boundary  detracts the strength of  material most, and the void inside $\alpha_2$ phase  have less impact on the strength.
+Void at $\alpha_2$/$\gamma$ phase boundary  detracts the strength of  material most, and the void inside $\alpha_2$ phase  have less impact on the strength.
 Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by
 \begin{equation} \label{eq:section} 
-\sigma^* = \sigma_0 \cdot \frac{A^*}{A_0}
+\sigma^* = \sigma_0 \cdot({A^*}/{A_0})
 \end{equation}
-where $\sigma_0$ is the strength of model without void defects 5.3 Gpa, and $A_0$ is initial section area,  $A^*$ is effective section area.
+where $\sigma_0$ is the strength of model without void defects 5.3 Gpa, and $A_0$ represents initial section area,  $A^*$ is effective section area in consider of the area detraction by void.
 In classic theory, the relationship between void size and strength of the model is linear.
 However, simulation results reveals that two phase Ti-Al alloy is sensitive to existence of void defect.
-Comparing with the strength determined by molecular dynamics simulation and the result4s calculated with formulation (\ref{eq:section}), it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.
+Comparing with the strength determined by molecular dynamics simulation and the result4s calculated with formulation (\ref{eq:section}), it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects have dramatic influence on the yield and fracture process of the materials.
 
@@
 \subsection{Evolution of spherical void}
+The role of void can be concluded as two main parts: source of dislocations and obstacles to dislocations, which part is dominant depends on the location of void.
+Void inside $\alpha_2$ phase plays a role of inclusion, in other words, this type of void possess similar properties as second phase particles.
 
-The role of void can be concluded as two main parts: source and obstacles to dislocations, and which part is dominant depends on the location of void.
-Void inside $\alpha$ phase plays a role of second phase particles, in other words, this type of void possess similar properties as second phase particles.
-Void at $\alpha/\gamma$ boundary act as source of dislocation.
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\linewidth]{"img/orowan"}
+	\caption{Orowan process in $\alpha_2$-phase (atoms with regular arrangement have been removed)}
+	\label{fig:orowan}
+\end{figure}
+Void inside $\alpha_2$ phase induce considerable misfit-stress fields and thus can influence material properties pronouncedly.
+Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and 'free' atoms surounded the void.
+That's a possibly favorable effect of second-phase particles that void defect contribution to the enhancement of mechanical strength.
+The strengthening effect of the particle inside single phase TiAl alloy have been verified by experiment \cite{Zghal1998}.
+Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength.
+The defect evolution neighboring the void during yield stage is given by Fig.
+\ref{fig:orowan}(a), the role of void is similar to second-phase particles.
+It can serve as obstacles for dislocation migration which is shown by Fig.
+\ref{fig:orowan}(b): the stress fields surrounding the second-phase particles can be of block propagation of the stress field of a migrating dislocation, the void particle acts as pinning point.
+The dislocation can pass two pinning points a critical shear stress is needed that depends on the distance between  obstacles, which can be regarded as second-phase particles\cite{Xiong2015}:
+\begin{equation} \label{eq:orowan} 
+\tau_0 = Gb/d
+\end{equation}
+where $d$ represents the distance between two obstacles A and B in Fig.
+\ref{fig:orowan} , reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution.
+This mechanism for hardening is designated as the Orowan process with $\tau_0$ as the Orowan shear stress.
+As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles.
+Consequently, the effective average distance between the second phase particles has decreased to d which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide.
+The width of a burgers vector, will be generated at both sides of a crystal along the direction of  burgers vector after dislocation traversing the entire crystal, as is shown in the third sub-figure of Fig.
+\ref{fig:orowan}(b).
 
@@
 \end{figure}
-
-Void at $\alpha_2/\gamma$ phase boundary lowered yield strength of the material down to 5.1 Gpa, and caused fracture along the phase boundary.
-
-Void inside $\alpha_2$ phase induce considerable misfit-stress fields and thus can influence material properties pronouncedly.
-Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and 'free' atoms surounded the void.Is a possibly favorable effect of second-phase particles that void defect contribution to the enhancement of mechanical strength.
-The strengthening effect of the particle inside single phase TiAl alloy have been verified by experiment \cite{Zghal1998}.
-Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=1\linewidth]{"img/orowan"}
-	\caption{Orowan process in $\alpha$-phase ($\alpha$ phase atoms have been removed)}
-	\label{fig:orowan}
-\end{figure}
-
-The defect evolution neighboring the void during yield stage is given by Fig.
-\ref{fig:orowan}(a), the role of void is similar to second-phase particles.
-It can serve as obstacles for dislocation migration which is shown by Fig.
-\ref{fig:orowan}(b): the stress fields surrounding the second-phase particles can be of block propagation of the stress field of a migrating dislocation, the void particle acts as pinning point.
-It was already indicated that a dislocation can pass two pinning points a critical shear stress is needed that depends on the distance between  obstacles, which can be regarded as second-phase particles\cite{Xiong2015}:
-\begin{equation} \label{eq:orowan} 
-\tau_0 = Gb/d
-\end{equation}
-where $d$ represents the distance between two obstacle A and B in , reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution.
-This mechanism for hardening is designated as the Orowan process with $\tau_0$ as the Orowan (shear) stress.
-
-As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles.
-Consequently, the effective average distance between the second-phase particles has decreased to d which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide.
-The width of a burgers vector, will be generated at both sides of a crystal along the direction of the burgers vector after dislocation traversing the entire crystal, as is shown in \ref{fig:orowan}.
-A small tep will be formed at spherical void surface toward the void interior after dislocation absorption at spherical void surfaces.
-If a great number of dislocation slip along their respective systems towards the spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from the dash circle
-
+Effect of voids at different positions on the crack mode of the material are shown by Fig.
+\ref{fig:void-gb}(a).
+The model with void fractured cross the grain, and the model with void at $\alpha_2 / \gamma$ boundary resulted a large crack along the boundary under tensile loading.
+The difference of crack mode can attribute to the position of void and the evolution of the defect.
+Nucleation, emission of Shockley partial dislocation affect the evolution of the void at boundary greatly due to the anisotropy of two phases on the both sides of the phase boundary.
+The void weaken the strength of the grain it locates,  $\alpha_2$ phase grain is easy to deformed under shear stress, thus that caused the crack initiated inside grain and finally caused fracture across the grain.
+Deformation mechanism of the model with void at boundary can be  more complex due to the interaction between void and phase boundary.
+In elastic stage, the system composed of $\alpha_2$ phase, $\gamma$ phase and void is in equilibrium, internal stress are balanced under compatible deformation as is shown by the first sub-figure of Fig.
+\ref{fig:void-gb}(b).
+In the middle moment of yield stage, partial dislocation with Burgers vector $1/6[\overline{2}\ \overline{1}\ 1]$ emitted from surface of void in Fig.
+\ref{fig:void-gb}(b)-2.
+The micro crack initialed from the zone neighbor  the interface between void and boundary, that quickly caused abrupt decohension of phase boundary.
+That accounts for the reason that material with void at $\alpha_2 / \gamma$ phase boundary is weaker than other cases.
 \section{conclusion}
-In this paper, deformation behavior of two phase TiAl alloy under tensile loading was simulated with MD method.
-The mechanism of deformation was investigated under atomic scale, and the effect of void defect on the properties of two phase TiAl alloy was also studied.
+In this paper, deformation behavior of two phase Ti-Al alloy under tensile loading was simulated with MD method.
+The mechanism of deformation was investigated under atomic scale, and the effect of void defect on the properties of two phase Ti-Al alloy was also studied.
 The conclusions are as follows:\\
-(1) The major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha$ phase is harder to be deformed, this inhomogeneity results in cracks at interface of the two phase. \\
-(2) The effect of the void defect on the strength of the two phase alloy is sensitive to the location of the void.
-The void located inside the grain decrease the strength to the material because this type defect weaken the grain thus caused even more serious stress concentration, and the void at phase boundary have less impact on the strength of the material because this type void help to release of local stress at grain boundary.
+(1) Major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha_2$ phase is harder to be deformed, this inhomogeneity results in cracks at interface of the two phase. \\
+(2) Effect of  void defect on the strength of the two phase alloy is sensitive to the location of  void.
+Void inside grain have less detraction to the strength of material because of strengthening mechanism similar to second phase particle.
+Void at $\alpha_2 / \gamma$ boundary is most risky situation for two phase alloy because of fast fracture along boundary.
 

### 2018-11-23 code/Temp.py

@@ -3,7 +3,7 @@ import os.path
 
 #plt.rcParams["font.family"] = 'Times New Roman'
 import matplotlib.pyplot as plt
-plt.rcParams.update({'font.size': 14})
+plt.rcParams.update({'font.size': 16})
 from matplotlib import rc
 rc('text', usetex=True)
 #csfont = {'fontname':'Times New Roman'}

### 2018-11-23 code/allline.py

@@ -53,7 +53,7 @@ p3 = plt.plot((ds3.strain-0.015)*1.2, ds3.stress, color = 'R')
 p2 = plt.plot((ds2.strain-0.015)*1.2, ds2.stress, color = 'G')
 p4 = plt.plot((ds4.strain-0.015)*1.2, ds4.stress, color = 'B')
 
-plt.legend([ 'no void',r'void inside $\alpha$ phase',r'void at \textbf{$\alpha$-$\gamma$} phase boundary'], frameon=False)
+plt.legend([ 'no void',r'void inside $\alpha_2$ phase',r'void at \textbf{$\alpha_2$/$\gamma$} phase boundary'], frameon=False)
 
 # config title and label
 

### 2018-11-23 code/data/size/size_summary.py

@@ -17,7 +17,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import matplotlib.pyplot as plt
 from scipy.optimize import curve_fit as fit
-plt.rcParams.update({'font.size': 14})
+plt.rcParams.update({'font.size': 16})
 from matplotlib import rc
 rc('text', usetex=True)
 plt.rcParams["font.family"] = 'Times New Roman'
@@ -36,7 +36,7 @@ plt.plot(size, agmax, marker='^',color='B')
 
 # color='darkorange'
 # color='steelblue'
-plt.legend(['calculated value',r'void inside $\alpha$ phase', r'void at \textbf{$\alpha$-$\gamma$} phase boundary'], frameon=False)
+plt.legend(['calculated value',r'void inside $\alpha_2$ phase', r'void at \textbf{$\alpha_2$/$\gamma$} phase boundary'], frameon=False)
 plt.ylim(4.8,5.5)
 plt.xlabel(r'Radius of Void/ \AA')
 plt.ylabel('Yield strength/GPa')

### 2018-11-23 code/dissum.py

@@ -11,7 +11,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import rc
 rc('text', usetex=True)
-plt.rcParams.update({'font.size': 14})
+plt.rcParams.update({'font.size': 16})
 WDIR = os.path.dirname(__file__)
 # loadpath = os.path.join(WDIR,'data','stress_strain')
 writepath = os.path.join(WDIR,'..','draft','img')

### 2018-11-23 draft/alexpub.tex
part1 added

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Cold deformation behavior of poly crystalline metallic material is affected by intrinsic defects such as dislocation, etc.
-Existing studies on $\alpha_2(\rm{Ti_3Al})$+$\gamma(\rm{TiAl})$  two phase Ti-Al alloy covers about deformation behavior mainly on macro scale.
-This paper focus on the cold deformation mechanism of two phase Ti-Al alloy at micro scale, and  the role of void defect in deformation process.
-Molecular dynamics simulations were performed to study the evolution of micro structure in the material under uniaxial tension.
+\abstract{Cold deformation behavior of poly crystalline metallic material is affected by intrinsic defects such as dislocation, void, inclusion etc.
+Existing studies on $\alpha_2(\rm{Ti_3Al})$+$\gamma(\rm{TiAl})$  two phase Ti-Al alloy cover about deformation behavior mainly on macro scale.
+This paper focuses on the cold deformation mechanism of two phase Ti-Al alloy at micro scale, and  the role of void  in deformation process.
+Molecular dynamics simulations were performed to study the evolution of micro structure of material under uniaxial tension.
 Interaction between spherical nano void with different size and position was also examined in the simulation.
-The results show that (1) $\gamma$ phase is the major deformation source of the two phase alloy; (2) Void defect detracts the strength of the two phase alloy, however the position of void affect the degree of this subtraction, voids located at the $\alpha_2$/$\gamma$ phase boundary have significant detraction to strength.}
+The results show that (1) $\gamma$ phase is the major deformation source of the two phase alloy; (2) Void defect detracts the strength of the two phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
 % Keywords
@@
 Titanium  aluminum based intermetallic alloys are promising high temperature structural materials because of their great corrosion resistance and strength at high temperature.
-Comparing with nickle based alloy,  Ti-Al based alloys have lower density and are pron to be utilized in combustion engine, turbine, and other components work at high temperature ranging from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius} \cite{Clemens2016}.
+Compared with nickle based alloy,  Ti-Al based alloys have lower density and are pron to be utilized in combustion engine, turbine, and other components working at high temperature from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius} \cite{Clemens2016}.
 The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20\% because the weight of components decreased from 30\% to 40\% \cite{Bewlay2016}.
-With the advancement of non-ferrous metallurgy, Ti-Al based alloy components has better economic efficiency than ever before.
+With the advancement of non-ferrous metallurgy, Ti-Al based alloy components have better economic efficiency than ever before.
 Ti-Al based alloys have good prospects for applications in aerospace and automobile industry.
@@
 Much of the work has been performed on single phase $\gamma$-TiAl alloys and polysynthetically twinned crystals(PTC)\cite{Appel2016}.
-Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially easily formed in the casting process, such as voids and inclusions \cite{Tang2014}.
-A great number of literatures cover a wide range of factors such as alloy composition, microstructure and deformation temperature,some reports come up with idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}.
-Void defect can arise due to specific volume differences induced by precipitation or by different thermal expansion or shrinkage upon heating or cooling the specimen.
+Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}.
+A great number of literatures cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}.
+Void defect can be arose due to specific volume differences induced by precipitation, different thermal expansion or shrinkage upon heating or cooling the specimen.
 It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
-The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study about  mechanisms of deformation and cracking, these defects are known to play a fundamental role in the deformation of materials.
-Multiscale method have been applied to study deformation behavior of polycrystal with single aluminum \cite{Groh2009} and titanium element respectively \cite{Liu2018}.
+The initiation of crack at microscopic scale is a dynamic process, which results in difficulties on study of  mechanisms about deformation and cracking, these defects are known playing a fundamental role in the deformation of materials.
+Multiscale method has been applied to study deformation behavior of polycrystal with single aluminum \cite{Groh2009} and titanium element respectively \cite{Liu2018}.
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
@@
 Therefore, it is necessary to study the deformation response of intermetallics structural materials with the consideration of microstructure evolution.
-Previous study on void growth in single crystal $\gamma$-TiAl reveals that void with high volume fraction detracts yield strength, and emission of dislocation \cite{Tang2014, Xu2011}.
-Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations, \cite{Jing2018a,Elkhateeb2018}, voids inside material are soures of dislocation and affects the properties of materials differently because of difference in size and position.
+Previous study on void growth in single crystal $\gamma$-TiAl reveals that void with high volume fraction detracts yield strength \cite{Tang2014, Xu2011}.
+Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations, \cite{Jing2018a,Elkhateeb2018}, voids inside material are soures of dislocation and affects the properties of materials differently because of differences in size and position.
 The deformation and fracture mechanisms in the duplex microstructure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang2014}.
@@
 Defects are inevitable as micro-pores and loosen from casting, and in the actual work environment with radiation.
-A lot of work carried out on the  effect of various defects on the behavior of different materials, show that point defects may affect the properties of materials greatly.
+A lot of work carried out on the  effect of various defects on the behavior of different materials, showing that point defects may affect the properties of materials greatly.
 The mechanical performance of irradiated copper is affected by the interaction between irradiation and dislocation \cite{Kiener2011}.
@@
 Ti-Al alloy is a type of typical brittle material, thus it can be assumed that its properties are sensitive to the existence of void defect.
-Surface defects such as small notches can caused low and high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$-TiAl is also lowered by point defect \cite{Wu2016}.
-The resistance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was markedly reduced due to earlier crack initiation.
-The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small micro-cracks in the damaged zone.
+Surface defects such as small notches can cause low and high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$-TiAl is also lowered by point defect \cite{Wu2016}.
+The resistance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was reduced due to earlier crack initiation.
+The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small cracks in the damaged zone.
 Due to difficulties in observing the dynamic process during deformation wit experiments, MD simulation has become an effective method to investigate micro deformation mechanism.
-Defects such as grain boundary, void and segregation play a significant role in the process of fracture \cite{Larsen2016}.
-This paper focus on the evolution of microstructure, tend to find out its connection to cold deformation behavior of two phase TiAl alloy.
+Defects such as grain boundary, void and segregation play significant roles in the process of fracture \cite{Larsen2016}.
+This paper focus on the evolution of microstructure, tending to find out its connection to cold deformation behavior of two phase TiAl alloy.
 MD simulation including model creation and analysis method is given in Section \ref{section:method}, Results and discussion are in Section \ref{section:RD}.
@@
 \ref{fig:tial-cell}, constructing parameters of the two type of unit cell are given by table \ref{tab:lattice_parameter}.
-Periodic boundary conditions (PBC) are applied along all three directions, that makes polycrystal with periodic nanovoid structures.
+Periodic boundary conditions (PBC) are applied along three directions, which makes polycrystal with periodic nanovoid structures.
 The initial dimension of simulation cell is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model contains about 460,000 atoms.
@@
 According to stress response under constant rate of strain rate, the whole tensile process can be divided into four stages:
-stage - \uppercase\expandafter{\romannumeral1}: elastic stage, ranging from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1,
+stage - \uppercase\expandafter{\romannumeral1}: elastic stage, from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1,
 stage - \uppercase\expandafter{\romannumeral2}: yield stage, ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6,
-stage - \uppercase\expandafter{\romannumeral3}: cracking stage, ranging from $\epsilon = 0.101$ to $\epsilon = 0.112$, including key pint 7 to 10,
+stage - \uppercase\expandafter{\romannumeral3}: cracking stage, ranging from $\epsilon = 0.101$ to $\epsilon = 0.112$, including key point 7 to 10,
 stage - \uppercase\expandafter{\romannumeral4}: fracture stage.
@@
 \ref{fig:Defect}(c) and (d), the defects of $\alpha_2$ phase have been left.
-The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of material is under typical elastic deformation and the size of simulation box enlarged due to the loading, deformation of the two phase are compatible.
+The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of material is under typical elastic deformation, the size of simulation box enlarged due to the loading.
+In this stage, deformation of the two phase are compatible.
 Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}.
-A  great number of dislocation emitted inside $\gamma$ phase at earlier part of stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\alpha_2$ phase was emitted at the end of stage \uppercase\expandafter{\romannumeral2} shown by Fig.
+A  great number of dislocation emitted inside $\gamma$ phase at earlier part of stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\alpha_2$ phase was emitted at the end of stage \uppercase\expandafter{\romannumeral2} is shown by Fig.
 \ref{fig:Defect}(c).
@@
 The  velocity  of dislocation movement rise along with increase of  stress, the mobility  of dislocation is relatively poor at 298 K.
-Due to motion of dislocation is inactive inside $\alpha_2$ phase, piling up of dislocations, the typical strengthening mechanism closely related with interaction between grain boundary and dislocation can not be dramatic at room temperature.
-That is in good agreement with simulation results shown by in Fig.
-\ref{fig:Defect}, there was few dislocation piling up at near boundaries.
+Due to motion of dislocations is inactive inside $\alpha_2$ phase,  typical strengthening mechanism closely related with interaction between grain boundary and dislocation can not be dramatic at room temperature, piling up of dislocations is not observed in this simulation, which is shown in Fig.
+\ref{fig:Defect}.
 \begin{figure}[ht]
@@
 \ref{fig:disum}.
-Dislocations are recognized and identified using the dislocation analysis (DXA) of OVITO.
-The length of Shorckley dislocation with Burgers vector $1/6[1 1 2]$ increase sharply during yield stage of the deformation process in Fig.
-\ref{fig:disum}, but the length of perfect dislocation fluctuate at a low level.
-Decomposition of the perfect  dislocations split into Shockley partial dislocations as formulation (\ref{eq:dis-1}) and (\ref{eq:dis-2}).
-The structure spontaneously transform into intrinsic stacking fault (ISF), it can be observed in Fig.
+Dislocations are recognized and identified using the dislocation analysis (DXA) of ovito.
+The length of Shorckley dislocation with Burgers vector $1/6[1 1 2]$ increased sharply during yield stage of the deformation process in Fig.
+\ref{fig:disum}, but the length of perfect dislocation fluctuated at a low level.
+Perfect  dislocations split into Shockley partial dislocations, this decomposition process  can be given by formulation (\ref{eq:dis-1}) and (\ref{eq:dis-2}).
+The structure spontaneously transformed into intrinsic stacking fault (ISF), which can be observed in Fig.
 \ref{fig:Defect}(a).
@@
 \end{equation}
-Interaction between dislocation with Burgers vector of $1/6 [112] $ and $ 1/6 [11\overline{2}]$ follows the decomposition of perfect dislocation.
-The process produce leading dislocation and a trailing dislocation, when the two leading Shockley partials combine, they form Lomer–Cottrell junction, a separate dislocation.
-It's sessile and immobile in the slip plane, plays a role of barrier against other dislocations in the plane.
-This process can be given by :
+Interaction between dislocations with Burgers vector of $1/6 [112] $ and $ 1/6 [11\overline{2}]$ follows the decomposition of perfect dislocation.
+The process produced leading dislocation and trailing dislocation, when the two leading Shockley partials combined, they form Lomer–Cottrell junction, a separate dislocation.
+It's sessile in the slip plane, playing a role of barrier against other dislocations in the plane.
+This process is given by :
 \begin{equation}\label{eq:dis-3}
@@
 \end{equation}
-According to results calculated by first principle, the stacking faulting energy for TiAl is much smaller than $\rm{Ti_3Al}$, as a consequence calculated shear strength of TiAl and $Ti_3Al$is 4.1 Gpa and 2.86 Gpa along their easy slip plane respectively\cite{Liu2007}.
+According tothe  results calculated by first principle, the stacking fault energy of TiAl is much smaller than $\rm{Ti_3Al}$, as a consequence, calculated shear strength of TiAl and $\rm{Ti_3Al}$is 4.1 Gpa and 2.86 Gpa along their easy slip plane respectively\cite{Liu2007}.
 This calculation reveals that tensile behaviour in single crystal is mainly controlled by the type of the structure.
@@
 Mobility of dislocation is affected by structure of crystal, loading condition and temperature.
-$\alpha_2$ phase is made up of hcp  structured grain, grain with this type of structure possess less slip system compering with grain with fcc structure \cite{Zhu2012}, thus $\alpha_2$ phase is difficult do be deformed under uniaxial tensile loading.
+And $\alpha_2$ phase is made up of hcp  structured grain, grains with this type of structure possess less slip system compared with grain with fcc structure \cite{Zhu2012}, thus $\alpha_2$ phase is difficult do deform under uniaxial tensile loading.
 
-Main reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase.
-TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3[11\overline{2}0]$ prism planes shown by Fig.
+Main reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is  the strong plastic anisotropy of  $\alpha_2$ phase.
+TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of  $\alpha_2$ phase is carried by local slip of dislocations with the Burgers vector $1/3[11\overline{2}0]$ prism planes shown by Fig.
 \ref{fig:Defect}(b), which is by far the easiest slip system in $\alpha_2$ single crystals.
-The core of a dislocation intersecting an interface often needs to be transformed.
-For example, an ordinary 1/2 [110] dislocation gliding in one $\gamma$ grain has to be converted into a $[101]$ super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain.
-At the $\alpha_2/\gamma$ interface, dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $\rm{L1_0}$ structure.
-These core transformations are associated with a change of the dislocation line energy because the lengths of Burgers vectors and the shear module are different.
-Dislocations crossing semi-coherent boundaries have to intersect the misfit dislocation, a process that involves elastic interaction, jog formation and the incorporation of gliding dislocations into the mismatch structure of the interface.
-When slip is forced to cross $\alpha_2$ phase, pyramidal slip of the $\alpha_2$ phase is required, which needs an extremely high shear stress.
+Dislocation neighboring interfaces often needs to be transformed.
+For example, an ordinary 1/2 [110] dislocation gliding in one $\gamma$ grain has to be converted into $[101]$ super dislocation when the double Burgers vectors gliding in an adjacent $\gamma$ grain.
+At the $\alpha_2/\gamma$ interface, dislocations existing in  $D0_{19}$ structure  transform into dislocations, which is consistent with the $\rm{L1_0}$ structure.
+These core transformations are associated with the change of the dislocation line energy because of the differences of the length and the shear module.
+Pyramidal slip of the $\alpha_2$ phase is required, when slip is forced to cross $\alpha_2$ phase, this process needs an extremely high shear stress.
 
@@
 \ref{fig:stress&strain}, there is a critical value of void radius about 15 \AA, the void greater than 15 \AA\ cause serious detraction of strength of material.
-The decrease rate of loading area are smaller comparing with the detraction of strength, so it can be assumed that the  yield behavior and strength is much more related with local behavior of grain boundaries and void.
+The decrease rate of loading area are smaller  with the detraction of strength, so it can be assumed that the  yield behavior and strength is much more related with local behavior of grain boundaries and void.
 Grain and phase boundaries are obstacles to deformation process, thus the stability of boundaries have great impact on the strength of materials.

### 2018-11-23 draft/alexpub.tex
part2 added

@@
 % \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
-\Title{Micromechanism of  Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with Void Defect}
+\Title{Micromechanism of  Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with void}
 % Author Orchid ID: enter ID or remove command
@@
 Interaction between spherical nano void with different size and position was also examined in the simulation.
-The results show that (1) $\gamma$ phase is the major deformation source of the two phase alloy; (2) Void defect detracts the strength of the two phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
+The results show that (1) $\gamma$ phase is the major deformation source of the two phase alloy; (2) void detracts the strength of the two phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
 % Keywords
@@
 A great number of literatures cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}.
-Void defect can be arose due to specific volume differences induced by precipitation, different thermal expansion or shrinkage upon heating or cooling the specimen.
+void can be arose due to specific volume differences induced by precipitation, different thermal expansion or shrinkage upon heating or cooling the specimen.
 It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
@@
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
-The effect of void defect is another great concern about properties and deformation mechanism  of TiAl alloy.
+The effect of void is another great concern about properties and deformation mechanism  of TiAl alloy.
 Therefore, it is necessary to study the deformation response of intermetallics structural materials with the consideration of microstructure evolution.
@@
 Al bulk results in an increase of strength \cite{Yang1998}.
-Ti-Al alloy is a type of typical brittle material, thus it can be assumed that its properties are sensitive to the existence of void defect.
+Ti-Al alloy is a type of typical brittle material, thus it can be assumed that its properties are sensitive to the existence of void.
 Surface defects such as small notches can cause low and high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$-TiAl is also lowered by point defect \cite{Wu2016}.
@@
 Uniaxial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$.
-% In order to study the deformation mechanism of the two phase alloy and the effect of void defect, three types of models were created: Type-1.model without any void defect; Type-2.
+% In order to study the deformation mechanism of the two phase alloy and the effect of void, three types of models were created: Type-1.model without any void; Type-2.
 models with different size void inside $\alpha_2$ phase; Type-3.
@@
 	\includegraphics[width=1\linewidth]{img/tens}
-	\caption{Deformation process of the model without void defect}
+	\caption{Deformation process of the model without void}
 	\label{fig:deformation-pf}
@@
 %	/home/alex/Documents/violet/draft/img/perfect-line.pdf
-Deformation process of the model without void defect is shown in Fig.
+Deformation process of the model without void is shown in Fig.
 \ref{fig:deformation-pf}.
-The strength of the model without void defect is 5.3 GPa.
+The strength of the model without void is 5.3 GPa.
 According to stress response under constant rate of strain rate, the whole tensile process can be divided into four stages:
@@
 % Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
-\subsection{Deformation Mechanism of Two Phase TiAl Alloy without Void Defects}
+\subsection{Deformation Mechanism of Two Phase TiAl Alloy without voids}
 Snapshots of atom configuration at the 3 of 10 key points are shown by Fig.
@@
 \end{equation}
-According tothe  results calculated by first principle, the stacking fault energy of TiAl is much smaller than $\rm{Ti_3Al}$, as a consequence, calculated shear strength of TiAl and $\rm{Ti_3Al}$is 4.1 Gpa and 2.86 Gpa along their easy slip plane respectively\cite{Liu2007}.
+According to the  results calculated by first principle, the stacking fault energy of TiAl is much smaller than $\rm{Ti_3Al}$, as a consequence, calculated shear strength of TiAl and $\rm{Ti_3Al}$is 4.1 Gpa and 2.86 Gpa along their easy slip plane respectively\cite{Liu2007}.
 This calculation reveals that tensile behaviour in single crystal is mainly controlled by the type of the structure.
@@
 These core transformations are associated with the change of the dislocation line energy because of the differences of the length and the shear module.
-Pyramidal slip of the $\alpha_2$ phase is required, when slip is forced to cross $\alpha_2$ phase, this process needs an extremely high shear stress.
+Pyramidal slip of the $\alpha_2$ phase is required  when slip is forced to cross $\alpha_2$ phase, this process needs an extremely high shear stress.
 
@@
 	\includegraphics[width=1\linewidth]{img/slice-view}
-	\caption{ Model with no void defect (b), with void inside $\alpha_2$ phase (c) with void at $\alpha_2-\gamma$ interface (d)}
+	\caption{ Model with no void (b), with void inside $\alpha_2$ phase (c) with void at $\alpha_2-\gamma$ interface (d)}
 	\label{fig:model-creation}
@@
 In Fig.
-\ref{fig:model-creation}, voids with different size: 2\AA, 5\AA, 10\AA, 15\AA\ were placed  at $\alpha_2$/$\gamma$ phase boundary, inside $\gamma$ phase respectively.
+\ref{fig:model-creation}, voids with different size of 2\AA, 5\AA, 10\AA and 15\AA\ were placed  at $\alpha_2$/$\gamma$ phase boundary, inside $\gamma$ phase respectively.
 The strength of materials with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}.
-The existence of void have little impact on the elastic properties of the material, and the model without void defect has the best strength 5.3 GPa, the yield stress of model with void is smaller.
+The existence of void have little impact on the elastic properties of the material, and the model without void has the largest strength 5.3 GPa, the yield stress of model with void is smaller.
 Void at $\alpha_2$/$\gamma$ phase boundary  detracts the strength of  material most, and the void inside $\alpha_2$ phase  have less impact on the strength.
@@
 \end{equation}
-where $\sigma_0$ is the strength of model without void defects 5.3 Gpa, and $A_0$ represents initial section area,  $A^*$ is effective section area in consider of the area detraction by void.
+where $\sigma_0$ is the strength of model without voids of 5.3 Gpa, and $A_0$ represents initial section area,  $A^*$ is effective section area in consideration of the area detraction by void.
 In classic theory, the relationship between void size and strength of the model is linear.
-However, simulation results reveals that two phase Ti-Al alloy is sensitive to existence of void defect.
-Comparing with the strength determined by molecular dynamics simulation and the result4s calculated with formulation (\ref{eq:section}), it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects have dramatic influence on the yield and fracture process of the materials.
+However, simulation results reveals that two phase Ti-Al alloy is sensitive to defect of void.
+Comparing the strength determined from molecular dynamics simulation and the result4s calculated with formulation (\ref{eq:section}), it can be seen that the main factor that affects the strength of materials is local behavior of the materials, thus evolution of defects have dramatic influence on the yield and fracture process of the materials.
 
@@
 It has been observed in Fig.
-\ref{fig:strength} that voids detracts the strengths of  material.
-The max stress  of the simulation cell decreases as the volume of voids are larger.
-From Fig.
-\ref{fig:stress&strain}, there is a critical value of void radius about 15 \AA, the void greater than 15 \AA\ cause serious detraction of strength of material.
-The decrease rate of loading area are smaller  with the detraction of strength, so it can be assumed that the  yield behavior and strength is much more related with local behavior of grain boundaries and void.
-Grain and phase boundaries are obstacles to deformation process, thus the stability of boundaries have great impact on the strength of materials.
-Interactive between grain boundary and void determines the fracture mode of the TiAl alloy.
+\ref{fig:strength} that voids detract the strength of  materials.
+The max stress  of the simulation cell decreases as the volume of voids increases.
+It can be seen from Fig.
+\ref{fig:stress&strain}, there is a critical value of void radius about 15 \AA, the void greater than 15 \AA\ causes serious detraction of strength of material.
+The decrease rate of loading area are smaller compared  with the detraction of strength, so it can be assumed that the  yield behavior and strength is more related with local behavior of grain boundaries and void.
+Grain and phase boundaries are obstacles to deformation process, thus the stability of boundaries have a great impact on the strength of materials.
+Interactive between grain boundary and void determines the fracture mode of   Ti-Al alloy.
 
 \subsection{Evolution of spherical void}
-The role of void can be concluded as two main parts: source of dislocations and obstacles to dislocations, which part is dominant depends on the location of void.
+The role of void can be concluded as two main parts: source of dislocations and obstacles to dislocations, which is dominant depends on the location of void.
 Void inside $\alpha_2$ phase plays a role of inclusion, in other words, this type of void possess similar properties as second phase particles.
@@
 \end{figure}
-Void inside $\alpha_2$ phase induce considerable misfit-stress fields and thus can influence material properties pronouncedly.
-Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and 'free' atoms surounded the void.
-That's a possibly favorable effect of second-phase particles that void defect contribution to the enhancement of mechanical strength.
-The strengthening effect of the particle inside single phase TiAl alloy have been verified by experiment \cite{Zghal1998}.
+Void inside $\alpha_2$ phase induced considerable misfit-stress fields and thus can influence material properties pronouncedly.
+Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and surface atoms surounding the void.
+That's a possibly favorable effect of second-phase particles that void contribution to the enhancement of mechanical strength.
+The strengthening effect of the particle inside single phase TiAl alloy has been verified by experiment \cite{Zghal1998}.
 Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength.
-The defect evolution neighboring the void during yield stage is given by Fig.
+The defect evolution neighboring the void during yield stage is shown in Fig.
 \ref{fig:orowan}(a), the role of void is similar to second-phase particles.
-It can serve as obstacles for dislocation migration which is shown by Fig.
-\ref{fig:orowan}(b): the stress fields surrounding the second-phase particles can be of block propagation of the stress field of a migrating dislocation, the void particle acts as pinning point.
-The dislocation can pass two pinning points a critical shear stress is needed that depends on the distance between  obstacles, which can be regarded as second-phase particles\cite{Xiong2015}:
+It servers as obstacles for dislocation migration which is shown by Fig.
+\ref{fig:orowan}(b): the stress fields surrounding the second-phase particles block migrating dislocation, the void particle acts as pinning point.
+The dislocation can pass two pinning points under shear  stress , and the critic value depends on the distance between  obstacles, it is be given by \cite{Xiong2015}:
 \begin{equation} \label{eq:orowan} 
@@
 As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles.
-Consequently, the effective average distance between the second phase particles has decreased to d which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide.
-The width of a burgers vector, will be generated at both sides of a crystal along the direction of  burgers vector after dislocation traversing the entire crystal, as is shown in the third sub-figure of Fig.
+Consequently, the effective average distance between the second phase particles has decreased to $d$ which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide.
+The width of a burgers vector, will be generated at both sides of a crystal along the direction of  burgers vector after dislocation traversing the entire crystal, as is shown in the third subfigure of Fig.
 \ref{fig:orowan}(b).
@@
 Deformation mechanism of the model with void at boundary can be  more complex due to the interaction between void and phase boundary.
-In elastic stage, the system composed of $\alpha_2$ phase, $\gamma$ phase and void is in equilibrium, internal stress are balanced under compatible deformation as is shown by the first sub-figure of Fig.
+In elastic stage, the system composed of $\alpha_2$ phase, $\gamma$ phase and void is in equilibrium, internal stress are balanced under compatible deformation as is shown by the first subfigure of Fig.
 \ref{fig:void-gb}(b).
@@
 In this paper, deformation behavior of two phase Ti-Al alloy under tensile loading was simulated with MD method.
-The mechanism of deformation was investigated under atomic scale, and the effect of void defect on the properties of two phase Ti-Al alloy was also studied.
+The mechanism of deformation was investigated under atomic scale, and the effect of void on the properties of two phase Ti-Al alloy was also studied.
 The conclusions are as follows:\\
 (1) Major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha_2$ phase is harder to be deformed, this inhomogeneity results in cracks at interface of the two phase. \\
-(2) Effect of  void defect on the strength of the two phase alloy is sensitive to the location of  void.
-Void inside grain have less detraction to the strength of material because of strengthening mechanism similar to second phase particle.
+(2) Effect of  void on the strength of the two phase alloy is sensitive to the location of  void.
+Void inside grain hasss detraction to the strength of material because the engthening mechanism similar to second phase particle.
 Void at $\alpha_2 / \gamma$ boundary is most risky situation for two phase alloy because of fast fracture along boundary.
@@
 51665030) and the Program for Changjiang Scholars and Innovative Research Team in Universities of the Ministry of Education of China (No.
-IRT-15R30) and the Doctoral Research Foundation of Lanzhou University of Technology.}
+IRT-15R30), the Hongliu First-class  Disciplines Development Program of Lanzhou University of Technology, and the Doctoral Research Foundation of Lanzhou University of Technology.}
 

### 2018-11-23 draft/alexpub.tex
小改毕

@@
 Interaction between spherical nano void with different size and position was also examined in the simulation.
-The results show that (1) $\gamma$ phase is the major deformation source of the two phase alloy; (2) void detracts the strength of the two phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
+The results show that (1) $\gamma$ phase is the major deformation source of the two phase alloy.
+(2) void detracts the strength of the two phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
 % Keywords
-\keyword{two phase Ti-Al alloy, void, molecular dynamics, cold deformation}
+\keyword{two phase Ti-Al alloy; void; molecular dynamics; cold deformation}
 
@@
 
-The interaction of particle in the material is determined by interatomic potential.
+The interaction of particles in the material is determined by interatomic potential.
 Many reported simulation cases of deform and crack propagation in metal materials were performed with embedded atomic method due to its better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015,Zepeda-Ruiz2017,Fan2018a}.
 Embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study.
-The simulation is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}.
-We performed constant-pressure and constant-temperature (NPT) molecular dynamics simulation at room temperature (298K).
-The definition of potential is as following:
+The simulation is performed  with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}.
+We performed constant-pressure and constant-temperature (NPT) MD simulation at room temperature (298K).
+Definition of the potential is as following:
 
@@
 The initial dimension of simulation cell is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model contains about 460,000 atoms.
-The grain orientation and size were randomly created with Voronoi method by code ATOMSK \cite{Hirel2015}, and resulting in the arbitrary shape and orientation of the grains.
+The model contains 6 grains, with random shape and orientation were created with Voronoi method.
 Uniaxial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$.
@@
 \subsection{Analysis method}
-In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010a}.Dislocation is visualized by DXA method, and Centro-symmetry parameter(CSP) is used to tell grain boundary from  $\alpha_2$ phase and $\gamma$ phase.
+In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010a}.Dislocation is visualized by DXA method, and centro-symmetry parameter(CSP) is used to deffer grain boundaries from  $\alpha_2$ phase and $\gamma$ phase.
 The definition of CSP is as following:
@@
 stage - \uppercase\expandafter{\romannumeral4}: fracture stage.
-Following discussion concentrates on deformation phenomena that rely on the elastro-plastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in two phase alloys.
+Following discussion concentrates on deformation phenomena that rely on the elastro-plastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurred in two phase alloys.
 
@@
 		\centering
-		\caption{Dislocation length under differentstrain }
+		\caption{Summary of didderent types of dislocation under different strain }
 		\label{fig:disum}
@@
 	\includegraphics[width=1\linewidth]{img/slice-view}
-	\caption{ Model with no void (b), with void inside $\alpha_2$ phase (c) with void at $\alpha_2-\gamma$ interface (d)}
+	\caption{Model of the simulation(a) and sliced view of the model with no void(b), with void inside $\alpha_2$ phase(c) with void at $\alpha_2 / \gamma$ interface(d)}
 	\label{fig:model-creation}
@@
 		\centering
-		\caption{Stress-strain response of models}
+		\caption{Stress-strain response of the materials under tensile loading}
 		\label{fig:stress&strain}
@@
 		\centering
-		\caption{Yield strength of material with void}
+		\caption{Yield strength of the materials with different size void}
 		\label{fig:strength}
@@
 	\includegraphics[width=1\linewidth]{"img/orowan"}
-	\caption{Orowan process in $\alpha_2$-phase (atoms with regular arrangement have been removed)}
+	\caption{Orowan process occurred inside $\alpha_2$ phase grain (removed atoms with regular arrangement)}
 	\label{fig:orowan}
@@
 	\includegraphics[width=1\linewidth]{"img/void-gb"}
-	\caption{(a) Fracture mode of two types of model  (b)Evolution of void at  phase boundary}
+	\caption{(a) Fracture mode of two types of model  (b)Evolution of void at $\alpha_2 / \gamma$ phase boundary}
 	\label{fig:void-gb}

### 2018-11-23 draft/wmm2.tex
小改毕

--- 2018-11-23 draft/alexpub.tex
@@
 Deformation phenomena of Ti-Al alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
-Much of the work has been performed on single phase $\gamma$-TiAl alloys and polysynthetically twinned crystals(PTC)\cite{Appel2016}.
+Much of the work has been performed on single phase $\gamma$-TiAl alloys and polysynthetically twinned crystals (PTC)\cite{Appel2016}.
 Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}.
 A great number of literatures cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}.
-void can be arose due to specific volume differences induced by precipitation, different thermal expansion or shrinkage upon heating or cooling the specimen.
+void can be produced due to specific volume differences induced by precipitation, different thermal expansion or shrinkage upon heating or cooling the specimen.
 It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
@@
 Previous study on void growth in single crystal $\gamma$-TiAl reveals that void with high volume fraction detracts yield strength \cite{Tang2014, Xu2011}.
-Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations, \cite{Jing2018a,Elkhateeb2018}, voids inside material are soures of dislocation and affects the properties of materials differently because of differences in size and position.
+Evolution of void in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations, \cite{Jing2018a,Elkhateeb2018}, voids inside material are sources of dislocation and affects the properties of materials differently because of differences in size and position.
 The deformation and fracture mechanisms in the duplex microstructure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang2014}.
@@
 The velocity  of dislocation movement rise along with increase of  stress, the mobility  of dislocation is relatively poor at 298 K.
-Due to motion of dislocations is inactive inside $\alpha_2$ phase,  typical strengthening mechanism closely related with interaction between grain boundary and dislocation can not be dramatic at room temperature, piling up of dislocations is not observed in this simulation, which is shown in Fig.
+Due to motion of dislocations is inactive inside $\alpha_2$ phase,  typical strengthening mechanism closely related with interaction between grain boundary and dislocation is not dramatic at room temperature, piling up of dislocations is not observed in this simulation, which is shown in Fig.
 \ref{fig:Defect}.
@@
 It's sessile in the slip plane, playing a role of barrier against other dislocations in the plane.
-This process is given by :
+This process is given by
 \begin{equation}\label{eq:dis-3}
@@
 The existence of void have little impact on the elastic properties of the material, and the model without void has the largest strength 5.3 GPa, the yield stress of model with void is smaller.
-Void at $\alpha_2$/$\gamma$ phase boundary  detracts the strength of  material most, and the void inside $\alpha_2$ phase  have less impact on the strength.
+Void at $\alpha_2$/$\gamma$ phase boundary detracts the strength of material most, and the void inside $\alpha_2$ phase has less impact on the strength.
 Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by
@@
 The decrease rate of loading area are smaller compared with the detraction of strength, so it can be assumed that the  yield behavior and strength is more related with local behavior of grain boundaries and void.
-Grain and phase boundaries are obstacles to deformation process, thus the stability of boundaries have a great impact on the strength of materials.
+Grain and phase boundaries are obstacles to deformation, thus the stability of boundaries have a great impact on the strength of materials.
 Interactive between grain boundary and void determines the fracture mode of   Ti-Al alloy.
@@
 The role of void can be concluded as two main parts: source of dislocations and obstacles to dislocations, which is dominant depends on the location of void.
-Void inside $\alpha_2$ phase plays a role of inclusion, in other words, this type of void possess similar properties as second phase particles.
+Void inside $\alpha_2$ phase plays a role of inclusion, in other words, this type of void possesses similar properties as second phase particles.
 
@@
 Void inside $\alpha_2$ phase induced considerable misfit-stress fields and thus can influence material properties pronouncedly.
-Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and surface atoms surounding the void.
+Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and surface atoms surrounding the void.
 That's a possibly favorable effect of second-phase particles that void contribution to the enhancement of mechanical strength.
@@
 \ref{fig:orowan}(a), the role of void is similar to second-phase particles.
-It servers as obstacles for dislocation migration which is shown by Fig.
+It functions as obstacles for dislocation migration which is shown by Fig.
 \ref{fig:orowan}(b): the stress fields surrounding the second-phase particles block migrating dislocation, the void particle acts as pinning point.
@@
 The difference of crack mode can attribute to the position of void and the evolution of the defect.
-Nucleation, emission of Shockley partial dislocation affect the evolution of the void at boundary greatly due to the anisotropy of two phases on the both sides of the phase boundary.
-The void weaken the strength of the grain it locates,  $\alpha_2$ phase grain is easy to deformed under shear stress, thus that caused the crack initiated inside grain and finally caused fracture across the grain.
-Deformation mechanism of the model with void at boundary can be  more complex due to the interaction between void and phase boundary.
+Nucleation, emission of Shockley partial dislocation affects the evolution of the void at boundary greatly due to the anisotropy of two phases on the both sides of the phase boundary.
+The void weakened the strength of the grain it locates, $\alpha_2$ phase grain is easy to deformed under shear stress, thus that caused the crack initiated inside grain and finally caused fracture across the grain.
+Deformation mechanism of the model with void at boundary is more complex due to the interaction between void and phase boundary.
 In elastic stage, the system composed of $\alpha_2$ phase, $\gamma$ phase and void is in equilibrium, internal stress are balanced under compatible deformation as is shown by the first subfigure of Fig.
@@
 \ref{fig:void-gb}(b)-2.
-The micro crack initialed from the zone neighbor  the interface between void and boundary, that quickly caused abrupt decohension of phase boundary.
+The micro crack initialed from the zone neighboring the interface between void and boundary, that quickly caused abrupt decohension of phase boundary.
 That accounts for the reason that material with void at $\alpha_2 / \gamma$ phase boundary is weaker than other cases.
@@
 The conclusions are as follows:\\
-(1) Major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha_2$ phase is harder to be deformed, this inhomogeneity results in cracks at interface of the two phase. \\
+(1) Major deformation component of the two phase TiAl alloy is $\gamma$ phase, $\alpha_2$ phase is harder to be deformed, this inhomogeneity results in cracks at interface of the two phases. \\
 (2) Effect of  void on the strength of the two phase alloy is sensitive to the location of  void.
-Void inside grain hasss detraction to the strength of material because the engthening mechanism similar to second phase particle.
+Void inside grain has detraction to the strength of material because the strengthening mechanism similar to second phase particle.
 Void at $\alpha_2 / \gamma$ boundary is most risky situation for two phase alloy because of fast fracture along boundary.

### 2018-11-23 draft/alexpub.tex
add

@@
 	\includegraphics[width=1\linewidth]{img/slice-view}
-	\caption{Model of the simulation(a) and sliced view of the model with no void(b), with void inside $\alpha_2$ phase(c) with void at $\alpha_2 / \gamma$ interface(d)}
+	\caption{Model of the simulation(a) and sliced view of the model with no void(b), inside $\alpha_2$ phase(c) at $\alpha_2 / \gamma$ phase boundary(d)}
 	\label{fig:model-creation}

### 2018-11-25 draft/alexpub.tex
few

@@
 %=================================================================
-\documentclass[Unknown,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi} 
+\documentclass[materials,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi} 
 \usepackage{siunitx}
@@
 % Full title of the paper (Capitalized)
-% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
-\Title{Micromechanism of  Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with void}
+
+\Title{Micromechanism of  Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with Void}
 % Author Orchid ID: enter ID or remove command
@@
 Poor ductility of Ti-Al alloy  at room temperature strongly affects the safety of structures like turbo of aircraft engine and combustion generator \cite{Munz2017}.
+
 Deformation phenomena of Ti-Al alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
 Much of the work has been performed on single phase $\gamma$-TiAl alloys and polysynthetically twinned crystals(PTC)\cite{Appel2016}.
-Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}.
-A great number of literatures cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}.
+Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}.Mess research  cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}.
 void can be arose due to specific volume differences induced by precipitation, different thermal expansion or shrinkage upon heating or cooling the specimen.
 It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important \cite{Hempel2017a}.
-The initiation of crack at microscopic scale is a dynamic process, which results in difficulties on study of  mechanisms about deformation and cracking, these defects are known playing a fundamental role in the deformation of materials.
+The initiation of crack at microscopic scale is a dynamic process, which results in difficulties on study of  mechanism about deformation and cracking, these defects are known playing a fundamental role in the deformation of materials.
 Multiscale method has been applied to study deformation behavior of polycrystal with single aluminum \cite{Groh2009} and titanium element respectively \cite{Liu2018}.
 It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.
+
 The effect of void is another great concern about properties and deformation mechanism  of TiAl alloy.
@@
 \subsection{Analysis method}
-In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010a}.Dislocation is visualized by DXA method, and centro-symmetry parameter(CSP) is used to deffer grain boundaries from  $\alpha_2$ phase and $\gamma$ phase.
+In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010a}.Dislocation is visualized by DXA method, and centro-symmetry parameter(CSP) is used to differ grain boundaries from  $\alpha_2$ phase and $\gamma$ phase.
 The definition of CSP is as following:
@@
 According to the  results calculated by first principle, the stacking fault energy of TiAl is much smaller than $\rm{Ti_3Al}$, as a consequence, calculated shear strength of TiAl and $\rm{Ti_3Al}$is 4.1 Gpa and 2.86 Gpa along their easy slip plane respectively\cite{Liu2007}.
-This calculation reveals that tensile behaviour in single crystal is mainly controlled by the type of the structure.
+This calculation reveals that tensile behavior in single crystal is mainly controlled by the type of the structure.
 However, in two phase Ti-Al alloy, deformation of $\alpha_2$ phase is earlier than $\gamma$ phase during yield stage, thus local displacement of two phases are incompatible during yield stage.
@@
 \end{figure}
-Void inside $\alpha_2$ phase induced considerable misfit-stress fields and thus can influence material properties pronouncedly.
-Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and surface atoms surounding the void.
+Void inside $\alpha_2$ phase induced considerable misfit-stress fields and thus can influence material properties.
+Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and surface atoms surrounding the void.
 That's a possibly favorable effect of second-phase particles that void contribution to the enhancement of mechanical strength.
@@
 	\includegraphics[width=1\linewidth]{"img/void-gb"}
-	\caption{(a) Fracture mode of two types of model  (b)Evolution of void at $\alpha_2 / \gamma$ phase boundary}
+	\caption{(a) Fracture mode of two types of mode,  (b)Evolution of void at $\alpha_2 / \gamma$ phase boundary}
 	\label{fig:void-gb}
@@
 That accounts for the reason that material with void at $\alpha_2 / \gamma$ phase boundary is weaker than other cases.
-\section{conclusion}
+\section{Conclusion}
 In this paper, deformation behavior of two phase Ti-Al alloy under tensile loading was simulated with MD method.
@@
 (2) Effect of  void on the strength of the two phase alloy is sensitive to the location of  void.
-Void inside grain hasss detraction to the strength of material because the engthening mechanism similar to second phase particle.
+Void inside grain has detraction to the strength of material because the strengthening mechanism similar to second phase particle.
 Void at $\alpha_2 / \gamma$ boundary is most risky situation for two phase alloy because of fast fracture along boundary.
@@
 \bibliography{ref/VIOLET-ref.bib}
-\funding{This research was funded by the National Natural Science Foundation of China (No.
-51665030) and the Program for Changjiang Scholars and Innovative Research Team in Universities of the Ministry of Education of China (No.
+\funding{This research was funded by the National Natural Science Foundation of China (No.51665030, No.51865027) and the Program for Changjiang Scholars and Innovative Research Team in Universities of the Ministry of Education of China (No.
 IRT-15R30), the Hongliu First-class  Disciplines Development Program of Lanzhou University of Technology, and the Doctoral Research Foundation of Lanzhou University of Technology.}

### 2018-12-27 MDPI-Materials/1stEdt/subm/alexpub.tex
2nd Review

--- 2018-11-25 draft/alexpub.tex
@@
 % Authors, for the paper (add full first names)
-\Author{Author \orcidA{}}
-%\Author{Ruicheng Feng $^{1,2}$\orcidA{}, Maomao Wang $^{1}$\orcidB{}}
-
-% Authors, for metadata in PDF
-%\AuthorNames{Maomao Wang $^{1,\dagger,\ddagger}$\orcidB{}, Firstname Lastname and Firstname Lastname}
-
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-% $^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com (R.F.); 15620864891@163.com (M.W.)\\
-$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China;\\
+%\Author{Author \orcidA{}}
+\Author{Ruicheng Feng$^{1,2}$\orcidA{}; Maomao Wang $^{1,*}$\orcidB{}; Haiyan Li$^{1,*}$; Yongnian Qi$^{1}$; Qi Wang$^{1}$; Zhiyuan Rui$^{1,2}$}
+\address{
+$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com(R.F.); 15620864891@163.com(M.W.); y5217@163.com(H.L.); 13893591491@163.com(Y.Q.); 18350122524@163.com(Q.W); zhiy\underline{ \ }rui@163.com(Z.R.)\\
 % $^{2}$ \quad Key Laboratory of Digital Manufacturing Technology and Application, Ministry of Education, Lanzhou University of Technology, Lanzhou 730050, China
@@
 % Contact information of the corresponding author
-\corres{Correspondence: e-mail@e-mail.com; Tel.: +x-xxx-xxx-xxxx}
+\corres{Correspondence: 15620864891@163.com; y5217@163.com}
 
@@
 Dislocations are recognized and identified using the dislocation analysis (DXA) of ovito.
-The length of Shorckley dislocation with Burgers vector $1/6[1 1 2]$ increased sharply during yield stage of the deformation process in Fig.
+The length of Shockley dislocation with Burgers vector $1/6[1 1 2]$ increased sharply during yield stage of the deformation process in Fig.
 \ref{fig:disum}, but the length of perfect dislocation fluctuated at a low level.
@@
 \reftitle{References}
-\bibliography{ref/VIOLET-ref.bib}
+\bibliography{ref.bib}
 \funding{This research was funded by the National Natural Science Foundation of China (No.51665030, No.51865027) and the Program for Changjiang Scholars and Innovative Research Team in Universities of the Ministry of Education of China (No.
-IRT-15R30), the Hongliu First-class  Disciplines Development Program of Lanzhou University of Technology, and the Doctoral Research Foundation of Lanzhou University of Technology.}
+IRT-15R30), the Hongliu First-class  Disciplines Development Program of Lanzhou University of Technology.}
 

### 2018-12-27 MDPI-Materials/2ndEdt/2ndEdt.tex
2nd Review

--- 2018-12-27 MDPI-Materials/1stEdt/subm/alexpub.tex
@@
 \Author{Ruicheng Feng$^{1,2}$\orcidA{}; Maomao Wang $^{1,*}$\orcidB{}; Haiyan Li$^{1,*}$; Yongnian Qi$^{1}$; Qi Wang$^{1}$; Zhiyuan Rui$^{1,2}$}
-\address{
+
+% Authors, for metadata in PDF
+%\AuthorNames{ }
+% frcly@163.com(R.F.);15620864891@163.com(M.W.); y5217@163.com(H.L.);13893591491@163.com(Y.Q.);18350122524@163.com(Q.W);zhiy_rui@163.com(Z.R)
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+%$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com (R.F.); 15620864891@163.com (M.W.)\\
 $^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com(R.F.); 15620864891@163.com(M.W.); y5217@163.com(H.L.); 13893591491@163.com(Y.Q.); 18350122524@163.com(Q.W); zhiy\underline{ \ }rui@163.com(Z.R.)\\
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Cold deformation behavior of poly crystalline metallic material is affected by intrinsic defects such as dislocation, void, inclusion etc.
+\abstract{Cold deformation behavior of polycrystalline metallic material is affected by intrinsic defects such as dislocation, void, inclusion etc.
 Existing studies on $\alpha_2(\rm{Ti_3Al})$+$\gamma(\rm{TiAl})$  two phase Ti-Al alloy cover about deformation behavior mainly on macro scale.
@@
 Interaction between spherical nano void with different size and position was also examined in the simulation.
-The results show that (1) $\gamma$ phase is the major deformation source of the two phase alloy.
-(2) void detracts the strength of the two phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
+The results show that (1) In elastic stage, deformation of the two phase is coordinated, but $\rm{Ti_3Al}$ is more deformable;(2) In plastic stage, $\gamma$ phase is the major dislocation  source in two phase alloy; (3) void detracts the strength of the two phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
 % Keywords
@@
 Titanium  aluminum based intermetallic alloys are promising high temperature structural materials because of their great corrosion resistance and strength at high temperature.
-Compared with nickle based alloy,  Ti-Al based alloys have lower density and are pron to be utilized in combustion engine, turbine, and other components working at high temperature from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius} \cite{Clemens2016}.
+Compared with nickel based alloy,  Ti-Al based alloys have lower density, it can be used in combustion engine, turbine, and other components working at high temperature from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius} \cite{Clemens2016}.
 The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20\% because the weight of components decreased from 30\% to 40\% \cite{Bewlay2016}.
@@
 
-Deformation phenomena of Ti-Al alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.
-Much of the work has been performed on single phase $\gamma$-TiAl alloys and polysynthetically twinned crystals(PTC)\cite{Appel2016}.
-Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}.Mess research  cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}.
+Deformation phenomena of Ti-Al alloys have been widely studied in order to overcome the problems associated with the poor ductility and damage tolerance.
+Much of the work has been performed on single phase $\gamma$-TiAl, $\rm{Ti_3Al}$ alloys, and polysynthetically twinned crystals(PTC)\cite{Appel2016}.
+Experiments reveals that  the dominant deformation mode in $\rm{Ti_3Al}$ at low temperature is slip activity without any twinning, and fracture type is cleavage\cite{sastry1980plastic}.
+Around 1990s, experimental studies on the two phase lamellae Ti-Al alloys show that  mechanical twin and glide of  dislocation are major sources of deformation\cite{Farenc1993,Appel2005,Appel1998a}.
+Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale, defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}.Mess research  cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}.
+In situ experiments have shown that TiAl and $\rm{Ti_3Al}$ in two phase alloy exhibit different properties comparing in single phase alloys\cite{Singh2006}.
 void can be arose due to specific volume differences induced by precipitation, different thermal expansion or shrinkage upon heating or cooling the specimen.
@@
 A lot of work carried out on the  effect of various defects on the behavior of different materials, showing that point defects may affect the properties of materials greatly.
-The mechanical performance of irradiated copper is affected by the interaction between irradiation and dislocation \cite{Kiener2011}.
+The mechanical performance of irradiated copper is affected by the interaction between irradiation and dislocation \cite{Kiener2011b}.
 Vacancy concentration in single crystal and polycrystal Fe–40 at.
@@
 The interaction of particles in the material is determined by interatomic potential.
-Many reported simulation cases of deform and crack propagation in metal materials were performed with embedded atomic method due to its better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015,Zepeda-Ruiz2017,Fan2018a}.
-Embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study.
+Many reported simulation cases of deforming and crack propagation in metal materials were performed with embedded atomic method due to its better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015,Zepeda-Ruiz2017,Fan2018a}.
+Embedded atom method (EAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study.
 The simulation is performed  with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}.
-We performed constant-pressure and constant-temperature (NPT) MD simulation at room temperature (298K).
+We did constant-pressure and constant-temperature (NPT) MD simulation at room temperature (298K).
 Definition of the potential is as following:
@@
 
-\subsection{Model Creation of Crystalline}
+\subsection{Modeling}
 \begin{figure}[ht]
@@
 
-Two phase Ti-Al alloy is composed of $\gamma $-TiAl and $\alpha_2$-$\rm Ti_3Al$ has a fcc type cell with an $L1_0$ structure, and $\alpha_2$-$\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Fig.
-\ref{fig:tial-cell}, constructing parameters of the two type of unit cell are given by table \ref{tab:lattice_parameter}.
-Periodic boundary conditions (PBC) are applied along three directions, which makes polycrystal with periodic nanovoid structures.
-The initial dimension of simulation cell is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model contains about 460,000 atoms.
-The model contains 6 grains, with random shape and orientation were created with Voronoi method.
-Uniaxial load was applied to the model at a strain rate of $5\times10^8\ \rm{s}^{-1}$.
+Two phase Ti-Al alloy is composed of $\gamma $-TiAl and $\alpha_2$-$\rm Ti_3Al$, TiAl has a fcc type cell with an $L1_0$ structure, and $\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Fig.
+\ref{fig:tial-cell}.
+Geometry parameters of the two type of unit cell are given by table \ref{tab:lattice_parameter}.
+Periodic boundary conditions (PBC) were applied along three directions, which makes polycrystal with periodic nanovoid structures.
+The initial size of simulation box is $L_x =200$ \si{\angstrom}, $L_y = $180\si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model  about 460,000 atoms.
+The model includes 6 grains, with random shape and orientation created by Voronoi method.
+Total simulation time is restricted to computer power, thus strain rate in molecular dynamic simulation is much greater than physical experiments.
+Attempts have been done to find decent time step and strain rate for tensile test with MD simulation.
+If the strain rate is too high and time step is too large in the simulation, the model cannot predict the real behavior of dislocations.
+Previous work \cite{Zhu2008,Wu2016}  reveals that a strain rate from  $10^8\ \rm{s}^{-1}$ to $10^9\ \rm{s}^{-1}$ is appropriate for system composed of metal atoms like Ti-Al metallic materials.
+Thus the strain rate of uniaxial loading was set as $5\times10^8\ \rm{s}^{-1}$.
+
 % In order to study the deformation mechanism of the two phase alloy and the effect of void, three types of models were created: Type-1.model without any void; Type-2.
@@
 \subsection{Analysis method}
-In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010a}.Dislocation is visualized by DXA method, and centro-symmetry parameter(CSP) is used to differ grain boundaries from  $\alpha_2$ phase and $\gamma$ phase.
+In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito\cite{Stukowski2010}.Dislocation is visualized by DXA method, and centro-symmetry parameter(CSP) is used to differ grain boundaries, $\alpha_2$ phase grains and $\gamma$ phase grains.
 The definition of CSP is as following:
-
 	\begin{equation} \label{eq:csp} 
@@
 	\end{equation}
-
 where $\vec{R_i}$ and ${\vec{R}}_{i+6}$ are the vectors corresponding to the six pairs of opposite nearest neighbors in the fcc lattice.
@@
 By removing all the perfect and surface atoms within the bulk, atoms around defected zone are visualized.
-
+ \subsection{Model Verification}
+The results of molecular dynamics simulation greatly rely on accuracy of potential and controlling parameters such as strain rate, temperature and relaxation time.
+Thus we performed model verification on a simplified model and then compared the results with experiments and simulation done by others.
+ \begin{figure}[ht]
+ 	\centering
+ 	\includegraphics[width=1\linewidth]{img/cold-fracture2}
+ 	\caption{(a) Verifying model: TiAl single crystal bulk (b) Cracked surface of atomic model\\ (c) Cracked surface from experiment\cite{CHEN2015365}}
+ 	\label{fig:verify}
+ \end{figure}
+ uniaxial tensile loading  was applied to single crystal $\gamma$-TiAl bulk shown by Fig.
+\ref{fig:verify}(a), potential and relaxation parameters are as same as which applied to the polycrystalline model.
+When temperature is 300K, the sample was tensioned along [0 0 1] direction at a constant stain rate of $5\times10^8\ \rm{s}^{-1}$.
+The yield strength of the single crystal TiAl alloy is 9.5 GPa  and that is in good agreement with  work by Tang\cite{Tang2010} in consideration of size effect.
+And the snapshoot of the fracture surface is shown by Fig.
+\ref{fig:verify}, and compared with experiment results by Cao\cite{CHEN2015365} shown in Fig.
+\ref{fig:verify}(c).
+It should be noticed that the image from SEM is in a greater scale than our simulation cell.
+However, the cracked surface in atomic model exhibits two major characteristics of TiAl alloy.
+First, the fracture type of TiAl at room temperate is typical brittle failure.
+Second, the fracture surface  of atomic model in Fig.
+\ref{fig:verify} (b) is typical cleavage surface.
+This verification case has proven that the EAM potential is efficiency and accurate enough, and the simulation work flow is valid to predict failure behavior of  the system composed of Ti-Al.
 \section{Results and Discussion}\label{section:RD}
@@
 
+\subsection{Deformation Mechanism of Two Phase Ti-Al Alloy }
+
 % Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
-\subsection{Deformation Mechanism of Two Phase TiAl Alloy without voids}
-Snapshots of atom configuration at the 3 of 10 key points are shown by Fig.
+% \subsection{Plastic }
+During elastic stage, the deformation of $\alpha_2$ phase and $\gamma$ phase grains is compatible, however the properties of two phases are different.
+The elastic constants given by  experiments\cite{Schwarz1995,Tanaka1996} are listed in  table \ref{tab:elastic}.
+$C_{11}^{\alpha_2}$ is 176, which is smaller than $C_{11}^{\gamma}$, other 5 parameters but $C_{33}$ of $\rm{Ti_3Al}$ are also smaller than TiAl.
+In order to quantify the difference of the two phase, deformation gradient was calculated by formulation:
+\begin{equation}
+\label{eq:strain-grade}
+\mathbf { F^e } = \frac { \partial \mathbf { x } } { \partial \mathbf { X } } = \operatorname { Grad } \mathbf { x } , \quad F _ { i J } = \frac { \partial x _ { i } } { \partial X _ { J } }
+\end{equation}
+we computes the atomic level elastic strain and deformation gradient tensors in crystalline systems with the numerical method proposed by \cite{Singh2006}.
+When global strain is 0.015, local elastic strain $F_{xx}$ of the model is measured along the line cross center of the model and shown by Fig.
+\ref{fig:strain}.
+In te figure, $\alpha_2$ phase located in the central part of the axial, and other parts on the axial are $\gamma$ phase.
+It should be noticed that atomic level elastic strain effected by random thermal displacements of atoms, thus fluctuation value exists in Fig.
+\ref{fig:strain}.
+The local strain of $\alpha_2$ phase grain is greater than $\gamma$ phase grain when global strain of model is 0.015.
+From the value of local strain we can conclude that $\gamma$ phase less deformable than $\alpha_2$ phase during elastic stage.
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=0.75\linewidth]{img/strgrad}
+	\caption{Local strain along tensile direction }
+	\label{fig:strain}
+\end{figure}
+
+\begin{table}[ht]
+	\caption{Elastic constants of TiAl and $\rm{Ti_3Al}$}
+	\centering
+	\begin{tabular}{l c c c c c c c c c c}
+		\toprule
+		\textbf{ } &$C_{11}$ &$C_{12}$ &$C_{13}$ &$C_{33}$ &$C_{44}$ &$C_{66}$\\		 
+		\midrule
+		TiAl\cite{Schwarz1995} &186 &72 &74 & 176 &101 &77	 \\
+		\midrule
+		% Time/ps	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.Fu = sin20 & 0.21 & 0.22 & 0.23 \\
+		% \midule
+		$\rm{Ti_3Al}$\cite{Tanaka1996}	& 176 &  87.8 & 61.2 & 218.7 & 91.9 & 62.4   \\
+		\bottomrule
+	\end{tabular} 
+	\label{tab:elastic}
+\end{table}
+%\begin{equation}
+%	\label{eq:strin-grade2}
+%		\mathbf{e} = 1 / 2 \left[ I - \left( \mathbf{F ^ { e }} \right) ^ { - T } \left(\mathbf{ F ^ { e }} \right) ^ { - 1 } \right]
+%\end{equation}
+%\begin{equation}
+%\begin{aligned} d $\mathbf { x } & = \frac { \partial \mathbf { x } } { \partial \mathbf { X } } d \mathbf { X } \\ & = \nabla \chi ( \mathbf { X } , t ) d \mathbf { X } = \mathbf { F } ( \mathbf { X } , t ) d \mathbf { X }$
+%\end{aligned} 
+%\end{equation}
+Snapshots of atoms configuration at the 3 of 10 key points are shown by Fig.
 \ref{fig:Defect}.
@@
 \end{equation}
-According to the  results calculated by first principle, the stacking fault energy of TiAl is much smaller than $\rm{Ti_3Al}$, as a consequence, calculated shear strength of TiAl and $\rm{Ti_3Al}$is 4.1 Gpa and 2.86 Gpa along their easy slip plane respectively\cite{Liu2007}.
+According to the  results calculated by first principle, the stacking fault energy of TiAl is much smaller than $\rm{Ti_3Al}$, as a consequence, calculated shear strength of TiAl and $\rm{Ti_3Al}$is 4.1 GPa and 2.86 GPa along their easy slip plane respectively\cite{Liu2007}.
 This calculation reveals that tensile behavior in single crystal is mainly controlled by the type of the structure.
@@
 
-Main reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is  the strong plastic anisotropy of  $\alpha_2$ phase.
 TEM examinations performed on tensile tested lamellar alloys have revealed that the limited plasticity of  $\alpha_2$ phase is carried by local slip of dislocations with the Burgers vector $1/3[11\overline{2}0]$ prism planes shown by Fig.
@@
 Pyramidal slip of the $\alpha_2$ phase is required  when slip is forced to cross $\alpha_2$ phase, this process needs an extremely high shear stress.
+Two components($\alpha_2$ and $\gamma$ phase) exhibit different properties in two phase alloy comparing they are single phase alloy respectively.
+$\gamma$ phase is the major source of dislocation in two phase alloy, that is in good agreement with experiments\cite{Singh2006a,Appel1998a,Singh2006}.
+When global strain is greater than 0.07, the reason why Ti3Al exhibits less plastic deformation is the absence of twinning in Ti3Al under tensile loading, which have been observed by experiments\cite{sastry1980plastic}.
+The deformation $\rm{Ti_3Al}$ is mainly constrained by loading conditions, as compression loading is applied, Ti3Al activates more moveable dislocation, thus exhibits better elasticity\cite{intro-structure}.
 
@@
 \end{equation}
-where $\sigma_0$ is the strength of model without voids of 5.3 Gpa, and $A_0$ represents initial section area,  $A^*$ is effective section area in consideration of the area detraction by void.
+where $\sigma_0$ is the strength of model without voids of 5.3 GPa, and $A_0$ represents initial section area,  $A^*$ is effective section area in consideration of the area detraction by void.
 In classic theory, the relationship between void size and strength of the model is linear.
@@
 The conclusions are as follows:\\
-(1) Major deformation component of the two phase TiAl alloy is $\gamma$ phase,$\alpha_2$ phase is harder to be deformed, this inhomogeneity results in cracks at interface of the two phase. \\
-(2) Effect of  void on the strength of the two phase alloy is sensitive to the location of  void.
+(1) Deformation behavior of two types of grain inside $\alpha_2+\gamma$ two phase Ti-Al alloy are different due to their crystal structure.
+$\alpha_2$ phase $\rm{Ti_3Al}$ grain is easy to be deformed during elastic stage.\\
+(2) During yield stage, majority of dislocations in two phase TiAl alloy activated inside $\gamma$ phase, $\alpha_2$ phase is harder to slip due to its hcp structure, this inhomogeneity results in cracks at interface of the two phase.
+\\
+(3) Effect of  void on the strength of  two phase alloy is sensitive to the location of void.
 Void inside grain has detraction to the strength of material because the strengthening mechanism similar to second phase particle.
@@
 \reftitle{References}
+
 \bibliography{ref.bib}
+
 \funding{This research was funded by the National Natural Science Foundation of China (No.51665030, No.51865027) and the Program for Changjiang Scholars and Innovative Research Team in Universities of the Ministry of Education of China (No.
 IRT-15R30), the Hongliu First-class  Disciplines Development Program of Lanzhou University of Technology.}
-
+\acknowledgments{ Fig.\ref{fig:verify}(c) is from Chen, J.H.; Cao, R.
+Chapter 9 - Brittle Fracture of TiAl Alloys and NiTi Memory Alloys.
+In Micromechanism of Cleavage Fracture of Metals; Chen, J.H.; Cao, R., Eds.; Butterworth-Heinemann: Boston, 2015; pp.
+365–443.
+Author have get permission from publisher.
+License number:4492240737073 }
 \end{document}

### 2018-12-27 code/strgrad.py

@@ -1,0 +1,69 @@
+# 读取输出文件，绘制应力应变曲线
+'''
+violet
+├── code
+│   ├── data
+│   │   ├── size
+│   │   ├── stress_strain
+│   │   └── surf
+│   └── pict
+└── draft
+    ├── bkp
+    ├── img
+    ├── material
+    └── ref
+'''
+
+import os
+import os.path
+from os import listdir
+import matplotlib.pyplot as plt
+import pandas as pd
+from matplotlib import rc
+import matplotlib.pyplot as plt
+plt.rcParams.update({'font.size': 14})
+plt.rcParams["font.family"] = 'Times New Roman'
+
+rc('text', usetex=True)
+
+# rc('text', usetex=True)
+#csfont = {'fontname':'Times New Roman'}
+#plt.rcParams["font.family"] = "Times New Roman"
+WDIR = os.path.dirname(__file__)
+loadpath = os.path.join(WDIR,'data')
+writepath = os.path.join(WDIR,'..','draft','img')
+# pre-set head name
+
+
+
+prop = ['step', 'strain', 'stress', 'energy']
+# import data from .csv file:
+#ds1 = pd.read_csv(os.path.join(loadpath,'aa.csv'), sep=' ', skiprows=1, names=prop)
+ds1 = pd.read_csv(os.path.join(loadpath,'bin-g'), sep=' ', skiprows=1,names=['position','strgrad'])
+ds2 = pd.read_csv(os.path.join(loadpath,'bin-a'), sep=' ', skiprows=1,names=['position','strgrad'])
+
+# plot lines
+p1 = plt.scatter(ds1.position, ds1.strgrad, color = 'B')
+p2 = plt.scatter(ds2.position, ds2.strgrad, color = 'G')
+
+#p3 = plt.plot((ds.strain-0.015)*1.2, ds3.stress, color = 'R')
+#p2 = plt.plot((ds2.strain-0.015)*1.2, ds2.stress, color = 'G')
+#p4 = plt.plot((ds4.strain-0.015)*1.2, ds4.stress, color = 'B')
+
+# plt.legend('stress gradient', frameon=False)
+
+# config title and label
+
+#plt.title('stress-strain curve')
+plt.xlabel('Position')
+plt.ylabel('Strain gradient')
+#plt.ylim(ymin=0)
[…]

### 2018-12-27 crackdis.py

@@ -1,0 +1,31 @@
+import sys
+import numpy as np
+import matplotlib.pyplot as plt
+v = np.array([3.36, 3.69, 4.33, 5.02, 6.39, 8.03, 10.16, 12.6, 15.36, 18.15, 21.23, 23.91, 25.38, 26.27, 26.13, 25.56, 25.71])
+u = np.linspace(0, len(v)-1, len(v))
+plt.plot(u,v)
+plt.show()
+
+
+plt.rcParams['figure.figsize'] = (5,2.5)
+plt.xlabel('Position')
+plt.ylabel('Temperatrue')
+plt.rcParams.update({'font.size': 9})
+plt.tight_layout()
+
+# line color
+# set1: red,green,blue
+# set2: frebrick,forestgreen,darkgreen
+plt.plot(u,v,color='firebrick',marker='o',markevery=1,mew=0.25)
+# plt.plot(b,v,color='forestgreen',marker='o',markevery=10,mew=0.25)
+# plt.plot(c,w,color='darkblue',marker='s',markevery=10,mew=0.25)
+# create legend without frame
+# plt.legend(['L1','L2','L3'],frameon=False)
+# plt.xlim(0,8)
+# plt.ylim(-3,3)
+# plt.savefig('plt.svg')
+# plt.savefig('plt.pdf',dpi=300)
+plt.savefig('crackdis.pdf')
+
+plt.show()
+sys.exit(0)

### 2019-01-09 3rdEdt/materials-405695.tex
Published

%=================================================================
\documentclass[materials,article,accept,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi}
\usepackage{siunitx}
\usepackage{multirow}
%\preto{\abstractkeywords}{\nolinenumbers}
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{12}
\issuenum{1}
\articlenumber{184}
\pubyear{2019}
\copyrightyear{2019}
%\externaleditor{Academic Editor: name}
\history{Received: 27 November 2018; Accepted: 3 January 2019; Published: 7 January 2019}

% Full title of the paper (Capitalized)

\Title{Micromechanism of  Cold Deformation of Two-Phase Polycrystalline Ti--Al Alloy with Void}
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-8385-4439} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-9582-6301} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
%\Author{Author \href{https://orcid.org/0000-0001-8385-4439}{\orcidicon}}
\Author{{Ruicheng Feng} $^{1,2}$\orcidA{}, Maomao Wang $^{1,*}$\orcidB{}, Haiyan Li $^{1,*}$,  Yongnian Qi $^{1}$, Qi Wang $^{1}$ and Zhiyuan~Rui~$^{1,2}$} % Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading.

% Authors, for metadata in PDF
%\AuthorNames{ }
% frcly@163.com(R.F.);15620864891@163.com(M.W.); y5217@163.com(H.L.);13893591491@163.com(Y.Q.);18350122524@163.com(Q.W);zhiy_rui@163.com(Z.R)
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
%$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com (R.F.); 15620864891@163.com (M.W.)\\
$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com (R.F.); 13893591491@163.com (Y.Q.); 18350122524@163.com (Q.W.); zhiy\_rui@163.com~(Z.R.)\\
% $^{2}$ \quad Key Laboratory of Digital Manufacturing Technology and Application, Ministry of Education, Lanzhou University of Technology, Lanzhou 730050, China
%*; e-mail@e-mail.com}
$^{2}$ \quad State Key Laboratory of Advanced Processing and Recycling of Non-ferrous Metals, \mbox{Lanzhou University of Technology}, Lanzhou 730050, China}
% Contact information of the corresponding author
\corres{Correspondence: 15620864891@163.com (M.W.); y5217@163.com (H.L.)}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3}
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{Cold deformation behavior of polycrystalline metallic material is affected by intrinsic defects such as dislocations, voids, inclusions etc.  Existing studies on $\alpha_2(\rm{Ti_3Al})$ + $\gamma(\rm{TiAl})$  two-phase Ti--Al alloy cover about deformation behavior mainly on macro scale. This paper focuses on the cold deformation mechanism of two-phase Ti--Al alloy at micro scale, and  the role of voids  in deformation process. Molecular dynamics simulations were performed to study the evolution of micro structure of material under uniaxial tension. Interaction between spherical nano voids with different size and position was also examined in the simulation. The results show that (1) In elastic stage, deformation of the two-phase is coordinated, but $\rm{Ti_3Al}$ is more deformable; (2) In plastic stage, $\gamma$ phase is the major dislocation  source in two-phase alloy; (3) voids detracts the strength of the two-phase alloy, while the position of void affect the degree of this subtraction, voids located at the boundary of $\alpha_2$/$\gamma$ phase have significant detraction to strength.}
% Keywords
\keyword{two-phase Ti--Al alloy; void; molecular dynamics; cold deformation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\section{Introduction}
% and brittle rapture failure
Titanium--aluminum-based intermetallic alloys are promising high temperature structural materials because of their great corrosion resistance and strength at high temperature. Compared with nickel-based alloy,  Ti--Al-based alloys have lower density, it can be used in combustion engine, turbine, and other components working at high temperatures from 500 \si{\degreeCelsius} to 900 \si{\degreeCelsius} \cite{Clemens2016}. The performance of inner combustion engine with components made of Ti-6Al-4V was improved  20\% because the weight of components decreased from 30\% to 40\% \cite{Bewlay2016}. With the advancement of non-ferrous metallurgy, Ti--Al-based alloy components have better economic efficiency than ever before. Ti--Al-based alloys have good prospects for applications in aerospace and automobile industry.
Poor ductility of Ti--Al alloy  at room temperature strongly affects the safety of structures like turbo of aircraft engine and combustion generator \cite{Munz2017}.

Deformation phenomena of Ti--Al alloys have been widely studied in order to overcome the problems associated with the poor ductility and damage tolerance.  Much of the work has been performed on single-phase $\gamma$-TiAl, $\rm{Ti_3Al}$ alloys, and polysynthetically twinned crystals (PTC) \cite{Appel2016}. Experiments reveals that  the dominant deformation mode in $\rm{Ti_3Al}$ at low temperature is slip activity without any twinning, and the fracture type is cleavage \cite{sastry1980plastic}. Around  the1990s, experimental studies on the two-phase lamellae Ti--Al alloys showed that  mechanical twin and glide of  dislocation are major sources of deformation \cite{Farenc1993,Appel2005,Appel1998a}. Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale, defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}. Mess research  covers a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two-phase Titanium--aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}. In situ experiments have shown that Ti--Al and $\rm{Ti_3Al}$ in two-phase alloy exhibit different properties comparing in single-phase alloys \cite{Singh2006}. voids can be arose due to specific volume differences induced by precipitation, different thermal expansion or shrinkage upon heating or cooling the specimen. It has been known that nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which voids growth is particularly important \cite{Hempel2017a}. The initiation of crack at microscopic scale is a dynamic process, which results in difficulties on study of  mechanism about deformation and cracking, these defects are known playing a fundamental role in the deformation of materials. Multiscale method has been applied to study deformation behavior of polycrystal with single aluminum \cite{Groh2009} and titanium element respectively \cite{Liu2018}. It is necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale.

The effect of voids is another great concern of properties and deformation mechanism  of Ti--Al alloys.  Therefore, it is necessary to study the deformation response of intermetallics structural materials with the consideration of microstructure evolution. Previous study on voids growth in single crystal $\gamma$-TiAl reveals that voids with high volume fraction detracts yield strength \cite{Tang2014, Xu2011}. Evolution of voids in ductile polycrystalline was studied in nanoscale with molecular dynamics(MD) simulations, \cite{Jing2018a,Elkhateeb2018}, voids inside material are sources of dislocation and affects the properties of materials differently because of differences in size and position.  The deformation and fracture mechanisms in the duplex microstructure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang2014}. It reveals that existence of voids alone may contribute to strain hardening because they are barriers to dislocation movement in ductile fcc structure metal \cite{Xiong2015}. However, few studies deal with the deformation mechanism of two-phase Ti--Al alloys and the role of voids in atomic scale. Defects are inevitable as micro-pores and loosen from casting, and in the actual work environment with radiation. A lot of work carried out on the  effect of various defects on the behavior of different materials, showing that point defects may affect the properties of materials greatly. The mechanical performance of irradiated copper is affected by the interaction between irradiation and dislocation \cite{Kiener2011b}. Vacancy concentration in single crystal and polycrystal Fe–40 at. Al bulk results in an increase of strength~\cite{Yang1998}. Ti--Al alloy is a type of typical brittle material, thus, it can be assumed that its properties are sensitive to the existence of void. Surface defects such as small notches can cause low and high cycle fatigue strength of the Ti–47Al–2W–0.5Si alloy \cite{Nazmy2001}, and the strength of single crystal $\gamma$-TiAl is also lowered by point defect \cite{Wu2016}. The resistance of Ti–6Al–4V alloy, which was processed for typical fan blade applications, to high-cycle fatigue in the presence of foreign- object damage was reduced due to earlier crack initiation.  The nucleation and subsequent near-threshold growth of crack was primarily affected by the stress concentration associated with the foreign-object damage and the presence of small cracks in the damaged zone. Due to difficulties in observing the dynamic process during deformation wit experiments, MD simulation has become an effective method to investigate micro deformation mechanism. Defects such as grain boundary, voids and segregation play significant roles in the process of fracture \cite{Larsen2016}. This paper focus on the evolution of microstructure, tending to find out its connection to cold deformation behavior of two-phase Ti--Al alloys. MD simulation including model creation and analysis method is given in Section \ref{section:method}, Results and discussion are in Section \ref{section:RD}.

\section{Molecular Dynamics Simulation \label{section:method}}
\unskip
\subsection{Atomic Potential}

The interaction of particles in the material is determined by interatomic potential. Many reported simulation cases of deforming and crack propagation in metal materials were performed with embedded atomic method due to its better accuracy in metal lattice compare with F-S and L/J~\cite{Ko2015,Zepeda-Ruiz2017,Fan2018a}. Embedded atom method (EAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study. The simulation is performed  with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}. We did constant-pressure and constant-temperature (NPT) MD simulation at room temperature (298K). Definition of the potential is as following:

\begin{equation} \label{eq:eam}
E_{total}= \displaystyle\sum F_i(\rho_{h,i})+\frac{1}{2}\sum_i\sum_{j(\neq1)}\phi_{ij}(R_{ij})
\end{equation}
where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system, $F_i(\rho)$ represents the energy for embedding atom $i$ into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ gives the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$. It can be noted that $F_i$ only depends on the element of atom $i$ and $\phi_{ij}$ only depends on the elements of atoms $i$ and $j$.

\subsection{Modeling}

Two phase Ti--Al alloy is composed of $\gamma $-TiAl and $\alpha_2$-$\rm Ti_3Al$, TiAl has a fcc type cell with an $L1_0$ structure, and $\rm Ti_3Al$ has a hcp structure, these two types of initial cells are shown in Figure \ref{fig:tial-cell}. Geometry parameters of the two type of unit cell are given by Table \ref{tab:lattice_parameter}. Periodic boundary conditions (PBC) were applied along three directions, which makes polycrystal with periodic nanovoids structures. The initial size of simulation box is $L_x =200$ \si{\angstrom}, $L_y = $180 \si{\angstrom}, $L_z = 210$ \si{\angstrom}, and each model  about 460,000 atoms. The model includes 6 grains, with random shape and orientation created by Voronoi method. Total simulation time is restricted to computer power, thus, strain rate in molecular dynamic simulation is much greater than physical experiments. Attempts have been done to find decent time step and strain rate for tensile test with MD simulation. If the strain rate is too high and time step is too large in the simulation, the model cannot predict the real behavior of dislocations.  Previous work \cite{Zhu2008,Wu2016}  reveals that a strain rate from  $10^8\ \rm{s}^{-1}$ to $10^9\ \rm{s}^{-1}$ is appropriate for a system composed of metal atoms like Ti--Al metallic materials. thus, the strain rate of uniaxial loading was set as $5\times10^8\ \rm{s}^{-1}$.

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{img/modeling}
\caption{Unit cell of \rm{TiAl} (\textbf{a}), $\rm{Ti_3Al}$ (\textbf{b}) and two-phase Ti--Al model (\textbf{c}).}
\label{fig:tial-cell}
\end{figure}
\unskip
\begin{table}[H]
\caption{Parameters of nanocrystalline.}
\centering
\begin{tabular}{cccc}
\toprule
\textbf{Phase}			& \textbf{Space Group}		& \textbf{Designation} 		& \textbf{Parameters} \\
\midrule
$\alpha_2$ - $\rm{Ti_3Al}$		& $\rm P6_3/mmc$ 	& $\rm 0_{19}$ 		& $a$ = 0.5765 \\
&					&					& $c$ = 0.46833 \\\midrule
$\gamma$ - $\rm{TiAl}$ 		& $\rm tP4$ 		& $\rm L1_0$		& $a$ = 0.3997 \\
&					&					& $c$ = 0.4062 \\
\bottomrule
\end{tabular}
\label{tab:lattice_parameter}
\end{table}

% In order to study the deformation mechanism of the two-phase alloy and the effect of void, three types of models were created: Type-1.model without any void; Type-2. models with different size voids inside $\alpha_2$ phase; Type-3. models with void at $\alpha_2-\gamma$ interface. \ref{tab:lattice_parameter}. The simulation cells of two-phase polycrystalline with an initially spherical void at different position are shown in figure .
\subsection{Analysis Method}
In order to identify typical defects in the deformed model, a hybrid analysis method was used with free code ovito \cite{Stukowski2010}. Dislocation is visualized by DXA method, and centro-symmetry parameter (CSP) is used to differ grain boundaries, $\alpha_2$ phase grains and $\gamma$ phase grains. The definition of CSP is as~following:
\begin{equation} \label{eq:csp}
P = \displaystyle\sum_{i=1}^{6}|\vec{R_i}+{\vec{R}}_{i+6}|^2
\end{equation}
where $\vec{R_i}$ and ${\vec{R}}_{i+6}$ are the vectors corresponding to the six pairs of opposite nearest neighbors in the fcc lattice. The centro-symmetry parameter (CSP) is zero for atoms in a perfect lattice. In other words, if the lattice is distorted, the value of P will not be zero. Instead, the parameter will have a value within the range corresponding to a particular defect. By removing all the perfect and surface atoms within the bulk, atoms around defected zones are visualized.

\subsection{Model Verification}
The results of the molecular dynamics simulation greatly rely on accuracy of potential and controlling parameters such as strain rate, temperature and relaxation time. Thus, we performed model verification on a simplified model and then compared the results with experiments and simulation done by others.  Uniaxial tensile loading  was applied to single crystal $\gamma$-TiAl bulk shown by Figure~\ref{fig:verify}a, potential and relaxation parameters are the same as those which applied to the polycrystalline model. When temperature is 300 K, the sample was tensioned along [0 0 1] direction at a constant stain rate of $5\times10^8\ \rm{s}^{-1}$. The yield strength of the single crystal Ti--Al alloy is 9.5 GPa  and that is in good agreement with  work by Tang~\cite{Tang2010} in consideration of size effect, and the snapshoot of the fracture surface is shown by Figure~\ref{fig:verify}, and compared with experiment results by Cao \cite{CHEN2015365} shown in Figure \ref{fig:verify}c. It should be noticed that the image from SEM is in a greater scale than our simulation cell. However, the cracked surface in atomic model exhibits two major characteristics of TiAl alloy. First, the fracture type of TiAl at room temperate is typical brittle failure. Second, the fracture surface  of atomic model in Figure \ref{fig:verify}b is typical cleavage surface. This verification case has proven that the EAM potential is of high efficiency and accurate enough, and the simulation work flow is valid to predict failure behavior of  the system composed of Ti--Al.

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{img/cold-fracture2}
\caption{(\textbf{a}) Verifying model: TiAl single crystal bulk; (\textbf{b}) Cracked surface of atomic model; (\textbf{c}) Cracked surface from experiment \cite{CHEN2015365}.}
\label{fig:verify}
\end{figure}

\section{Results and Discussion}\label{section:RD}

%	/home/alex/Documents/violet/draft/img/perfect-line.pdf
Deformation process of the model without void is shown in Figure \ref{fig:deformation-pf}, the strain of model at 10 key points are given by Table \ref{tab:key-point}. The strength of the model without void is 5.3 GPa. According to stress response under constant rate of strain rate, the whole tensile process can be divided into four stages:
stage-\uppercase\expandafter{\romannumeral1}: elastic stage, from $\epsilon = 0$ to $\epsilon = 0.092$, including key point 1,
stage-\uppercase\expandafter{\romannumeral2}: yield stage, ranging from $\epsilon = 0.092$ to $\epsilon = 0.101$, including key points 2 to 6,
stage-\uppercase\expandafter{\romannumeral3}: cracking stage, ranging from $\epsilon = 0.101$ to $\epsilon = 0.112$, including key point 7 to 10,
stage-\uppercase\expandafter{\romannumeral4}: fracture stage. Following discussion concentrates on deformation phenomena that rely on the elastro-plastic code formation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurred in two-phase alloys.

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{img/tens}
\caption{Deformation process of the model without void}
\label{fig:deformation-pf}
\end{figure}
\unskip
\begin{table}[H]
\caption{{Key points during tensile process}.} % This table has not been referred to within the text of the manuscript.
\centering
\begin{tabular}{lcccccccccc}
\toprule
\textbf{Number} &\textbf{1} &\textbf{2} &\textbf{3} &\textbf{4} &\textbf{5} &\textbf{6} &\textbf{7} &\textbf{8} &\textbf{9} &\textbf{10}\\
\midrule
\textbf{Stage} &\uppercase\expandafter{\romannumeral1} &\uppercase\expandafter{\romannumeral1} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral2} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3} &\uppercase\expandafter{\romannumeral3}	 \\
\midrule
% Time/ps	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.Fu = sin20 & 0.21 & 0.22 & 0.23 \\
% \midule
\textbf{Strain}	& 0.05 &  0.088 & 0.092 & 0.096 & 0.099 & 0.101 & 0.104 & 0.107 & 0.110 & 0.112  \\
\bottomrule
\end{tabular}
\label{tab:key-point}
\end{table}

\subsection{Deformation Mechanism of Two Phase Ti--Al Alloy }

% Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
% \subsection{Plastic }
During the elastic stage, the deformation of $\alpha_2$ phase and $\gamma$ phase grains is compatible, however the properties of two phases are different. The elastic constants given by  experiments \cite{Schwarz1995,Tanaka1996} are listed in  Table \ref{tab:elastic}. $C_{11}^{\alpha_2}$ is 176, which is smaller than $C_{11}^{\gamma}$, other five parameters but $C_{33}$ of $\rm{Ti_3Al}$ are also smaller than Ti--Al. In order to quantify the difference of the two-phase deformation gradient was calculated by~formulation:
\begin{equation}
\label{eq:strain-grade}
\mathbf { F^e } = \frac { \partial \mathbf { x } } { \partial \mathbf { X } } = \operatorname { Grad } \mathbf { x } , \quad F _ { i J } = \frac { \partial x _ { i } } { \partial X _ { J } }
\end{equation}
we computes the atomic level elastic strain and deformation gradient tensors in crystalline systems with the numerical method proposed by \cite{Singh2006}. When global strain is 0.015, local elastic strain $F_{xx}$ of the model is measured along the line cross center of the model and shown by Figure \ref{fig:strain}. In te figure, $\alpha_2$ phase located in the central part of the axial, and other parts on the axial are $\gamma$ phase.  It should be noticed that atomic level elastic strain effected by random thermal displacements of atoms, thus, fluctuation value exists in Figure \ref{fig:strain}. The local strain of $\alpha_2$ phase grain is greater than $\gamma$ phase grain when global strain of the model is 0.015. From the value of local strain, we can conclude that $\gamma$ phase less deformable than $\alpha_2$ phase during elastic stage.

Snapshots of atoms configuration at the three of ten key points are shown by Figure \ref{fig:Defect}.  Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Figure \ref{fig:Defect}a,b,\ $\alpha_2$ phase and defects inside grains have been left. Similarly, $\gamma$ phase grain have been removed in Figure \ref{fig:Defect}c,d, the defects of $\alpha_2$ phase have been left.  The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of material is under typical elastic deformation, the size of simulation box enlarged due to the loading. In this stage, deformation of the two-phase are compatible. Emission of dislocation and evolution of defects initiated at the end of the stage \uppercase\expandafter{\romannumeral1}. A  great number of dislocation emitted inside $\gamma$ phase at earlier part of stage \uppercase\expandafter{\romannumeral2}, however, the dislocation inside $\alpha_2$ phase was emitted at the end of stage \uppercase\expandafter{\romannumeral2} is shown by Figure \ref{fig:Defect}c.

\begin{table}[H]
\caption{Elastic constants of TiAl and $\rm{Ti_3Al}$.}
\centering
\begin{tabular}{l c c c c c c c c c c}
\toprule
\textbf{ } &\boldmath$C_{11}$ &\boldmath$C_{12}$ &\boldmath$C_{13}$ &\boldmath$C_{33}$ &\boldmath$C_{44}$ &\boldmath$C_{66}$\\
\midrule
TiAl \cite{Schwarz1995} &186 &72 &74 & 176 &101 &77	 \\
\midrule
% Time/ps	& 0 & 0.15 & 0.16 & 0.17 & 0.18 & 0.19 & 0.Fu = sin20 & 0.21 & 0.22 & 0.23 \\
% \midule
$\rm{Ti_3Al}$ \cite{Tanaka1996}	& 176 &  87.8 & 61.2 & 218.7 & 91.9 & 62.4   \\
\bottomrule
\end{tabular}
\label{tab:elastic}
\end{table}
\unskip
\begin{figure}[H]
\centering
\includegraphics[width=0.75\linewidth]{img/strgrad}
\caption{Local strain along tensile direction.}
\label{fig:strain}
\end{figure}
\unskip

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{img/def-box}
\caption{Microstructure evolution inside $\gamma$ phase (\textbf{a},\textbf{b}), $\alpha_2$ phase (\textbf{c},\textbf{d}) during yield stage.}
\label{fig:Defect}
\end{figure}
Experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature \cite{Stein1960}. The brittleness of two-phase Ti--Al alloy attributed to the poor mobility of dislocation at room temperature. Velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it~can be written as:
\begin{equation}\label{eq:temp-dis}
v = v_0\ e^{-\Delta H(\tau^*)/kT}
\end{equation}
where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ represents the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions. The effect of temperature on the mobility can be evaluated under different loading conditions, thus, we chose  $\tau_1^*>\tau_2^*>\tau_3^*$ in Formulation (\ref{eq:temp-dis}), normalized velocity of dislocation motion is shown by Figure  \ref{fig:temp}. The  velocity  of dislocation movement rise along with increase of  stress, the~mobility  of dislocation is relatively poor at 298 K. Due to motion of dislocations is inactive inside $\alpha_2$ phase,  typical strengthening mechanism closely related to the interaction between grain boundary and dislocation can not be dramatic at room temperature, piling up of dislocations is not observed in this simulation, which is shown in Figure \ref{fig:Defect}.
\begin{figure}[H]
\centering
\includegraphics[width=0.5\linewidth]{img/temp}
\caption{Normalized velocity of dislocation motion under different loading conditions.}
\label{fig:temp}
\end{figure}

Length of different types of dislocations are given at four stages in Figure \ref{fig:disum}. Dislocations are recognized and identified using the dislocation analysis (DXA) of ovito. The length of Shockley dislocation with Burgers vector $1/6[1 1 2]$ increased sharply during yield stage of the deformation process in Figure \ref{fig:disum}, but the length of perfect dislocation fluctuated at a low level. Perfect  dislocations split into Shockley partial dislocations, this decomposition process  can be given by Formulations (\ref{eq:dis-1}) and (\ref{eq:dis-2}). The structure spontaneously transformed into intrinsic stacking fault (ISF), which can be observed in Figure \ref{fig:Defect}a.

%\begin{equation}\label{eq:dis-1}
%[\ 0\ 1\ \overline{1}\ ] \to 1/2 [\ 1\ 1\ \overline{2}\ ]+1/2[\ \overline{1}\ 1\ 0\ ]\\
%\end{equation}

\begin{equation}\label{eq:dis-1}
1/2 [\ 0\ 1\ 1\ ] \to 1/6[\ 1\ 1\ 2\ ]+1/6[\ \overline{1}\ 2\ 1\ ]
\end{equation}
\begin{equation}\label{eq:dis-2}
1/2 [\ 1\ 0\ \overline{1}\ ] \to 1/6 [\ 1\ 1\ \overline{2}\ ] + 1/6[\ 2\ \overline{1}\ \overline{1}\ ]
\end{equation}
Interaction between dislocations with Burgers vector of $1/6 [112] $ and $ 1/6 [11\overline{2}]$ follows the decomposition of perfect dislocation. The process produced leading dislocation and trailing dislocation, when the two leading Shockley partials combined, they form Lomer–Cottrell junction, a separate dislocation. It's sessile in the slip plane, playing a role of barrier against other dislocations in the plane. This process is given by :
\begin{equation}\label{eq:dis-3}
1/6 [\ 1\ 1\ 2\ ] + 1/6 [\ 1\ 1\  \overline{2}\ ] \to 1/3 [\ 1\ 1\ 0\ ]
\end{equation}
According to the  results calculated by first principle, the stacking fault energy of Ti--Al is much smaller than $\rm{Ti_3Al}$, as a consequence, calculated shear strength of Ti--Al and $\rm{Ti_3Al}$is 4.1 GPa and 2.86 GPa along their easy slip plane respectively \cite{Liu2007}. This calculation reveals that tensile behavior in single crystal is mainly controlled by the type of the structure. However, in two-phase Ti--Al alloy, deformation of $\alpha_2$ phase is earlier than $\gamma$ phase during yield stage, thus, local displacement of two phases are incompatible during yield stage.  Mobility of dislocation is affected by structure of crystal, loading condition and temperature, and $\alpha_2$ phase is made up of hcp  structured grain, grains with this type of structure possess less slip system compared with grain with fcc structure \cite{Zhu2012}, thus, $\alpha_2$ phase is difficult do deform under uniaxial tensile loading.

\begin{figure}[H]
\centering
\includegraphics[width=0.5\linewidth]{img/dis-summary}
\caption{Summary of didderent types of dislocation under different strain.}
\label{fig:disum}
\end{figure}

TEM examinations performed on tensile-tested lamellar alloys have revealed that the limited plasticity of  $\alpha_2$ phase is carried by local slip of dislocations with the Burgers vector $1/3[11\overline{2}0]$ prism planes shown by Figure \ref{fig:Defect}b, which is by far the easiest slip system in $\alpha_2$ single crystals.  Dislocation neighboring interfaces often needs to be transformed. For example, an ordinary 1/2 [110] dislocation gliding in one $\gamma$ grain has to be converted into $[101]$ super dislocation when the double Burgers vectors gliding in an adjacent $\gamma$ grain. At the $\alpha_2/\gamma$ interface, dislocations existing in  $D0_{19}$ structure  transform into dislocations, which is consistent with the $\rm{L1_0}$ structure. These core transformations are associated with the change of the dislocation line energy because of the differences of the length and the shear module.  Pyramidal slip of the $\alpha_2$ phase is required  when slip is forced to cross $\alpha_2$ phase, this process needs an extremely high shear stress. Two components ($\alpha_2$ and $\gamma$ phase) exhibit different properties in two-phase alloy comparing they are single-phase alloy respectively. $\gamma$ phase is the major source of dislocation in two-phase alloy, that is in good agreement with experiments \cite{Appel1998a,Singh2006}. When global strain is greater than 0.07, the reason why Ti3Al exhibits less plastic deformation is the absence of twinning in Ti3Al under tensile loading, which have been observed by experiments \cite{sastry1980plastic}. The deformation $\rm{Ti_3Al}$ is mainly constrained by loading conditions, as compression loading is applied, Ti3Al activates more moveable dislocation, thus, exhibits better elasticity \cite{intro-structure}.

\subsection{The Effect of Void on the Strength of Material}

In Figure \ref{fig:model-creation}, voids with different size of 2 \AA, 5 \AA, 10 \AA\ and 15 \AA\ were placed  at $\alpha_2$/$\gamma$ phase boundary, inside $\gamma$ phase respectively. The strength of materials with void in different size and at different position is shown in Figure \ref{fig:stress&strain}. The existence of void have little impact on the elastic properties of the material, and the model without void has the largest strength 5.3 GPa, the yield stress of model with void is smaller. Void at $\alpha_2$/$\gamma$ phase boundary  detracts the strength of  material most, and the void inside $\alpha_2$ phase  have less impact on the strength.
Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated~by
\begin{equation} \label{eq:section}
\sigma^* = \sigma_0 \cdot({A^*}/{A_0})
\end{equation}
where $\sigma_0$ is the strength of model without voids of 5.3 GPa, and $A_0$ represents initial section area,  $A^*$ is effective section area in consideration of the area detraction by void.  In classic theory, the~relationship between void size and strength of the model is linear. However, simulation results reveals that two-phase Ti--Al alloy is sensitive to defect of void.  Comparing the strength determined from molecular dynamics simulation and the results calculated with Formulation (\ref{eq:section}), it can be seen that the main factor that affects the strength of materials is local behavior of the materials, thus, evolution of defects have dramatic influence on the yield and fracture process of the materials.

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{img/slice-view}
\caption{Model of the simulation (\textbf{a}) and sliced view of the model with no void (\textbf{b}), inside $\alpha_2$ phase (\textbf{c}) at $\alpha_2 / \gamma$ phase boundary (\textbf{d}).}
\label{fig:model-creation}
\end{figure}
\unskip
\begin{figure}[H]
\centering
\includegraphics[width=0.5\linewidth]{img/allline}
\caption{Stress-strain response of the materials under tensile loading.}
\label{fig:stress&strain}
\end{figure}

%%%
%\begin{figure}[ht]
%%	\includegraphics[width=1\linewidth]{"img/fracture3"}
%	\caption{Yield process of the models}
%	\label{fig:yield}
%\end{figure}

It has been observed in Figure \ref{fig:strength} that voids detract the strength of  materials. The max stress  of the simulation cell decreases as the volume of voids increases. It can be seen from Figure \ref{fig:stress&strain} that there is a critical value of void radius about 15 \AA, the void greater than 15 \AA\ causes serious detraction of strength of material.  The decreased rate of loading area is smaller compared  with the detraction of strength, so it can be assumed that the  yield behavior and strength is more related with local behavior of grain boundaries and void. Grain and phase boundaries are obstacles to deformation process, thus, the stability of boundaries has a great impact on the strength of materials. Interaction between grain boundary and void determines the fracture mode of   Ti--Al alloy.

\begin{figure}[H]
\centering
\includegraphics[width=0.5\linewidth]{img/effect_of_vol}
\caption{Yield strength of the materials with different size void.}
\label{fig:strength}
\end{figure}

\subsection{Evolution of Spherical Void}
The role of void can be concluded as two main parts: source of dislocations and obstacles to dislocations, which is dominant depends on the location of void. Void inside $\alpha_2$ phase plays a role of inclusion, in other words, this type of void possess similar properties as second phase particles.

\textls[-5]{Void inside $\alpha_2$ phase induced considerable misfit-stress fields and thus, can influence material properties. Such stress fields surrounding the second-phase particles can be due to misfit between $\alpha_2$ phase atoms and surface atoms surrounding the void. That is a possible favorable effect of second-phase particles that void contribute to the enhancement of mechanical strength. The strengthening effect of the particle inside single-phase Ti--Al alloy has been verified by experiment \cite{Zghal1998}. Considering yielding of a material as related to glide of dislocations, any mechanism obstructing dislocation glide improves the mechanical strength. The defect evolution neighboring the void during yield stage is shown in Figure  \ref{fig:orowan}a; the role of void is similar to second-phase particles. It servers as obstacles for dislocation migration which is shown by Figure \ref{fig:orowan}b: the stress fields surrounding the second-phase particles block migrating dislocation, the void particle acts as pinning point. The dislocation can pass two pinning points under shear  stress , and the critic value depends on the distance between  obstacles, it is be given~by~\cite{Xiong2015}:}
\begin{equation} \label{eq:orowan}
\tau_0 = Gb/d
\end{equation}
where $d$ represents the distance between two obstacles A and B in Figure \ref{fig:orowan} , reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution. This mechanism for hardening is designated as the Orowan process with $\tau_0$ as the Orowan shear stress. As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles. Consequently, the effective average distance between the second phase particles has decreased to $d$ which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide. The width of a Burgers vector, will be generated at both sides of a crystal along the direction of  burgers vector after dislocation traversing the entire crystal, as is shown in the third subfigure of Figure \ref{fig:orowan}b.

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{"img/orowan"}
\caption{(\textbf{a}) {Orowan process} occurred inside $\alpha_2$ phase grain (removed atoms with regular arrangement).(\textbf{b}) Schematic of Orowan process.} % There is no explanation for (a) and (b) in the figure.
\label{fig:orowan}
\end{figure}

Effect of voids at different positions on the crack mode of the material are shown by Figure \ref{fig:void-gb}a. The model with void fractured cross the grain, and the model with void at $\alpha_2 / \gamma$ boundary resulted a large crack along the boundary under tensile loading. The difference of crack mode can attribute to the position of void and the evolution of the defect. Nucleation and emission of Shockley partial dislocation affect the evolution of the void at boundary greatly due to the anisotropy of two phases on the both sides of the phase boundary. The void weakens the strength of the grain it locates,  $\alpha_2$ phase grain is easy to deformed under shear stress, thus, that caused the crack initiated inside grain and finally caused fracture across the grain. Deformation mechanisms of the model with void at boundary can be  more complex due to the interaction between void and phase boundary. In the elastic stage, the~system composed of $\alpha_2$ phase, $\gamma$ phase and void is in equilibrium, internal stress are balanced under compatible deformation as is shown by the first subfigure of Figure \ref{fig:void-gb}b. In the middle moment of yield stage, partial dislocation with Burgers vector $1/6[\overline{2}\ \overline{1}\ 1]$ emitted from surface of void in Figure~\ref{fig:void-gb}b-2. The micro crack initialed from the zone neighbor  the interface between void and boundary, that quickly caused abrupt decohension of phase boundary. That accounts for the reason that material with void at $\alpha_2 / \gamma$ phase boundary is weaker than other cases.

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{"img/void-gb"}
\caption{(\textbf{a}) Fracture mode of two types of mode;  (\textbf{b}) Evolution of void at $\alpha_2 / \gamma$ phase boundary.}
\label{fig:void-gb}
\end{figure}

\section{Conclusions}

In this paper, deformation behavior of two-phase Ti--Al alloy under tensile loading was simulated with MD method. The mechanism of deformation was investigated under atomic scale, and the effect of void on the properties of two-phase Ti--Al alloy was also studied.  The conclusions are as follows:

(1) Deformation behavior of two types of grain inside $\alpha_2+\gamma$ two-phase Ti--Al alloy are different due to their crystal structure. $\alpha_2$ phase $\rm{Ti_3Al}$ grain is easy to be deformed during elastic stage.

(2) During the yield stage, the majority of dislocations in two-phase Ti--Al alloy activated inside $\gamma$ phase, $\alpha_2$ phase is harder to slip due to its hcp structure, this inhomogeneity results in cracks at interface of the two phases.

(3) Effect of  void on the strength of the two-phase alloy is sensitive to the location of void. Void inside grain has detraction to the strength of material because the strengthening mechanism is similar to second-phase particles. Void at $\alpha_2 / \gamma$ boundary is the most risky situation for the two-phase alloy because of fast fractures along boundary.

\vspace{6pt}
\authorcontributions{Conceptualization, M.W.; Funding acquisition, R.F.; Investigation, M.W.; Methodology, M.W.; Project administration, Z.R.; Resources, H.L.; Software, Y.Q.; Supervision, R.F.; Visualization, Q.W.} % please add author contributions.

\funding{This research was funded by the National Natural Science Foundation of China (No. 51665030, No. 51865027) and the Program for Changjiang Scholars and Innovative Research Team in Universities of the Ministry of Education of China (No. IRT-15R30), the Hongliu First-class  Disciplines Development Program of Lanzhou University of Technology.}

\acknowledgments{The work was carried out at LvLiang Cloud Computing Center of China, and the calculations were performed on TianHe-2. Figure \ref{fig:verify}c is from Chen, J.H.; Cao, R. Chapter 9---Brittle Fracture of TiAl Alloys and NiTi Memory Alloys. In Micromechanism of Cleavage Fracture of Metals; Chen, J.H.; Cao, R., Eds.; Butterworth-Heinemann: Boston, 2015; pp. 365--443. Author have get permission from publisher. License number: 4492240737073.}

\conflictsofinterest{The authors declare no conflict of interest.} % please add conflicts of interest.

\reftitle{References}
\begin{thebibliography}{999}

\bibitem[Clemens and Mayer(2016)]{Clemens2016}
Clemens, H.; Mayer, S.
\newblock {Advanced Intermetallic TiAl Alloys}.
\newblock {\em Mater. Sci. Forum} {\bf 2016}, {\em 879},~113--118. [\href{http://dx.doi.org/10.4028/www.scientific.net/MSF.879.113}{CrossRef}]

\bibitem[Bewlay \em{et~al.}(2016)Bewlay, Nag, Suzuki, and Weimer]{Bewlay2016}
Bewlay, B.P.; Nag, S.; Suzuki, A.; Weimer, M.J.
\newblock {TiAl alloys in commercial aircraft engines}.
\newblock {\em Mater. High Temp.} {\bf 2016}, {\em 33},~549--559. [\href{http://dx.doi.org/10.1080/09603409.2016.1183068}{CrossRef}]

\bibitem[Mart{\'{i}}nkov{\'{a}} \em{et~al.}(2004)Mart{\'{i}}nkov{\'{a}},
Nov{\'{a}}, Sablina, Graphodatsky, and Zima]{Munz2017}
Mart{\'{i}}nkov{\'{a}}, N.; Nov{\'{a}}, P.; Sablina, O.V.; Graphodatsky, A.S.;
Zima, J.
\newblock {Karyotypic relationships of the Tatra vole (Microtus tatricus)}.
\newblock {\em Folia Zool.} {\bf 2004}, {\em 53},~279--284. [\href{http://dx.doi.org/10.1007/s13398-014-0173-7.2}{CrossRef}]

\bibitem[Appel \em{et~al.}(2016)Appel, Clemens, and Fischer]{Appel2016}
Appel, F.; Clemens, H.; Fischer, F.D.
\newblock {Modeling concepts for intermetallic titanium aluminides}.
\newblock {\em \mbox{Prog. Mater. Sci.}} {\bf 2016}, {\em 81},~55--124. [\href{http://dx.doi.org/10.1016/j.pmatsci.2016.01.001}{CrossRef}]

\bibitem[Sastry and Lipsitt(1980)]{sastry1980plastic}
Sastry, S.M.L.; Lipsitt, H.A.
\newblock {Plastic deformation of TiAl and Ti3Al}.
\newblock  In Proceedings of the 4th International Conference on Titanium,  {Kyoto, Japan,  19--22  May} 1980;
pp. 1231--1243. % Newly added information, please confirm.

\bibitem[Farenc \em{et~al.}(1993)Farenc, Coujou, and Couret]{Farenc1993}
Farenc, S.; Coujou, A.; Couret, A.
\newblock {An in situ study of twin propagation in TiAl}.
\newblock {\em Philos. Mag. A  Phys. Condens. Matter
Struct. Defects  Mech. Prop.} {\bf 1993}, {\em 67},~127--142. [\href{http://dx.doi.org/10.1080/01418619308207147}{CrossRef}]

\bibitem[Appel(2005)]{Appel2005}
Appel, F.
\newblock {An electron microscope study of mechanical twinning and fracture in
TiAl alloys}.
\newblock {\em Philos. Mag.} {\bf 2005}, {\em 85},~205--231. [\href{http://dx.doi.org/10.1080/14786430412331315662}{CrossRef}]

\bibitem[Appel and Wagner(1998)]{Appel1998a}
Appel, F.; Wagner, R.
\newblock {Microstructure and deformation of two-phase $\gamma$-titanium
aluminides}.
\newblock {\em Mater. Sci. Eng. R  Rep.} {\bf 1998}, {\em
22},~187--268. [\href{http://dx.doi.org/10.1016/S0927-796X(97)00018-1}{CrossRef}]

\bibitem[Tang \em{et~al.}(2014)Tang, Cai, Bao, Xue, Lu, Zhu, and Rui]{Tang2014}
Tang, F.L.; Cai, H.M.; Bao, H.W.; Xue, H.T.; Lu, W.J.; Zhu, L.; Rui, Z.Y.
\newblock {Molecular dynamics simulations of void growth in $\gamma$-TiAl
single crystal}.
\newblock {\em Comput. Mater. Sci.} {\bf 2014}, {\em 84},~232--237. [\href{http://dx.doi.org/10.1016/j.commatsci.2013.12.014}{CrossRef}]

\bibitem[Kim(1995)]{Kim1995}
Kim, Y.W.
\newblock {Effects of microstructure on the deformation and fracture of
$\gamma$-TiAl alloys}.
\newblock {\em Mater. Sci. Eng. A} {\bf 1995}, {\em
192--193},~519--533. [\href{http://dx.doi.org/10.1016/0921-5093(94)03271-8}{CrossRef}]

\bibitem[Singh \em{et~al.}(2006)Singh, Mol{\'{e}}nat, Sundararaman, Banerjee,
Saada, Veyssi{\`{e}}re, and Couret]{Singh2006}
{Singh, J.B.}; Mol{\'{e}}nat, G.; Sundararaman, M.; Banerjee, S.; Saada, G.;
Veyssi{\`{e}}re, P.; Couret, A. In situ straining investigation of slip transfer across $\alpha$ 2
lamellae at room temperature in a lamellar TiAl alloy. {\em \mbox{Philos. Mag. Lett.}} {\bf 2006}, {\em 86},~47--60. [\href{http://dx.doi.org/10.1080/09500830500497066}{CrossRef}]% ref. 11 and ref. 39 are same, please confirm it.

\bibitem[Hempel \em{et~al.}(2017)Hempel, Bunn, Nitschke-Pagel, Payzant, and
Dilger]{Hempel2017a}
Hempel, N.; Bunn, J.R.; Nitschke-Pagel, T.; Payzant, E.A.; Dilger, K.
\newblock {Study on the residual stress relaxation in girth-welded steel pipes
under bending load using diffraction methods}.
\newblock {\em Mater. Sci. Eng. A} {\bf 2017}, {\em
688},~289--300. [\href{http://dx.doi.org/10.1016/j.msea.2017.02.005}{CrossRef}]

\bibitem[Groh \em{et~al.}(2009)Groh, Marin, Horstemeyer, and Zbib]{Groh2009}
Groh, S.; Marin, E.B.; Horstemeyer, M.F.; Zbib, H.M.
\newblock {Multiscale modeling of the plasticity in an aluminum single
crystal}.
\newblock {\em Int. J. Plast.} {\bf 2009}, {\em
25},~1456--1473. [\href{http://dx.doi.org/10.1016/j.ijplas.2008.11.003}{CrossRef}]

\bibitem[Trout(1972)]{Liu2018}
Trout, P.E.
\newblock {Plastic Contaminants: Bad News for the Paper Recycler.}
\newblock {\em Tappi} {\bf 1972}, {\em 55},~956--958. [\href{http://dx.doi.org/10.1016/j.cma.2018.06.026}{CrossRef}]

\bibitem[Xu \em{et~al.}(2011)Xu, Hao, Su, Yu, Wan, and Hu]{Xu2011}
Xu, S.Z.; Hao, Z.M.; Su, Y.Q.; Yu, Y.; Wan, Q.; Hu, W.J.
\newblock {An analysis on nanovoid growth in body-centered cubic single
crystalline vanadium}.
\newblock {\em Comput. Mater. Sci.} {\bf 2011}, {\em
50},~2411--2421. [\href{http://dx.doi.org/10.1016/j.commatsci.2011.03.019}{CrossRef}]

\bibitem[Jing \em{et~al.}(2018)Jing, Yuan, Shivpuri, Xu, Zhang, Shan, and
Guo]{Jing2018a}
Jing, P.; Yuan, L.; Shivpuri, R.; Xu, C.; Zhang, Y.; Shan, D.; Guo, B.
\newblock {Evolution of spherical nanovoids within copper polycrystals during
plastic straining: Atomistic investigation}.
\newblock {\em Int. J. Plast.} {\bf 2018}, {\em
100},~122--141. [\href{http://dx.doi.org/10.1016/j.ijplas.2017.09.016}{CrossRef}]

\bibitem[Elkhateeb and Shin(2018)]{Elkhateeb2018}
Elkhateeb, M.G.; Shin, Y.C.
\newblock {Molecular dynamics-based cohesive zone representation of Ti6Al4V/TiC
composite interface}.
\newblock {\em Mater. Des.} {\bf 2018}, {\em 155},~161--169. [\href{http://dx.doi.org/10.1016/j.matdes.2018.05.054}{CrossRef}]

\bibitem[Xiong \em{et~al.}(2015)Xiong, Xu, McDowell, and Chen]{Xiong2015}
Xiong, L.; Xu, S.; McDowell, D.L.; Chen, Y.
\newblock {Concurrent atomistic-continuum simulations of dislocation-void
interactions in fcc crystals}.
\newblock {\em Int. J. Plast.} {\bf 2015}, {\em
65},~33--42. [\href{http://dx.doi.org/10.1016/j.ijplas.2014.08.002}{CrossRef}]

\bibitem[Kiener \em{et~al.}(2011)Kiener, Hosemann, Maloy, and
Minor]{Kiener2011b}
Kiener, D.; Hosemann, P.; Maloy, S.A.; Minor, A.M.
\newblock {In situ nanocompression testing of irradiated copper}.
\newblock {\em Nat. Mater.} {\bf 2011}, {\em 10},~608--613. [\href{http://dx.doi.org/10.1038/nmat3055}{CrossRef}]

\bibitem[Yang and Baker(1998)]{Yang1998}
Yang, Y.; Baker, I.
\newblock {The influence of vacancy concentration on the mechanical behavior of
Fe-40Al}.
\newblock {\em Intermetallics} {\bf 1998}, {\em 6},~167--175. [\href{http://dx.doi.org/10.1016/S0966-9795(97)00062-9}{CrossRef}]

\bibitem[Nazmy \em{et~al.}(2001)Nazmy, Staubli, Onofrio, and Lupinc]{Nazmy2001}
Nazmy, M.; Staubli, M.; Onofrio, G.; Lupinc, V.
\newblock {Surface defect tolerance of a cast TiAl alloy in fatigue}.
\newblock {\em Scr.~Mater.} {\bf 2001}, {\em 45},~787--792. [\href{http://dx.doi.org/10.1016/S1359-6462(01)01097-1}{CrossRef}]

\bibitem[Brimmo \em{et~al.}(2014)Brimmo, Hassan, and Shatilla]{Wu2016}
Brimmo, A.T.; Hassan, M.I.; Shatilla, Y.
\newblock {Transient heat transfer computational model for the stopped
aluminium reduction pot---Cooling techniques evaluation}.
\newblock {\em Appl. Therm. Eng.} {\bf 2014}, {\em 73},~114--125. [\href{http://dx.doi.org/10.1016/j.applthermaleng.2014.07.014}{CrossRef}]

\bibitem[Larsen \em{et~al.}(2016)Larsen, Schmidt, and Schi{\O}tz]{Larsen2016}
Larsen, P.M.; Schmidt, S.; Schi{\O}tz, J.
\newblock {Robust structural identification via polyhedral template matching}.
\newblock {\em Model. Simul. Mater. Sci. Eng.}
{\bf 2016}, {\em 24},~055007. [\href{http://dx.doi.org/10.1088/0965-0393/24/5/055007}{CrossRef}]

\bibitem[Ko \em{et~al.}(2015)Ko, Grabowski, and Neugebauer]{Ko2015}
Ko, W.S.; Grabowski, B.; Neugebauer, J.
\newblock {Development and application of a Ni-Ti interatomic potential with
high predictive accuracy of the martensitic phase transition}.
\newblock {\em Phys. Rev. B Condens. Matter Mater. Phys.} {\bf
2015}, {\em 92},~134107. [\href{http://dx.doi.org/10.1103/PhysRevB.92.134107}{CrossRef}]

\bibitem[Zepeda-Ruiz \em{et~al.}(2017)Zepeda-Ruiz, Stukowski, Oppelstrup, and
Bulatov]{Zepeda-Ruiz2017}
Zepeda-Ruiz, L.A.; Stukowski, A.; Oppelstrup, T.; Bulatov, V.V.
\newblock {Probing the limits of metal plasticity with molecular dynamics
simulations}.
\newblock {\em Nature} {\bf 2017}, {\em 550},~492--495. [\href{http://dx.doi.org/10.1038/nature23472}{CrossRef}] [\href{http://www.ncbi.nlm.nih.gov/pubmed/28953878}{PubMed}]

\bibitem[Fan \em{et~al.}(2018)Fan, Zhu, El-Awady, and Raabe]{Fan2018a}
Fan, H.; Zhu, Y.; El-Awady, J.A.; Raabe, D.
\newblock {Precipitation hardening effects on extension twinning in magnesium
alloys}.
\newblock {\em Int. J. Plast.} {\bf 2018}, {\em
106},~186--202. [\href{http://dx.doi.org/10.1016/j.ijplas.2018.03.008}{CrossRef}]

\bibitem[Zope and Mishin(2003)]{Zope2003}
Zope, R.R.; Mishin, Y.
\newblock {Interatomic potentials for atomistic simulations of the Ti--Al
system}.
\newblock {\em Phys. Rev. B   Condens. Matter Mater. Phys.} {\bf
2003}, {\em 68},~024102. [\href{http://dx.doi.org/10.1103/PhysRevB.68.024102}{CrossRef}]

\bibitem[Plimpton(1995)]{Plimpton1995}
Plimpton, S.
\newblock {Fast parallel algorithms for short-range molecular dynamics}.
\newblock {\em J. Comput. Phys.} {\bf 1995}, {\em 117},~1--19. [\href{http://dx.doi.org/10.1006/jcph.1995.1039}{CrossRef}]

\bibitem[Zhu \em{et~al.}(2008)Zhu, Li, Samanta, Leach, and Gall]{Zhu2008}
Zhu, T.; Li, J.; Samanta, A.; Leach, A.; Gall, K.
\newblock {Temperature and strain-rate dependence of surface dislocation
nucleation}.
\newblock {\em Phys. Rev. Lett.} {\bf 2008}, {\em 100},~025502. [\href{http://dx.doi.org/10.1103/PhysRevLett.100.025502}{CrossRef}]

\bibitem[Stukowski(2010)]{Stukowski2010}
Stukowski, A.
\newblock {Visualization and analysis of atomistic simulation data with
OVITO-the Open Visualization Tool}.
\newblock {\em Model. Simul. Mater. Sci. Eng.}
{\bf 2010}, {\em 18},~015012. [\href{http://dx.doi.org/10.1088/0965-0393/18/1/015012}{CrossRef}]

\bibitem[Tang \em{et~al.}(2010)Tang, Kim, and Horstemeyer]{Tang2010}
Tang, T.; Kim, S.; Horstemeyer, M.F.
\newblock {Molecular dynamics simulations of void growth and coalescence in
single crystal magnesium}.
\newblock {\em Acta Mater.} {\bf 2010}, {\em 58},~4742--4759. [\href{http://dx.doi.org/10.1016/j.actamat.2010.05.011}{CrossRef}]

\bibitem[Chen and Cao(2015)]{CHEN2015365}
Chen, J.H.; Cao, R.
\newblock {Chapter 9 - Brittle Fracture of TiAl Alloys and NiTi Memory Alloys}.
In {\em Micromechanism of Cleavage Fracture of Metals}; Chen, J.H., Cao, R.,
Eds.; Butterworth-Heinemann: Boston, MA, USA, 2015; pp.~365--443.

\bibitem[He \em{et~al.}(1995)He, Schwarz, Migliori, and Whang]{Schwarz1995}
He, Y.; Schwarz, R.; Migliori, A.; Whang, S.
\newblock {Elastic constants of single crystal $\gamma$---TiAl}.
\newblock {\em J. Mater. Res.} {\bf 1995}, {\em 10},~1187--1195. [\href{http://dx.doi.org/10.1557/JMR.1995.1187}{CrossRef}]

\bibitem[Tanaka \em{et~al.}(1996)Tanaka, Okamoto, Inul, Mlnonishl, Yamaguch,
and Koiwa]{Tanaka1996}
Tanaka, K.; Okamoto, K.; Inul, H.; Mlnonishl, Y.; Yamaguch, M.; Koiwa, M.
\newblock {Elastic constants and their temperature dependence for the
intermetallic compound Ti3Al}.
\newblock {\em Philos. Mag. A  Phys. Condens. Matter
Struct. Defects Mech. Prop.} {\bf 1996}, {\em
73},~1475--1488. [\href{http://dx.doi.org/10.1080/01418619608245145}{CrossRef}]

\bibitem[Stein and Low(1960)]{Stein1960}
Stein, D.F.; Low, J.R.
\newblock {Mobility of edge dislocations in silicon-iron crystals}.
\newblock {\em J. Appl. Phys.} {\bf 1960}, {\em 31},~362--369. [\href{http://dx.doi.org/10.1063/1.1735574}{CrossRef}]

\bibitem[Escaig(1968)]{Escaig1968}
Escaig, B.
\newblock {L'activation thermique des d{\'{e}}viations sous faibles contraintes
dans les structures h.c. et c.c. Par}.
\newblock {\em Phys. Status Solidi (B)} {\bf 1968}, {\em 28},~463--474. [\href{http://dx.doi.org/10.1002/pssb.19680280203}{CrossRef}]

\bibitem[Liu \em{et~al.}(2007)Liu, Liu, Wang, and Ye]{Liu2007}
Liu, Y.L.; Liu, L.M.; Wang, S.Q.; Ye, H.Q.
\newblock {First-principles study of shear deformation in TiAl alloys}.
\newblock {\em \mbox{J. Alloys Compd.}} {\bf 2007}, {\em
440},~287--294. [\href{http://dx.doi.org/10.1016/j.jallcom.2006.09.027}{CrossRef}]

\bibitem[R{\"{o}}sner \em{et~al.}(2004)R{\"{o}}sner, Markmann, and
Weissm{\"{u}}ller]{Zhu2012}
R{\"{o}}sner, H.; Markmann, J.; Weissm{\"{u}}ller, J.
\newblock {Deformation twinning in nanocrystalline Pd}.
\newblock {\em Philos. Mag. Lett.} {\bf 2004}, {\em 84},~321--334. [\href{http://dx.doi.org/10.1080/09500830410001675687}{CrossRef}]

\bibitem[{Fritz Appel} \em{et~al.}(2011){habil. Fritz Appel}, Paul,
Oehring, and Microstructures]{intro-structure}
Appel, F. , Paul, J. D. and Oehring, M.
\newblock {Deformation Behavior of Two-Phase $\alpha$2(Ti3Al) + $\gamma$(TiAl)
Alloys}.
\newblock {\em Gamma Titan. Alum. Alloys} {\bf 2011}, {\em 2},~125--248. [\href{http://dx.doi.org/10.1002/9783527636204.ch6}{CrossRef}]

\bibitem[Zghal \em{et~al.}(1998)Zghal, Menand, and Couret]{Zghal1998}
Zghal, S.; Menand, A.; Couret, A.
\newblock {Pinning points anchoring ordinary and shockley dislocations in TiAl
alloys}.
\newblock {\em Acta Mater.} {\bf 1998}, {\em 46},~5899--5905. [\href{http://dx.doi.org/10.1016/S1359-6454(98)00233-X}{CrossRef}]

\end{thebibliography}

\end{document}

### 2019-01-09 Source/draft/alexpub.tex
Published

--- 2018-12-27 MDPI-Materials/1stEdt/subm/alexpub.tex
@@
 \reftitle{References}
-\bibliography{ref.bib}
+\bibliography{ref/VIOLET-ref.bib}
 \funding{This research was funded by the National Natural Science Foundation of China (No.51665030, No.51865027) and the Program for Changjiang Scholars and Innovative Research Team in Universities of the Ministry of Education of China (No.

### 2019-01-09 Source/draft/wmm2.tex
Published

--- 2018-11-23 draft/wmm2.tex
@@
 Rapture failure at the macroscopic scale can be attributed to abrupt nucleation, growth and propagation of cracks, but at the microscopic scale defects are initially formed in the casting process, such as voids and inclusions \cite{Tang2014}.
-A great number of literatures cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}.
+Numerous studies cover a wide range of factors such as alloy composition, microstructure and deformation temperature, some reports come up with the idea that two phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\alpha_2$($\rm Ti_3Al$) alloy \cite{Kim1995}.
 void can be produced due to specific volume differences induced by precipitation, different thermal expansion or shrinkage upon heating or cooling the specimen.

### 2019-01-09 Source/code/Temp.py

@@ -1,0 +1,41 @@
+import os
+import os.path
+
+#plt.rcParams["font.family"] = 'Times New Roman'
+import matplotlib.pyplot as plt
+plt.rcParams.update({'font.size': 16})
+from matplotlib import rc
+rc('text', usetex=True)
+#csfont = {'fontname':'Times New Roman'}
+plt.rcParams["font.family"] = "Times New Roman"
+WDIR = os.path.dirname(__file__)
+# loadpath = os.path.join(WDIR,'data','stress_strain')
+writepath = os.path.join(WDIR,'..','draft','img')
+import numpy as np
+import matplotlib.pyplot as plt
+
+T = np.linspace(0,1100,100)
+key = 20*np.e**(-150/298)/20
+key1=[298,298]
+key2=[0,1]
+# u = 20*np.e**(-300/T)/20
+# v = 20*np.e**(-350/T)/20
+# w = 20*np.e**(-450/T)/20
+u = 20*np.e**(-350/T)/20
+v = 20*np.e**(-400/T)/20
+w = 20*np.e**(-450/T)/20
+plt.xlabel('Temperature / K')
+plt.ylabel('Normalized velocity of dislocation motion')
+plt.ylim(ymax=1)
+plt.plot(T,u, color='R')
+plt.plot(T,v, color='G')
+plt.plot(T,w, color='B')
+plt.legend([r'$v_1 (\tau_1^*)$', r'$v_2 (\tau_2^*)$',r'$v_3 (\tau_3^*)$'], frameon=False,loc='best')
+plt.text(450,0.85,r'$\tau_1^*>\tau_2^*>\tau_3^*$')
+plt.annotate('298 K',xy=(290,0.35),xytext=(80,0.45),arrowprops=dict(arrowstyle="->",connectionstyle="arc3"))
+plt.plot(key1,key2,linestyle='--',color='black')
+
+plt.savefig(os.path.join(writepath, 'temp.pdf'))
+
+plt.show()
+

### 2019-01-09 Source/code/allline.py

@@ -1,0 +1,69 @@
+# 读取输出文件，绘制应力应变曲线
+'''
+violet
+├── code
+│   ├── data
+│   │   ├── size
+│   │   ├── stress_strain
+│   │   └── surf
+│   └── pict
+└── draft
+    ├── bkp
+    ├── img
+    ├── material
+    └── ref
+'''
+
+import os
+import os.path
+from os import listdir
+import matplotlib.pyplot as plt
+import pandas as pd
+from matplotlib import rc
+import matplotlib.pyplot as plt
+plt.rcParams.update({'font.size': 14})
+plt.rcParams["font.family"] = 'Times New Roman'
+
+rc('text', usetex=True)
+
+# rc('text', usetex=True)
+#csfont = {'fontname':'Times New Roman'}
+#plt.rcParams["font.family"] = "Times New Roman"
+WDIR = os.path.dirname(__file__)
+loadpath = os.path.join(WDIR,'data','stress_strain')
+writepath = os.path.join(WDIR,'..','draft','img')
+# pre-set head name
+
+
+
+prop = ['step', 'strain', 'stress', 'energy']
+# import data from .csv file:
+#ds1 = pd.read_csv(os.path.join(loadpath,'aa.csv'), sep=' ', skiprows=1, names=prop)
+ds2 = pd.read_csv(os.path.join(loadpath,'ag.csv'), sep=' ', skiprows=1, names=prop)
+ds3 = pd.read_csv(os.path.join(loadpath,'pf.csv'), sep=' ', skiprows=1, names=prop)
+ds4 = pd.read_csv(os.path.join(loadpath,'ia.csv'), sep=' ', skiprows=1, names=prop)
+fct = 10e6*0.75
+px2=ds2.step/fct
+px3=ds3.step/fct
+px4=ds4.step/fct
+
+# plot lines
+#p1 = plt.plot(ds1.step, ds1.stress, label='aa')
+p3 = plt.plot((ds3.strain-0.015)*1.2, ds3.stress, color = 'R')
+p2 = plt.plot((ds2.strain-0.015)*1.2, ds2.stress, color = 'G')
+p4 = plt.plot((ds4.strain-0.015)*1.2, ds4.stress, color = 'B')
+
+plt.legend([ 'no void',r'void inside $\alpha_2$ phase',r'void at \textbf{$\alpha_2$/$\gamma$} phase boundary'], frameon=False)
+
+# config title and label
+
[…]

### 2019-01-09 Source/code/crack.py

@@ -1,0 +1,41 @@
+import os
+import os.path
+import numpy as np
+import matplotlib.pyplot as plt
+plt.rcParams.update({'font.size': 12})
+
+
+#WDIR = os.getcwd()
+WDIR = os.path.dirname(__file__)
+loadpath = os.path.join(WDIR,'data','surf')
+#writepath = os.path.join(WDIR,'draft','img')
+writepath = os.path.join(WDIR,'..','draft','img')
+
+#plt.savefig(os.path.join(WDIR,'draft','img','surf.pdf'))
+#loadpath = os.path.join(WDIR,'code','data','surf')
+ag =np.loadtxt(os.path.join(loadpath,'surf_ag.txt'))
+ia =np.loadtxt(os.path.join(loadpath,'surf_ia.txt'))
+ig =np.loadtxt(os.path.join(loadpath,'surf_ig.txt'))
+pf =np.loadtxt(os.path.join(loadpath,'surf_pf.txt'))
+#d_pf = np.gradient(pf)
+imglist =[ag, ig, pf]
+dv1st = list(map(np.gradient,imglist))
+#colorlist = ['g','b','r']
+# markerlist = ['s','^','o']
+max = list(map(np.max,dv1st))
+min = np.min(np.abs(ag))
+for img in dv1st:
+    pxx = np.linspace(0,np.dot(0.005,len(img)),len(img))/10
+    plt.plot(pxx, img/np.max(max))
+# plt.title('1st Deviation of Area of Surface of Crack')
+plt.xlabel('Strain')
+plt.ylabel('Relative Crack Propagation Indicator')
+plt.xlim(xmax=0.03)
+plt.legend(["ag","ig", "pf"],frameon=False)
+# plt.legend()
+plt.savefig(os.path.join(writepath,'1stdiv.pdf'))
+
+plt.show()
+plt.cla
+plt.clf()
+

### 2019-01-09 Source/code/data/crack-str/crack-str.py

@@ -1,0 +1,24 @@
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+strmax = np.zeros(17)
+u = np.linspace(20, 35, 16)
+k = 1
+for i in u:
+
+    nami = str(int(i))
+    ds = pd.read_csv('%s'%nami, sep=' ',skiprows=1)
+    maxst = np.array(ds.values)
+    np.nan_to_num(maxst,0)
+    np.max(maxst)
+    print(nami)
+    print(np.max(maxst))
+    strmax[k] = np.max(maxst)
+    k=k+1
+
+v = np.array(
+        [3.36, 3.69, 4.33, 5.02, 6.39, 8.03, 10.16, 12.6, 15.36, 18.15, 21.23, 23.91, 25.38, 26.27, 26.13, 25.56,
+         25.71])
+plt.plot(v,strmax,marker='o')
+np.savetxt('crack-str.txt',[v,strmax])
+plt.show()

### 2019-01-09 Source/code/data/size/filelist.py

@@ -1,0 +1,37 @@
+import os
+import os.path
+from os import listdir
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+plt.rcParams["font.family"] = 'Times New Roman'
+
+dirlist = listdir(os.path.dirname(__file__))
+print('Scaning dir: %s' %dirlist)
+txtlist = []
+itemlist = []
+strmax = []
+plt.rcParams["font.family"] = 'Times New Roman'
+for i in dirlist:
+    if os.path.splitext(i)[1] == ".txt":
+        print('%s found' %i)
+        txtlist.append(i)
+        itemlist.append(os.path.splitext(i)[0])
+count = 0
+for node in txtlist:
+    label = node.split('.')[0]
+    prop = ['step', 'stress', 'strain']
+    ds1 = pd.read_csv(node, sep=' ', skiprows=2, names=prop)
+    strmax.append(np.max(ds1.stress))
+    plt.plot(ds1.step, ds1.stress)
+    plt.ylim(ymax=6)
+    plt.xlim(xmax=4.5e5)
+    #plt.title()
+    plt.title([label,max(ds1.stress)])
+    plt.savefig('fig.%s.pdf' % label)
+    plt.clf()
+    plt.cla
+    print('%s over'%label)
+    count +=count
+
+

### 2019-01-09 Source/code/data/size/size_summary.py

@@ -1,0 +1,53 @@
+'''
+violet
+├── code
+│   ├── data
+│   │   ├── size
+│   │   ├── stress_strain
+│   │   └── surf
+│   └── pict
+└── draft
+    ├── bkp
+    ├── img
+    ├── material
+    └── ref
+'''
+import os
+import matplotlib.pyplot as plt
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit as fit
+plt.rcParams.update({'font.size': 16})
+from matplotlib import rc
+rc('text', usetex=True)
+plt.rcParams["font.family"] = 'Times New Roman'
+
+WDIR = os.path.dirname(__file__)
+writepath = os.path.join(WDIR,'..','..','..','draft','img')
+
+size = np.array([0, 2, 5, 10, 15, 20])
+iamax = np.array([5.3, 5.26, 5.25, 5.22, 5.19, 4.96])
+agmax = np.array([5.3, 5.25, 5.17, 5.11, 5.09, 4.87])
+fac = (1-(np.pi*(size/2)**2)/(210*180))*iamax[0]
+# pia = fit.gaussian(size,iamax)
+plt.plot(size, fac, marker='o',linestyle='--',color='R')
+plt.plot(size, iamax,marker='s',color='G')
+plt.plot(size, agmax, marker='^',color='B')
+
+# color='darkorange'
+# color='steelblue'
+plt.legend(['calculated value',r'void inside $\alpha_2$ phase', r'void at \textbf{$\alpha_2$/$\gamma$} phase boundary'], frameon=False)
+plt.ylim(4.8,5.5)
+plt.xlabel(r'Radius of Void/ \AA')
+plt.ylabel('Yield strength/GPa')
+plt.savefig(os.path.join(writepath,'effect_of_vol.pdf'))
+plt.show()
+
+# import matplotlib as plt
+# print(plt.get_cachedir())
+# comments
+
+'''
+UserWarning: findfont: Font family ['Times New Roman'] not found. Falling back to DejaVu Sans
+  (prop.get_family(), self.defaultFamily[fontext]))
+'''

### 2019-01-09 Source/code/dissum.py

@@ -1,0 +1,64 @@
+
+import os
+import os.path
+
+#plt.rcParams["font.family"] = 'Times New Roman'
+import matplotlib.pyplot as plt
+
+#csfont = {'fontname':'Times New Roman'}
+plt.rcParams["font.family"] = 'Times New Roman'
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import rc
+rc('text', usetex=True)
+plt.rcParams.update({'font.size': 16})
+WDIR = os.path.dirname(__file__)
+# loadpath = os.path.join(WDIR,'data','stress_strain')
+writepath = os.path.join(WDIR,'..','draft','img')
+pf = [744, 290, 212, 530]
+shockley = [1343, 1470, 3581, 4367]
+stair_rode = [0, 123, 259, 295]
+hirth = [0, 407, 1100, 557]
+frank = [0, 375, 211, 500]
+
+
+# data to plot
+n_groups = 4
+
+# create plot
+fig, ax = plt.subplots()
+index = np.arange(n_groups)
+bar_width = 0.22
+opacity = 0.8
+
+rects1 = plt.bar(index, pf, bar_width,
+                 alpha=opacity,
+                 color='R',
+                 label='Perfect')
+
+rects2 = plt.bar(index + bar_width, shockley, bar_width,
+                 alpha=opacity,
+                 color='B',
+                 label='Shockley')
+
+rects3 = plt.bar(index + 2*bar_width, stair_rode, bar_width,
+                 alpha=opacity,
+                 color='G',
+                 label='Stair-rod')
+
+rects4 = plt.bar(index + 3*bar_width, frank, bar_width,
+                 alpha=opacity,
+                 color='black',
+                 label='Frank')
+
+plt.xlabel('Strain')
+plt.ylabel(r'Dislocation length / \AA')
+plt.ylim(ymax=5000)
+# plt.title('Scores by person')
+plt.xticks(index + bar_width, ('0.005','0.092','0.101','0.112'))
+plt.legend(frameon = False,title='Type of dislocation')
+
+plt.savefig(os.path.join(writepath, 'dis-summary.pdf'))
+
+#plt.tight_layout()
+plt.show()

### 2019-01-09 Source/code/plot-sample.py

@@ -1,0 +1,37 @@
+# import packages
+import matplotlib.pyplot as plt
+import numpy as np
+import sys
+# 常用字体: ’Dejavu Sans‘,’Times New Roman‘,'Arial'
+# 设置图片尺寸  set size of fgure units cm
+plt.rcParams['figure.figsize'] = (5,2.5)
+plt.xlabel('Position')
+plt.ylabel('Temperatrue')
+plt.rcParams.update({'font.size': 9})
+# 采用紧凑布局
+plt.tight_layout()
+# 生成数据
+a = np.linspace(0,10,100)
+b = 0.8*a
+c = 1.2*a
+u = np.sin(a)
+v = np.cos(b)
+w = u+v
+# line color
+# set 是经典的RGB色，简直辣眼睛
+# set1: red,green,blue
+# set2: frebrick,forestgreen,darkgreen
+plt.plot(a,u,color='firebrick',marker='^',markevery=10,mew=0.25)
+plt.plot(b,v,color='forestgreen',marker='o',markevery=10,mew=0.25)
+plt.plot(c,w,color='darkblue',marker='s',markevery=10,mew=0.25)
+# create legend without frame
+plt.title('Sample Figure')
+# 绘制图例，不要框框
+plt.legend(['L1','L2','L3'],frameon=False)
+plt.xlim(0,8)
+plt.ylim(-3,3)
+# 亲测SVG能插入最word2016
+plt.savefig('plt.svg')
+# 可用格式有 png pdf ...
+plt.savefig('plt.pdf',dpi=300)
+plt.show()

### 2019-01-09 code/Temp.py

@@ -1,41 +1,0 @@
-import os
-import os.path
-
-#plt.rcParams["font.family"] = 'Times New Roman'
-import matplotlib.pyplot as plt
-plt.rcParams.update({'font.size': 16})
-from matplotlib import rc
-rc('text', usetex=True)
-#csfont = {'fontname':'Times New Roman'}
-plt.rcParams["font.family"] = "Times New Roman"
-WDIR = os.path.dirname(__file__)
-# loadpath = os.path.join(WDIR,'data','stress_strain')
-writepath = os.path.join(WDIR,'..','draft','img')
-import numpy as np
-import matplotlib.pyplot as plt
-
-T = np.linspace(0,1100,100)
-key = 20*np.e**(-150/298)/20
-key1=[298,298]
-key2=[0,1]
-# u = 20*np.e**(-300/T)/20
-# v = 20*np.e**(-350/T)/20
-# w = 20*np.e**(-450/T)/20
-u = 20*np.e**(-350/T)/20
-v = 20*np.e**(-400/T)/20
-w = 20*np.e**(-450/T)/20
-plt.xlabel('Temperature / K')
-plt.ylabel('Normalized velocity of dislocation motion')
-plt.ylim(ymax=1)
-plt.plot(T,u, color='R')
-plt.plot(T,v, color='G')
-plt.plot(T,w, color='B')
-plt.legend([r'$v_1 (\tau_1^*)$', r'$v_2 (\tau_2^*)$',r'$v_3 (\tau_3^*)$'], frameon=False,loc='best')
-plt.text(450,0.85,r'$\tau_1^*>\tau_2^*>\tau_3^*$')
-plt.annotate('298 K',xy=(290,0.35),xytext=(80,0.45),arrowprops=dict(arrowstyle="->",connectionstyle="arc3"))
-plt.plot(key1,key2,linestyle='--',color='black')
-
-plt.savefig(os.path.join(writepath, 'temp.pdf'))
-
-plt.show()
-

### 2019-01-09 code/allline.py

@@ -1,69 +1,0 @@
-# 读取输出文件，绘制应力应变曲线
-'''
-violet
-├── code
-│   ├── data
-│   │   ├── size
-│   │   ├── stress_strain
-│   │   └── surf
-│   └── pict
-└── draft
-    ├── bkp
-    ├── img
-    ├── material
-    └── ref
-'''
-
-import os
-import os.path
-from os import listdir
-import matplotlib.pyplot as plt
-import pandas as pd
-from matplotlib import rc
-import matplotlib.pyplot as plt
-plt.rcParams.update({'font.size': 14})
-plt.rcParams["font.family"] = 'Times New Roman'
-
-rc('text', usetex=True)
-
-# rc('text', usetex=True)
-#csfont = {'fontname':'Times New Roman'}
-#plt.rcParams["font.family"] = "Times New Roman"
-WDIR = os.path.dirname(__file__)
-loadpath = os.path.join(WDIR,'data','stress_strain')
-writepath = os.path.join(WDIR,'..','draft','img')
-# pre-set head name
-
-
-
-prop = ['step', 'strain', 'stress', 'energy']
-# import data from .csv file:
-#ds1 = pd.read_csv(os.path.join(loadpath,'aa.csv'), sep=' ', skiprows=1, names=prop)
-ds2 = pd.read_csv(os.path.join(loadpath,'ag.csv'), sep=' ', skiprows=1, names=prop)
-ds3 = pd.read_csv(os.path.join(loadpath,'pf.csv'), sep=' ', skiprows=1, names=prop)
-ds4 = pd.read_csv(os.path.join(loadpath,'ia.csv'), sep=' ', skiprows=1, names=prop)
-fct = 10e6*0.75
-px2=ds2.step/fct
-px3=ds3.step/fct
-px4=ds4.step/fct
-
-# plot lines
-#p1 = plt.plot(ds1.step, ds1.stress, label='aa')
-p3 = plt.plot((ds3.strain-0.015)*1.2, ds3.stress, color = 'R')
-p2 = plt.plot((ds2.strain-0.015)*1.2, ds2.stress, color = 'G')
-p4 = plt.plot((ds4.strain-0.015)*1.2, ds4.stress, color = 'B')
-
-plt.legend([ 'no void',r'void inside $\alpha_2$ phase',r'void at \textbf{$\alpha_2$/$\gamma$} phase boundary'], frameon=False)
-
-# config title and label
-
[…]

### 2019-01-09 code/alllinel.py

@@ -1,70 +1,0 @@
-# 读取输出文件，绘制应力应变曲线
-'''
-violet
-├── code
-│   ├── data
-│   │   ├── size
-│   │   ├── stress_strain
-│   │   └── surf
-│   └── pict
-└── draft
-    ├── bkp
-    ├── img
-    ├── material
-    └── ref
-'''
-
-import os
-import matplotlib
-import os.path
-from os import listdir
-import matplotlib.pyplot as plt
-import pandas as pd
-from matplotlib import rc
-import matplotlib.pyplot as plt
-plt.rcParams.update({'font.size': 12})
-
-# rc('text', usetex=True)
-#csfont = {'fontname':'Times New Roman'}
-#plt.rcParams["font.family"] = "Times New Roman"
-WDIR = os.path.dirname(__file__)
-loadpath = os.path.join(WDIR,'data','stress_strain')
-writepath = os.path.join(WDIR,'..','draft','img')
-# pre-set head name
-
-
-
-prop = ['step', 'strain', 'stress', 'energy']
-# import data from .csv file:
-#ds1 = pd.read_csv(os.path.join(loadpath,'aa.csv'), sep=' ', skiprows=1, names=prop)
-ds2 = pd.read_csv(os.path.join(loadpath,'ag.csv'), sep=' ', skiprows=1, names=prop)
-ds3 = pd.read_csv(os.path.join(loadpath,'pf.csv'), sep=' ', skiprows=1, names=prop)
-ds4 = pd.read_csv(os.path.join(loadpath,'ia.csv'), sep=' ', skiprows=1, names=prop)
-fct = 10e6*0.75
-px2=ds2.step/fct
-px3=ds3.step/fct
-px4=ds4.step/fct
-
-# plot lines
-#p1 = plt.plot(ds1.step, ds1.stress, label='aa')
-fig = matplotlib.pyplot.gcf()
-fig.set_size_inches(8, 3)
-
-p3 = plt.plot((ds3.strain-0.015)*1.2, ds3.stress, color = 'R')
-p2 = plt.plot((ds2.strain-0.015)*1.2, ds2.stress, color = 'G')
-p4 = plt.plot((ds4.strain-0.015)*1.2, ds4.stress, color = 'B')
-
-plt.legend([ 'no void','void at boundary','void inside grain'], frameon=False)
-
-# config title and label
-
-#plt.title('stress-strain curve')
[…]

### 2019-01-09 code/crack.py

@@ -1,41 +1,0 @@
-import os
-import os.path
-import numpy as np
-import matplotlib.pyplot as plt
-plt.rcParams.update({'font.size': 12})
-
-
-#WDIR = os.getcwd()
-WDIR = os.path.dirname(__file__)
-loadpath = os.path.join(WDIR,'data','surf')
-#writepath = os.path.join(WDIR,'draft','img')
-writepath = os.path.join(WDIR,'..','draft','img')
-
-#plt.savefig(os.path.join(WDIR,'draft','img','surf.pdf'))
-#loadpath = os.path.join(WDIR,'code','data','surf')
-ag =np.loadtxt(os.path.join(loadpath,'surf_ag.txt'))
-ia =np.loadtxt(os.path.join(loadpath,'surf_ia.txt'))
-ig =np.loadtxt(os.path.join(loadpath,'surf_ig.txt'))
-pf =np.loadtxt(os.path.join(loadpath,'surf_pf.txt'))
-#d_pf = np.gradient(pf)
-imglist =[ag, ig, pf]
-dv1st = list(map(np.gradient,imglist))
-#colorlist = ['g','b','r']
-# markerlist = ['s','^','o']
-max = list(map(np.max,dv1st))
-min = np.min(np.abs(ag))
-for img in dv1st:
-    pxx = np.linspace(0,np.dot(0.005,len(img)),len(img))/10
-    plt.plot(pxx, img/np.max(max))
-# plt.title('1st Deviation of Area of Surface of Crack')
-plt.xlabel('Strain')
-plt.ylabel('Relative Crack Propagation Indicator')
-plt.xlim(xmax=0.03)
-plt.legend(["ag","ig", "pf"],frameon=False)
-# plt.legend()
-plt.savefig(os.path.join(writepath,'1stdiv.pdf'))
-
-plt.show()
-plt.cla
-plt.clf()
-

### 2019-01-09 code/data/crack-str/crack-str.py

@@ -1,24 +1,0 @@
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-strmax = np.zeros(17)
-u = np.linspace(20, 35, 16)
-k = 1
-for i in u:
-
-    nami = str(int(i))
-    ds = pd.read_csv('%s'%nami, sep=' ',skiprows=1)
-    maxst = np.array(ds.values)
-    np.nan_to_num(maxst,0)
-    np.max(maxst)
-    print(nami)
-    print(np.max(maxst))
-    strmax[k] = np.max(maxst)
-    k=k+1
-
-v = np.array(
-        [3.36, 3.69, 4.33, 5.02, 6.39, 8.03, 10.16, 12.6, 15.36, 18.15, 21.23, 23.91, 25.38, 26.27, 26.13, 25.56,
-         25.71])
-plt.plot(v,strmax,marker='o')
-np.savetxt('crack-str.txt',[v,strmax])
-plt.show()

### 2019-01-09 code/data/size/filelist.py

@@ -1,37 +1,0 @@
-import os
-import os.path
-from os import listdir
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-plt.rcParams["font.family"] = 'Times New Roman'
-
-dirlist = listdir(os.path.dirname(__file__))
-print('Scaning dir: %s' %dirlist)
-txtlist = []
-itemlist = []
-strmax = []
-plt.rcParams["font.family"] = 'Times New Roman'
-for i in dirlist:
-    if os.path.splitext(i)[1] == ".txt":
-        print('%s found' %i)
-        txtlist.append(i)
-        itemlist.append(os.path.splitext(i)[0])
-count = 0
-for node in txtlist:
-    label = node.split('.')[0]
-    prop = ['step', 'stress', 'strain']
-    ds1 = pd.read_csv(node, sep=' ', skiprows=2, names=prop)
-    strmax.append(np.max(ds1.stress))
-    plt.plot(ds1.step, ds1.stress)
-    plt.ylim(ymax=6)
-    plt.xlim(xmax=4.5e5)
-    #plt.title()
-    plt.title([label,max(ds1.stress)])
-    plt.savefig('fig.%s.pdf' % label)
-    plt.clf()
-    plt.cla
-    print('%s over'%label)
-    count +=count
-
-

### 2019-01-09 code/data/size/size_summary.py

@@ -1,53 +1,0 @@
-'''
-violet
-├── code
-│   ├── data
-│   │   ├── size
-│   │   ├── stress_strain
-│   │   └── surf
-│   └── pict
-└── draft
-    ├── bkp
-    ├── img
-    ├── material
-    └── ref
-'''
-import os
-import matplotlib.pyplot as plt
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.optimize import curve_fit as fit
-plt.rcParams.update({'font.size': 16})
-from matplotlib import rc
-rc('text', usetex=True)
-plt.rcParams["font.family"] = 'Times New Roman'
-
-WDIR = os.path.dirname(__file__)
-writepath = os.path.join(WDIR,'..','..','..','draft','img')
-
-size = np.array([0, 2, 5, 10, 15, 20])
-iamax = np.array([5.3, 5.26, 5.25, 5.22, 5.19, 4.96])
-agmax = np.array([5.3, 5.25, 5.17, 5.11, 5.09, 4.87])
-fac = (1-(np.pi*(size/2)**2)/(210*180))*iamax[0]
-# pia = fit.gaussian(size,iamax)
-plt.plot(size, fac, marker='o',linestyle='--',color='R')
-plt.plot(size, iamax,marker='s',color='G')
-plt.plot(size, agmax, marker='^',color='B')
-
-# color='darkorange'
-# color='steelblue'
-plt.legend(['calculated value',r'void inside $\alpha_2$ phase', r'void at \textbf{$\alpha_2$/$\gamma$} phase boundary'], frameon=False)
-plt.ylim(4.8,5.5)
-plt.xlabel(r'Radius of Void/ \AA')
-plt.ylabel('Yield strength/GPa')
-plt.savefig(os.path.join(writepath,'effect_of_vol.pdf'))
-plt.show()
-
-# import matplotlib as plt
-# print(plt.get_cachedir())
-# comments
-
-'''
-UserWarning: findfont: Font family ['Times New Roman'] not found. Falling back to DejaVu Sans
-  (prop.get_family(), self.defaultFamily[fontext]))
-'''

### 2019-01-09 code/data/size/strplt.py

@@ -1,20 +1,0 @@
-# plot step-stress line
-
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-#txtpath=['stagsz2','stagsz5','stagsz15','stagsz20'\
-           'stiasz2','stiasz5', 'stiasz15','stiasz20']
-
-prop = ['step', 'stress', 'strain']
-ds1 = pd.read_csv(txtpath, sep=' ', skiprows=2, names=prop)
-p1 = plt.scatter(ds1.step, ds1.stress)
-# maxstep = np.max(ds1.step)
-# maxstre = np.max(ds1.stress)
-# print('max step is %d\nmax stress is %f\n' %(maxstep, maxstre))
-# plt.xlabel('Step')
-# plt.ylabel('Stress (GPa)')
-# plt.legend()
-# plt.show()
-
-

### 2019-01-09 code/dissum.py

@@ -1,64 +1,0 @@
-
-import os
-import os.path
-
-#plt.rcParams["font.family"] = 'Times New Roman'
-import matplotlib.pyplot as plt
-
-#csfont = {'fontname':'Times New Roman'}
-plt.rcParams["font.family"] = 'Times New Roman'
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib import rc
-rc('text', usetex=True)
-plt.rcParams.update({'font.size': 16})
-WDIR = os.path.dirname(__file__)
-# loadpath = os.path.join(WDIR,'data','stress_strain')
-writepath = os.path.join(WDIR,'..','draft','img')
-pf = [744, 290, 212, 530]
-shockley = [1343, 1470, 3581, 4367]
-stair_rode = [0, 123, 259, 295]
-hirth = [0, 407, 1100, 557]
-frank = [0, 375, 211, 500]
-
-
-# data to plot
-n_groups = 4
-
-# create plot
-fig, ax = plt.subplots()
-index = np.arange(n_groups)
-bar_width = 0.22
-opacity = 0.8
-
-rects1 = plt.bar(index, pf, bar_width,
-                 alpha=opacity,
-                 color='R',
-                 label='Perfect')
-
-rects2 = plt.bar(index + bar_width, shockley, bar_width,
-                 alpha=opacity,
-                 color='B',
-                 label='Shockley')
-
-rects3 = plt.bar(index + 2*bar_width, stair_rode, bar_width,
-                 alpha=opacity,
-                 color='G',
-                 label='Stair-rod')
-
-rects4 = plt.bar(index + 3*bar_width, frank, bar_width,
-                 alpha=opacity,
-                 color='black',
-                 label='Frank')
-
-plt.xlabel('Strain')
-plt.ylabel(r'Dislocation length / \AA')
-plt.ylim(ymax=5000)
-# plt.title('Scores by person')
-plt.xticks(index + bar_width, ('0.005','0.092','0.101','0.112'))
-plt.legend(frameon = False,title='Type of dislocation')
-
-plt.savefig(os.path.join(writepath, 'dis-summary.pdf'))
-
-#plt.tight_layout()
-plt.show()

### 2019-01-09 code/plot-sample.py

@@ -1,37 +1,0 @@
-# import packages
-import matplotlib.pyplot as plt
-import numpy as np
-import sys
-# 常用字体: ’Dejavu Sans‘,’Times New Roman‘,'Arial'
-# 设置图片尺寸  set size of fgure units cm
-plt.rcParams['figure.figsize'] = (5,2.5)
-plt.xlabel('Position')
-plt.ylabel('Temperatrue')
-plt.rcParams.update({'font.size': 9})
-# 采用紧凑布局
-plt.tight_layout()
-# 生成数据
-a = np.linspace(0,10,100)
-b = 0.8*a
-c = 1.2*a
-u = np.sin(a)
-v = np.cos(b)
-w = u+v
-# line color
-# set 是经典的RGB色，简直辣眼睛
-# set1: red,green,blue
-# set2: frebrick,forestgreen,darkgreen
-plt.plot(a,u,color='firebrick',marker='^',markevery=10,mew=0.25)
-plt.plot(b,v,color='forestgreen',marker='o',markevery=10,mew=0.25)
-plt.plot(c,w,color='darkblue',marker='s',markevery=10,mew=0.25)
-# create legend without frame
-plt.title('Sample Figure')
-# 绘制图例，不要框框
-plt.legend(['L1','L2','L3'],frameon=False)
-plt.xlim(0,8)
-plt.ylim(-3,3)
-# 亲测SVG能插入最word2016
-plt.savefig('plt.svg')
-# 可用格式有 png pdf ...
-plt.savefig('plt.pdf',dpi=300)
-plt.show()

### 2019-01-09 code/strgrad.py

@@ -1,69 +1,0 @@
-# 读取输出文件，绘制应力应变曲线
-'''
-violet
-├── code
-│   ├── data
-│   │   ├── size
-│   │   ├── stress_strain
-│   │   └── surf
-│   └── pict
-└── draft
-    ├── bkp
-    ├── img
-    ├── material
-    └── ref
-'''
-
-import os
-import os.path
-from os import listdir
-import matplotlib.pyplot as plt
-import pandas as pd
-from matplotlib import rc
-import matplotlib.pyplot as plt
-plt.rcParams.update({'font.size': 14})
-plt.rcParams["font.family"] = 'Times New Roman'
-
-rc('text', usetex=True)
-
-# rc('text', usetex=True)
-#csfont = {'fontname':'Times New Roman'}
-#plt.rcParams["font.family"] = "Times New Roman"
-WDIR = os.path.dirname(__file__)
-loadpath = os.path.join(WDIR,'data')
-writepath = os.path.join(WDIR,'..','draft','img')
-# pre-set head name
-
-
-
-prop = ['step', 'strain', 'stress', 'energy']
-# import data from .csv file:
-#ds1 = pd.read_csv(os.path.join(loadpath,'aa.csv'), sep=' ', skiprows=1, names=prop)
-ds1 = pd.read_csv(os.path.join(loadpath,'bin-g'), sep=' ', skiprows=1,names=['position','strgrad'])
-ds2 = pd.read_csv(os.path.join(loadpath,'bin-a'), sep=' ', skiprows=1,names=['position','strgrad'])
-
-# plot lines
-p1 = plt.scatter(ds1.position, ds1.strgrad, color = 'B')
-p2 = plt.scatter(ds2.position, ds2.strgrad, color = 'G')
-
-#p3 = plt.plot((ds.strain-0.015)*1.2, ds3.stress, color = 'R')
-#p2 = plt.plot((ds2.strain-0.015)*1.2, ds2.stress, color = 'G')
-#p4 = plt.plot((ds4.strain-0.015)*1.2, ds4.stress, color = 'B')
-
-# plt.legend('stress gradient', frameon=False)
-
-# config title and label
-
-#plt.title('stress-strain curve')
-plt.xlabel('Position')
-plt.ylabel('Strain gradient')
-#plt.ylim(ymin=0)
[…]

### 2019-01-09 crackdis.py

@@ -1,31 +1,0 @@
-import sys
-import numpy as np
-import matplotlib.pyplot as plt
-v = np.array([3.36, 3.69, 4.33, 5.02, 6.39, 8.03, 10.16, 12.6, 15.36, 18.15, 21.23, 23.91, 25.38, 26.27, 26.13, 25.56, 25.71])
-u = np.linspace(0, len(v)-1, len(v))
-plt.plot(u,v)
-plt.show()
-
-
-plt.rcParams['figure.figsize'] = (5,2.5)
-plt.xlabel('Position')
-plt.ylabel('Temperatrue')
-plt.rcParams.update({'font.size': 9})
-plt.tight_layout()
-
-# line color
-# set1: red,green,blue
-# set2: frebrick,forestgreen,darkgreen
-plt.plot(u,v,color='firebrick',marker='o',markevery=1,mew=0.25)
-# plt.plot(b,v,color='forestgreen',marker='o',markevery=10,mew=0.25)
-# plt.plot(c,w,color='darkblue',marker='s',markevery=10,mew=0.25)
-# create legend without frame
-# plt.legend(['L1','L2','L3'],frameon=False)
-# plt.xlim(0,8)
-# plt.ylim(-3,3)
-# plt.savefig('plt.svg')
-# plt.savefig('plt.pdf',dpi=300)
-plt.savefig('crackdis.pdf')
-
-plt.show()
-sys.exit(0)
